### 2019-05-03 meeting.tex
adding meeting files

\documentclass[10pt,a4paper,twoside]{mins}

\usepackage{enumitem}
\usepackage{booktabs}

\setcommittee{BEMOSS Research Project}
\setshortcommittee{Committee Short}
\setmembers{
	\role{Dr. Miah}{},
    \role{Brian Lauer}{}
}

\setdate{\today, 3:00 pm}

\apologies{} %If no-one gives apologies, leave blank and will be dropped
\absent{} %If no-one is absent, leave blank, and it will be dropped
\alsopresent{} %If no-one is a visitor, leave blank and it will be dropped

\setisAgenda{}%leave as blank for regular minutes. Set to True if agenda.

\begin{document}
\begin{minutes}
\begin{center}\emph{Meeting Opened at [3:31pm]}\end{center}
\begin{business}
\item Bob and I met for around 20 minutes to discuss

\item  Scholarship discussion

\item Grant proposal

Research grant proposal under BEMOSS May 3
\item Github repository
All documentation will be maintained in a github repository.
Create Github account and send username to Dr. Miah. A Google Drive with the same name as the Github repository will be created. 
It is named docsBemoss.

\item
Talk to Mr. Mattus about getting a laptop for research. It must be installed with Ubuntu administrative privileges.

Send him an email:

Hello Mr. Mattus, I will be working on a project with Dr. Miah. For that we would like to request a laptop available in the department if possible so that we can install Ubuntu operating system.

Try to go see him in the afternoon.
\item Learn Github Bash terminal commands:

Git add
Git commit -m adding files
Git remote add origin 'url'

Go through Github tutorials.

\item Upload latex file to Drive

\end{business};
\begin{center}\emph{Meeting Closed at [4:32pm]}\end{center}
\end{minutes}
\nextmeeting{[Some Date], [Some Time], [Some Place]}
\newpage
\begin{minutes}
    \begin{business}
        \item Email Mr. Mattus again on Monday, May 6.
        \item Need to get a laptop

    \end{business}
\end{minutes}

\end{document}

### 2019-05-31 presentationNotes.tex

\documentclass[
12pt,draftcls,onecolumn%
%journal
%9pt,technote
]{IEEEtran}
%\usepackage{epstopdf}
%\epstopdfsetup{suffix={}}

\usepackage{graphicx}  % Written by David Carlisle and Sebastian Rahtz
\usepackage{subfigure}  % Written by Steven Douglas Cochran
\graphicspath{
{figs/matlab/}
{figs/ipe/}
{figs/img/}
}

\usepackage{amssymb}    % added by w.g.
\usepackage{amsmath,bm}    % From the American Mathematical Society
\usepackage{amsthm}
\usepackage{mathrsfs}

\usepackage{hyperref}

%%%%\usepackage[width=11cm,font=footnotesize,labelfont=bf, %
%%%%format=default,justification=centerlast]{caption} % Figure caption text customization 
%%%\usepackage{hyperref}
\usepackage[colorinlistoftodos]{todonotes} %side notes and comments
%%%
\usepackage{siunitx} % for units like degree, ...
\sisetup{unitsep=\cdot} % for commands like \SI{50}{\ohm} etc.

%%%\DeclareMathOperator*{\smargmin}{arg\,min}
%%%\DeclareMathOperator*{\smargmax}{arg\,max}
%%%
\newtheorem{theorem}{Theorem}
\newtheorem{assumption}{Assumption}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{corollary}{Corollary}
%%%% correct bad hyphenation here
%%%\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
%\title{Time Varying Operator for Controlling Nonholonomic Systems with Drift}
\title{Universal Control Law for Nonholonomic Systems with Drift}

\author{Md Suruz~Miah,~\IEEEmembership{Senior Member,~IEEE}% and 
%		N.~U.~Ahmed                
\thanks{S.~Miah is with the Electrical and Computer Engineering Department, Bradley University, Peoria, IL, 61625, USA. e-Mails:~smiah@bradley.edu}% <-this % stops a space
%\thanks{S.~Miah is with the Electrical and Computer Engineering Department, Bradley University, Peoria, IL, 61625, USA. e-Mail:~smiah@bradley.edu}% <-this % stops a space

%\thanks{N.~Ahmed is with the School of Electrical Engineering and Computer Science, University of Ottawa, Ottawa, ON, K1N 6N5, CANADA. e-Mail:~\{ahmed\}@eecs.uottawa.ca}% <-this % stops a space

\thanks{This research supported in part by Caterpillar Inc.}
}
% The paper headers
%\markboth{Journal of \LaTeX\ Class Files,~Vol.~6, No.~1, January~2007}%

% make the title area
\maketitle

\begin{abstract}
A universal control law for nonholonomic systems with drift is considered. While the development of feedback control laws for controlling nonlinear dynamical systems are well-established in the literature to date, the need of a control theoretic method to establish a universal control law for a class of nonlinear systems is significant. 
This is simply because the formulation of feedback control laws  relies on types of dynamical systems to be controlled which lead to a significant technical challenge for researchers.% to propose a general feedback law for a class of  nonlinear dynamical systems. %This task is even more challenging when the system is only partially observable. 
%
Here we underscore the need for a universal control law  that is aimed to address the trajectory tracking problem of nonholonomic systems with drift. For that, we propose to develop a time-varying feedback operator (called  herein a universal control law), to solve the tracking problem. The objective of the current manuscript is to prove the existence and to establish necessary conditions of the proposed time-varying feedback operator for nonholonomic systems with drift. The performance of the time-varying feedback operator will be backed up by a set of computer simulations. The novelty of this research lies in the modularity of the control law despite inherent non-linearity of nonholonoic systems. 
%
%complex dynamical systems.%, such as differential drive mobile robots, underwater or flying vehicles, and  competitive systems (\textit{e.g.,} mixing of renewable and nonrenewable energy sources).

\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Generalized control law, nonholonomic systems, drift, Pontryagin's minimum principle.
\end{IEEEkeywords}
\IEEEpeerreviewmaketitle

%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

\section{Notations and Preliminaries}\label{sec:notations}
Throughout this paper, scalar and vector quantities will be denoted by non-bold letters and lower-case bold letters, respectively. Upper-case bold letters will denote matrices. For any positive integer $n$, $\mathbb{R}^n$ denotes the Euclidean space. For any vector ${\bf x,y}\in\mathbb{R}^n$, the standard Euclidean norm and the scalar product are given by
\begin{equation*}
\|{\bf x}\| \equiv  \left[\sum_{i=1}^n \left |x_i\right |^2\right]^{1/2}~\hbox{and}~~ {\bf (x\cdot y)}\equiv{\bf x}^T{\bf y}\equiv\sum_{i=1}^n x_i y_i, 
\end{equation*}
respectively. We shall use $\mathbb{R}^{m\times n}$ to denote the space of $m\times n$ matrices with entries from $\mathbb{R}$.  Let ${\bf X,Y}\in\mathbb{R}^{m\times n}$, then the standard norm and their scalar product are also given by 
\begin{equation*}
\begin{split}
\|{\bf X}\|\equiv\left[\sum_{i=1}^m \sum_{j=1}^n\left |x_{i,j}\right |^2\right]^{1/2}~\text{and}~{\bf (X\cdot Y)}\equiv Tr\left[{\bf X}^T{\bf Y}\right]\equiv Tr\left[{\bf X}{\bf Y}^T\right],
\end{split}
\end{equation*}
respectively, where $\mathrm{Tr}\left[\cdot\right]$ denotes the trace of matrix $\left[\cdot\right]$. Clearly, $\mathrm{Tr}\left[{\bf X}^T{\bf X}\right]=\|{\bf X}\|^2$. ${\bf X}\otimes {\bf Y}$ is the Kronecker product of two matrices ${\bf X,Y},$ where $\mathbb{R}^{m^2\times n^2}\ni {\bf Z} = {\bf X}\otimes {\bf Y}.$ $C({\cal I}, \mathbb{R}^n)$ is the class of all continuous function on the time interval ${\cal I}$ taking values from~$\mathbb{R}^n.$

If the function $J:\mathbb{R}^n\to \mathbb{R}$ is differentiable at ${\bf x}\in \mathbb{R}^n$, then for any ${\bf v}\in\mathbb{R}^n$, $dJ({\bf x};{\bf v})$ denotes the Gateaux (directional) derivative in the direction of ${\bf v}$, which is given by
%
\begin{equation*}
dJ({\bf x};{\bf v}) = {\bf v}^T\nabla J=\lim_{\varepsilon\to 0} \frac{J({\bf x} + \varepsilon{\bf v}) - J({\bf x})}{\varepsilon}, 
\end{equation*}
where $\nabla J$ denotes the gradient of $J$.
%
However, if $J:\mathbb{R}^{m\times n}\to \mathbb{R}$, then for any ${\bf X},{\bf V}\in\mathbb{R}^{m\times n}$, the directional derivative in the direction of ${\bf V}$ is defined by
\begin{equation*}
dJ({\bf X};{\bf V}) = Tr[{\bf V}^T\nabla J] = \lim_{\varepsilon\to 0} \frac{J({\bf X} + \varepsilon{\bf V}) - J({\bf X})}{\varepsilon}. 
\end{equation*}
For any bounded time interval ${\cal I} \equiv [0, t_f],~t_f>0,$ $C({\cal I},\mathbb{R}^n)$ denotes the class of all continuous functions on ${\cal I}$ taking values in $\mathbb{R}^n$. Let $p \in [1,\infty)$ and  any finite time interval ${\cal I}$, we use  ${\cal L}_p({\cal I},\mathbb{R}^n)$ to denote the set of Lebesgue measurable functions $\{{\bf f}\}$ defined on ${\cal I}$ and taking values in $\mathbb{R}^n$ whose norms are $p$-th power integrable,~\textit{i.e.,}~
%\begin{equation*}
$L_p({\bf f}) = \left(\int_{0}^{t_f}\|{\bf f}\|^p \mathrm{dt}\right)^{1/p}<\infty,$ 
%\end{equation*}
%
where $L_p({\bf f})$ denotes the $p$th norm of the function ${\bf f}$~\cite{Royden2010,Khalil2002}. For $p=\infty$, ${\cal L}_{\infty}({\cal I},R^n)$ denotes the space  of Lebesgue measurable functions $\{{\bf f}\}$ defined on ${\cal I}$ and taking values in $\mathbb{R}^n$ satisfying 
%
%\begin{equation*}
$\text{ess sup} \{ \|{\bf f}(t)\|, t \in {\cal I}\} < \infty.$
%\end{equation*}
%
% Similarly, ${\cal L}_p^{\ell oc}([0,\infty),\mathbb{R}^n)$ are locally convex topological vector spaces of $p$-th power locally integrable functions containing the  spaces ${\cal L}_p(I,\mathbb{R}^n)$.
%We use $\mathrm{diag}(a_1,\ldots,a_n)$ to represent a matrix whose diagonal entries starting in the upper left corner are $a_1,\ldots,a_n$.

\section{System Model and Problem Statement}
\label{sec:systemModel}
\subsection{System Model}
We consider a class of dynamical systems described by 
\begin{subequations}
\label{eq:system}
\begin{align}
\label{eq:systemModel}
\dot{{\bf q}}(t) & = \bar{{\bf g}}({\bf q}(t)) + \sum_{j=1}^m{\bf g}_j({\bf q}(t))u_j(t),\\
\label{eq:controlLaw}
u_j(t) & = {\bf k}_j^T(t) {\bf q}(t), 
\end{align}
\end{subequations}
where ${\bf q}(t)\in{\cal Q}\subset\mathbb{R}^n$ is the state of the system at time $t\ge 0$ with ${\cal Q}$ being its state space, $u_j$ is the $j$th, $j=1,\ldots, m$ control variable, and ${\bf k}_j: \mathbb{R}\to \mathbb{R}^n$ is the time-varying feedback operator of the $j$th control variable for positive integer $n,$ $m$ with $n>m$. The drift vector field $\bar{{\bf g}}:\mathbb{R}^n\to\mathbb{R}^n$ represents natural unforced motion of the system and ${\bf g}_j:\mathbb{R}^n\to\mathbb{R}^n,$ $j=1,\ldots,m,$ are linearly independent control vector fields~\cite{Choset2004}. When no ambiguity arises, we shall drop the argument $(t)$ for clarity. System~\eqref{eq:system} can also be written in compact form as
%
\begin{subequations}
\label{eq:system1}
\begin{align}
\label{eq:systemModel1}
\dot{{\bf q}} & = \bar{{\bf g}}({\bf q}) + {\bf G}({\bf q}){\bf u},\\
\label{eq:controlLaw1}
{\bf u} & = {\bf K}(t) {\bf q}, 
\end{align}
\end{subequations}
%
where ${\bf u}\in{\cal U}\subset \mathbb{R}^m$ is the vector of $m$ control inputs to the system, ${\bf G}:\mathbb{R}^n\to\mathbb{R}^{n\times m},$ and the time varying feedback operator ${\bf K}:\mathbb{R}_0^+\to{\cal K}_{\mathrm{ad}}\subset\mathbb{R}^{m\times n}.$

Note the difference in the feedback control law in~\eqref{eq:controlLaw1} with other existing control laws in the literature. It is simply a matter of determining the universal matrix (herein called feedback operator) ${\bf K}(t)\in{\cal K}\subset\mathbb{R}^{m\times n}.$

\subsection{Problem Formulation} 
Let ${\bf q}^d(t)$ be the desired (reference) trajectory that the system~\eqref{eq:systemModel1} is supposed to track and $e(t) = \|{\bf q}(t)-{\bf q}^d(t)\|_{\mathbb{R}^n}$ denotes its state tracking error, for $t\in {\cal I}$. The objective is to find the optimal time-varying feedback operator  ${\bf K}(t)\in {\cal K}_{ad}$ that generates the trajectory ${\bf q}(t)\in{\cal Q}$ while minimizing the average cumulative state tracking error, $\mathscr{E}_{\mathrm{avg}}$, given by 
\begin{equation}
\mathscr{E}_{\mathrm{avg}} = \frac{1}{t_f}\int_{0}^{t_f}e(t)\mathrm{dt},~~t_f>0.
\label{eq:tracking-error}
\end{equation}

Given the system model~\eqref{eq:system1}, the problem can be stated as follows:
\begin{equation}
\inf_{\{{\bf q}\in{\cal Q},~{\bf K}\in{\cal K}_{ad}\}} [\mathscr{E}_{\mathrm{avg}}].
\label{eq:problem}
\end{equation}

\section{Proposed Universal Control Law}
\label{sec:feedbackOperator}
This section details the design procedure of the proposed universal time-varying control law, which is the main contribution of this manuscript. Substituting~\eqref{eq:controlLaw1} in~\eqref{eq:systemModel1}, yields the following full-state feedback system:
\begin{equation}
\begin{split}
\dot{{\bf q}}  = \bar{{\bf g}}({\bf q}) + {\bf G}({\bf q}){\bf K}(t) {\bf q} \equiv{\bf f}({\bf q},{\bf K}),
\end{split}
\label{eq:systemFeedbackFull}
\end{equation}
with ${\bf q}(0)={\bf q}_0.$ We emphasize that the generalized linear time varying operator ${\bf K}(t)$ completely characterizes the feedback law~\eqref{eq:systemFeedbackFull} for solving the trajectory tracking problem.

\begin{lemma}[Solutions of feedback system]
\label{lem:feedback-sol}
Given the feedback system~\eqref{eq:systemFeedbackFull}, which is defined over the finite time horizon of ${\cal I}$, then for every initial condition ${\bf q}(0)\in\mathbb{R}^n$, and feedback operator ${\bf K}(t)\in {\cal K}_{ad}$, the system~\eqref{eq:systemFeedbackFull} has a unique absolutely continuous solution ${\bf q}(t)\in C({\cal I}, \mathbb{R}^n)$. Furthermore, the solution set ${\cal Q}\equiv\left\{{\bf q}(t) \equiv{\bf q}[t,{\bf K}(t)]\in C({\cal I},\mathbb{R}^n):{\bf K}(t)\in {\cal K}_{ad}\right \}$ is a bounded subset of $C({\cal I}, \mathbb{R}^n)$. 
\end{lemma}
%\begin{IEEEproof}
The proof of this lemma is classical and follows from a similar technique in~\cite[page~89]{Ahmed2006}. %
%\end{IEEEproof}
Hence, the actual trajectory of the of the vehicle can then be symbolically represented by 
\begin{equation}
{\bf q}(t) = {\bf q}(0) + \int_{0}^{t}{\bf f}[{\bf q}(\tau),{\bf K}(\tau)]d\tau,
\label{eq:actual-trajectory-full} 
\end{equation}
for $t\in {\cal I}$. In order to solve the trajectory tracking problem of nonholonomic systems with drift, let us introduce the cost functional as
\begin{equation}
J({\bf K}) = \Phi [t_f,{\bf q}(t_f)] + \int_{0}^{t_f} \ell [t,{\bf q}(t,{\bf K})]\mathrm{dt},~~\mathrm{with}
\label{eq:cost-fn}
\end{equation}
\begin{multline*}
\Phi [t_f,{\bf q}(t_f)]= \frac{1}{2} [{\bf q}(t_f)-{\bf q}^d(t_f)]^T{\bf P}(t_f)[{\bf q}(t_f)-{\bf q}^d(t_f)] ~\mathrm{and}~\\
\ell [t,{\bf q}(t)] =\frac{1}{2}[{\bf q}(t)-{\bf q}^d(t)]^T{\bf Q}(t)[{\bf q}(t)-{\bf q}^d(t)],
%\label{eq:cost-fn}
\end{multline*}
where the weight matrix ${\bf P}(t_f) \in\mathbb{R}^{n\times n}$ and the  tracking weight ${\bf Q}(t)\in\mathbb{R}^{n\times n}$ are symmetric positive definite matrices that indicate the relative importance of the error components along $\mathbb{R}^n.$ %
%
%If the vehicle's purpose is to stabilize on a fixed configuration, then ${\bf P}(t_f)$ must be higher than ${\bf Q}(t)$ and the desired trajectory is set to a \emph{fixed} configuration. However, the opposite is true for the vehicle to track a desired trajectory. 
%
The performance index $J({\bf K})$ in~\eqref{eq:cost-fn} depends on the feedback operator ${\bf K}(t)$ through the state variable ${\bf q}(t)$ as it is clear from the feedback system~\eqref{eq:systemFeedbackFull}. Note that $\Phi[\cdot]$ and $\ell[\cdot]$ of~\eqref{eq:cost-fn} are referred to as the terminal and tracking cost functionals, respectively. The task now becomes solving the following problem:
\begin{equation}
\inf_{{\bf K}\in{\cal K}_{ad}} [J({\bf K})],
\label{eq:problem1}
\end{equation}
which yields ${\bf q}(t) \to {\bf q}^d(t)$ as $J({\bf K})\longrightarrow 0$, for $t\in {\cal I}$. It is important to point out that, solving the problem~\eqref{eq:problem1} will eventually solve  the problem~\eqref{eq:problem}. Hence, the problem~\eqref{eq:problem1} can be solved if there exists a generalized optimal feedback operator ${\bf K}^*(t)$, for $t\in {\cal I}.$ However, it is worth noting the following remark before we proceed determining the generalized control law ${\bf K}(t).$ 
%

\begin{remark}
Note that the optimal feedback gain ${\bf K}(t)$ can be determined by following the classical Pontryagin's minimum principle~\cite[Chaper~8]{Ahmed2006} with ${\bf K}(t)$ being the open--loop control input to the feedback system~\eqref{eq:systemFeedbackFull}. For that, let $\mathrm{vec}({\bf K}(t))$ transforms the matrix ${\bf K}(t)$ into a column vector, which is formed by stacking the rows of ${\bf K}(t).$ The feedback model~\eqref{eq:systemFeedbackFull} can be rewritten as 
\begin{equation}
  {\bf \dot q} = \bar{{\bf g}}({\bf q}) + \left({\bf q}^T\otimes{\bf G}({\bf q})\right){\bf \bar k},
  \label{eq:systemFeedbackFull1}  
\end{equation}
where $\mathbb{R}^{nm}\ni{\bf \bar k}=\mathrm{vec}({\bf K})$ is now the control input vector that can be solved by following the standard gradient descent technique presented in~\cite[Chapter~3]{Stengel1994}~\cite[Chaper~8]{Ahmed2006}. By rearranging the elements of the optimal vector ${\bf \bar k}^*,$ we can reconstruct the optimal feedback operator ${\bf K}^*$ which is then substituted in the feedback law~\eqref{eq:systemFeedbackFull} to generate the optimal control input vector ${\bf u}^*(t),$ for $t\in{\cal I}.$  Nevertheless,  we emphasize in determining the optimal feedback operator ${\bf K}^*(t)$ directly by modifying the classical Pontryagin's minimum principle, which has applications in solving problems of a general class of partially observed dynamic systems. 
\end{remark}

\subsection{Existence of Generalized Control Law}
In this section, we provide the proof of the existence of the proposed generalized time-varying control law, ${\bf K}(t),$ that essentially solves the tracking problems of nonholonomic systems with drift.

\begin{theorem}\label{thm:existence-K}
Given a nonholonomic system modeled by \eqref{eq:systemModel1}, there exists a generalized optimal control law ${\bf K}^*(t) \in {\cal K}_{ad}$ for the controller modeled in~\eqref{eq:controlLaw1} that drives the system~\eqref{eq:systemModel1} to the desired trajectory ${\bf q}^d(t)$ while finding the optimal solution for the problem~\eqref{eq:problem}. 
\end{theorem}
%%See Appendix~\ref{app:thm:existence-K} for its complete proof. %
 \begin{proof} 
Following the well known Alaoglu's theorem\footnote{\href{https://en.wikipedia.org/wiki/Banach/wiki/Banach–Alaoglu_theorem}{https://en.wikipedia.org/wiki/Banach/wiki/Banach–Alaoglu\_theorem}},  ${\cal K}_{ad} \subset {\cal K}\subset\mathbb{R}^{m\times n}$  is a (weak star) $w^*$ compact set and it suffices to prove that ${\bf K} \longmapsto J({\bf K})$ is sequentially weak star continuous. Let $\{{\bf K}^i, i \in \mathbb{N}\} \in {\cal K}_{ad}$ be a sequence  and suppose   ${\bf K}^i \buildrel w^* \over \to {\bf K}^*.$ Since ${\cal K}_{ad}$ is $w^*$ closed,  we have ${\bf K}^* \in {\cal K}_{ad}$, see~\cite{AhMi2011-j1}.

Suppressing the variable $t$ for clarity, let $\{{\bf q}^i,~i\in \mathbb{N}\}$ and ${\bf q}^*$ denote the  solutions of the system~\eqref{eq:systemFeedbackFull} corresponding to $\{{\bf K}^i,~i\in \mathbb{N}\}$ and ${\bf K}^*$, respectively. Hence, the corresponding state equation becomes 
\begin{align*}
{\bf \dot q}^i = {\bf f}({\bf q}^i,{\bf K}^i)~\text{and}~
{\bf \dot q}^* = {\bf f}({\bf q}^*,{\bf K}^*),~{\bf q}^i_0={\bf q}^*_0={\bf q}_0.
\end{align*}
%
Using~\eqref{eq:actual-trajectory-full}, the solutions of the above two state-space models can be described by
\begin{equation*}
\begin{split}
{\bf q}^i(t) = {\bf q}_0 + \int_{0}^{t}{\bf f}[{\bf q}^i(\tau),{\bf K}^i(\tau)]d\tau,~\text{and}~~
{\bf q}^*(t)= {\bf q}_0 + \int_{0}^{t}{\bf f}[{\bf q}^*(\tau),{\bf K}^*(\tau)]d\tau.
\end{split}
\end{equation*}
%
Subtracting one from another, we get
\begin{align}
{\bf q}^i(t)-{\bf q}^*(t) = \int_{0}^t\left({\bf f}[{\bf q}^i(\tau),{\bf K}^i(\tau)]- {\bf f}[{\bf q}^*(\tau),{\bf K}^*(\tau)]\right)d\tau.
\label{eq:existence-temp1}
\end{align}
Note that ${\bf G}({\bf q}^i),~i\in \mathbb{N}$ and ${\bf G}({\bf q}^*)$ are uniformly bounded functions and satisfy Lipschitz condition
\begin{align*}
\|{\bf G}({\bf q}^i)-{\bf G}({\bf q}^*)\|&\leq L_{c2}\|{\bf q}^i-{\bf q}^*\|,\\
\|\bar{{\bf g}}({\bf q}^i)-\bar{{\bf g}}({\bf q}^*)\|&\leq L_{c1}\|{\bf q}^i-{\bf q}^*\|,\\
\end{align*}
where $L_{c1}$ and $L_{c2}$ are Lipschitz constants. Taking the Euclidean norm in both sides of expression~\eqref{eq:existence-temp1} and using the triangle inequality yield
\begin{align*}
\|{\bf q}^i(t)-{\bf q}^*(t)\| \leq v^i(t)+\int_{0}^t\beta(\tau)\|{\bf q}^i(\tau)-{\bf q}^*(\tau)\|d\tau,~\text{where}
\end{align*}
%
\begin{equation*}
v^i(t) = \Big\Vert\int_{0}^t\left[{\bf G}({\bf q}^i)({\bf K}^i-{\bf K}^*){\bf q}^i\right]d\tau\Big\Vert,
\end{equation*}
${\beta}(t) = (L_{c1} + c_1(t) + c_2(t)L_{c2}) \in{\cal L}_1^{+}({\cal I})$, with 
\begin{align*}
c_1(t)=[\sup \|{\bf G}({\bf q}^i)\|][\sup \|{\bf K}\|],~c_2(t) = \sup(\|{\bf K}^*\|\|{\bf q}\|),
\end{align*}
for $i\in \mathbb{N},~{\bf K}\in{\cal K},~\text{and}~{\bf q}\in{\cal Q}$ (see Theorem 8.3.4 of~\cite[page 273]{Ahmed2006} for more details). Thus,  it follows from Gronwall inequality that 
\begin{equation} 
\parallel {\bf q}^i(t) - {\bf q}^*(t)\parallel \leq v^i(t) + 
\int_{0}^t \exp\{\int_{\tau}^t \beta(s)\mathrm{ds}\} \beta(\tau) v^i(\tau) d\tau.
\label{eq:gronwall}
\end{equation} 
Clearly, $v^i(t)\to 0$, for $t\in {\cal I}$, $i\in \mathbb{N}$, as ${\bf K}^i\buildrel w^* \over \to {\bf K}^*$. Thus, it follows from inequality~\eqref{eq:gronwall} that ${\bf q}^i\buildrel {\bf K}^*\over \to {\bf q}^*.$ 
%
Since both $\ell (t,\cdot)$ and $\Phi(t,\cdot)$ are continuous on $\mathbb{R}^n,$ we have  $\ell[t,{\bf q}_i(t)] \longrightarrow \ell[t,{\bf q}^*(t)] $ for almost all $t \in {\cal I}$ and $\Phi[t,{\bf q}^i(t_f)] \longrightarrow \Phi[t,{\bf q}^*(t_f)] $ as $i \rightarrow \infty.$ Thus it follows from the expression \eqref{eq:cost-fn} that  $ \lim_{i \rightarrow \infty} J({\bf K}^i)  =  J({\bf K}^*)$ proving weak star continuity of  $J$ on ${\cal K}_{ad}.$ Since ${\cal K}_{ad}$ weak  star compact, $J$  attains its minimum on ${\cal K}_{ad}.$ 
\end{proof}
% 
Theorem~\ref{thm:existence-K} guarantees that there exists an optimal universal control law ${\bf K}^*$ for nonholonomic systems modeled by~\eqref{eq:systemModel}. In the following, we provide the necessary conditions for the proposed universal control law.

\subsection{Necessary Conditions}
\label{sec:necessaryConditions}

To solve for the optimal trajectory that minimizes the objective functional~\eqref{eq:cost-fn}, we need to derive the necessary conditions of optimality. These necessary conditions are most readily found if the integrand of the cost functional~\eqref{eq:cost-fn} is recast in terms of Hamiltonian 
%\begin{equation*}
$\mathcal{H}:{\cal I}\times \mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^{m\times n} \longrightarrow \mathbb{R}$,
%\end{equation*}
which is expressed by
%
\begin{equation}
\mathcal{H}[t, {\bf q}(t), \boldsymbol{\psi}(t),{\bf K}(t)] = \boldsymbol{\psi}^T(t){\bf f}[{\bf q}(t),{\bf K}(t)] + \ell[t,{\bf q}(t)],
\label{eq:hamiltonian}
\end{equation}
%
where $\boldsymbol{\psi}(t)\in\mathbb{R}^n,~t\in {\cal I}$, is a vector of Lagrange multipliers whose elements are the co-states of the system~\cite{Ahmed1988}. We now derive the necessary conditions of optimality feedback model~\eqref{eq:systemFeedbackFull}.

\begin{theorem}
\label{thm:necessary-conditions}
Since the optimal universal feedback operator (control law) ${\bf K}^*(t),~t\in {\cal I}$ exists, the optimal trajectory ${\bf q}^*(t),~t\in {\cal I}$ for the feedback model~\eqref{eq:systemFeedbackFull} can be obtained if there exists an optimal multiplier $\boldsymbol{\psi}^*(t)\in C({\cal I},\mathbb{R}^n)$ such that the triple $\{{\bf q}^*,\boldsymbol{\psi}^*,{\bf K}^*\}$ satisfies the following necessary conditions:
\begin{subequations}
\begin{align}
\label{eq:inequality-H}
{\cal H}[t,{\bf q}^*(t),\boldsymbol{\psi}^*(t),{\bf K}(t)] & \geq{\cal H}[t,{\bf q^*}(t),\boldsymbol{\psi}^*(t),{\bf K^*}(t)], ~~{\bf K}(t)\in {\cal K},\\
\label{eq:state}
{\bf \dot q}^* &=\frac{\partial{\cal H}}{\partial\boldsymbol{\psi}} [t,{\bf q}^*(t),\boldsymbol{\psi}^*(t),{\bf K^*}(t)],~{\bf q}^*(0)={\bf q_0},\\
\label{eq:costate}
\boldsymbol{\dot\psi}^* &= -\frac{\partial{\cal H}}{\partial{\bf q}} [t,{\bf q}^*(t),\boldsymbol{\psi}^*(t),{\bf K}^*(t),~\boldsymbol{\psi}^*(t_f) = \frac{\partial\Phi}{\partial{\bf q}}[t_f,{\bf q}(t_f)].
\end{align}
\end{subequations}
\end{theorem}
%% The detailed and comprehensive proof of this Theorem is given in Appendix~\ref{app:thm:necessary-conditions}. %
\begin{proof}
Let ${\bf q}(t)\equiv{\bf q}[t,{\bf K}(t)]$ be the solution of the feedback system~\eqref{eq:systemFeedbackFull}, with the cost functional~\eqref{eq:cost-fn} for any choice of ${\bf K}(t)\in{\cal K}_{ad}$. Since ${\bf K}^*(t)$ is optimal with the associated trajectory ${\bf q}^*(t)$, it is clear that
\begin{equation*}
J({\bf K}^*) \leq J({\bf K}),~~\forall~{\bf K}(t)\in{\cal K}_{ad},~t\in {\cal I}. 
\end{equation*}
Suppressing the variable $t$ for clarity and for any $\varepsilon\in [0,1]$, we define ${\bf K}^{\varepsilon}={\bf K}^* + \varepsilon ({\bf K-K^*})$. Since ${\cal K}$ is a closed convex set, ${\cal K}_{ad}$ is also a closed convex subset of ${\cal L}_{\infty}({\cal I},\mathbb{R}^{m\times n})$ and therefore ${\bf K}^{\varepsilon}\in{\cal K}_{ad}$. Thus $J({\bf K^*}) \leq J({\bf K}^{\varepsilon})$, which follows that
\begin{equation}
dJ({\bf K}^*;{\bf K}-{\bf K}^*)=\mathrm{Tr}\left[\left({\bf K}-{\bf K}^*\right)^T\nabla J({\bf K}^*)\right]\geq 0,
\label{eq:dJ}
\end{equation}
where $dJ({\bf K}^*;{\bf K}-{\bf K}^*)$ denotes the Gateaux (directional) derivative of $J$ evaluated at ${\bf K}={\bf K}^*$ in the direction of $({\bf K}-{\bf K}^*)$ and $\nabla J({\bf K}^*)$ is the gradient of $J$ evaluated at ${\bf K}^*$.

Let ${\bf q}^{\varepsilon}$ be the solution of the feedback system~\eqref{eq:systemFeedbackFull} corresponding to the control law ${\bf K}^{\varepsilon}$ with the same initial state ${\bf q}^{\varepsilon}(0)={\bf q}_0$. It is easy to verify that
%
\begin{align*}
  \lim_{\varepsilon\to 0} {\bf K}^{\varepsilon}(t) = {\bf K}^*(t),~~\text{and}~~
  \lim_{\varepsilon\to 0} {\bf q}^{\varepsilon}(t) = {\bf q}^*(t).
\end{align*}
% 
Hence, the state trajectories ${\bf q}^{\varepsilon}(t)$ and ${\bf q}^*(t),t\in {\cal I}$  are described by
%
\begin{equation*}
\begin{split}
{\bf \dot q}^\varepsilon &= {\bf f}({\bf q}^\varepsilon,{\bf K}^\varepsilon),~~{\bf q}^\varepsilon(0) = {\bf q}_0~\text{and}\\
{\bf \dot q^*} &= {\bf f}({\bf q}^*,{\bf K}^*),~~{\bf q}^*(0) = {\bf q}_0.
\end{split}
\end{equation*}
%
Subtracting one from the other we have the following equation
\begin{equation}
{\bf \dot q}^\varepsilon - {\bf \dot q}^* = {\bf f} ({\bf q}^\varepsilon,{\bf K}^*) - {\bf f} ({\bf q}^*,{\bf K}^*) + \varepsilon {\bf \bar f} ({\bf q}^\varepsilon,{\bf K}-{\bf K}^*),
\label{eq:temp1}
\end{equation}
where ${\bf \bar f} ({\bf q}^\varepsilon,{\bf K}-{\bf K}^*) = {\bf G}({\bf q}^{\varepsilon})({\bf K} - {\bf K}^*){\bf q}^\varepsilon.$ 
%See Appendix~\ref{app:variational} for its derivation. 
Dividing by $\varepsilon$ and denoting
\begin{equation*}
\boldsymbol{\eta} (t)\equiv \lim_{\varepsilon\to 0}\left(\frac{{\bf q}^{\varepsilon}(t)-{\bf q}^*(t)}{\varepsilon}\right),
\end{equation*}
it follows from the expression~\eqref{eq:temp1} that $\boldsymbol{\eta}(t)$ must satisfy the following initial value problem
\begin{equation}
\begin{split}
\boldsymbol{\dot\eta} = \frac{\partial {\bf f}}{\partial{\bf q}}({\bf q}^*,{\bf K}^*)\boldsymbol{\eta} + {\bf \bar{f}}({\bf q}^*,{\bf K}-{\bf K}^*),~~\boldsymbol{\eta}(0)  = 0.
\end{split}
\label{eq:variational}
\end{equation}
%The detail derivation of the variational Equation~\eqref{eq:variational} is given in Appendix~\ref{app:variational}. 
Equation~\eqref{eq:variational} is a linear non-homogeneous equation with ${\bf \bar{f}}({\bf q}^*,{\bf K}-{\bf K}^*)$ being the driving force. As a result, it has a continuous solution $\boldsymbol{\eta}(t)\in C({\cal I},\mathbb{R}^n)$, which is continuously dependent on ${\bf \bar{f}}({\bf q}^*,{\bf K}-{\bf K}^*).$

By definition of Gateaux (directional) derivative we can derive the following expression
\begin{multline*}
dJ({\bf K}^*;{\bf K}-{\bf K}^*) =\lim_{\varepsilon\to 0}\frac{J[{\bf K}^*+\varepsilon({\bf K}-{\bf K}^*)] - J({\bf K}^*)}{\varepsilon}\\
=\boldsymbol{\eta}^T(t)\frac{\partial\Phi}{\partial{\bf q}}[t_f,{\bf q}(t_f)] + \int_{0}^{t_f}\boldsymbol{\eta}^T(t)\frac{\partial\ell}{\partial{\bf q}} [t,{\bf q}(t)]\mathrm{dt}.
\end{multline*}
Hence, inequality~\eqref{eq:dJ} yields
\begin{equation}
\boldsymbol{\eta}^T(t)\frac{\partial\Phi}{\partial{\bf q}}[t_f,{\bf q}(t_f)] + \int_{0}^{t_f}\boldsymbol{\eta}^T(t) \frac{\partial\ell}{\partial{\bf q}} [t,{\bf q}(t)]\mathrm{dt} \geq 0.
\label{eq:ineq1}
\end{equation}  
%
Since $\boldsymbol{\eta}(t)$ of the variational equation~\eqref{eq:variational} is continuously dependent on ${\bf \bar f}({\bf q}^*,{\bf K}-{\bf K}^*)$, the map
\begin{equation*}
{\bf \bar f}({\bf q}^*,{\bf K}-{\bf K}^*) \longmapsto \boldsymbol{\eta}(t)
\end{equation*}
is continuous from ${\cal L}_1({\cal I},\mathbb{R}^n)$ to $C({\cal I},\mathbb{R}^n)$~\cite[p.~260]{Ahmed2006}. Hence, the map 
\begin{equation*}
\boldsymbol{\eta}(t) \longmapsto \boldsymbol{\eta}^T(t)\frac{\partial\Phi}{\partial{\bf q}}[t_f,{\bf q}(t_f)] + \int_{0}^{t_f}\boldsymbol{\eta}^T(t)\frac{\partial\ell}{\partial{\bf q}} [t,{\bf q}(t)]\mathrm{dt}
\end{equation*}
is a continuous linear functional on $C({\cal I},\mathbb{R}^n)$. Thus, the composition map 
\begin{equation*}
%\begin{split}
{\bf \bar f}({\bf q}^*,{\bf K}-{\bf K}^*) \longmapsto \boldsymbol{\eta}^T(t)\frac{\partial\Phi}{\partial{\bf q}}[t_f,{\bf q}(t_f)] +\int_{0}^{t_f}\boldsymbol{\eta}^T(t) \frac{\partial\ell}{\partial{\bf q}} [t,{\bf q}(t)]\mathrm{dt}
%\end{split}
\end{equation*}
is a continuous linear functional on ${\cal L}_1({\cal I},\mathbb{R}^n)$, where ${\bf f}({\bf q}^*,{\bf K}-{\bf K}^*)\in {\cal L}_1({\cal I},\mathbb{R}^n)$. Therefore, by the Riesz representation theorem or by the duality between ${\cal L}_1({\cal I},\mathbb{R}^n)$ and ${\cal L}_{\infty}({\cal I},\mathbb{R}^n)$, we may conclude that there exists an element $\boldsymbol{\psi}^*\in {\cal L}_{\infty}({\cal I},\mathbb{R}^n)$ such that
\begin{multline}
dJ({\bf K}^*;{\bf K}-{\bf K}^*) = \boldsymbol{\eta}^T(t) \frac{\partial\Phi}{\partial{\bf q}}[t_f,{\bf q}(t_f) +
\int_{0}^{t_f}\boldsymbol{\eta}^T(t)\frac{\partial\ell}{\partial{\bf q}}(t,{\bf q}(t))\mathrm{dt}=\\
\int_{0}^{t_f} \left(\boldsymbol{\psi}^*\right)^T{\bf \bar f}({\bf q}^*,{\bf K}-{\bf K}^*)\mathrm{dt}.
\label{eq:temp2}
\end{multline}
It follows from inequality~\eqref{eq:ineq1} that 
\begin{equation}
\int_{0}^{t_f} \left(\boldsymbol{\psi}^*\right)^T{\bf \bar f}({\bf q}^*,{\bf K}-{\bf K}^*)\mathrm{dt} \geq 0,~~\forall~{\bf K}\in {\cal K}_{ad}.
\label{eq:ineq2}
\end{equation}
Using the variational equation~\eqref{eq:variational}, it follows from the second identity of~\eqref{eq:temp2} that
\begin{multline}
\boldsymbol{\eta}^T(t)\frac{\partial\Phi}{\partial{\bf q}}[t_f,{\bf q}(t_f)] +\int_{0}^{t_f}\boldsymbol{\eta}^T(t) \frac{\partial\ell}{\partial{\bf q}} [t,{\bf q}(t)]\mathrm{dt}=\\
\int_{0}^{t_f}\left\{\left(\boldsymbol{\psi}^*\right)^T\left[\boldsymbol{\dot\eta}-\frac{\partial{\bf f}}{\partial{\bf q}}({\bf q}^*,{\bf K}^*) \boldsymbol{\eta}(t)\right]\right\}\mathrm{dt}.
\label{eq:temp3}
\end{multline}
Integrating by parts and since $\boldsymbol{\eta}(0) = 0$, 
\begin{multline*}
\int_{0}^{t_f}\left(\boldsymbol{\psi}^*\right)^T\left[\boldsymbol{\dot\eta}(t)-\frac{\partial{\bf f}}{\partial{\bf q}}({\bf q}^*,{\bf K}^*)\boldsymbol{\eta}(t)\right]\mathrm{dt}=\\
\boldsymbol{\eta}^T(t_f)\boldsymbol{\psi}^*(t_f) + \int_{0}^{t_f}\boldsymbol{\eta}^T(t)\left(-\boldsymbol{\dot\psi}-\left\{\frac{\partial{\bf f}}{\partial{\bf q}}({\bf q}^*,{\bf K}^*)\right\}^T\boldsymbol{\psi}^*\right)\mathrm{dt}.
\end{multline*}
%
Expression~\eqref{eq:temp3} can now be written as
\begin{multline}
\boldsymbol{\eta}^T(t)\frac{\partial\Phi}{\partial{\bf q}}[t_f,{\bf q}(t_f)] +\int_{0}^{t_f}\boldsymbol{\eta}^T(t) \frac{\partial\ell}{\partial{\bf q}} [t,{\bf q}(t)]\mathrm{dt}=\\
\boldsymbol{\eta}^T(t_f)\boldsymbol{\psi}^*(t_f) + \int_{0}^{t_f}\boldsymbol{\eta}^T\left\{-\boldsymbol{\dot\psi}^*-\left[\frac{\partial{\bf f}}{\partial{\bf q}}({\bf q}^*,{\bf K}^*)\right]^T\boldsymbol{\psi}^*\right\}\mathrm{dt}
\label{eq:costate1}
\end{multline}
It is clear from~\eqref{eq:costate1} that
\begin{equation}
\boldsymbol{\dot\psi}^* = -\left[\frac{\partial{\bf f}}{\partial{\bf q}}({\bf q}^*,{\bf K}^*)\right]^T\boldsymbol{\psi}^*-\frac{\partial\ell}{\partial{\bf q}}[t,{\bf q}^*(t)],~\text{with}~
\boldsymbol{\psi}^*(t_f) = \frac{\partial\Phi}{\partial{\bf q}}[t_f,{\bf q}(t_f)].
\label{eq:costate2}
\end{equation}
The costate dynamics~\eqref{eq:costate2} is linear along the optimal trajectories. Thus, the necessary conditions of optimality is given by the integral inequality~\eqref{eq:ineq2}, the costate dynamics~\eqref{eq:costate2}, and the state equation~\eqref{eq:systemFeedbackFull}. In other words, the choice of ${\bf K}\in{\cal K}_{ad}$ determines the optimality conditions~\eqref{eq:ineq2},~\eqref{eq:costate2}, and~\eqref{eq:systemFeedbackFull}.

Consider the optimality condition~\eqref{eq:ineq2} and rewriting it as follows
\begin{equation}
\begin{split}
\int_{0}^{t_f} \left(\boldsymbol{\psi}^*\right)^T{\bf f}({\bf q}^*,{\bf K})\mathrm{dt} \geq
\int_{0}^{t_f} \left(\boldsymbol{\psi}^*\right)^T{\bf f}({\bf q}^*,{\bf K}^*)\mathrm{dt},~\forall~{\bf K}\in {\cal K}_{ad}.
\end{split}
\label{eq:ineq3}
\end{equation}
Using the integral inequality~\eqref{eq:ineq3}, it is easy to derive the point-wise inequality~\cite{Ahmed2006}
\begin{equation}
\begin{split}
\left(\boldsymbol{\psi}^*\right)^T{\bf f}({\bf q}^*,{\bf K}) \geq
\left(\boldsymbol{\psi}^*\right)^T{\bf f}({\bf q}^*,{\bf K}^*),~~\forall~{\bf K}\in {\cal K}_{ad}.
\end{split}
\label{eq:ineq4}
\end{equation}
Now adding the term $\ell[t,{\bf q}^*(t)]$ in both sides of~\eqref{eq:ineq4} yields
%
\begin{equation*}
\begin{split}
\left(\boldsymbol{\psi}^*\right)^T{\bf f}({\bf q}^*,{\bf K}) +\ell[t,{\bf q}^*(t)]\geq
\left(\boldsymbol{\psi}^*\right)^T{\bf f}({\bf q}^*,{\bf K}^*) +\ell[t,{\bf q}^*(t)],
\end{split}
%\label{eq:ineq4}
\end{equation*}
which gives the Hamiltonian inequality
\begin{equation*}
{\cal H}[t,{\bf q}^*(t),\boldsymbol{\psi}^*(t),{\bf K}(t)] \geq{\cal H}[t,{\bf q}^*(t),\boldsymbol{\psi}^*(t),{\bf K}^*(t)].
\end{equation*}
This is the same as inequality~\eqref{eq:inequality-H} stated in the theorem. Differentiating ${\cal H}$ with respect to the costate variable $\boldsymbol{\psi}$, we get
\begin{equation*}
\frac{\partial{\cal H}}{\partial\boldsymbol{\psi}}[t,{\bf q}^*(t),\boldsymbol{\psi}^*(t),{\bf K}^*(t)] = {\bf f}[{\bf q}^*(t),{\bf K}^*(t)],
\end{equation*}
which leads to the state equation
\begin{equation*}
{\bf \dot q}^* = \frac{\partial{\cal H}}{\partial\boldsymbol{\psi}}^* [t,{\bf q}^*(t),\boldsymbol{\psi}^*(t),{\bf K}^*(t)],~~{\bf q}^*(0)={\bf q}_0,
\end{equation*}
as defined in~\eqref{eq:state}.

Differentiating ${\cal H}$ with respect to the state variable ${\bf q}$ yields
\begin{equation*}
\frac{\partial{\cal H}}{\partial{\bf q}}[t,{\bf q}^*(t),\boldsymbol{\psi}^*(t),{\bf K}^*(t)] =\left[\frac{\partial{\bf f}}{\partial{\bf q}}({\bf q}^*,{\bf K}^*)\right]^T\boldsymbol{\psi}^*+\frac{\partial\ell}{\partial{\bf q}}[t,{\bf q}^*(t)] = -\boldsymbol{\dot\psi}^*.
\end{equation*}
Hence, the costate dynamics~\eqref{eq:costate2} can be expressed in terms of Hamiltonian as
\begin{equation*}
\begin{split}
\boldsymbol{\dot\psi}^* = -\frac{\partial{\cal H}}{\partial{\bf q}}^* [t,{\bf q}^*(t),\boldsymbol{\psi}^*(t),{\bf K}^*(t)],~\text{and}~
\boldsymbol{\psi}^*(t_f) = \frac{\partial\Phi}{\partial{\bf q}}[t_f,{\bf q}(t_f)],
\end{split}
\end{equation*}
which is the condition~\eqref{eq:costate}. 
\end{proof}
%
It is clear that Theorem~\ref{thm:necessary-conditions} provides the necessary conditions for the feedback law ${\bf K}(t)$ to be optimal. However, in order to solve for this optimal feedback operator, we express the gradient of the Hamiltonian defined in~\eqref{eq:hamiltonian} and set it to zero, \textit{i.e.,}
%
\begin{align}
\mathcal{H}_{{\bf K}}\equiv\frac{\partial {\cal H}}{\partial {\bf K}} = {\bf G}^T[{\bf q}(t,{\bf K})]\bm{\psi}(t) {\bf q}^T(t,{\bf K})={\bf 0},
\label{eq:gradient}
\end{align}
which characterizes the direction of convergence of the system's actual trajectory to the desired trajectory modeled by~\eqref{eq:actual-trajectory-full}. Note that the expression in~\eqref{eq:gradient} is dependent on the feedback operator  ${\bf K}$ through the solution of the state feedback model~\eqref{eq:systemFeedbackFull} for ${\bf q}(t,{\bf K}).$  Hence, the problem boils down to finding ${\bf K}(t),~t\in{\cal I},$ such that the system's actual trajectory from~\eqref{eq:actual-trajectory-full} and the costate trajectory from~\eqref{eq:costate} satisfy~\eqref{eq:gradient}. The optimal feedback operator  ${\bf K}^*$ can be determined by satisfying the Hamiltonian inequality~\eqref{eq:inequality-H}. In other words, the choice of ${\bf K}$ is to be adaptively tuned to minimize the vehicle's tracking error.

\begin{corollary}[Adapting the control law ${\bf K}$~]
\label{cor:convergence}
Consider the system's feedback model~\eqref{eq:systemFeedbackFull} defined over the time horizon ${\cal I}.$ Adapting the operator ${\bf K}$ according to the following offline update rule 
\begin{equation}
{\bf K}^{new} = {\bf K}^{old} - \epsilon \mathcal{H}_{{\bf K}},
\label{eq:update-rule}
\end{equation}
for small $\epsilon$ satisfies the Hamiltonian inequality~\eqref{eq:inequality-H} and, hence, guarantees the convergence of the system's trajectory to follow its reference trajectory. 
\end{corollary}

\begin{proof}
Let 
%
\begin{equation}
{\bf K}^* = {\bf K} - \epsilon {\cal H}_{{\bf K}} \thinspace ,
\label{eq:proof-4}
\end{equation}
%
for some ${\bf K} \in \mathbb{R}^{m\times n}.$  The corresponding Hamiltonian is 
%
\begin{equation*}
{\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}^*) 
={\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}-\epsilon {\cal H}_{{\bf K}}) \thinspace ,
%\label{eq:proof-5}
\end{equation*}
%
where ${\bf q}^*$ and $\bm{\psi}^*$ are the system's state and the costate variable corresponding to ${\bf K}^*.$ Taking the Taylor series expansion of the right hand side about ${\bf K}^*$, we get
%
\begin{equation*}
  {\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}^*)  = {\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}) 
  +\mathrm{Tr} \left[{\cal H}_{{\bf K}}^T{\bf (K^*-K)}\right]+{\cal O}(\varepsilon) \thinspace .
\end{equation*}
%
Neglecting the higher order terms of the above expression yields
%
\begin{equation*}
\begin{split}
  {\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}^*) \equiv {\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}) 
  -\epsilon \mathrm{Tr}\left[{\cal H}_{{\bf K}}^T {\cal H}_{{\bf K}}\right]
   = {\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}) -\epsilon\|{\cal H}_{{\bf K}}\|^2
 < {\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}) 
\end{split}
%\label{eq:proof-6}
\end{equation*}
%
since $\epsilon\|{\cal H}_{{\bf K}}\|^2 > 0$. Hence, update rule~\eqref{eq:proof-4} guarantees that the Hamiltonian ${\cal H}$ is monotonically decreasing, which proves that the adaptation law~\eqref{eq:update-rule} eventually leads to the optimal feedback control law ${\bf K}^*.$
\end{proof}
%
%\begin{remark}
%Theoretically, if ${\bf K}^*$ be any arbitrary feedback gain that satisfies the Hamiltonian inequality~\eqref{eq:inequality-H}
%\begin{equation*}
%{\cal H}(t,{\bf q}^*,\bm{\psi}^*,{\bf K}^*) \leq {\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}), ~\forall~{\bf K}\in {\cal K}_{ad}, 
%\end{equation*}
%then the update rule 
%\begin{equation}
%{\bf K}^{'}={\bf K}^*+\varepsilon ({\bf K}-{\bf K}^*),~\forall~{\bf K}\in {\cal K}_{ad}~\text{and}~\varepsilon\in[0,1]
%\label{eq:update-rule-temp}
%\end{equation}
%yields the inequality~\eqref{eq:inequality-H}
%\begin{equation}
%{\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}^*) \leq {\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}^*+\varepsilon ({\bf K}-{\bf K}^*)).
%\label{eq:proof-1}
%\end{equation}
%By taking the Taylor series expansion of the right hand side of~\eqref{eq:proof-1} about ${\bf K}^*$, we get
%%
%\begin{equation}
%\begin{split}
% {\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}^*) \leq {\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}^*) + 
%\varepsilon Tr\smclose{{\cal H}_{{\bf K}}^T({\bf K}-{\bf K}^*)}+{\cal O}(\varepsilon),
%\end{split}
%\label{eq:proof-2}
%\end{equation}
%where ${\cal O}(\varepsilon)$ is the higher order terms of the Taylor series. Neglecting the higher order terms of~\eqref{eq:proof-2}, we can write
%\begin{equation}
%\begin{split}
%0\leq \varepsilon Tr\smclose{{\cal H}_{{\bf K}}^T({\bf K}-{\bf K}^*)} =\varepsilon Tr\smclose{({\bf K}-{\bf K}^*)^T {\cal H}_{{\bf K}}},
%\smimplies Tr\smclose{({\bf K}^*)^T {\cal H}_{{\bf K}}} \leq Tr\smclose{{\bf K}^T {\cal H}_{{\bf K}}},
%\end{split}
%\label{eq:proof-3}
%\end{equation} 
%which shows that ${\bf K}^*$ in~\eqref{eq:update-rule-temp} is the optimal feedback gain. However, the problem of the update rule~\eqref{eq:update-rule-temp} is to find proper feedback gain ${\bf K}$ that satisfies the inequality~\eqref{eq:proof-3}. Hence, the update rule~\eqref{eq:update-rule} in Corollary~\ref{cor:convergence} is a perfect choice to find the optimal feedback gain ${\bf K}^*$. 
%\end{remark}
%
In the following, we numerically solve for the control law ${\bf K}$ such that~\eqref{eq:gradient} is satisfied, aggregating the components described earlier.

\section{Numerical Computation Control Law}
\label{sec:control-optimization}
For the dynamic system~\eqref{eq:systemFeedbackFull} to solve the trajectory tracking problem, we illustrate the key steps to determine the proposed universal control law ${\bf K}$, aggregating the components described in the previous sections.

Let ${\bf K}_i\equiv{\bf K}_i(t)$, $t\in {\cal I}$, be the gain at the $i$-th iteration of the optimization procedure.
\vskip6pt
\noindent
{\bf Step 0 (initialization):} Subdivide the time interval ${\cal I}\equiv [0,t_f]$ into $N$ subintervals. Assume a piecewise-constant ${\bf K}_i(t)={\bf K}_i(t_k)$, $t\in[t_k,t_{k+1}]$, for $k=0,1,\ldots,N-1.$

\noindent
Find ${\bf K}^*$ by repeating {\bf Steps~1--5} until the stopping criterion in {\bf Step~5} is met.

\noindent
{\bf Step 1:} Integrate the system's feedback system~\eqref{eq:systemFeedbackFull} as in~\eqref{eq:actual-trajectory-full} with ${\bf K}\equiv{\bf K_i}(t)$, $t \in {\cal I}$.
% and the initial vehicle's configuration ${\bf q}(0)$, and record the solution as trajectory ${\bf q_i}\equiv{\bf q_i}(t),~\text{for}~t \in I$.

\noindent
{\bf Step 2:} Solve costate equation~\eqref{eq:costate} backward for $\bm{\psi}_i$.

\noindent
{\bf Step 3:} Define the Hamiltonian ${\cal H}({\bf q}_i, \bm{\psi}_i,{\bf K}_i)$ as in~\eqref{eq:hamiltonian}.

\noindent
{\bf Step 4:} Compute the cost function $J({\bf K}_i)$ using~\eqref{eq:cost-fn}, the gradients of the Hamiltonian ${\cal H}_{{\bf K}}$ using~\eqref{eq:gradient}, and its corresponding intergrated norm 
\(
\int_{0}^{t_f}\|{\cal H}_{{\bf K}}\|^2 \mathrm{dt}.
\)

\noindent
{\bf Step 5:} If $J({\bf K}_i)\leq\delta_1$ or $\int_{0}^{t_f}\|{\cal H}_{{\bf K}}\|^2 \mathrm{dt} \leq \delta_2$, for pre-defined small positive tolerance constants $\delta_1$ and $\delta_2$, then ${\bf K_i}$ is regarded close enough to its optimal value, and so the algorithm is halted.\\
Otherwise, use the following update rule to adjust the piecewise-constant feedback gain:
%
\begin{align*}
{\bf K}_{i+1}(t_k) & = {\bf K}_i(t_k) - \epsilon \thinspace {\cal H}_{{\bf K}(t_k)} + \lambda \thinspace \Delta{\bf K}_i(t_k) 
\\
\Delta{\bf K}_i(t_k) & = {\bf K}_{i}(t_k) - {\bf K}_{i-1}(t_k)
\end{align*}
%
for $k=0,1,\ldots,N-1,$ where $\epsilon$ and $\lambda$ are the step size and the momentum constant (for faster convergence), respectively. We now have the optimal feedback operator ${\bf K}\approx{\bf K}^*.$ The optimal control inputs can thus be computed using~\eqref{eq:controlLaw1} for the system to follow any desired trajectory defined by ${\bf q}^d(t),~t\in {\cal I}.$

\section{Example}
\label{sec:example}
Consider vehicle with Ackermann steering whose kinematic model is given by %
%
\begin{align}
\label{eq:modelVehicle}
{\bf \dot q}(t) &= {\bf G}[{\bf q}(t)]{\bf u}(t),~~\mathrm{and}\\
\label{eq:feedbackControlSimulation}
{\bf u}(t) & = {\bf K}(t){\bf q}(t)
\end{align}
where the vehicle's control input vector ${\bf u}(t)\equiv [\nu_f(t)~\omega_f(t)]^T\in{\cal U}\subset\mathbb{R}^2$, with $\nu_f(t)$ and $\omega_f(t)$ being the front wheels' linear and steering velocities, respectively, ${\bf K} \in \mathbb{R}^{2\times 4}$ is the control law for the vehicle,  and
\begin{equation*}
{\bf G}[{\bf q}(t)]=
\begin{bmatrix}
\cos\phi(t)\cos\theta (t) &0\\
\cos\phi(t)\sin\theta (t) & 0\\
\frac{1}{l}\sin\phi(t) & 0\\
0& 1
\end{bmatrix}.
\end{equation*}   
%In addition, due to the vehicle's limit on its velocities, the inputs are constrained as
%\begin{equation}
%\smabs{\nu_f(t)}\leq \nu_f^{max}~~\text{and}~\smabs{\omega_f(t)}\leq \omega_f^{max},~t\in I,
%\label{eq:constraint-u}
%\end{equation}
%where $\nu_f^{max}$ and $\omega_f^{max}$ is the maximum linear and steering velocities of the vehicle. In other words, ${\bf u}(t)$ must be chosen from a set of admissible controls, $\smset{U}_{ad}$,~\smie~${\bf u}(t)\in\smset{U}_{ad}\subset\Reals^m$ which are used to generate the set of state trajectories $\smset{Q}$. %
%
%shown in Fig.~\ref{fig:car-model}, where the front and rear axles lock the front and rear wheels, respectively. 
%Hence, each axle collapse two wheels into a single wheel acting on its midpoint, which yields $(x_r,y_r)$ and $(x_f,y_f)$ to be the active points of the rear and front wheels, respectively. 
%
Model~\eqref{eq:modelVehicle} is similar to~\eqref{eq:systemModel} except that the drift is absent in a car-like vehicle. If ${\cal Q}$ denotes the set of state trajectories of the vehicle, its configuration at any time $t$ is represented by the vector ${\bf q}(t)=[x(t)~~y(t)~~\theta(t)~~\phi(t)]^T\in{\cal Q}\subset\mathbb{R}^4,$ where $(x(t),y(t))$ is the Cartesian position of the midpoint of the line of length $l$ connecting two axles dividing at their midpoints.% as shown in Fig.~\ref{fig:car-model}, % 
$\theta(t)\in(-\pi,\pi]$ is the orientation of the car body with respect to X-axis, and $\phi(t)\in(-\pi/2,\pi/2)$ is the steering angle of the front wheels with respect the car body.
%\begin{figure}[htbp]
%	\centering
%	\includegraphics[scale = 0.75]{car-model}
%	\caption{Kinematic model of a vehicle with Ackermann geometry.}
%	\label{fig:car-model}
%\end{figure} 
%The vehicle is subject to the nonholonomic constraints given by
%\begin{equation}
%\begin{split}
%&\dot x\sin(\theta+\phi) - \dot y\cos(\theta+\phi) -l\dot\theta\cos\phi = 0~\text{and}\\
%&\dot x\sin\theta - \dot y\cos\theta = 0,\\
%\end{split}
%\label{eq:constraint-car}
%\end{equation} 
%which act on each wheel to prevent it from slipping laterally. The constraints~\eqref{eq:constraint-car} can be used to derive the vehicle's (front wheel driving) kinematic model

Let us consider that the vehicle has to follow a feasible and smooth desired trajectory given in terms of Cartesian positions $(x^d(t), y^d(t))$, for $t\in {\cal I}\equiv [0~60]~\si{\second}$.  $x^d(t) = 2\cos(2\pi t/60)~\text{and}~y^d(t) = 2\sin(2\pi t/60)$. The optimal universal control law ${\bf K}^*(t),~t\in[0,60]~\si{\second}$ for ~\eqref{eq:feedbackControlSimulation} is then computed as per {\bf Step 1} to {\bf Step~5} using the vehicle model~\eqref{eq:modelVehicle}. The vehicle could still perfectly track the circle from the initial state of $(1,0,0\si{\degree},45\si{\degree})$ as it is clear from Fig.~\ref{fig:circle-trajectory}. The state tracking errors are revealed in Fig.~\ref{fig:circle-error}, which are zero almost all the time after converging to the circle after time $t=\SI{20}{\second}.$ The vehicle has maintained the boundedness of its vehicle velocities and has stopped at the end of the trajectory, $(2,0)~\si{\meter}$, where velocity is zero as shown in Fig.~\ref{fig:circle-control-velocity} with the corresponding optimal universal feedback operator ${\bf K}^*(t)$ in Fig.~\ref{fig:circle-feedback-gain}. Due to the vehicle's speed limits each element of the control law ${\bf K}$ is bounded, as expected.  
\begin{figure}[htbp]%
\centering
\subfigure[][]{%
    \label{fig:circle-trajectory}%
    \includegraphics[width=0.48\textwidth,height=0.295\textheight]{circle/trajectory} }
 \subfigure[][]{%
    \label{fig:circle-error}%
    \includegraphics[width=0.48\textwidth,height=0.295\textheight]{circle/error} }
\\
 \subfigure[][]{%
    \label{fig:circle-control-velocity}%
    \includegraphics[width=0.48\textwidth,height=0.295\textheight]{circle/control-velocity} }
\subfigure[][]{
  \label{fig:circle-feedback-gain}
    \includegraphics[width=0.48\textwidth,height=0.295\textheight]{circle/feedback-gain}} 
\caption[Performance of circle trajectory.]{Controller's performance in tracking circle trajectory
   \subref{fig:circle-trajectory} trajectory,
   \subref{fig:circle-error} state tracking error, and
    \subref{fig:circle-control-velocity} velocity (control input), and
    \subref{fig:circle-feedback-gain} optimal control law, ${\bf K}^*(t).$
}%
  \label{fig:circle}%
\end{figure}

Hence, the proposed control law ${\bf K}(t),$ is able to provide necessary control actions for the vehicle to track a pre-defined trajectory. It is important to articulate the fact that the proposed universal control law is able to solve trajectory tracking problem of any nonlinear systems of the form~\eqref{eq:systemModel}, but the model~\eqref{eq:modelVehicle} was chosen for the demonstration purpose only.

 %%%%%%%%%%%%%%%%%%%%
 \section{Summary and Conclusions}
 \label{sec:conclusion}
 We examined a novel universal control law for solving the trajectory tracking problem of a class of nonholonomic systems with drift. Both existence and necessary conditions of optimality for the control law are presented along with their proofs. Numerical results on computing control law and its application in a vehicle with Ackermann steering are presented. As can be seen, vehicle is able to track a predefined trajectory using the proposed control law. It can be shown that this control law is able to solve trajectory tracking problems of other nonholonomic systems, such as unicycle, differential drive mobile robots, and hopping robot in flight-phase. Computation of control law is offline, which is its only drawback and we are currently investing to determine online solution to the proposed universal control law.  It is interesting to note that the system model is not required to be linearized to follow a certain reference trajectory in finite time. However, the proposed control law assumes that the system's state is completely observable, which may be a too restrictive and non realistic hypothesis to model a real-vehicle's control law. Designing partially-observed feedback optimal laws is another possible future research avenue of  this current work. Moreover, the practical realization of this proposed optimal feedback control law on a commercial vehicle is possible as the algorithm can be implemented on a microcontroller due to its computational efficiency.

% \appendices
% \section{Proof of the First Zonklar Equation}
% Some text for the appendix.

% use section* for acknowledgement
%\section*{Acknowledgment}
%
%The authors would like to thank...

\bibliographystyle{IEEEtran}        % Include this if you use bibtex

\bibliography{bib/refsBooksTRTheses,bib/refsGenericControl,bib/refsSuruzWeb}

\end{document}

### 2019-05-31 presentationNotes.tex
comment

@@
 %\title{Time Varying Operator for Controlling Nonholonomic Systems with Drift}
-\title{Universal Control Law for Nonholonomic Systems with Drift}
+\title{Introduction to Robot Operating System (ROS)}
 
-\author{Md Suruz~Miah,~\IEEEmembership{Senior Member,~IEEE}% and 
+\author{Amr Elhussein, Advisor: Dr. Suruz Miah %~\IEEEmembership{Senior Member,~IEEE}% and 
 %		N.~U.~Ahmed                
-\thanks{S.~Miah is with the Electrical and Computer Engineering Department, Bradley University, Peoria, IL, 61625, USA. e-Mails:~smiah@bradley.edu}% <-this % stops a space
+%\thanks{S.~Miah is with the Electrical and Computer Engineering Department, Bradley University, Peoria, IL, 61625, USA. e-Mails:~smiah@bradley.edu}% <-this % stops a space
 %\thanks{S.~Miah is with the Electrical and Computer Engineering Department, Bradley University, Peoria, IL, 61625, USA. e-Mail:~smiah@bradley.edu}% <-this % stops a space
@@
 
-\thanks{This research supported in part by Caterpillar Inc.}
+%\thanks{This research supported in part by Caterpillar Inc.}
 }
@@
 
-\begin{abstract}
-A universal control law for nonholonomic systems with drift is considered.
+%\begin{abstract}
+%A universal control law for nonholonomic systems with drift is considered.
 While the development of feedback control laws for controlling nonlinear dynamical systems are well-established in the literature to date, the need of a control theoretic method to establish a universal control law for a class of nonlinear systems is significant.
-This is simply because the formulation of feedback control laws  relies on types of dynamical systems to be controlled which lead to a significant technical challenge for researchers.% to propose a general feedback law for a class of  nonlinear dynamical systems.
+%This is simply because the formulation of feedback control laws  relies on types of dynamical systems to be controlled which lead to a significant technical challenge for researchers.% to propose a general feedback law for a class of  nonlinear dynamical systems.
 %This task is even more challenging when the system is only partially observable.
 %
-Here we underscore the need for a universal control law  that is aimed to address the trajectory tracking problem of nonholonomic systems with drift.
+%Here we underscore the need for a universal control law  that is aimed to address the trajectory tracking problem of nonholonomic systems with drift.
 For that, we propose to develop a time-varying feedback operator (called  herein a universal control law), to solve the tracking problem.
@@
 
-\end{abstract}
+%\end{abstract}
 
 % Note that keywords are not normally used for peerreview papers.
-\begin{IEEEkeywords}
-Generalized control law, nonholonomic systems, drift, Pontryagin's minimum principle.
-\end{IEEEkeywords}
-\IEEEpeerreviewmaketitle
+%\begin{IEEEkeywords}
+%Generalized control law, nonholonomic systems, drift, Pontryagin's minimum principle.
+%\end{IEEEkeywords}
+%\IEEEpeerreviewmaketitle
 
 %%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-
-\section{Notations and Preliminaries}\label{sec:notations}
-Throughout this paper, scalar and vector quantities will be denoted by non-bold letters and lower-case bold letters, respectively.
-Upper-case bold letters will denote matrices.
-For any positive integer $n$, $\mathbb{R}^n$ denotes the Euclidean space.
-For any vector ${\bf x,y}\in\mathbb{R}^n$, the standard Euclidean norm and the scalar product are given by
-\begin{equation*}
-\|{\bf x}\| \equiv  \left[\sum_{i=1}^n \left |x_i\right |^2\right]^{1/2}~\hbox{and}~~ {\bf (x\cdot y)}\equiv{\bf x}^T{\bf y}\equiv\sum_{i=1}^n x_i y_i, 
-\end{equation*}
-respectively.
-We shall use $\mathbb{R}^{m\times n}$ to denote the space of $m\times n$ matrices with entries from $\mathbb{R}$.
-Let ${\bf X,Y}\in\mathbb{R}^{m\times n}$, then the standard norm and their scalar product are also given by
-\begin{equation*}
-\begin{split}
-\|{\bf X}\|\equiv\left[\sum_{i=1}^m \sum_{j=1}^n\left |x_{i,j}\right |^2\right]^{1/2}~\text{and}~{\bf (X\cdot Y)}\equiv Tr\left[{\bf X}^T{\bf Y}\right]\equiv Tr\left[{\bf X}{\bf Y}^T\right],
-\end{split}
-\end{equation*}
-respectively, where $\mathrm{Tr}\left[\cdot\right]$ denotes the trace of matrix $\left[\cdot\right]$.
-Clearly, $\mathrm{Tr}\left[{\bf X}^T{\bf X}\right]=\|{\bf X}\|^2$.
-${\bf X}\otimes {\bf Y}$ is the Kronecker product of two matrices ${\bf X,Y},$ where $\mathbb{R}^{m^2\times n^2}\ni {\bf Z} = {\bf X}\otimes {\bf Y}.$ $C({\cal I}, \mathbb{R}^n)$ is the class of all continuous function on the time interval ${\cal I}$ taking values from~$\mathbb{R}^n.$
-
-If the function $J:\mathbb{R}^n\to \mathbb{R}$ is differentiable at ${\bf x}\in \mathbb{R}^n$, then for any ${\bf v}\in\mathbb{R}^n$, $dJ({\bf x};{\bf v})$ denotes the Gateaux (directional) derivative in the direction of ${\bf v}$, which is given by
-%
-\begin{equation*}
-dJ({\bf x};{\bf v}) = {\bf v}^T\nabla J=\lim_{\varepsilon\to 0} \frac{J({\bf x} + \varepsilon{\bf v}) - J({\bf x})}{\varepsilon}, 
-\end{equation*}
-where $\nabla J$ denotes the gradient of $J$.
-%
-However, if $J:\mathbb{R}^{m\times n}\to \mathbb{R}$, then for any ${\bf X},{\bf V}\in\mathbb{R}^{m\times n}$, the directional derivative in the direction of ${\bf V}$ is defined by
-\begin{equation*}
-dJ({\bf X};{\bf V}) = Tr[{\bf V}^T\nabla J] = \lim_{\varepsilon\to 0} \frac{J({\bf X} + \varepsilon{\bf V}) - J({\bf X})}{\varepsilon}. 
-\end{equation*}
-For any bounded time interval ${\cal I} \equiv [0, t_f],~t_f>0,$ $C({\cal I},\mathbb{R}^n)$ denotes the class of all continuous functions on ${\cal I}$ taking values in $\mathbb{R}^n$.
-Let $p \in [1,\infty)$ and  any finite time interval ${\cal I}$, we use  ${\cal L}_p({\cal I},\mathbb{R}^n)$ to denote the set of Lebesgue measurable functions $\{{\bf f}\}$ defined on ${\cal I}$ and taking values in $\mathbb{R}^n$ whose norms are $p$-th power integrable,~\textit{i.e.,}~
-%\begin{equation*}
-$L_p({\bf f}) = \left(\int_{0}^{t_f}\|{\bf f}\|^p \mathrm{dt}\right)^{1/p}<\infty,$ 
-%\end{equation*}
-%
-where $L_p({\bf f})$ denotes the $p$th norm of the function ${\bf f}$~\cite{Royden2010,Khalil2002}.
-For $p=\infty$, ${\cal L}_{\infty}({\cal I},R^n)$ denotes the space  of Lebesgue measurable functions $\{{\bf f}\}$ defined on ${\cal I}$ and taking values in $\mathbb{R}^n$ satisfying
-%
-%\begin{equation*}
-$\text{ess sup} \{ \|{\bf f}(t)\|, t \in {\cal I}\} < \infty.$
-%\end{equation*}
-%
-% Similarly, ${\cal L}_p^{\ell oc}([0,\infty),\mathbb{R}^n)$ are locally convex topological vector spaces of $p$-th power locally integrable functions containing the  spaces ${\cal L}_p(I,\mathbb{R}^n)$.
-%We use $\mathrm{diag}(a_1,\ldots,a_n)$ to represent a matrix whose diagonal entries starting in the upper left corner are $a_1,\ldots,a_n$.
-
-\section{System Model and Problem Statement}
-\label{sec:systemModel}
-\subsection{System Model}
-We consider a class of dynamical systems described by 
-\begin{subequations}
-\label{eq:system}
-\begin{align}
-\label{eq:systemModel}
-\dot{{\bf q}}(t) & = \bar{{\bf g}}({\bf q}(t)) + \sum_{j=1}^m{\bf g}_j({\bf q}(t))u_j(t),\\
-\label{eq:controlLaw}
-u_j(t) & = {\bf k}_j^T(t) {\bf q}(t), 
-\end{align}
-\end{subequations}
-where ${\bf q}(t)\in{\cal Q}\subset\mathbb{R}^n$ is the state of the system at time $t\ge 0$ with ${\cal Q}$ being its state space, $u_j$ is the $j$th, $j=1,\ldots, m$ control variable, and ${\bf k}_j: \mathbb{R}\to \mathbb{R}^n$ is the time-varying feedback operator of the $j$th control variable for positive integer $n,$ $m$ with $n>m$.
-The drift vector field $\bar{{\bf g}}:\mathbb{R}^n\to\mathbb{R}^n$ represents natural unforced motion of the system and ${\bf g}_j:\mathbb{R}^n\to\mathbb{R}^n,$ $j=1,\ldots,m,$ are linearly independent control vector fields~\cite{Choset2004}.
-When no ambiguity arises, we shall drop the argument $(t)$ for clarity.
-System~\eqref{eq:system} can also be written in compact form as
-%
-\begin{subequations}
-\label{eq:system1}
-\begin{align}
-\label{eq:systemModel1}
-\dot{{\bf q}} & = \bar{{\bf g}}({\bf q}) + {\bf G}({\bf q}){\bf u},\\
-\label{eq:controlLaw1}
-{\bf u} & = {\bf K}(t) {\bf q}, 
-\end{align}
-\end{subequations}
-%
-where ${\bf u}\in{\cal U}\subset \mathbb{R}^m$ is the vector of $m$ control inputs to the system, ${\bf G}:\mathbb{R}^n\to\mathbb{R}^{n\times m},$ and the time varying feedback operator ${\bf K}:\mathbb{R}_0^+\to{\cal K}_{\mathrm{ad}}\subset\mathbb{R}^{m\times n}.$
-
-Note the difference in the feedback control law in~\eqref{eq:controlLaw1} with other existing control laws in the literature.
-It is simply a matter of determining the universal matrix (herein called feedback operator) ${\bf K}(t)\in{\cal K}\subset\mathbb{R}^{m\times n}.$
-
-\subsection{Problem Formulation} 
-Let ${\bf q}^d(t)$ be the desired (reference) trajectory that the system~\eqref{eq:systemModel1} is supposed to track and $e(t) = \|{\bf q}(t)-{\bf q}^d(t)\|_{\mathbb{R}^n}$ denotes its state tracking error, for $t\in {\cal I}$.
-The objective is to find the optimal time-varying feedback operator  ${\bf K}(t)\in {\cal K}_{ad}$ that generates the trajectory ${\bf q}(t)\in{\cal Q}$ while minimizing the average cumulative state tracking error, $\mathscr{E}_{\mathrm{avg}}$, given by
-\begin{equation}
-\mathscr{E}_{\mathrm{avg}} = \frac{1}{t_f}\int_{0}^{t_f}e(t)\mathrm{dt},~~t_f>0.
-\label{eq:tracking-error}
-\end{equation}
-
-Given the system model~\eqref{eq:system1}, the problem can be stated as follows:
-\begin{equation}
-\inf_{\{{\bf q}\in{\cal Q},~{\bf K}\in{\cal K}_{ad}\}} [\mathscr{E}_{\mathrm{avg}}].
-\label{eq:problem}
-\end{equation}
-
-\section{Proposed Universal Control Law}
-\label{sec:feedbackOperator}
-This section details the design procedure of the proposed universal time-varying control law, which is the main contribution of this manuscript.
-Substituting~\eqref{eq:controlLaw1} in~\eqref{eq:systemModel1}, yields the following full-state feedback system:
-\begin{equation}
-\begin{split}
-\dot{{\bf q}}  = \bar{{\bf g}}({\bf q}) + {\bf G}({\bf q}){\bf K}(t) {\bf q} \equiv{\bf f}({\bf q},{\bf K}),
-\end{split}
-\label{eq:systemFeedbackFull}
-\end{equation}
-with ${\bf q}(0)={\bf q}_0.$ We emphasize that the generalized linear time varying operator ${\bf K}(t)$ completely characterizes the feedback law~\eqref{eq:systemFeedbackFull} for solving the trajectory tracking problem.
-
-\begin{lemma}[Solutions of feedback system]
-\label{lem:feedback-sol}
-Given the feedback system~\eqref{eq:systemFeedbackFull}, which is defined over the finite time horizon of ${\cal I}$, then for every initial condition ${\bf q}(0)\in\mathbb{R}^n$, and feedback operator ${\bf K}(t)\in {\cal K}_{ad}$, the system~\eqref{eq:systemFeedbackFull} has a unique absolutely continuous solution ${\bf q}(t)\in C({\cal I}, \mathbb{R}^n)$.
-Furthermore, the solution set ${\cal Q}\equiv\left\{{\bf q}(t) \equiv{\bf q}[t,{\bf K}(t)]\in C({\cal I},\mathbb{R}^n):{\bf K}(t)\in {\cal K}_{ad}\right \}$ is a bounded subset of $C({\cal I}, \mathbb{R}^n)$.
-\end{lemma}
-%\begin{IEEEproof}
-The proof of this lemma is classical and follows from a similar technique in~\cite[page~89]{Ahmed2006}. %
-%\end{IEEEproof}
-Hence, the actual trajectory of the of the vehicle can then be symbolically represented by 
-\begin{equation}
-{\bf q}(t) = {\bf q}(0) + \int_{0}^{t}{\bf f}[{\bf q}(\tau),{\bf K}(\tau)]d\tau,
-\label{eq:actual-trajectory-full} 
-\end{equation}
-for $t\in {\cal I}$. In order to solve the trajectory tracking problem of nonholonomic systems with drift, let us introduce the cost functional as
-\begin{equation}
-J({\bf K}) = \Phi [t_f,{\bf q}(t_f)] + \int_{0}^{t_f} \ell [t,{\bf q}(t,{\bf K})]\mathrm{dt},~~\mathrm{with}
-\label{eq:cost-fn}
-\end{equation}
-\begin{multline*}
-\Phi [t_f,{\bf q}(t_f)]= \frac{1}{2} [{\bf q}(t_f)-{\bf q}^d(t_f)]^T{\bf P}(t_f)[{\bf q}(t_f)-{\bf q}^d(t_f)] ~\mathrm{and}~\\
-\ell [t,{\bf q}(t)] =\frac{1}{2}[{\bf q}(t)-{\bf q}^d(t)]^T{\bf Q}(t)[{\bf q}(t)-{\bf q}^d(t)],
-%\label{eq:cost-fn}
-\end{multline*}
-where the weight matrix ${\bf P}(t_f) \in\mathbb{R}^{n\times n}$ and the  tracking weight ${\bf Q}(t)\in\mathbb{R}^{n\times n}$ are symmetric positive definite matrices that indicate the relative importance of the error components along $\mathbb{R}^n.$ %
-%
-%If the vehicle's purpose is to stabilize on a fixed configuration, then ${\bf P}(t_f)$ must be higher than ${\bf Q}(t)$ and the desired trajectory is set to a \emph{fixed} configuration.
-However, the opposite is true for the vehicle to track a desired trajectory.
-%
-The performance index $J({\bf K})$ in~\eqref{eq:cost-fn} depends on the feedback operator ${\bf K}(t)$ through the state variable ${\bf q}(t)$ as it is clear from the feedback system~\eqref{eq:systemFeedbackFull}.
-Note that $\Phi[\cdot]$ and $\ell[\cdot]$ of~\eqref{eq:cost-fn} are referred to as the terminal and tracking cost functionals, respectively.
-The task now becomes solving the following problem:
-\begin{equation}
-\inf_{{\bf K}\in{\cal K}_{ad}} [J({\bf K})],
-\label{eq:problem1}
-\end{equation}
-which yields ${\bf q}(t) \to {\bf q}^d(t)$ as $J({\bf K})\longrightarrow 0$, for $t\in {\cal I}$.
-It is important to point out that, solving the problem~\eqref{eq:problem1} will eventually solve  the problem~\eqref{eq:problem}.
-Hence, the problem~\eqref{eq:problem1} can be solved if there exists a generalized optimal feedback operator ${\bf K}^*(t)$, for $t\in {\cal I}.$ However, it is worth noting the following remark before we proceed determining the generalized control law ${\bf K}(t).$
-%
-
-\begin{remark}
-Note that the optimal feedback gain ${\bf K}(t)$ can be determined by following the classical Pontryagin's minimum principle~\cite[Chaper~8]{Ahmed2006} with ${\bf K}(t)$ being the open--loop control input to the feedback system~\eqref{eq:systemFeedbackFull}.
-For that, let $\mathrm{vec}({\bf K}(t))$ transforms the matrix ${\bf K}(t)$ into a column vector, which is formed by stacking the rows of ${\bf K}(t).$ The feedback model~\eqref{eq:systemFeedbackFull} can be rewritten as
-\begin{equation}
-  {\bf \dot q} = \bar{{\bf g}}({\bf q}) + \left({\bf q}^T\otimes{\bf G}({\bf q})\right){\bf \bar k},
-  \label{eq:systemFeedbackFull1}  
-\end{equation}
-where $\mathbb{R}^{nm}\ni{\bf \bar k}=\mathrm{vec}({\bf K})$ is now the control input vector that can be solved by following the standard gradient descent technique presented in~\cite[Chapter~3]{Stengel1994}~\cite[Chaper~8]{Ahmed2006}.
-By rearranging the elements of the optimal vector ${\bf \bar k}^*,$ we can reconstruct the optimal feedback operator ${\bf K}^*$ which is then substituted in the feedback law~\eqref{eq:systemFeedbackFull} to generate the optimal control input vector ${\bf u}^*(t),$ for $t\in{\cal I}.$  Nevertheless,  we emphasize in determining the optimal feedback operator ${\bf K}^*(t)$ directly by modifying the classical Pontryagin's minimum principle, which has applications in solving problems of a general class of partially observed dynamic systems.
-\end{remark}
-
-\subsection{Existence of Generalized Control Law}
-In this section, we provide the proof of the existence of the proposed generalized time-varying control law, ${\bf K}(t),$ that essentially solves the tracking problems of nonholonomic systems with drift.
-
-\begin{theorem}\label{thm:existence-K}
-Given a nonholonomic system modeled by \eqref{eq:systemModel1}, there exists a generalized optimal control law ${\bf K}^*(t) \in {\cal K}_{ad}$ for the controller modeled in~\eqref{eq:controlLaw1} that drives the system~\eqref{eq:systemModel1} to the desired trajectory ${\bf q}^d(t)$ while finding the optimal solution for the problem~\eqref{eq:problem}.
-\end{theorem}
-%%See Appendix~\ref{app:thm:existence-K} for its complete proof. %
- \begin{proof} 
-Following the well known Alaoglu's theorem\footnote{\href{https://en.wikipedia.org/wiki/Banach/wiki/Banach–Alaoglu_theorem}{https://en.wikipedia.org/wiki/Banach/wiki/Banach–Alaoglu\_theorem}},  ${\cal K}_{ad} \subset {\cal K}\subset\mathbb{R}^{m\times n}$  is a (weak star) $w^*$ compact set and it suffices to prove that ${\bf K} \longmapsto J({\bf K})$ is sequentially weak star continuous.
-Let $\{{\bf K}^i, i \in \mathbb{N}\} \in {\cal K}_{ad}$ be a sequence  and suppose   ${\bf K}^i \buildrel w^* \over \to {\bf K}^*.$ Since ${\cal K}_{ad}$ is $w^*$ closed,  we have ${\bf K}^* \in {\cal K}_{ad}$, see~\cite{AhMi2011-j1}.
-
-Suppressing the variable $t$ for clarity, let $\{{\bf q}^i,~i\in \mathbb{N}\}$ and ${\bf q}^*$ denote the  solutions of the system~\eqref{eq:systemFeedbackFull} corresponding to $\{{\bf K}^i,~i\in \mathbb{N}\}$ and ${\bf K}^*$, respectively.
-Hence, the corresponding state equation becomes
-\begin{align*}
-{\bf \dot q}^i = {\bf f}({\bf q}^i,{\bf K}^i)~\text{and}~
-{\bf \dot q}^* = {\bf f}({\bf q}^*,{\bf K}^*),~{\bf q}^i_0={\bf q}^*_0={\bf q}_0.
-\end{align*}
-%
-Using~\eqref{eq:actual-trajectory-full}, the solutions of the above two state-space models can be described by
-\begin{equation*}
-\begin{split}
-{\bf q}^i(t) = {\bf q}_0 + \int_{0}^{t}{\bf f}[{\bf q}^i(\tau),{\bf K}^i(\tau)]d\tau,~\text{and}~~
-{\bf q}^*(t)= {\bf q}_0 + \int_{0}^{t}{\bf f}[{\bf q}^*(\tau),{\bf K}^*(\tau)]d\tau.
-\end{split}
-\end{equation*}
-%
-Subtracting one from another, we get
-\begin{align}
-{\bf q}^i(t)-{\bf q}^*(t) = \int_{0}^t\left({\bf f}[{\bf q}^i(\tau),{\bf K}^i(\tau)]- {\bf f}[{\bf q}^*(\tau),{\bf K}^*(\tau)]\right)d\tau.
-\label{eq:existence-temp1}
-\end{align}
-Note that ${\bf G}({\bf q}^i),~i\in \mathbb{N}$ and ${\bf G}({\bf q}^*)$ are uniformly bounded functions and satisfy Lipschitz condition
-\begin{align*}
-\|{\bf G}({\bf q}^i)-{\bf G}({\bf q}^*)\|&\leq L_{c2}\|{\bf q}^i-{\bf q}^*\|,\\
-\|\bar{{\bf g}}({\bf q}^i)-\bar{{\bf g}}({\bf q}^*)\|&\leq L_{c1}\|{\bf q}^i-{\bf q}^*\|,\\
-\end{align*}
-where $L_{c1}$ and $L_{c2}$ are Lipschitz constants. Taking the Euclidean norm in both sides of expression~\eqref{eq:existence-temp1} and using the triangle inequality yield
-\begin{align*}
-\|{\bf q}^i(t)-{\bf q}^*(t)\| \leq v^i(t)+\int_{0}^t\beta(\tau)\|{\bf q}^i(\tau)-{\bf q}^*(\tau)\|d\tau,~\text{where}
-\end{align*}
-%
-\begin{equation*}
-v^i(t) = \Big\Vert\int_{0}^t\left[{\bf G}({\bf q}^i)({\bf K}^i-{\bf K}^*){\bf q}^i\right]d\tau\Big\Vert,
-\end{equation*}
-${\beta}(t) = (L_{c1} + c_1(t) + c_2(t)L_{c2}) \in{\cal L}_1^{+}({\cal I})$, with 
-\begin{align*}
-c_1(t)=[\sup \|{\bf G}({\bf q}^i)\|][\sup \|{\bf K}\|],~c_2(t) = \sup(\|{\bf K}^*\|\|{\bf q}\|),
-\end{align*}
-for $i\in \mathbb{N},~{\bf K}\in{\cal K},~\text{and}~{\bf q}\in{\cal Q}$ (see Theorem 8.3.4 of~\cite[page 273]{Ahmed2006} for more details). Thus,  it follows from Gronwall inequality that 
-\begin{equation} 
-\parallel {\bf q}^i(t) - {\bf q}^*(t)\parallel \leq v^i(t) + 
-\int_{0}^t \exp\{\int_{\tau}^t \beta(s)\mathrm{ds}\} \beta(\tau) v^i(\tau) d\tau.
-\label{eq:gronwall}
-\end{equation} 
-Clearly, $v^i(t)\to 0$, for $t\in {\cal I}$, $i\in \mathbb{N}$, as ${\bf K}^i\buildrel w^* \over \to {\bf K}^*$.
-Thus, it follows from inequality~\eqref{eq:gronwall} that ${\bf q}^i\buildrel {\bf K}^*\over \to {\bf q}^*.$
-%
-Since both $\ell (t,\cdot)$ and $\Phi(t,\cdot)$ are continuous on $\mathbb{R}^n,$ we have  $\ell[t,{\bf q}_i(t)] \longrightarrow \ell[t,{\bf q}^*(t)] $ for almost all $t \in {\cal I}$ and $\Phi[t,{\bf q}^i(t_f)] \longrightarrow \Phi[t,{\bf q}^*(t_f)] $ as $i \rightarrow \infty.$ Thus it follows from the expression \eqref{eq:cost-fn} that  $ \lim_{i \rightarrow \infty} J({\bf K}^i)  =  J({\bf K}^*)$ proving weak star continuity of  $J$ on ${\cal K}_{ad}.$ Since ${\cal K}_{ad}$ weak  star compact, $J$  attains its minimum on ${\cal K}_{ad}.$
-\end{proof}
-% 
-Theorem~\ref{thm:existence-K} guarantees that there exists an optimal universal control law ${\bf K}^*$ for nonholonomic systems modeled by~\eqref{eq:systemModel}.
-In the following, we provide the necessary conditions for the proposed universal control law.
-
-\subsection{Necessary Conditions}
-\label{sec:necessaryConditions}
-
-To solve for the optimal trajectory that minimizes the objective functional~\eqref{eq:cost-fn}, we need to derive the necessary conditions of optimality.
-These necessary conditions are most readily found if the integrand of the cost functional~\eqref{eq:cost-fn} is recast in terms of Hamiltonian
-%\begin{equation*}
-$\mathcal{H}:{\cal I}\times \mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^{m\times n} \longrightarrow \mathbb{R}$,
-%\end{equation*}
-which is expressed by
-%
-\begin{equation}
-\mathcal{H}[t, {\bf q}(t), \boldsymbol{\psi}(t),{\bf K}(t)] = \boldsymbol{\psi}^T(t){\bf f}[{\bf q}(t),{\bf K}(t)] + \ell[t,{\bf q}(t)],
-\label{eq:hamiltonian}
-\end{equation}
-%
-where $\boldsymbol{\psi}(t)\in\mathbb{R}^n,~t\in {\cal I}$, is a vector of Lagrange multipliers whose elements are the co-states of the system~\cite{Ahmed1988}.
-We now derive the necessary conditions of optimality feedback model~\eqref{eq:systemFeedbackFull}.
-
-\begin{theorem}
-\label{thm:necessary-conditions}
-Since the optimal universal feedback operator (control law) ${\bf K}^*(t),~t\in {\cal I}$ exists, the optimal trajectory ${\bf q}^*(t),~t\in {\cal I}$ for the feedback model~\eqref{eq:systemFeedbackFull} can be obtained if there exists an optimal multiplier $\boldsymbol{\psi}^*(t)\in C({\cal I},\mathbb{R}^n)$ such that the triple $\{{\bf q}^*,\boldsymbol{\psi}^*,{\bf K}^*\}$ satisfies the following necessary conditions:
-\begin{subequations}
-\begin{align}
-\label{eq:inequality-H}
-{\cal H}[t,{\bf q}^*(t),\boldsymbol{\psi}^*(t),{\bf K}(t)] & \geq{\cal H}[t,{\bf q^*}(t),\boldsymbol{\psi}^*(t),{\bf K^*}(t)], ~~{\bf K}(t)\in {\cal K},\\
-\label{eq:state}
-{\bf \dot q}^* &=\frac{\partial{\cal H}}{\partial\boldsymbol{\psi}} [t,{\bf q}^*(t),\boldsymbol{\psi}^*(t),{\bf K^*}(t)],~{\bf q}^*(0)={\bf q_0},\\
-\label{eq:costate}
-\boldsymbol{\dot\psi}^* &= -\frac{\partial{\cal H}}{\partial{\bf q}} [t,{\bf q}^*(t),\boldsymbol{\psi}^*(t),{\bf K}^*(t),~\boldsymbol{\psi}^*(t_f) = \frac{\partial\Phi}{\partial{\bf q}}[t_f,{\bf q}(t_f)].
-\end{align}
-\end{subequations}
-\end{theorem}
-%% The detailed and comprehensive proof of this Theorem is given in Appendix~\ref{app:thm:necessary-conditions}. %
-\begin{proof}
-Let ${\bf q}(t)\equiv{\bf q}[t,{\bf K}(t)]$ be the solution of the feedback system~\eqref{eq:systemFeedbackFull}, with the cost functional~\eqref{eq:cost-fn} for any choice of ${\bf K}(t)\in{\cal K}_{ad}$.
-Since ${\bf K}^*(t)$ is optimal with the associated trajectory ${\bf q}^*(t)$, it is clear that
-\begin{equation*}
-J({\bf K}^*) \leq J({\bf K}),~~\forall~{\bf K}(t)\in{\cal K}_{ad},~t\in {\cal I}. 
-\end{equation*}
-Suppressing the variable $t$ for clarity and for any $\varepsilon\in [0,1]$, we define ${\bf K}^{\varepsilon}={\bf K}^* + \varepsilon ({\bf K-K^*})$.
-Since ${\cal K}$ is a closed convex set, ${\cal K}_{ad}$ is also a closed convex subset of ${\cal L}_{\infty}({\cal I},\mathbb{R}^{m\times n})$ and therefore ${\bf K}^{\varepsilon}\in{\cal K}_{ad}$.
-Thus $J({\bf K^*}) \leq J({\bf K}^{\varepsilon})$, which follows that
-\begin{equation}
-dJ({\bf K}^*;{\bf K}-{\bf K}^*)=\mathrm{Tr}\left[\left({\bf K}-{\bf K}^*\right)^T\nabla J({\bf K}^*)\right]\geq 0,
-\label{eq:dJ}
-\end{equation}
-where $dJ({\bf K}^*;{\bf K}-{\bf K}^*)$ denotes the Gateaux (directional) derivative of $J$ evaluated at ${\bf K}={\bf K}^*$ in the direction of $({\bf K}-{\bf K}^*)$ and $\nabla J({\bf K}^*)$ is the gradient of $J$ evaluated at ${\bf K}^*$.
-
-Let ${\bf q}^{\varepsilon}$ be the solution of the feedback system~\eqref{eq:systemFeedbackFull} corresponding to the control law ${\bf K}^{\varepsilon}$ with the same initial state ${\bf q}^{\varepsilon}(0)={\bf q}_0$.
-It is easy to verify that
-%
-\begin{align*}
-  \lim_{\varepsilon\to 0} {\bf K}^{\varepsilon}(t) = {\bf K}^*(t),~~\text{and}~~
-  \lim_{\varepsilon\to 0} {\bf q}^{\varepsilon}(t) = {\bf q}^*(t).
-\end{align*}
-% 
-Hence, the state trajectories ${\bf q}^{\varepsilon}(t)$ and ${\bf q}^*(t),t\in {\cal I}$  are described by
-%
-\begin{equation*}
-\begin{split}
-{\bf \dot q}^\varepsilon &= {\bf f}({\bf q}^\varepsilon,{\bf K}^\varepsilon),~~{\bf q}^\varepsilon(0) = {\bf q}_0~\text{and}\\
-{\bf \dot q^*} &= {\bf f}({\bf q}^*,{\bf K}^*),~~{\bf q}^*(0) = {\bf q}_0.
-\end{split}
-\end{equation*}
-%
-Subtracting one from the other we have the following equation
-\begin{equation}
-{\bf \dot q}^\varepsilon - {\bf \dot q}^* = {\bf f} ({\bf q}^\varepsilon,{\bf K}^*) - {\bf f} ({\bf q}^*,{\bf K}^*) + \varepsilon {\bf \bar f} ({\bf q}^\varepsilon,{\bf K}-{\bf K}^*),
-\label{eq:temp1}
-\end{equation}
-where ${\bf \bar f} ({\bf q}^\varepsilon,{\bf K}-{\bf K}^*) = {\bf G}({\bf q}^{\varepsilon})({\bf K} - {\bf K}^*){\bf q}^\varepsilon.$ 
-%See Appendix~\ref{app:variational} for its derivation. 
-Dividing by $\varepsilon$ and denoting
-\begin{equation*}
-\boldsymbol{\eta} (t)\equiv \lim_{\varepsilon\to 0}\left(\frac{{\bf q}^{\varepsilon}(t)-{\bf q}^*(t)}{\varepsilon}\right),
-\end{equation*}
-it follows from the expression~\eqref{eq:temp1} that $\boldsymbol{\eta}(t)$ must satisfy the following initial value problem
-\begin{equation}
-\begin{split}
-\boldsymbol{\dot\eta} = \frac{\partial {\bf f}}{\partial{\bf q}}({\bf q}^*,{\bf K}^*)\boldsymbol{\eta} + {\bf \bar{f}}({\bf q}^*,{\bf K}-{\bf K}^*),~~\boldsymbol{\eta}(0)  = 0.
-\end{split}
-\label{eq:variational}
-\end{equation}
-%The detail derivation of the variational Equation~\eqref{eq:variational} is given in Appendix~\ref{app:variational}. 
-Equation~\eqref{eq:variational} is a linear non-homogeneous equation with ${\bf \bar{f}}({\bf q}^*,{\bf K}-{\bf K}^*)$ being the driving force.
-As a result, it has a continuous solution $\boldsymbol{\eta}(t)\in C({\cal I},\mathbb{R}^n)$, which is continuously dependent on ${\bf \bar{f}}({\bf q}^*,{\bf K}-{\bf K}^*).$
-
-By definition of Gateaux (directional) derivative we can derive the following expression
-\begin{multline*}
-dJ({\bf K}^*;{\bf K}-{\bf K}^*) =\lim_{\varepsilon\to 0}\frac{J[{\bf K}^*+\varepsilon({\bf K}-{\bf K}^*)] - J({\bf K}^*)}{\varepsilon}\\
-=\boldsymbol{\eta}^T(t)\frac{\partial\Phi}{\partial{\bf q}}[t_f,{\bf q}(t_f)] + \int_{0}^{t_f}\boldsymbol{\eta}^T(t)\frac{\partial\ell}{\partial{\bf q}} [t,{\bf q}(t)]\mathrm{dt}.
-\end{multline*}
-Hence, inequality~\eqref{eq:dJ} yields
-\begin{equation}
-\boldsymbol{\eta}^T(t)\frac{\partial\Phi}{\partial{\bf q}}[t_f,{\bf q}(t_f)] + \int_{0}^{t_f}\boldsymbol{\eta}^T(t) \frac{\partial\ell}{\partial{\bf q}} [t,{\bf q}(t)]\mathrm{dt} \geq 0.
-\label{eq:ineq1}
-\end{equation}  
-%
-Since $\boldsymbol{\eta}(t)$ of the variational equation~\eqref{eq:variational} is continuously dependent on ${\bf \bar f}({\bf q}^*,{\bf K}-{\bf K}^*)$, the map
-\begin{equation*}
-{\bf \bar f}({\bf q}^*,{\bf K}-{\bf K}^*) \longmapsto \boldsymbol{\eta}(t)
-\end{equation*}
-is continuous from ${\cal L}_1({\cal I},\mathbb{R}^n)$ to $C({\cal I},\mathbb{R}^n)$~\cite[p.~260]{Ahmed2006}. Hence, the map 
-\begin{equation*}
-\boldsymbol{\eta}(t) \longmapsto \boldsymbol{\eta}^T(t)\frac{\partial\Phi}{\partial{\bf q}}[t_f,{\bf q}(t_f)] + \int_{0}^{t_f}\boldsymbol{\eta}^T(t)\frac{\partial\ell}{\partial{\bf q}} [t,{\bf q}(t)]\mathrm{dt}
-\end{equation*}
-is a continuous linear functional on $C({\cal I},\mathbb{R}^n)$. Thus, the composition map 
-\begin{equation*}
-%\begin{split}
-{\bf \bar f}({\bf q}^*,{\bf K}-{\bf K}^*) \longmapsto \boldsymbol{\eta}^T(t)\frac{\partial\Phi}{\partial{\bf q}}[t_f,{\bf q}(t_f)] +\int_{0}^{t_f}\boldsymbol{\eta}^T(t) \frac{\partial\ell}{\partial{\bf q}} [t,{\bf q}(t)]\mathrm{dt}
-%\end{split}
-\end{equation*}
-is a continuous linear functional on ${\cal L}_1({\cal I},\mathbb{R}^n)$, where ${\bf f}({\bf q}^*,{\bf K}-{\bf K}^*)\in {\cal L}_1({\cal I},\mathbb{R}^n)$.
-Therefore, by the Riesz representation theorem or by the duality between ${\cal L}_1({\cal I},\mathbb{R}^n)$ and ${\cal L}_{\infty}({\cal I},\mathbb{R}^n)$, we may conclude that there exists an element $\boldsymbol{\psi}^*\in {\cal L}_{\infty}({\cal I},\mathbb{R}^n)$ such that
-\begin{multline}
-dJ({\bf K}^*;{\bf K}-{\bf K}^*) = \boldsymbol{\eta}^T(t) \frac{\partial\Phi}{\partial{\bf q}}[t_f,{\bf q}(t_f) +
-\int_{0}^{t_f}\boldsymbol{\eta}^T(t)\frac{\partial\ell}{\partial{\bf q}}(t,{\bf q}(t))\mathrm{dt}=\\
-\int_{0}^{t_f} \left(\boldsymbol{\psi}^*\right)^T{\bf \bar f}({\bf q}^*,{\bf K}-{\bf K}^*)\mathrm{dt}.
-\label{eq:temp2}
-\end{multline}
-It follows from inequality~\eqref{eq:ineq1} that 
-\begin{equation}
-\int_{0}^{t_f} \left(\boldsymbol{\psi}^*\right)^T{\bf \bar f}({\bf q}^*,{\bf K}-{\bf K}^*)\mathrm{dt} \geq 0,~~\forall~{\bf K}\in {\cal K}_{ad}.
-\label{eq:ineq2}
-\end{equation}
-Using the variational equation~\eqref{eq:variational}, it follows from the second identity of~\eqref{eq:temp2} that
-\begin{multline}
-\boldsymbol{\eta}^T(t)\frac{\partial\Phi}{\partial{\bf q}}[t_f,{\bf q}(t_f)] +\int_{0}^{t_f}\boldsymbol{\eta}^T(t) \frac{\partial\ell}{\partial{\bf q}} [t,{\bf q}(t)]\mathrm{dt}=\\
-\int_{0}^{t_f}\left\{\left(\boldsymbol{\psi}^*\right)^T\left[\boldsymbol{\dot\eta}-\frac{\partial{\bf f}}{\partial{\bf q}}({\bf q}^*,{\bf K}^*) \boldsymbol{\eta}(t)\right]\right\}\mathrm{dt}.
-\label{eq:temp3}
-\end{multline}
-Integrating by parts and since $\boldsymbol{\eta}(0) = 0$, 
-\begin{multline*}
-\int_{0}^{t_f}\left(\boldsymbol{\psi}^*\right)^T\left[\boldsymbol{\dot\eta}(t)-\frac{\partial{\bf f}}{\partial{\bf q}}({\bf q}^*,{\bf K}^*)\boldsymbol{\eta}(t)\right]\mathrm{dt}=\\
-\boldsymbol{\eta}^T(t_f)\boldsymbol{\psi}^*(t_f) + \int_{0}^{t_f}\boldsymbol{\eta}^T(t)\left(-\boldsymbol{\dot\psi}-\left\{\frac{\partial{\bf f}}{\partial{\bf q}}({\bf q}^*,{\bf K}^*)\right\}^T\boldsymbol{\psi}^*\right)\mathrm{dt}.
-\end{multline*}
-%
-Expression~\eqref{eq:temp3} can now be written as
-\begin{multline}
-\boldsymbol{\eta}^T(t)\frac{\partial\Phi}{\partial{\bf q}}[t_f,{\bf q}(t_f)] +\int_{0}^{t_f}\boldsymbol{\eta}^T(t) \frac{\partial\ell}{\partial{\bf q}} [t,{\bf q}(t)]\mathrm{dt}=\\
-\boldsymbol{\eta}^T(t_f)\boldsymbol{\psi}^*(t_f) + \int_{0}^{t_f}\boldsymbol{\eta}^T\left\{-\boldsymbol{\dot\psi}^*-\left[\frac{\partial{\bf f}}{\partial{\bf q}}({\bf q}^*,{\bf K}^*)\right]^T\boldsymbol{\psi}^*\right\}\mathrm{dt}
-\label{eq:costate1}
-\end{multline}
-It is clear from~\eqref{eq:costate1} that
-\begin{equation}
-\boldsymbol{\dot\psi}^* = -\left[\frac{\partial{\bf f}}{\partial{\bf q}}({\bf q}^*,{\bf K}^*)\right]^T\boldsymbol{\psi}^*-\frac{\partial\ell}{\partial{\bf q}}[t,{\bf q}^*(t)],~\text{with}~
-\boldsymbol{\psi}^*(t_f) = \frac{\partial\Phi}{\partial{\bf q}}[t_f,{\bf q}(t_f)].
-\label{eq:costate2}
-\end{equation}
-The costate dynamics~\eqref{eq:costate2} is linear along the optimal trajectories.
-Thus, the necessary conditions of optimality is given by the integral inequality~\eqref{eq:ineq2}, the costate dynamics~\eqref{eq:costate2}, and the state equation~\eqref{eq:systemFeedbackFull}.
-In other words, the choice of ${\bf K}\in{\cal K}_{ad}$ determines the optimality conditions~\eqref{eq:ineq2},~\eqref{eq:costate2}, and~\eqref{eq:systemFeedbackFull}.
-
-Consider the optimality condition~\eqref{eq:ineq2} and rewriting it as follows
-\begin{equation}
-\begin{split}
-\int_{0}^{t_f} \left(\boldsymbol{\psi}^*\right)^T{\bf f}({\bf q}^*,{\bf K})\mathrm{dt} \geq
-\int_{0}^{t_f} \left(\boldsymbol{\psi}^*\right)^T{\bf f}({\bf q}^*,{\bf K}^*)\mathrm{dt},~\forall~{\bf K}\in {\cal K}_{ad}.
-\end{split}
-\label{eq:ineq3}
-\end{equation}
-Using the integral inequality~\eqref{eq:ineq3}, it is easy to derive the point-wise inequality~\cite{Ahmed2006}
-\begin{equation}
-\begin{split}
-\left(\boldsymbol{\psi}^*\right)^T{\bf f}({\bf q}^*,{\bf K}) \geq
-\left(\boldsymbol{\psi}^*\right)^T{\bf f}({\bf q}^*,{\bf K}^*),~~\forall~{\bf K}\in {\cal K}_{ad}.
-\end{split}
-\label{eq:ineq4}
-\end{equation}
-Now adding the term $\ell[t,{\bf q}^*(t)]$ in both sides of~\eqref{eq:ineq4} yields
-%
-\begin{equation*}
-\begin{split}
-\left(\boldsymbol{\psi}^*\right)^T{\bf f}({\bf q}^*,{\bf K}) +\ell[t,{\bf q}^*(t)]\geq
-\left(\boldsymbol{\psi}^*\right)^T{\bf f}({\bf q}^*,{\bf K}^*) +\ell[t,{\bf q}^*(t)],
-\end{split}
-%\label{eq:ineq4}
-\end{equation*}
-which gives the Hamiltonian inequality
-\begin{equation*}
-{\cal H}[t,{\bf q}^*(t),\boldsymbol{\psi}^*(t),{\bf K}(t)] \geq{\cal H}[t,{\bf q}^*(t),\boldsymbol{\psi}^*(t),{\bf K}^*(t)].
-\end{equation*}
-This is the same as inequality~\eqref{eq:inequality-H} stated in the theorem. Differentiating ${\cal H}$ with respect to the costate variable $\boldsymbol{\psi}$, we get
-\begin{equation*}
-\frac{\partial{\cal H}}{\partial\boldsymbol{\psi}}[t,{\bf q}^*(t),\boldsymbol{\psi}^*(t),{\bf K}^*(t)] = {\bf f}[{\bf q}^*(t),{\bf K}^*(t)],
-\end{equation*}
-which leads to the state equation
-\begin{equation*}
-{\bf \dot q}^* = \frac{\partial{\cal H}}{\partial\boldsymbol{\psi}}^* [t,{\bf q}^*(t),\boldsymbol{\psi}^*(t),{\bf K}^*(t)],~~{\bf q}^*(0)={\bf q}_0,
-\end{equation*}
-as defined in~\eqref{eq:state}.
-
-Differentiating ${\cal H}$ with respect to the state variable ${\bf q}$ yields
-\begin{equation*}
-\frac{\partial{\cal H}}{\partial{\bf q}}[t,{\bf q}^*(t),\boldsymbol{\psi}^*(t),{\bf K}^*(t)] =\left[\frac{\partial{\bf f}}{\partial{\bf q}}({\bf q}^*,{\bf K}^*)\right]^T\boldsymbol{\psi}^*+\frac{\partial\ell}{\partial{\bf q}}[t,{\bf q}^*(t)] = -\boldsymbol{\dot\psi}^*.
-\end{equation*}
-Hence, the costate dynamics~\eqref{eq:costate2} can be expressed in terms of Hamiltonian as
-\begin{equation*}
-\begin{split}
-\boldsymbol{\dot\psi}^* = -\frac{\partial{\cal H}}{\partial{\bf q}}^* [t,{\bf q}^*(t),\boldsymbol{\psi}^*(t),{\bf K}^*(t)],~\text{and}~
-\boldsymbol{\psi}^*(t_f) = \frac{\partial\Phi}{\partial{\bf q}}[t_f,{\bf q}(t_f)],
-\end{split}
-\end{equation*}
-which is the condition~\eqref{eq:costate}. 
-\end{proof}
-%
-It is clear that Theorem~\ref{thm:necessary-conditions} provides the necessary conditions for the feedback law ${\bf K}(t)$ to be optimal.
-However, in order to solve for this optimal feedback operator, we express the gradient of the Hamiltonian defined in~\eqref{eq:hamiltonian} and set it to zero, \textit{i.e.,}
-%
-\begin{align}
-\mathcal{H}_{{\bf K}}\equiv\frac{\partial {\cal H}}{\partial {\bf K}} = {\bf G}^T[{\bf q}(t,{\bf K})]\bm{\psi}(t) {\bf q}^T(t,{\bf K})={\bf 0},
-\label{eq:gradient}
-\end{align}
-which characterizes the direction of convergence of the system's actual trajectory to the desired trajectory modeled by~\eqref{eq:actual-trajectory-full}.
-Note that the expression in~\eqref{eq:gradient} is dependent on the feedback operator  ${\bf K}$ through the solution of the state feedback model~\eqref{eq:systemFeedbackFull} for ${\bf q}(t,{\bf K}).$  Hence, the problem boils down to finding ${\bf K}(t),~t\in{\cal I},$ such that the system's actual trajectory from~\eqref{eq:actual-trajectory-full} and the costate trajectory from~\eqref{eq:costate} satisfy~\eqref{eq:gradient}.
-The optimal feedback operator  ${\bf K}^*$ can be determined by satisfying the Hamiltonian inequality~\eqref{eq:inequality-H}.
-In other words, the choice of ${\bf K}$ is to be adaptively tuned to minimize the vehicle's tracking error.
-
-\begin{corollary}[Adapting the control law ${\bf K}$~]
-\label{cor:convergence}
-Consider the system's feedback model~\eqref{eq:systemFeedbackFull} defined over the time horizon ${\cal I}.$ Adapting the operator ${\bf K}$ according to the following offline update rule 
-\begin{equation}
-{\bf K}^{new} = {\bf K}^{old} - \epsilon \mathcal{H}_{{\bf K}},
-\label{eq:update-rule}
-\end{equation}
-for small $\epsilon$ satisfies the Hamiltonian inequality~\eqref{eq:inequality-H} and, hence, guarantees the convergence of the system's trajectory to follow its reference trajectory. 
-\end{corollary}
-
-\begin{proof}
-Let 
-%
-\begin{equation}
-{\bf K}^* = {\bf K} - \epsilon {\cal H}_{{\bf K}} \thinspace ,
-\label{eq:proof-4}
-\end{equation}
-%
-for some ${\bf K} \in \mathbb{R}^{m\times n}.$  The corresponding Hamiltonian is 
-%
-\begin{equation*}
-{\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}^*) 
-={\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}-\epsilon {\cal H}_{{\bf K}}) \thinspace ,
-%\label{eq:proof-5}
-\end{equation*}
-%
-where ${\bf q}^*$ and $\bm{\psi}^*$ are the system's state and the costate variable corresponding to ${\bf K}^*.$ Taking the Taylor series expansion of the right hand side about ${\bf K}^*$, we get
-%
-\begin{equation*}
-  {\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}^*)  = {\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}) 
-  +\mathrm{Tr} \left[{\cal H}_{{\bf K}}^T{\bf (K^*-K)}\right]+{\cal O}(\varepsilon) \thinspace .
-\end{equation*}
-%
-Neglecting the higher order terms of the above expression yields
-%
-\begin{equation*}
-\begin{split}
-  {\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}^*) \equiv {\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}) 
-  -\epsilon \mathrm{Tr}\left[{\cal H}_{{\bf K}}^T {\cal H}_{{\bf K}}\right]
-   = {\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}) -\epsilon\|{\cal H}_{{\bf K}}\|^2
- < {\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}) 
-\end{split}
-%\label{eq:proof-6}
-\end{equation*}
-%
-since $\epsilon\|{\cal H}_{{\bf K}}\|^2 > 0$.
-Hence, update rule~\eqref{eq:proof-4} guarantees that the Hamiltonian ${\cal H}$ is monotonically decreasing, which proves that the adaptation law~\eqref{eq:update-rule} eventually leads to the optimal feedback control law ${\bf K}^*.$
-\end{proof}
-%
-%\begin{remark}
-%Theoretically, if ${\bf K}^*$ be any arbitrary feedback gain that satisfies the Hamiltonian inequality~\eqref{eq:inequality-H}
-%\begin{equation*}
-%{\cal H}(t,{\bf q}^*,\bm{\psi}^*,{\bf K}^*) \leq {\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}), ~\forall~{\bf K}\in {\cal K}_{ad}, 
-%\end{equation*}
-%then the update rule 
-%\begin{equation}
-%{\bf K}^{'}={\bf K}^*+\varepsilon ({\bf K}-{\bf K}^*),~\forall~{\bf K}\in {\cal K}_{ad}~\text{and}~\varepsilon\in[0,1]
-%\label{eq:update-rule-temp}
-%\end{equation}
-%yields the inequality~\eqref{eq:inequality-H}
-%\begin{equation}
-%{\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}^*) \leq {\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}^*+\varepsilon ({\bf K}-{\bf K}^*)).
-%\label{eq:proof-1}
-%\end{equation}
-%By taking the Taylor series expansion of the right hand side of~\eqref{eq:proof-1} about ${\bf K}^*$, we get
-%%
-%\begin{equation}
-%\begin{split}
-% {\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}^*) \leq {\cal H} (t,{\bf q}^*,\bm{\psi}^*,{\bf K}^*) + 
-%\varepsilon Tr\smclose{{\cal H}_{{\bf K}}^T({\bf K}-{\bf K}^*)}+{\cal O}(\varepsilon),
-%\end{split}
-%\label{eq:proof-2}
-%\end{equation}
-%where ${\cal O}(\varepsilon)$ is the higher order terms of the Taylor series. Neglecting the higher order terms of~\eqref{eq:proof-2}, we can write
-%\begin{equation}
-%\begin{split}
-%0\leq \varepsilon Tr\smclose{{\cal H}_{{\bf K}}^T({\bf K}-{\bf K}^*)} =\varepsilon Tr\smclose{({\bf K}-{\bf K}^*)^T {\cal H}_{{\bf K}}},
-%\smimplies Tr\smclose{({\bf K}^*)^T {\cal H}_{{\bf K}}} \leq Tr\smclose{{\bf K}^T {\cal H}_{{\bf K}}},
-%\end{split}
-%\label{eq:proof-3}
-%\end{equation} 
-%which shows that ${\bf K}^*$ in~\eqref{eq:update-rule-temp} is the optimal feedback gain.
-However, the problem of the update rule~\eqref{eq:update-rule-temp} is to find proper feedback gain ${\bf K}$ that satisfies the inequality~\eqref{eq:proof-3}.
-Hence, the update rule~\eqref{eq:update-rule} in Corollary~\ref{cor:convergence} is a perfect choice to find the optimal feedback gain ${\bf K}^*$.
-%\end{remark}
-%
-In the following, we numerically solve for the control law ${\bf K}$ such that~\eqref{eq:gradient} is satisfied, aggregating the components described earlier.
-
-\section{Numerical Computation Control Law}
-\label{sec:control-optimization}
-For the dynamic system~\eqref{eq:systemFeedbackFull} to solve the trajectory tracking problem, we illustrate the key steps to determine the proposed universal control law ${\bf K}$, aggregating the components described in the previous sections.
-
-Let ${\bf K}_i\equiv{\bf K}_i(t)$, $t\in {\cal I}$, be the gain at the $i$-th iteration of the optimization procedure.
-\vskip6pt
-\noindent
-{\bf Step 0 (initialization):} Subdivide the time interval ${\cal I}\equiv [0,t_f]$ into $N$ subintervals.
-Assume a piecewise-constant ${\bf K}_i(t)={\bf K}_i(t_k)$, $t\in[t_k,t_{k+1}]$, for $k=0,1,\ldots,N-1.$
-
-\noindent
-Find ${\bf K}^*$ by repeating {\bf Steps~1--5} until the stopping criterion in {\bf Step~5} is met.
-
-\noindent
-{\bf Step 1:} Integrate the system's feedback system~\eqref{eq:systemFeedbackFull} as in~\eqref{eq:actual-trajectory-full} with ${\bf K}\equiv{\bf K_i}(t)$, $t \in {\cal I}$.
-% and the initial vehicle's configuration ${\bf q}(0)$, and record the solution as trajectory ${\bf q_i}\equiv{\bf q_i}(t),~\text{for}~t \in I$.
-
-\noindent
-{\bf Step 2:} Solve costate equation~\eqref{eq:costate} backward for $\bm{\psi}_i$.
-
-\noindent
-{\bf Step 3:} Define the Hamiltonian ${\cal H}({\bf q}_i, \bm{\psi}_i,{\bf K}_i)$ as in~\eqref{eq:hamiltonian}.
-
-\noindent
-{\bf Step 4:} Compute the cost function $J({\bf K}_i)$ using~\eqref{eq:cost-fn}, the gradients of the Hamiltonian ${\cal H}_{{\bf K}}$ using~\eqref{eq:gradient}, and its corresponding intergrated norm
-\(
-\int_{0}^{t_f}\|{\cal H}_{{\bf K}}\|^2 \mathrm{dt}.
-\)
-
-\noindent
-{\bf Step 5:} If $J({\bf K}_i)\leq\delta_1$ or $\int_{0}^{t_f}\|{\cal H}_{{\bf K}}\|^2 \mathrm{dt} \leq \delta_2$, for pre-defined small positive tolerance constants $\delta_1$ and $\delta_2$, then ${\bf K_i}$ is regarded close enough to its optimal value, and so the algorithm is halted.\\
-Otherwise, use the following update rule to adjust the piecewise-constant feedback gain:
-%
-\begin{align*}
-{\bf K}_{i+1}(t_k) & = {\bf K}_i(t_k) - \epsilon \thinspace {\cal H}_{{\bf K}(t_k)} + \lambda \thinspace \Delta{\bf K}_i(t_k) 
-\\
-\Delta{\bf K}_i(t_k) & = {\bf K}_{i}(t_k) - {\bf K}_{i-1}(t_k)
-\end{align*}
-%
-for $k=0,1,\ldots,N-1,$ where $\epsilon$ and $\lambda$ are the step size and the momentum constant (for faster convergence), respectively.
-We now have the optimal feedback operator ${\bf K}\approx{\bf K}^*.$ The optimal control inputs can thus be computed using~\eqref{eq:controlLaw1} for the system to follow any desired trajectory defined by ${\bf q}^d(t),~t\in {\cal I}.$
-
-\section{Example}
-\label{sec:example}
-Consider vehicle with Ackermann steering whose kinematic model is given by %
-%
-\begin{align}
-\label{eq:modelVehicle}
-{\bf \dot q}(t) &= {\bf G}[{\bf q}(t)]{\bf u}(t),~~\mathrm{and}\\
-\label{eq:feedbackControlSimulation}
-{\bf u}(t) & = {\bf K}(t){\bf q}(t)
-\end{align}
-where the vehicle's control input vector ${\bf u}(t)\equiv [\nu_f(t)~\omega_f(t)]^T\in{\cal U}\subset\mathbb{R}^2$, with $\nu_f(t)$ and $\omega_f(t)$ being the front wheels' linear and steering velocities, respectively, ${\bf K} \in \mathbb{R}^{2\times 4}$ is the control law for the vehicle,  and
-\begin{equation*}
-{\bf G}[{\bf q}(t)]=
-\begin{bmatrix}
-\cos\phi(t)\cos\theta (t) &0\\
-\cos\phi(t)\sin\theta (t) & 0\\
-\frac{1}{l}\sin\phi(t) & 0\\
-0& 1
-\end{bmatrix}.
-\end{equation*}   
-%In addition, due to the vehicle's limit on its velocities, the inputs are constrained as
-%\begin{equation}
-%\smabs{\nu_f(t)}\leq \nu_f^{max}~~\text{and}~\smabs{\omega_f(t)}\leq \omega_f^{max},~t\in I,
-%\label{eq:constraint-u}
-%\end{equation}
-%where $\nu_f^{max}$ and $\omega_f^{max}$ is the maximum linear and steering velocities of the vehicle.
-In other words, ${\bf u}(t)$ must be chosen from a set of admissible controls, $\smset{U}_{ad}$,~\smie~${\bf u}(t)\in\smset{U}_{ad}\subset\Reals^m$ which are used to generate the set of state trajectories $\smset{Q}$.
-%
-%
-%shown in Fig.~\ref{fig:car-model}, where the front and rear axles lock the front and rear wheels, respectively. 
-%Hence, each axle collapse two wheels into a single wheel acting on its midpoint, which yields $(x_r,y_r)$ and $(x_f,y_f)$ to be the active points of the rear and front wheels, respectively. 
-%
-Model~\eqref{eq:modelVehicle} is similar to~\eqref{eq:systemModel} except that the drift is absent in a car-like vehicle.
-If ${\cal Q}$ denotes the set of state trajectories of the vehicle, its configuration at any time $t$ is represented by the vector ${\bf q}(t)=[x(t)~~y(t)~~\theta(t)~~\phi(t)]^T\in{\cal Q}\subset\mathbb{R}^4,$ where $(x(t),y(t))$ is the Cartesian position of the midpoint of the line of length $l$ connecting two axles dividing at their midpoints.% as shown in Fig.~\ref{fig:car-model}, %
-$\theta(t)\in(-\pi,\pi]$ is the orientation of the car body with respect to X-axis, and $\phi(t)\in(-\pi/2,\pi/2)$ is the steering angle of the front wheels with respect the car body.
-%\begin{figure}[htbp]
-%	\centering
-%	\includegraphics[scale = 0.75]{car-model}
-%	\caption{Kinematic model of a vehicle with Ackermann geometry.}
-%	\label{fig:car-model}
-%\end{figure} 
-%The vehicle is subject to the nonholonomic constraints given by
-%\begin{equation}
-%\begin{split}
-%&\dot x\sin(\theta+\phi) - \dot y\cos(\theta+\phi) -l\dot\theta\cos\phi = 0~\text{and}\\
-%&\dot x\sin\theta - \dot y\cos\theta = 0,\\
-%\end{split}
-%\label{eq:constraint-car}
-%\end{equation} 
-%which act on each wheel to prevent it from slipping laterally. The constraints~\eqref{eq:constraint-car} can be used to derive the vehicle's (front wheel driving) kinematic model
-
-Let us consider that the vehicle has to follow a feasible and smooth desired trajectory given in terms of Cartesian positions $(x^d(t), y^d(t))$, for $t\in {\cal I}\equiv [0~60]~\si{\second}$.
-$x^d(t) = 2\cos(2\pi t/60)~\text{and}~y^d(t) = 2\sin(2\pi t/60)$.
-The optimal universal control law ${\bf K}^*(t),~t\in[0,60]~\si{\second}$ for ~\eqref{eq:feedbackControlSimulation} is then computed as per {\bf Step 1} to {\bf Step~5} using the vehicle model~\eqref{eq:modelVehicle}.
-The vehicle could still perfectly track the circle from the initial state of $(1,0,0\si{\degree},45\si{\degree})$ as it is clear from Fig.~\ref{fig:circle-trajectory}.
-The state tracking errors are revealed in Fig.~\ref{fig:circle-error}, which are zero almost all the time after converging to the circle after time $t=\SI{20}{\second}.$ The vehicle has maintained the boundedness of its vehicle velocities and has stopped at the end of the trajectory, $(2,0)~\si{\meter}$, where velocity is zero as shown in Fig.~\ref{fig:circle-control-velocity} with the corresponding optimal universal feedback operator ${\bf K}^*(t)$ in Fig.~\ref{fig:circle-feedback-gain}.
-Due to the vehicle's speed limits each element of the control law ${\bf K}$ is bounded, as expected.
-\begin{figure}[htbp]%
-\centering
-\subfigure[][]{%
-    \label{fig:circle-trajectory}%
-    \includegraphics[width=0.48\textwidth,height=0.295\textheight]{circle/trajectory} }
- \subfigure[][]{%
-    \label{fig:circle-error}%
-    \includegraphics[width=0.48\textwidth,height=0.295\textheight]{circle/error} }
-\\
- \subfigure[][]{%
-    \label{fig:circle-control-velocity}%
-    \includegraphics[width=0.48\textwidth,height=0.295\textheight]{circle/control-velocity} }
-\subfigure[][]{
-  \label{fig:circle-feedback-gain}
-    \includegraphics[width=0.48\textwidth,height=0.295\textheight]{circle/feedback-gain}} 
-\caption[Performance of circle trajectory.]{Controller's performance in tracking circle trajectory
-   \subref{fig:circle-trajectory} trajectory,
-   \subref{fig:circle-error} state tracking error, and
-    \subref{fig:circle-control-velocity} velocity (control input), and
-    \subref{fig:circle-feedback-gain} optimal control law, ${\bf K}^*(t).$
-}%
-  \label{fig:circle}%
-\end{figure}
-
-Hence, the proposed control law ${\bf K}(t),$ is able to provide necessary control actions for the vehicle to track a pre-defined trajectory.
-It is important to articulate the fact that the proposed universal control law is able to solve trajectory tracking problem of any nonlinear systems of the form~\eqref{eq:systemModel}, but the model~\eqref{eq:modelVehicle} was chosen for the demonstration purpose only.
-
- %%%%%%%%%%%%%%%%%%%%
- \section{Summary and Conclusions}
- \label{sec:conclusion}
- We examined a novel universal control law for solving the trajectory tracking problem of a class of nonholonomic systems with drift.
-Both existence and necessary conditions of optimality for the control law are presented along with their proofs.
-Numerical results on computing control law and its application in a vehicle with Ackermann steering are presented.
-As can be seen, vehicle is able to track a predefined trajectory using the proposed control law.
-It can be shown that this control law is able to solve trajectory tracking problems of other nonholonomic systems, such as unicycle, differential drive mobile robots, and hopping robot in flight-phase.
-Computation of control law is offline, which is its only drawback and we are currently investing to determine online solution to the proposed universal control law.
-It is interesting to note that the system model is not required to be linearized to follow a certain reference trajectory in finite time.
-However, the proposed control law assumes that the system's state is completely observable, which may be a too restrictive and non realistic hypothesis to model a real-vehicle's control law.
-Designing partially-observed feedback optimal laws is another possible future research avenue of  this current work.
-Moreover, the practical realization of this proposed optimal feedback control law on a commercial vehicle is possible as the algorithm can be implemented on a microcontroller due to its computational efficiency.
-
-% \appendices
-% \section{Proof of the First Zonklar Equation}
-% Some text for the appendix.
-
-% use section* for acknowledgement
-%\section*{Acknowledgment}
-%
-%The authors would like to thank...
-
-\bibliographystyle{IEEEtran}        % Include this if you use bibtex
-
-\bibliography{bib/refsBooksTRTheses,bib/refsGenericControl,bib/refsSuruzWeb}
+\section{Slide 1: Outine}
+Hi every one my name is Amr Elhussein, mechanical enginering graduate student, i've been interested in working in robotics for four years now and i want to thank Dr.
+Miah to give me the chance to finally work in the field.
+In today's presentaion we will be talking about ROS, we will talk a litle bit about its origin, how was things done before ros, what ROS exactly is and some applications. 
+We will also walk through major concepts in ROS, how to install it and an overview on the future of ROS.
+\section{Slide 2: Historiccal Background}
+ROS started in 2007 as an outgrowth of Stanford AI robot (STAIR) and lately sponsored by willow grage a robotics incubator. 
+Ros is Currently extensively used in academia and industry. Currenlty ROS is supported by what is known as open source robotics foundation. 
+\section{Slide 3: Robot programming before ROS}
+Before ROS developing robots was very time consuming because there were no common platform for doing so. instead developers built every thing from scratch and implement algorithms on their own. 
+\section{Slide 4: ROS is } 
+A flexible framework for writing robot software. It is a collection of tools,
+libraries, and conventions that aim to simplify the task of creating complex
+and robust robot behavior across a wide variety of robotic platforms.
+\section{Slide 5: ROS Equation}
+To get more understanding of ROS, we can say that ROS is a combination of plumbing which are used to connect different parts of the robot, tools that are used in visualisation and other tasks one example of those tools is Gazebo which is a 3D visulisation tool used to simulate real world enviroments, Capabilities such as of the shelf algorithms that are ready to reuse and Ecosystem and community support which is an essential component of ROS.
+\section{Slide 6: Applications}
+As we mentioned earlier ROS is widely used in so many areas that includes : autonomus vehicles , warehouses and industrial applications.
+ROS also has been used to train robotics teams in First Robotics high school competion.
+\section{Slide 7: ROS Concepts, File System }
+When using ROS there are three levels of concepts one must deeply understand, the first level is the filesystem which consists of:
+\\Packages: the atomic unit of ROS which contains executable and supporting files that serve a specific purpose. 
+\\metapackages : which serves to represent a group pf related other packages.
 

### 2019-05-31 presentationNotes.tex
Add files via upload

@@
 %%%%%%%%%%%%%%%%%%%%%%
-\section{Slide 1: Outine}
+\section{Slide 2: Outine}
 Hi every one my name is Amr Elhussein, mechanical enginering graduate student, i've been interested in working in robotics for four years now and i want to thank Dr.
@@
 We will also walk through major concepts in ROS, how to install it and an overview on the future of ROS.
-\section{Slide 2: Historiccal Background}
+\section{Slide 3: Historiccal Background}
 ROS started in 2007 as an outgrowth of Stanford AI robot (STAIR) and lately sponsored by willow grage a robotics incubator. 
 Ros is Currently extensively used in academia and industry. Currenlty ROS is supported by what is known as open source robotics foundation. 
-\section{Slide 3: Robot programming before ROS}
+\section{Slide 4: Robot programming before ROS}
 Before ROS developing robots was very time consuming because there were no common platform for doing so. instead developers built every thing from scratch and implement algorithms on their own. 
-\section{Slide 4: ROS is } 
+\section{Slide 5: ROS is } 
 A flexible framework for writing robot software. It is a collection of tools,
@@
 and robust robot behavior across a wide variety of robotic platforms.
-\section{Slide 5: ROS Equation}
+\section{Slide 6: ROS Equation}
 To get more understanding of ROS, we can say that ROS is a combination of plumbing which are used to connect different parts of the robot, tools that are used in visualisation and other tasks one example of those tools is Gazebo which is a 3D visulisation tool used to simulate real world enviroments, Capabilities such as of the shelf algorithms that are ready to reuse and Ecosystem and community support which is an essential component of ROS.
-\section{Slide 6: Applications}
+\section{Slide 7: Applications}
 As we mentioned earlier ROS is widely used in so many areas that includes : autonomus vehicles , warehouses and industrial applications.
 ROS also has been used to train robotics teams in First Robotics high school competion.
-\section{Slide 7: ROS Concepts, File System }
-When using ROS there are three levels of concepts one must deeply understand, the first level is the filesystem which consists of:
+\section{Slide 8: ROS Concepts, File System }
+When using ROS there are three levels of concepts one must deeply understand, the first level is the filesystem which consists of
 \\Packages: the atomic unit of ROS which contains executable and supporting files that serve a specific purpose. 
 \\metapackages : which serves to represent a group pf related other packages.  
+\section{Slide 9: ROS Conceopts, Comutaion Graph}
+Computaion Graph is the peer to peer network processes that ROS perform on data.
+it contains \\nodes which are the codes files.
+and the master which is a node that ovesees the rest of the nodes and must be launched before other nodes.
+and those nodes exchange data either through messages and topics or through services.
+it also contains parameter server which allows data to be stored in a central location in addition to bags which is a format to store and playback data such as sensors data.
+\section{Slide 10 and 11, Master and nodes}
+this figures illustrates the relationship between the master and the other nodes and it shows that nodes don't exchange messages with the master. 
+\\next is an example for a camera application where you will be having three nodes on for the camera , one for processing the image and last one to display the image on your device. 
+\section{Slide 12: ROS Concepts, Community level}
+as we said the community level that support ROS contains an enclopydia , blogs , ROS answers and alot of other recources that help you to get things done. 
+\section{Slide 13 and 14: Installation }
+ROS is supported in debian based distributions such as ubuntu and its also supported in mac os but they say that its not stable. ROS is also supported in many robots. 
+\\there are two current supported distributions: kinetic kame and melodic morenia. 
+\\the installtion procedure is very simple and you can just follow the instruction on wiki.org which are basically configuring the repositories, setup sources list, set keys and install by sudo apt get install.
+\section{Slide 15: ROS Future}
+when the founders of ROS were asked about the future of ROS there answer was around three points.
+\\security: currently ROS 1 doesn't have any security which they want to inherit it in ROS2.
+\\critical mission and safety rather than R and D.
+\\increasing distributed processes.
+\section{ Slide 16: Thanks}
+ROS is a very complicated platform yet very useful , and you cannot fully understand it unless you get your hands dirty and do some actual work. I'll be pleased to answer any questions of yours.
 

### 2020-06-25 paperMIC2020/paperIEEE-MIC2020-V1.tex
Added paperMIC2020 folder

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{soul}
\usepackage{amssymb,amsmath,bm}
\usepackage{graphics,adjustbox}
\usepackage{tikz}
\usepackage{subfigure}
\usepackage{epstopdf}
\epstopdfsetup{suffix={}}
\usepackage{siunitx}
\sisetup{unitsep = \cdot}

\usepackage[figuresright]{rotating}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[english,algo2e,algoruled,vlined,linesnumbered]{algorithm2e}   % package for algorithm
\usepackage{enumerate}

\usepackage{easyReview}
\newtheorem{assumption}{Assumption}

\DeclareMathOperator*{\argmin}{arg min}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{A Novel Model-Free Learning Approach for Dynamic Target Tracking Problem and its Validation using Virtual Robot Experimentation Platform 
%  
% \thanks{This work was supported in part by the Bradley University’s Caterpillar fellowship grant.}
}

\author{%~
\IEEEauthorblockN{Amr Elhussein and Md Suruz Miah}
\IEEEauthorblockA{\textit{Electrical \& Computer Eng.} \\
\textit{Bradley University}, Peoria, Illinois, USA \\
smiah@bradley.edu  and aelhussein@mail.bradley.edu}
% \and
% \IEEEauthorblockN{Fazel Keshtkar}
% \IEEEauthorblockA{\textit{Div. of Computer Science, Math. and Science} \\
% \textit{St John's University}, Queens, NY, USA \\
% keshtkaf@stjohns.edu}
% \and
% \IEEEauthorblockN{Mohammed Abouheaf}
% \IEEEauthorblockA{\textit{School of EECS} \\
% \textit{Univ. of Ottawa}, Canada\\
% mabouhea@uottawa.ca}
%
}

\maketitle

\begin{abstract}
  %

\comment{This paper advances the previous work done by authors by validating a model-free actor-critic reinforcement learning approach to solve dynamic target tracking problem for a car-like mobile robot. The learning approach generates the linear velocity and steering angle of the robot and it does not require any prior knowledge of the dynamic model of the moving target. Policy iteration approach is employed through Bellman's principle of optimality to assess the cost of the control actions derived by the proposed learning method. The algorithm is tested by coducting a set of computer expeeriments for complex secnarios using virtual robot expirementation platform widely known as CoppeliaSim.        
}{Need to be rewritten}  
%
\end{abstract}

\begin{IEEEkeywords}
Leader-follower formation, mobile robots, reinforcement learning, policy iteration, trajectory tracking
\end{IEEEkeywords}

% \begin{nomenclature}
% \begin{deflist}[A]
% \defitem{ADP} \defterm{Approximate dynamic programming}
% \defitem{AL}\defterm{Approximate linearization}
% \defitem{RL}\defterm{Reinforcement learning}
% \end{deflist}
% \end{nomenclature}

\section{Introduction}
\label{sec:introduction}
\todo[inline]{Need to discuss in details the limitations of previous work, we can also add RL applications to robotics navigation}
Over the past years mobile robots has been used in several applications in commercial and military sectors such as surveillance, search and rescue missions,coverage optimization, cooperative localization and dynamic target tracking tasks. In all of these mentioned applications a fleet of robot i.e agents interact with each other to achieve a certain goal. Leader-Follower tracking problem has recieved an extensive amount of study and research in the world of cooperative control theory. In a typical leader follower formation a number of robots referred to as followers apply local control actions to follow leadr's robots in a specific predefined path such as \hl {cyclic, circular motion and time varying communication topologies.} \hl {limitations of other methods} many control methods were proposed however they have had the following limitations:
\\(1) rely on the mathemetical model such as...
\\(2) rely on the dynamic model even with following a computational intillegence approach such as ..
 \\The main contribution of this work is the development of a model-free learning approach to control the follower robot by which it overcome many of the limitations mentiond above as it does not rely on any prior information of the mathmetical model or the dynamic model. The steering angle and the linear speed of the follower robot are determined by collecting the position and orientation of both the leader and the follower. This set of information is gathered online over a finite period of time. The optimal control actions are then generated by utilizing Bellman's principal of optimality which acts as model free-reinfocment learning approach that allows the follower robot to follow the path of the leader while oviding collision by maintaining a safe distance. In this paper the proposed algorithm is further validated using a commercially available robot simulator, CoppeliaSim. This paper acts as first milestone in generalizing the algorithm to solve more sophisticated problem such as coverage and mapping. \hl{cite area coverage papers}
 \\The rest of the paper is orgnized as follows. Section II lays down the problem setting of the leader follower problem and mathemetical models of the robots and the state error. The model free actor-critic reinforcment learning and its key steps are described in section III.Section IV illustrates computer simulations for different secnarios that reflects the effectivness of the proposed method followed by conlusion and future work presented in section V.

\section{Dynamic target tracking and problem setting} 
\todo[inline]{Needs to re-written}
 \label{sec:problemSetup}

Suppose that a wheeled mobile robot (follower) with coordinate $(x,y)$ and orientation $\theta\in[-\pi,\pi)~\si{\radian}$ with respect to the global X-Y coordinate has a linear speed $\nu$ and steering angle $\gamma$ which are considered as the two control actions. Let the posistion and orientation (pose) of the target i.e leader be ${\bf q}_k\equiv[x_k,y_k,\theta_k]$. The robot and the target are deployed in a 2D configuration in which the Follower is to follow the target trajectory defined by  $(\mathbf{p}_k^{[\ell]})^T=[x_k^{[\ell]},y_k^{[\ell]}(t)]$ at time $t\ge 0$ with $t=k \, T_s,$ $k\in\mathbb{N}_0,$ and $T_s>0$ being the sampling time. Note that this trajectory is completley random. The target motion is modeled by the following discrete-time system:
 \begin{align}
   \label{eq:leaderDT}
   \mathbf{p}_{k+1}^{[\ell]} = \mathbf{p}_k^{[\ell]} + T_s \, \mathbf{u}_k^{[\ell]},
 \end{align}  
with $\mathbf{u}_k^{[\ell]}\in\mathbb{R}^2$ being the control inputs of the target movment. 
\\ The follower robot is to maintain a constant safe-distance $d>0$ from target. The dynamic car-like model of the follower robot is defined as follows:
  \begin{figure}
\todo[inline]{redraw figure and add coppelia sim figures}
   \centering
   \fcolorbox{gray!10}{gray!5}{
     \includegraphics[width=0.45\textwidth]{figs/ipe/LF-Setup}
`     }
   \caption{Mobile robot and its leader-follower problem setup.}
   \label{fig:leaderFollowerSetup}
 \end{figure}
 \begin{subequations}
   \begin{align}
     x_{k+1}& =x_{k}+T_s\nu_{k}\cos{(\theta_{k}+\gamma_{k})} + \zeta_1,\\  
     y_{k+1}& =y_{k}+T_s\nu_{k}\sin{(\theta_{k}+\gamma_{k})}+ \zeta_2,\\
     \theta_{k+1}&=\theta_{k}+T_s\nu_{k}\frac{\sin{(\gamma_{k})}}{l}+ \zeta_3,
   \end{align}
 \label{eq:robotModel1-DT}
 \end{subequations}
 \\
\hl{Note that the follower dynamic model obeys Ackermann steering principle where $\gamma_k\in(-\frac{\pi}{2},\frac{\pi}{2})$ is the front wheel steering angle with respect to the robot's orientation $\theta_k\in[-\pi,\pi),$ $\nu_k$ is the linear speed, $l$ is the distance between the drive wheels of the robot, and $\zeta_1,\zeta_2,\zeta_3\in\mathbb{R}$ are the model uncertainties.} 
\\
We then define the error vector as:
 \begin{multline}
     \label{eq:stateError}
   \mathbf{e}_k^T = [x_e,y_e,\theta_e]^T = \\
   \begin{bmatrix}
     x_k^{[\ell]} - x_k - d\cos\theta_k^{'},
     y_k^{[\ell]} - y_k - d\sin\theta_k^{'},
     \theta_k^{'} - \theta_k
   \end{bmatrix},
 \end{multline}

 where $\theta_k^{'} = \mathrm{atan2}\left(y_k^{[\ell]}-y_k, x_k^{[\ell]}-x_k\right).$  
\\
\hl{The control problem can then be formally stated as follows}: Find $\nu_k$ and $\gamma_k$ such that ${\bf e}_k\to {\bf 0}$ as  $k\to\infty$ subject to~\eqref{eq:leaderDT}~\text{and}~\eqref{eq:robotModel1-DT}.

%
%
%  In the next section, a conventional trajectory tracking method is investigated to solve the problem~\eqref{eq:problem}. This is followed by the proposed approximate dynamic programming technique which is illustrated in section~\ref{sec:solutionADP}.

\section{Proposed actor-critic RL Approach}
\todo[inline]{Needs to be rewritten}

 \label{sec:RLSolution}

 The solution of the leader-follower formation problem is realized using a reinforcement learning approach. It employs model-free strategies for solving a temporal difference equation developed herein. This solution is equivalent to solving the underlying Bellman optimality equation for  the dynamical error model~\eqref{eq:stateError}. The relative importance of the states in the error vector ${\bf e}_k$ and the control decisions (linear velocity and steering angle) of the follower-robot are evaluated using the  performance (cost) index: %
 \begin{align}
 \label{eq:costFunctional}
 J = \sum_{k=0}^\infty \frac{1}{2}\left[{\bf e}_k^T \, {\bf Q} \, {\bf e}_k + {\bf u}_k^T \, {\bf R} \, {\bf u_k}\right],
 \end{align}    
 where ${\bf Q}\in\mathbb{R}^{3\times 3}$ and ${\bf R}\in\mathbb{R}^{2\times 2}$ are symmetric positive definite weighting matrices. The objective of the optimization problem, following~\cite{Lewis2013-Reinforcement}, is to find an optimal sequence of control polices $\{\mathbf{u}^*_k\}_{k=0}^\infty$ that minimizes the cost index $J$ along the state-trajectories~\eqref{eq:leaderDT}~and~\eqref{eq:robotModel1-DT}. Motivated by the structure of the convex quadratic cost functional~\eqref{eq:costFunctional}, let the solution of the tracking control problem employ the value function $V({\bf e}_k,{\bf u}_k)$ defined by %
 %
 \begin{equation*}
 \label{eq:valueFunction}
 V({\bf e}_k,{\bf u}_k) = \sum_{\kappa=k}^\infty \frac{1}{2}\left({\bf e}_\kappa^T\, {\bf Q}\, {\bf e}_\kappa + {\bf u}_\kappa^T \, {\bf R}\, {\bf u_\kappa}\right).
 \end{equation*}
 %
 This structure yields a temporal difference form (i.e., Bellman equation) as follows
 \begin{equation*}
 \label{eq:tempraldiffeq}
 V({\bf e}_k,{\bf u}_k)= \frac{1}{2}\left[{\bf e}_k^T\, {\bf Q}\, {\bf e}_k + {\bf u}_k^T\, {\bf R}\, {\bf u_k}\right] +V({\bf e}_{k+1},{\bf u}_{k+1}).
 \end{equation*}
 %
 Applying Bellman's optimality principle yields the optimal control policies ${\bf u}_k^*,~k\ge 0,$ such that~\cite{Lewis2012} %
 %
 \begin{align*}
 {\bf u}^*_k = \argmin_{{\bf u}_k}\left[\frac{1}{2}\left[{\bf e}^T_k\,  {\bf Q}\, {\bf e}_k +{\bf u}^T_k\,  {\bf R} \,  {\bf u}_k\right]   +
 V({\bf e}_{k+1},{\bf u}_{k+1})\right].
 \label{eq:argMinControlAction}
 \end{align*}
 %
 Alternatively, this optimal  policy form is equivalent to ${\bf u}^*_k = \argmin_{{\bf u}_k}\left[
 V({\bf e}_{k},{\bf u}_{k})\right].$
 Therefore, the underlying Bellman optimality equation follows %
 %
 \begin{equation*}
 \label{eq:BellOpt}
 V^*({\bf e}_k,{\bf u}^*_k)= \frac{1}{2}\left[{\bf e}_k^T\, {\bf Q}\, {\bf e}_k + {\bf u}_k^{*T}\, {\bf R}\, {\bf u}^*_k\right] +V^*({\bf e}_{k+1},{\bf u}^*_{k+1}),
 \end{equation*}
 %
 where $V^*(\cdot,\cdot)$ is the optimal solution for Bellman optimality equation. This temporal difference equation is utilized by reinforcement learning process which solves the following temporal difference approximation form %
 %
 \begin{align}
 \hat{V}(\mathbf{z}_k) = \frac{1}{2}\mathbf{z}_k^T\, \bar{\mathbf{P}}\, \mathbf{z}_k + \hat{V}(\mathbf{z}_{k+1}),
 \label{eq:valueFunctionEstimated}
 \end{align}
 %
 where $\mathbf{z}_k = \left[\mathbf{e}_k ,\mathbf{u}_k\right]^T\in\mathbb{R}^5,$ $V\left(\mathbf{e}_k,\mathbf{u}_k\right) \approx \hat{V}(\mathbf{z}_k),$  and $\bar{\mathbf{P}}$ is a symmetric block-diagonal matrix formed using $(\mathbf{Q},\mathbf{R}),$~\textit{i.e.,~}$\bar{\mathbf{P}} = \mathrm{blockdiag}(\mathbf{Q},\mathbf{R}).$ %
 The approximation of the solving value function $\hat{V}(\mathbf{z}_k)$ employs a quadratic form so that $\hat{V}(\mathbf{z}_k)=\frac{1}{2}\mathbf{z}_k^T\, \mathbf{P}\, \mathbf{z}_k,$ where $\mathbf{P}\in\mathbb{R}^{5\times 5}$ is a positive definite matrix. Hence, the optimal control strategy $\mathbf{u}_k^*$ can be expressed as follows %
 %
 \begin{align}
 \label{eq:modelFreePolicy}    
 \mathbf{u}_k^* = \argmin_{\mathbf{u}_k}\left[\hat{V}(\mathbf{z}_k)\right] = -\,  \mathbf{P}_{uu}^{-1}\, \mathbf{P}_{ue}\, \mathbf{e}_k,
 \end{align}
 %
 where $\mathbf{P}_{uu}$ and $\mathbf{P}_{ue}$ are sub-blocks of symmetric matrix $\mathbf{P}.$ %   
 %

% A two-step solution mechanism that is based on policy iteration is employed to solve the temporal difference equation~\eqref{eq:valueFunctionEstimated} using the policy~\eqref{eq:modelFreePolicy}. First, the adaptive critics are used to approximate the solving value function $\hat V(\cdot)$ using a multi-layer critic neural network as shown in Fig.~\ref{fig:nnCritic}. %
 %
% \begin{figure}
%     \centering
%     \fcolorbox{blue}{gray!5}{
%         \begin{adjustbox}{max width = 0.45\textwidth}
%             \tikzset{%
%                 input neuron/.style={
%                     circle,
%                     fill=green!50,
%                     minimum size=0.7cm
%                 },
%                 neuron missing/.style={
%                     draw=none, 
%                     scale=1,
%                     fill=white,
%                     text height=0.01cm,
%                     execute at begin node=\color{black}$\vdots$
%                 },
%             }
%            
%%             \tikzset{%
%                 hidden neuron/.style={
%                     circle,
%                     fill=blue!50,
%                     minimum size=0.7cm
%                 },
%                 neuron missing/.style={
%                     draw=none, 
%                     scale=1,
%                     fill=white,
%                     text height=0.01cm,
%                     execute at begin node=\color{black}$\vdots$
%                 },
%
%             }
%            
%%             \tikzset{%
%                 output neuron/.style={
%                     circle,
%                     fill=red!50,
%                     minimum size=0.7cm
%                 },
%                 neuron missing/.style={
%                     draw=none, 
%                     scale=1,
%                     fill=white,
%                     text height=0.01cm,
%                     execute at begin node=\color{black}$\vdots$
%                 },
%             }
%            
%%             \begin{tikzpicture}[x=1.5cm, y=1.5cm]
%            
%%             \foreach \m/\l [count=\y] in {1,2,missing,3}
%             \node [input neuron/.try, neuron \m/.try] (input-\m) at (0,2.5-\y) {};
%            
%%             \foreach \m [count=\y] in {1,2,3,missing,4}
%             \node [hidden neuron/.try, neuron \m/.try ] (hidden-\m) at (2,2.5-\y*1.1) {};
%            
%%             \foreach \m [count=\y] in {1}
%             \node [output neuron/.try, neuron \m/.try] (output-\m) at (4,2.5-\y*2.8) {};
%            
%%             \foreach \l [count=\i] in {1,2,n+m}
%             \draw [<-] (input-\i) -- ++(-1,0)
%             node [above, midway] {$\mathbf{z}_{k,\l}$};
%            
%%             \foreach \l [count=\i] in {1,2,3,~\mbox{$\bar{n}$}}
%             \node [above] at (hidden-\i.north) {$\rho_{\l}$};
%            
%%             \foreach \l [count=\i] in {1}
%             \draw [->] (output-\i) -- ++(1,0)
%             node [above, midway] {$\hat{V}(\mathbf{z}_{k})$};
%             % node [above, midway] {$\hat{V}_\l$};
%            
%%             \foreach \i in {1,...,3}
%             \foreach \j in {1,...,4}
%             \draw [->] (input-\i) -- (hidden-\j);
%            
%%             \foreach \i in {1,...,4}
%             \foreach \j in {1}
%             \draw [->] (hidden-\i) -- (output-\j);
%            
%            
%            
%%             \foreach \l [count=\x from 0] in {Input, Hidden, Output}
%             \node [align=center, above] at (\x*2,1.9) {\l \\ layer};
%            
%%             \node [align=center, below] at (3,-2.5) {Weights \\ $\boldsymbol{\omega}$};
%             \draw[->,ultra thick](3,-2.5) -- (3,1.4);
%            
%%             \end{tikzpicture}
%         \end{adjustbox}      
%     }
%     \caption{Critic neural network structure for approximating value function.}
%     \label{fig:nnCritic}
%       \end{figure}
 %      
 Second, the policy evaluation step of this process updates the critic weights $\bm{\omega}$ in real-time without acquiring any formation about the dynamics of the leader or follower dynamical systems  (the calculation mechanism of the critic weighs $\boldsymbol{\omega}$ is explained later on). This is done to search for a strictly better policy. %
 %

% Note that, the policy iteration computational setup rearranges the temporal difference expression~\eqref{eq:valueFunctionEstimated} such that %
 %
 \begin{equation}
 \label{eq:const}
 \mathbf{z}_k^T\, \mathbf{P}\, \mathbf{z}_k - \mathbf{z}_{k+1}^T\, \mathbf{P}\, \mathbf{z}_{k+1} = \mathbf{z}_k^T\, \bar{\mathbf{P}}\, \mathbf{z}_k. 
 \end{equation}
 %
 This equation is utilized repeatedly in order to evaluate a certain policy during at least $\eta\ge \bar n, \bar n= (3+2)(3+2+1)/2$ evaluation steps (i.e., the lowest evaluation interval spans $k$ to $k+\bar n$ calculation samples) in order to update the critic weights vector  $\boldsymbol{\omega}=\mathrm{vec}(\mathbf{P}),$ which consists of connection weights between the neurons of the hidden layer and the output layer of the critic neural network shown in Fig.~\eqref{fig:nnCritic}. The operator $\mathrm{vec}(\mathbf{P})$ forms the columns of the $\mathbf{P}$ matrix into a column vector $\mathbf{\omega}$ of dimension $\bar{n}=15$ since the matrix $\mathbf{P}$ is a symmetric matrix. The left hand side of~\eqref{eq:const} is expressed using the following critic approximation form %
 %
 $$\hat{V}(\mathbf{z}_k)-\hat{V}(\mathbf{z}_{k+1})=\boldsymbol{\omega}^T\tilde{\bm{\rho}}(\mathbf{z}_{k,k+1}),$$
 %
 where $\tilde{\bm{\rho}}(\mathbf{z}_{k,k+1})=\bm{\rho}(\mathbf{z}_k)-\bm{\rho}(\mathbf{z}_{k+1}) \in \mathbb{R}^{15 \times 1}, \, \bm{\rho}(\mathbf{z}_k)=\left(\mathbf{z}^q_k\otimes\mathbf{z}^h_k\right)$ $(q=1,\dots, 5, \,\, h=q,\dots,5),$ and $\boldsymbol{\omega}^T = [0.5 \, P^{11},P^{12},P^{13},P^{14}, P^{15}, \, 0.5 \, P^{22}, P^{23},P^{24},P^{25},$ $\,0.5 \, P^{33}, P^{34},P^{35},\,0.5 \, P^{44},P^{45}, \,0.5 \, P^{55}]^T \in \mathbb{R}^{1\times 15}$ ($P^{ij}$ is the $ij^{th}$ entry of matrix $\mathbf{P}$). %
 %
 The critic weights $\boldsymbol{\omega}$ are updated using a gradient descent approach, where the tuning error $\varepsilon_k$ at each computational instance $k$ follows $\varepsilon_k =\boldsymbol{\omega}^T\tilde{\bm{\rho}}(\mathbf{z}_{k,k+1})-{v}_k,$ where $v_\kappa = \frac{1}{2}\mathbf{z}_{k}^T \, \bar{\mathbf{P}} \, \mathbf{z}_{k}$. As detailed earlier, it is required to perform at least $\eta \ge \bar n$ evaluation steps before updating the critic weights $\boldsymbol{\omega}$ (i.e., finding the new improved policy). Hence, it is required to minimize the sum of square errors such that %
 %
 \begin{multline*}
   \delta_c =\sum_{\kappa=0}^{\eta-1}\frac{1}{2}(\boldsymbol{\omega}^T\tilde{\bm{\rho}}(\mathbf{z}_{k+\kappa,k+\kappa+1})-{v}_{k+\kappa})^2 = \frac{1}{2}\| \mathbf{v} - \bm{\Lambda}\bm{\omega}\|^2\\
   =\frac{1}{2}\left(\mathbf{v} - \bm{\Lambda}\bm{\omega}\right)^T \left(\mathbf{v} - \bm{\Lambda}\bm{\omega}\right), 
 \end{multline*}
 where $\bm{\Lambda} = [{\bf o}_0,{\bf o}_1,\ldots,{\bf o}_{\eta-1}]^T \in \mathbb{R}^{\eta\times 15}$ with ${\bf o}_\kappa = \tilde{\bm{\rho}}^T({\bf z}_{k+\kappa, k+\kappa+1}) \in \mathbb{R}^{1\times 15}$ and ${\bf v} =[v_0,v_1,\ldots,v_{\eta-1}]^T \in \mathbb{R}^{\eta}$ with $v_\kappa = \frac{1}{2}\mathbf{z}_{k+\kappa}^T \, \bar{\mathbf{P}} \, \mathbf{z}_{k+\kappa}$ for $\kappa = 0,1,\ldots, \eta-1$. %
 Therefore, the update law of the critic weights using the gradient decent approach for at least $\bar n$ samples is given by %
 \begin{multline}
   \bm{\omega}^{[r+1]} = \bm{\omega}^{[r]} - \ell_c\frac{\partial\delta_c}{\partial \bm{\omega}} = \bm{\omega}^{[r]} - \ell_c\left(-\bm{\Lambda}^T\mathbf{v} + \bm{\Lambda}^T \bm{\Lambda}\bm{\omega}^{[r]}\right)\\ 
 =\bm{\omega}^{[r]} - \ell_c \bm{\Lambda}^T\left(\bm{\Lambda}\bm{\omega}^{[r]}-\mathbf{v}\right), 
 \label{eq:criticWeights}
 \end{multline}
 %
 where $0<\ell_c<1$ is a critic learning rate and $r$ is the  update index of the critic weights.

% The newly computed critic weights $\boldsymbol{\omega}$ are used to reconstruct the matrix ${\bf P}$ (i.e., updating the solving value function and hence calculating the associated policy) such that 
 %
 \begin{center}
 ${\bf P}=\begin{bmatrix} 
 2\,\omega^{1}    & \omega^{2}      & \omega^{3}       & \omega^{4}       & \omega^{5} \\ 
 \omega^{2}       &2\, \omega^{6}   & \omega^{7}       & \omega^{8}       & \omega^{9} \\
 \omega^{3}       & \omega^{7}      &2\, \omega^{10}   & \omega^{11}      & \omega^{12} \\
 \omega^{4}       & \omega^{8}      & \omega^{11}      & 2\,\omega^{13}   & \omega^{14} \\
 \omega^{5}       & \omega^{9}      & \omega^{12}      & \omega^{14}      & 2\,\omega^{15}   
 \end{bmatrix}\in \mathbb{R}^{5\times 5},$
 \end{center}
 %
 where $\omega^{i}$ is the $i^{th}$ entry of the weight vector $\bm{\omega}.$ The complete policy iteration solution process for the leader-follower problem is detailed out in Algorithm \ref{alg:ModelFreeTracking}. %
 %
 \begin{algorithm2e}
     \caption{\label{alg:ModelFreeTracking} Model-free reinforcement learning using the policy iteration solution.}
     \DontPrintSemicolon
     \KwIn{Sampling-time $T_s,$ $\mathbf{Q},~\text{and}~\mathbf{R}$ }
     \KwOut{Error trajectory $\mathbf{e}_k,$ for $k=0,1,\ldots$}
     % \KwData{Map representation using occupancy grid technique}
     % \KwResult{output******************************}
     \Begin{
         $k=0, r = 0$ \tcc*[h]{Discrete time and policy indices}\;
         $\eta = (n+m)(n+m+1)/2$\;
         Initialize $\mathbf{P}^{[0]}$ \tcc*[h]{Positive definite}\;
                 Set offset distance $d$\;
                 Given approximate initial poses of leader and follower, compute $\mathbf{e}_0$ using error model~\eqref{eq:stateError}\;
                 Compute follower's input $\mathbf{u}_0^{[0]}$ using policy~\eqref{eq:modelFreePolicy}\;
         \Repeat(\tcc*[h]{Main timing loop}){Tracking errors are zero}
         {
             Find $\mathbf{e}_{k+1}$ using~\eqref{eq:stateError}\;
             Compute policy $\mathbf{u}_{k+1}^{[r]}$ using~\eqref{eq:modelFreePolicy}\;
             %Evaluate and record Equation~\eqref{eq:modelFreeMatrixSolution}\;
             \If{[$(k+1)~\mathrm{modulo}~\eta]==0$ }
             {
                 $r\leftarrow r+1$\tcc*[h]{Evaluate policy}\;
                 Solve for the critic-weights $\bm{\omega}$ using~\eqref{eq:criticWeights}\;
                 Construct matrix $\mathbf{P}^{[r]}$ using vector $\bm{\omega}$\;
 %                \eIf{$\|\mathbf{P}^{[r]} - \mathbf{P}^{[r+1]}\|<\varepsilon$}{Set $\mathbf{u}_{k+1}^*\leftarrow\mathbf{u}_{k+1}^{[r]}$}{$k\leftarrow k+1$ }
             }
 %        {
 %                $k\leftarrow k+1$
 %            }
         $k\leftarrow k+1$
         }
     }
 \end{algorithm2e}

 \section{Computer Experiments and Results}
 \label{sec:resultsExperiments}
 In the sequel, computer experiments  are conducted to validate the performance of the proposed model-free adaptive learning algorithm in real-time. The results of computer experiments highlight the dynamics of the tracking errors and the convergence characteristics of the proposed algorithm (i.e., updating the critic weights). This will judge the ability of the follower robot to track independent motion trajectory of the leader robot under two different independent leader-motion trajectories. The computer experiments are realized using MATLAB simulation environment. The weighting matrices are set to $\mathbf{Q} = \mathrm{diag}[0.01,0.01,0.005]$ and $\mathbf{R} = \mathrm{diag}[10^{-6}, 10^{-6}].$ % 
  \[Q=0.001 
  \begin{bmatrix}
  10       & 0   & 0\\
  0       & 10   & 0\\
  0       & 0   &5 \\
  \end{bmatrix},
  R=0.000001
  \begin{bmatrix}
  1       & 0 \\
  0       & 1 
  \end{bmatrix}.\]
 The learning rate $\ell_c$ is set to  $0.0001$. The sampling time $T_s$ is set to $0.08 \sec.$ The desired distance offset between the leader and the follower is set to $ d = 0.5$ [m] for all scenarios.

% In the first scenario, the leader trajectory motion is described by a unicycle model so that %

%\begin{align*}
% $\dot x^{[\ell]}(t) = \nu^{[\ell]}(t)\cos\theta^{[\ell]}(t),$ %
% $\dot y^{[\ell]}(t) = \nu^{[\ell]}(t)\sin\theta^{[\ell]}(t).$
% \dot\theta^\ell(t) &= \omega(t),
%\end{align*}

 Initially, the leader's position is set to be the same for a short period of time with $\nu^{\ell} = 0 , \gamma^{\ell} = 0$. Then it starts to move on a horizontal line with $\nu^{\ell} = 0.1 $ [m/s], eventually the leader starts to move on an inclined path with $\nu^{\ell} = 0.2$ [m/s], $\gamma^{\ell} = 45\degree$. The leader is initially placed at $(x,y) = (5, 2)~\si{[\meter]}$ with an orientation of $\theta = 0 \degree $, while the follower  is initially placed at $(x,y) = (0, 0)~\si{[\meter]}$ with an orientation of $\theta = 0\degree$. Note that during this scenario, the critic weights converge rapidly and the tracking errors decay till the follower tracks the leader. The trajectory phase plan plot, tracking error states, control signals, and tuning of critic weights are shown in Fig.~\ref{fig:performanceRectilinearTrajectory}. %

% \begin{figure*}[htbp]%
%     \centering
%     \parbox[c]{0.48\textwidth}{\centering Parallel parking}
%     \parbox[c]{0.48\textwidth}{\centering Trajectory tracking}
%     \\
%     \subfigure[][]{%
%         \label{fig:trajectoryRectilinearDistance}%
%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/rectilinear/trajectoryRectlinearDistance} }
%     \subfigure[][]{%
%         \label{fig:stateErrorRectilinearDistance}%
%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/rectilinear/stateErrorRectlinearDistance} }
%     \\
%     \subfigure[][]{%
%         \label{fig:controlInputsRectilinearDistance}%
%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/rectilinear/controlInputRectlinearDistance} }
%     \subfigure[][]{%
%         \label{fig:weightRectilinearDistance}%
%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/rectilinear/weightRectilinearDistance} }
%     \caption[Leader-follower performance for rectilinear trajectory.]{First scenario (rectilinear trajectory): 
%         \subref{fig:trajectoryRectilinearDistance} leader-follower trajectories,~\subref{fig:stateErrorRectilinearDistance} state tracking errors,~\subref{fig:controlInputsRectilinearDistance} linear speed and steering angle of the follower, and    \subref{fig:weightRectilinearDistance} critic weights.}%
%     \label{fig:performanceRectilinearTrajectory}%
% \end{figure*}

 A relatively unplanned complex trajectory-tracking scenario is considered. The leader moves according to a sinusoidal trajectory so that %

%  \begin{align*}
% $x^{[\ell]}(t) = \alpha (t) \in [0,10\pi],$ %
% $y^{[\ell]}(t) = 5 \,\sin(\alpha t),$ and %
% $\theta^{[\ell]}(t) = cos(\alpha t).$  %
%        \end{align*}
% 
 The leader robot  was initially placed at $(x,y) = (0, 0)~\si{[\meter]}$ with an orientation of $\theta = 0 \degree$ while the follower robot was initially placed at a random position around $(x,y) = (0, 0)~\si{[\meter]}$ with a random orientation. The simulation results are summarized in Figure~\ref{fig:performanceSinewaveTrajectory}. It is observed that the critic weights take more time to converge compared to the earlier scenario,  which is reluctant to the complexity of the independent trajectory of the leader. This result emphasizes the adaptability of the proposed adaptive learning mechanism to different scenarios. Further, the follower starts to move away from the leader at the beginning of the simulation before it finally converges to the leader where the tracking errors are bounded by a safe distance $d.$ %

% \begin{figure*}[htbp]%
%     \centering
%     \parbox[c]{0.48\textwidth}{\centering Parallel parking}
%     \parbox[c]{0.48\textwidth}{\centering Trajectory tracking}
%     \\
%     \subfigure[][]{%
%         \label{fig:trajectorySinewave}%
%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/sinewave/trajectorySinewaveDistance} }
%     \subfigure[][]{%
%         \label{fig:stateErrorSinewave}%
%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/sinewave/stateErrorSinewaveDistance} }
%     \\
%     \subfigure[][]{%
%         \label{fig:controlInputSinewave}%
%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/sinewave/controlInputSinewaveDistance} }
%     \subfigure[][]{%
%         \label{fig:weightSinewaveDistance}%
%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/sinewave/weightSinewaveDistance} }
%     \caption[Leader-follower performance for nonlinear trajectory.]{Second scenario (sinusoidal trajectory): 
%         \subref{fig:trajectorySinewave} leader-follower trajectories,~\subref{fig:stateErrorSinewave} state tracking errors,~\subref{fig:controlInputSinewave} linear speed and steering angle of the follower, and    \subref{fig:weightSinewaveDistance} critic weights.}%
%     \label{fig:performanceSinewaveTrajectory}%
% \end{figure*}

In the third case study we rely on completley random path for the leader robot to evaluate the effectivenss of the proposed algorithm as a solution for the leader follower tracking problem. The leader is to follow a random path defined by the model described in (2), with $\gamma$ being a random value, The follwer is to maitain an offset distance of $d = 0.5 $ [m]. Note that the path of the leader is not pre defined and the algorithm being completlety model free. The results are summerized in Fig. \ref{fig:peformanceRandomTrajectory}. %

%The results are summarized in Fig.~\ref{fig:peformanceRandomTrajectory}. %
%
%\begin{figure*}[htbp]%
%\centering
%\parbox[c]{0.48\textwidth}{\centering Parallel parking}
%\parbox[c]{0.48\textwidth}{\centering Trajectory tracking}
%\\
%\subfigure[][]{%
%    \label{fig:trajectoryRandom}%
%    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/randomPath/trajectorySinewave} }
%\subfigure[][]{%
%    \label{fig:stateErrorRandom}%
%    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/randomPath/stateErrorSinewave} }
%\\
% \subfigure[][]{%
%    \label{fig:controlInputsRandom}%
%    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/randomPath/controlInputSinewave} }
% \subfigure[][]{%
%    \label{fig:weightRandomDistance}%
%    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/randomPath/weightRectilinearDistance} }
%\caption[Leader-follower performance for random trajectory.]{Performance in tracking random trajectory: 
%  \subref{fig:trajectoryRandom} leader-follower trajectories,~\subref{fig:stateErrorRandom} state error,~\subref{fig:controlInputsRandom} linear speed and steering angle of the follower; and    \subref{fig:weightRandomDistance} learning weights.}%
%  \label{fig:peformanceRandomTrajectory}%
%\end{figure*}

 \section{Conclusion} \label{sec:conclusion}

% A novel policy iteration mechanism based on a model-free reinforcement learning approach is presented for solving a conventional leader-follower formation problem using car-like mobile robots. The proposed approach does not rely on model parameters inherent in the mobile robots employed in this work. The follower robot is able to follow the leader robot that navigates along unplanned trajectories of various complexities while maintaining a nonzero safe distance between them. To the best of authors' knowledge, this is the first milestone of its kind where a model-free policy iteration based reinforcement learning approach is employed in a multi-robot formation control problem. The future work is going  to extend the learning algorithm for solving a time-varying formation control problem using networked robots.

% \section*{Acknowledgment}

% The preferred spelling of the word ``acknowledgment'' in America is without 
 an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
 G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
 acknowledgments in the unnumbered footnote on the first page.

\bibliographystyle{IEEEtran}
\bibliography{bib/refsSuruzWeb,bib/refsMultiAgent,bib/refsRoboticsJournals,bib/refsRoboticsConferences,bib/refsGenericControl,bib/refsBooksTRTheses,bib/refsReinforcementLearningADP,bib/refsRL-Keshtkar}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2020-06-25 paperMIC2020/paperIEEE-MIC2020-V1.tex
Updated introduction section with some hints

@@
 \label{sec:introduction}
-\todo[inline]{Need to discuss in details the limitations of previous work, we can also add RL applications to robotics navigation}
+\todo[inline]{Need to discuss in details the limitations of previous work, we
+  can also add RL applications to robotics navigation}
+
+Tracking a random moving target using a mobile robot, for instance, is a challenging task.
+This is mainly due to their inherent complex nonlinear dynamics dynamics.
+Most of the target tracking algorithms proposed in the literature either rely on A) complex mathematical models, B) simplified mathematical models, and C) nonlinear control techniques or driven by large amount of mostly offline data that leads to an overwhelming degree of computational complexity.
+
 Over the past years mobile robots has been used in several applications in commercial and military sectors such as surveillance, search and rescue missions,coverage optimization, cooperative localization and dynamic target tracking tasks.
@@
 The model free actor-critic reinforcment learning and its key steps are described in section III.Section IV illustrates computer simulations for different secnarios that reflects the effectivness of the proposed method followed by conlusion and future work presented in section V.
+
+\todo[inline]{Take some references from the following paragraphs}
+The task of localization and mapping in the context of leader-follower problems is very challenging.
+Such a task is becoming a ubiquitous  facet of modern life due to its promising application in addressing not only the leader-follower problem but also applicable in industry industry with heavy equipment trucks, in agriculture with autonomous crop maintenance, in home life with the autonomous vacuuming robot, along with research and design as seen in~\cite{Roberts2007,Durmus2015,Elara2014,HevrdejsKnoll2017-Indoor}.
+In most leader-follower problem addressed in the literature to date, it is assumed that leader/target's position/state is known \textit{a priori}, which may not be the case in many applications such as tracking a mobile point source~\cite{Xu2013}.
+Furthermore, the localization and mapping task is of a paramount importance in addressing the problem of mobile target tracking, which has a number of promising applications, such as robotic navigation, search and rescue mission, wildlife monitoring, autonomous surveillance, to name a few.
+A large body of research has been conducted in the literature to address the localization and mapping problem.
+Relatively few papers have addressed the localization and mapping problem in the context of leader-follower tasks, where either (i) a static leader/target is used~\cite{Fernando2015}, (ii) the leader/target's location is predetermined, or (iii) expensive hardware platforms are used to implement the mobile target tracking strategy (see the work presented in~\cite{Yang2014}, for example).
+
+The work done in this paper addresses some of the aforementioned issues by carrying out a cost-effective and easy-to-implement localization and mapping algorithm in the context of a leader--follower problem, a wheeled mobile robot is employed as a follower and a target moving on a two-dimensional (2D) plane is used as a leader.
+We emphasize that the position of the  leader is unknown to the follower robot \emph{a priori.} Therefore, the position and orientation of the follower robot and the position of the leader are to be simultaneously estimated while building the map of the environment of the robot using a set of networked wireless radio sensors placed on the ground.
+It is assumed that a radio sensor is mounted on the leader.
+The follower robot receives range measurements [herein the received signal strength indicator (RSSI) from radio sensors] from all radio sensors in its operating range.
+These measurements are then used to estimate the position and orientation of the follower robot, the 2D position of the leader, and the 2D positions of radio sensors placed in the robot's environment.
+Once the follower robot estimates its states (position and orientation) and the position of the leader, it moves towards the leader using the motion controller running onboard the follower robot.
+The design and implementation of the current work are based on the preliminary work of the robot navigation and mapping strategy conducted by the authors in~\cite{HevrdejsKnoll2017-Indoor,KnHeMi2017-c1,HeKnMi2017-c1}.
+Therefore, the main objective is to advance the work in~\cite{HevrdejsKnoll2017-Indoor,KnHeMi2017-c1,HeKnMi2017-c1} for a more general case, where a mobile robot is to follow a leader  whose position is unknown \emph{a priori.}
+n
 

### 2020-06-28 paperMIC2020/paperIEEE-MIC2020-V1.tex
update

--- 2020-06-25 paperMIC2020/paperIEEE-MIC2020-V1.tex
@@
 \label{sec:introduction}
-\todo[inline]{Need to discuss in details the limitations of previous work, we can also add RL applications to robotics navigation}
+\todo[inline]{Need to discuss in details the limitations of previous work, we
+  can also add RL applications to robotics navigation}
+
+Tracking a random moving target using a mobile robot, for instance, is a challenging task.
+This is mainly due to their inherent complex nonlinear dynamics dynamics.
+Most of the target tracking algorithms proposed in the literature either rely on A) complex mathematical models, B) simplified mathematical models, and C) nonlinear control techniques or driven by large amount of mostly offline data that leads to an overwhelming degree of computational complexity.
+
 Over the past years mobile robots has been used in several applications in commercial and military sectors such as surveillance, search and rescue missions,coverage optimization, cooperative localization and dynamic target tracking tasks.
 In all of these mentioned applications a fleet of robot i.e agents interact with each other to achieve a certain goal.
-Leader-Follower tracking problem has recieved an extensive amount of study and research in the world of cooperative control theory.
-In a typical leader follower formation a number of robots referred to as followers apply local control actions to follow leadr's robots in a specific predefined path such as \hl {cyclic, circular motion and time varying communication topologies.} \hl {limitations of other methods} many control methods were proposed however they have had the following limitations:
-\\(1) rely on the mathemetical model such as...
-\\(2) rely on the dynamic model even with following a computational intillegence approach such as ..
+Leader-Follower or dynamic target tracking problem has recieved an extensive amount of study and research in the world of cooperative control theory due to it's wide promising applications such as search and rescure missions, wildlife monitoring and survillance to name a few .
+In a typical leader follower formation a number of robots referred to as followers apply local control actions to follow leader's robots in a specific predefined path such as \hl {cyclic, circular motion and time varying communication topologies.} \hl {limitations of other methods} many control methods were proposed however they have had the following limitations:
+\\(1) a static leader/target is used.
+\\(2) the leade/target's location or dynamic model is predetermined.  
+\\(3) expensive hardware platforms are used to achieve the mobile target tracking. 
  \\The main contribution of this work is the development of a model-free learning approach to control the follower robot by which it overcome many of the limitations mentiond above as it does not rely on any prior information of the mathmetical model or the dynamic model.
@@
 
+%\textit{\todo[inline]{Take some references from the following paragraphs}
+%The task of localization and mapping in the context of leader-follower problems is very challenging.
+Such a task is becoming a ubiquitous  facet of modern life due to its promising application in addressing not only the leader-follower problem but also applicable in industry industry with heavy equipment trucks, in agriculture with autonomous crop maintenance, in home life with the autonomous vacuuming robot, along with research and design as seen in~\cite{Roberts2007,Durmus2015,Elara2014,HevrdejsKnoll2017-Indoor}.
+In most leader-follower problem addressed in the literature to date, it is assumed that leader/target's position/state is known \textit{a priori}, which may not be the case in many applications such as tracking a mobile point source~\cite{Xu2013}.
+Furthermore, the localization and mapping task is of a paramount importance in addressing the problem of mobile target tracking, which has a number of promising applications, such as robotic navigation, search and rescue mission, wildlife monitoring, autonomous surveillance, to name a few.
+A large body of research has been conducted in the literature to address the localization and mapping problem.
+Relatively few papers have addressed the localization and mapping problem in the context of leader-follower tasks, where either (i) a static leader/target is used~\cite{Fernando2015}, (ii) the leader/target's location is predetermined, or (iii) expensive hardware platforms are used to implement the mobile target tracking strategy (see the work presented in~\cite{Yang2014}, for example).
+%
+%The work done in this paper addresses some of the aforementioned issues by carrying out a cost-effective and easy-to-implement localization and mapping algorithm in the context of a leader--follower problem, a wheeled mobile robot is employed as a follower and a target moving on a two-dimensional (2D) plane is used as a leader.
+We emphasize that the position of the  leader is unknown to the follower robot \emph{a priori.} Therefore, the position and orientation of the follower robot and the position of the leader are to be simultaneously estimated while building the map of the environment of the robot using a set of networked wireless radio sensors placed on the ground.
+It is assumed that a radio sensor is mounted on the leader.
+The follower robot receives range measurements [herein the received signal strength indicator (RSSI) from radio sensors] from all radio sensors in its operating range.
+These measurements are then used to estimate the position and orientation of the follower robot, the 2D position of the leader, and the 2D positions of radio sensors placed in the robot's environment.
+Once the follower robot estimates its states (position and orientation) and the position of the leader, it moves towards the leader using the motion controller running onboard the follower robot.
+The design and implementation of the current work are based on the preliminary work of the robot navigation and mapping strategy conducted by the authors in~\cite{HevrdejsKnoll2017-Indoor,KnHeMi2017-c1,HeKnMi2017-c1}.
+Therefore, the main objective is to advance the work in~\cite{HevrdejsKnoll2017-Indoor,KnHeMi2017-c1,HeKnMi2017-c1} for a more general case, where a mobile robot is to follow a leader  whose position is unknown \emph{a priori.}
+%n}
+
 \section{Dynamic target tracking and problem setting} 
-\todo[inline]{Needs to re-written}
+\todo[inline]{Needs to reviewed}
  \label{sec:problemSetup}
@@
      \label{eq:stateError}
-   \mathbf{e}_k^T = [x_e,y_e,\theta_e]^T = \\
+   \mathbf{e}_k^T = [\sqrt{x_e^2-y_e^2},\theta_e]^T = \\
    \begin{bmatrix}
-     x_k^{[\ell]} - x_k - d\cos\theta_k^{'},
-     y_k^{[\ell]} - y_k - d\sin\theta_k^{'},
+     \sqrt{(x_k^{[\ell]} - x_k - d\cos\theta_k^{'})^2-
+     (y_k^{[\ell]} - y_k - d\sin\theta_k^{'})^2},
      \theta_k^{'} - \theta_k

### 2020-06-28 paperMIC2020/matlamSim/dynamicTargetTrackingV2.m

@@ -1,0 +1,519 @@
+% Odometric localization or dead reckoning%   Script for simulating mobile robot.
+%Edited by AMR Elhussein on May, 29,2020.
+%gradient descent Appraoch, three cases comined fixed point, horzintal and inclined line, 
+%converged Example
+function mainLF_OdometricLocalizationV7
+
+% Created by S. Miah on Nov. 03, 2015.
+%edited by AMR Elhussein on Aug, 30,2019.
+close all
+clear all
+clc
+
+disp('Please wait while the simulation runs ...');
+
+% ---------------------
+% SIMULATION PARAMETERS
+% ---------------------
+
+% Simulation time
+t0 = 0; tf = 10; % initial and final simulation time [s]
+T = 0.001;  % Sampling time [s]
+tsteps = ceil((tf-t0)/T); % number of time steps
+dt = T*(0:tsteps)'; % Discrete time vector (include time t0 to plot initial state too)
+
+d = 0.2; %[m] safe distance
+%ROBOT PARAMETERS
+%==========================================================================
+l = 0.381; % [m]
+rad = 0.0925; % [m] radius
+%==========================================================================
+
+%==========================================================================
+% ROS SETUP
+%==========================================================================
+%target position publishers
+[vpub_4,msg_4] = rospublisher('/cent1_pose','geometry_msgs/Vector3'); %Publishes on topic 
+%robot position publisher 
+posesub_1 = rossubscriber('/pioneerPose_1'); %Subscribes to topic '/pioneerPose_1'
+[vpub_1,msg_1] = rospublisher('/desiredVel_1','geometry_msgs/Vector3'); %Publishes on topic '/desiredVel_1'
+
+
+% dimension of system;
+N = 2;  % state vector dimension
+M = 2;  % input vector dimension
+
+
+% Leader's initial position
+pLeaderInit = [1;1]+rand(2,1); %[m]
[…]

### 2020-06-28 paperMIC2020/paperIEEE-MIC2020-V1.tex

@@
  \label{sec:resultsExperiments}
- In the sequel, computer experiments  are conducted to validate the performance of the proposed model-free adaptive learning algorithm in real-time.
+ This section adopts the theoritical results discussed in the previous section by simulating the Algorithm using the Pioneer 3-DX in CoppeliaSim.
+The results obtained by the authors in \hl{cite flairs paper here} are validated using the commercial robot simulator, CoppeliaSim as a prelminary step to implement the Algorithm experimantally in real world.
+we present the dynamics of the tracking error and the convergence characterisitcs of the actor and critic weights.
+The weighting matrices are set to $\mathbf{Q} = \mathrm{diag}[0.001,0.001]$ and $\mathbf{R} = \mathrm{diag}[10^{-5}, 10^{-5}].$ %
+  \[Q=0.001 
+  \begin{bmatrix}
+  1       & 0   \\
+  0       & 1   \\
+  \end{bmatrix},
+  R=0.00001
+  \begin{bmatrix}
+  1       & 0 \\
+  0       & 1 
+  \end{bmatrix}.\]
+ The actor and critic learning rates $\ell_c$ are set to  $0.01$ and $0.0001$.
+The sampling time $T_s$ is set to $0.001 \sec.$ The desired distance offset between the leader and the follower is set to $ d = 0.5$ [m] for all scenarios.
+ The CoppeliaSim simulator accuratly mimic what would happen in a realworld scenario following idustry standatrds and guidlines.
+The Pioneer robot model and the  was initally placed at position (-1,-2.5) m.The Target modeled as a cylinder was initially positioned on a random position around the origin (0,0).
+The simulation was run for
+\begin{figure}
+   \centering
+   \fcolorbox{gray!10}{gray!5}{
+     \includegraphics[width=0.45\textwidth]{figs/coppeliasim.png}
+`     }
+   \caption{CoppeliaSim Scene.}
+   \label{fig:CoppeliaSim Scene}
+ \end{figure}
+
+ \begin{figure*}[htbp]%
+ \subfigure[][]{%
+    \label{fig:trajectoryRandom}%
+    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/trajectoryRandomPathDistance.eps} }
+\subfigure[][]{%
+    \label{fig:stateErrorRandom}%
+    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/stateErrorRandomPathDistance.eps} }
+\\
+ \subfigure[][]{%
+    \label{fig:controlInputsRandom}%
+    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/controlInputRandomPathDistance.eps} }
+ \subfigure[][]{%
+    \label{fig:weightRandomDistance}%
+    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/weightRandomPathDistance.eps} }
+\caption[Leader-follower performance for random trajectory.]{Performance in tracking random trajectory: 
+  \subref{fig:trajectoryRandom} leader-follower trajectories,~\subref{fig:stateErrorRandom} state error,~\subref{fig:controlInputsRandom} linear speed and steering angle of the follower; and    \subref{fig:weightRandomDistance} learning weights.}%
+  \label{fig:peformanceRandomTrajectory}%
+\end{figure*}
+
+% \textit{In the sequel, computer experiments  are conducted to validate the performance of the proposed model-free adaptive learning algorithm in real-time.
 The results of computer experiments highlight the dynamics of the tracking errors and the convergence characteristics of the proposed algorithm (i.e., updating the critic weights).
@@
 The weighting matrices are set to $\mathbf{Q} = \mathrm{diag}[0.01,0.01,0.005]$ and $\mathbf{R} = \mathrm{diag}[10^{-6}, 10^{-6}].$ %
-  \[Q=0.001 
-  \begin{bmatrix}
-  10       & 0   & 0\\
-  0       & 10   & 0\\
-  0       & 0   &5 \\
-  \end{bmatrix},
-  R=0.000001
-  \begin{bmatrix}
-  1       & 0 \\
-  0       & 1 
-  \end{bmatrix}.\]
- The learning rate $\ell_c$ is set to  $0.0001$.
+%  \[Q=0.001 
+%  \begin{bmatrix}
+%  10       & 0   & 0\\
+%  0       & 10   & 0\\
+%  0       & 0   &5 \\
+%  \end{bmatrix},
+%  R=0.000001
+%  \begin{bmatrix}
+%  1       & 0 \\
+%  0       & 1 
+%  \end{bmatrix}.\]
+% The learning rate $\ell_c$ is set to  $0.0001$.
 The sampling time $T_s$ is set to $0.08 \sec.$ The desired distance offset between the leader and the follower is set to $ d = 0.5$ [m] for all scenarios.
+%
+%% In the first s\begin{figure*}[htbp]%
+%\centering
+%\parbox[c]{0.48\textwidth}{\centering Parallel parking}
+%\parbox[c]{0.48\textwidth}{\centering Trajectory tracking}
+%\\
 
-% In the first scenario, the leader trajectory motion is described by a unicycle model so that %
-
-%\begin{align*}
-% $\dot x^{[\ell]}(t) = \nu^{[\ell]}(t)\cos\theta^{[\ell]}(t),$ %
-% $\dot y^{[\ell]}(t) = \nu^{[\ell]}(t)\sin\theta^{[\ell]}(t).$
-% \dot\theta^\ell(t) &= \omega(t),
-%\end{align*}
-
- Initially, the leader's position is set to be the same for a short period of time with $\nu^{\ell} = 0 , \gamma^{\ell} = 0$.
+% 
+%%\begin{align*}
+%% $\dot x^{[\ell]}(t) = \nu^{[\ell]}(t)\cos\theta^{[\ell]}(t),$ %
+%% $\dot y^{[\ell]}(t) = \nu^{[\ell]}(t)\sin\theta^{[\ell]}(t).$
+%% \dot\theta^\ell(t) &= \omega(t),
+%%\end{align*}
+% 
+% Initially, the leader's position is set to be the same for a short period of time with $\nu^{\ell} = 0 , \gamma^{\ell} = 0$.
 Then it starts to move on a horizontal line with $\nu^{\ell} = 0.1 $ [m/s], eventually the leader starts to move on an inclined path with $\nu^{\ell} = 0.2$ [m/s], $\gamma^{\ell} = 45\degree$.
@@
 %
-
-% \begin{figure*}[htbp]%
-%     \centering
-%     \parbox[c]{0.48\textwidth}{\centering Parallel parking}
-%     \parbox[c]{0.48\textwidth}{\centering Trajectory tracking}
-%     \\
-%     \subfigure[][]{%
-%         \label{fig:trajectoryRectilinearDistance}%
-%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/rectilinear/trajectoryRectlinearDistance} }
-%     \subfigure[][]{%
-%         \label{fig:stateErrorRectilinearDistance}%
-%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/rectilinear/stateErrorRectlinearDistance} }
-%     \\
-%     \subfigure[][]{%
-%         \label{fig:controlInputsRectilinearDistance}%
-%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/rectilinear/controlInputRectlinearDistance} }
-%     \subfigure[][]{%
-%         \label{fig:weightRectilinearDistance}%
-%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/rectilinear/weightRectilinearDistance} }
-%     \caption[Leader-follower performance for rectilinear trajectory.]{First scenario (rectilinear trajectory): 
-%         \subref{fig:trajectoryRectilinearDistance} leader-follower trajectories,~\subref{fig:stateErrorRectilinearDistance} state tracking errors,~\subref{fig:controlInputsRectilinearDistance} linear speed and steering angle of the follower, and    \subref{fig:weightRectilinearDistance} critic weights.}%
-%     \label{fig:performanceRectilinearTrajectory}%
-% \end{figure*}
-
- A relatively unplanned complex trajectory-tracking scenario is considered. The leader moves according to a sinusoidal trajectory so that %
-
-%  \begin{align*}
-% $x^{[\ell]}(t) = \alpha (t) \in [0,10\pi],$ %
-% $y^{[\ell]}(t) = 5 \,\sin(\alpha t),$ and %
-% $\theta^{[\ell]}(t) = cos(\alpha t).$  %
-%        \end{align*}
 % 
- The leader robot  was initially placed at $(x,y) = (0, 0)~\si{[\meter]}$ with an orientation of $\theta = 0 \degree$ while the follower robot was initially placed at a random position around $(x,y) = (0, 0)~\si{[\meter]}$ with a random orientation.
+%% \begin{figure*}[htbp]%
+%%     \centering
+%%     \parbox[c]{0.48\textwidth}{\centering Parallel parking}
+%%     \parbox[c]{0.48\textwidth}{\centering Trajectory tracking}
+%%     \\
+%%     \subfigure[][]{%
+%%         \label{fig:trajectoryRectilinearDistance}%
+%%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/rectilinear/trajectoryRectlinearDistance} }
+%%     \subfigure[][]{%
+%%         \label{fig:stateErrorRectilinearDistance}%
+%%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/rectilinear/stateErrorRectlinearDistance} }
+%%     \\
+%%     \subfigure[][]{%
+%%         \label{fig:controlInputsRectilinearDistance}%
+%%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/rectilinear/controlInputRectlinearDistance} }
+%%     \subfigure[][]{%
+%%         \label{fig:weightRectilinearDistance}%
+%%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/rectilinear/weightRectilinearDistance} }
+%%     \caption[Leader-follower performance for rectilinear trajectory.]{First scenario (rectilinear trajectory): 
+%%         \subref{fig:trajectoryRectilinearDistance} leader-follower trajectories,~\subref{fig:stateErrorRectilinearDistance} state tracking errors,~\subref{fig:controlInputsRectilinearDistance} linear speed and steering angle of the follower, and    \subref{fig:weightRectilinearDistance} critic weights.}%
+%%     \label{fig:performanceRectilinearTrajectory}%
+%% \end{figure*}
+% 
+%
+%
+% A relatively unplanned complex trajectory-tracking scenario is considered. The leader moves according to a sinusoidal trajectory so that %
+% 
+%%  \begin{align*}
+%% $x^{[\ell]}(t) = \alpha (t) \in [0,10\pi],$ %
+%% $y^{[\ell]}(t) = 5 \,\sin(\alpha t),$ and %
+%% $\theta^{[\ell]}(t) = cos(\alpha t).$  %
+%%        \end{align*}
+%% 
+% The leader robot  was initially placed at $(x,y) = (0, 0)~\si{[\meter]}$ with an orientation of $\theta = 0 \degree$ while the follower robot was initially placed at a random position around $(x,y) = (0, 0)~\si{[\meter]}$ with a random orientation.
 The simulation results are summarized in Figure~\ref{fig:performanceSinewaveTrajectory}.
@@
 Further, the follower starts to move away from the leader at the beginning of the simulation before it finally converges to the leader where the tracking errors are bounded by a safe distance $d.$ %
-
-% \begin{figure*}[htbp]%
-%     \centering
-%     \parbox[c]{0.48\textwidth}{\centering Parallel parking}
-%     \parbox[c]{0.48\textwidth}{\centering Trajectory tracking}
-%     \\
-%     \subfigure[][]{%
-%         \label{fig:trajectorySinewave}%
-%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/sinewave/trajectorySinewaveDistance} }
-%     \subfigure[][]{%
-%         \label{fig:stateErrorSinewave}%
-%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/sinewave/stateErrorSinewaveDistance} }
-%     \\
-%     \subfigure[][]{%
-%         \label{fig:controlInputSinewave}%
-%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/sinewave/controlInputSinewaveDistance} }
-%     \subfigure[][]{%
-%         \label{fig:weightSinewaveDistance}%
-%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/sinewave/weightSinewaveDistance} }
-%     \caption[Leader-follower performance for nonlinear trajectory.]{Second scenario (sinusoidal trajectory): 
-%         \subref{fig:trajectorySinewave} leader-follower trajectories,~\subref{fig:stateErrorSinewave} state tracking errors,~\subref{fig:controlInputSinewave} linear speed and steering angle of the follower, and    \subref{fig:weightSinewaveDistance} critic weights.}%
-%     \label{fig:performanceSinewaveTrajectory}%
-% \end{figure*}
-
-In the third case study we rely on completley random path for the leader robot to evaluate the effectivenss of the proposed algorithm as a solution for the leader follower tracking problem.
+% 
+%% \begin{figure*}[htbp]%
+%%     \centering
+%%     \parbox[c]{0.48\textwidth}{\centering Parallel parking}
+%%     \parbox[c]{0.48\textwidth}{\centering Trajectory tracking}
+%%     \\
+%%     \subfigure[][]{%
+%%         \label{fig:trajectorySinewave}%
+%%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/sinewave/trajectorySinewaveDistance} }
+%%     \subfigure[][]{%
+%%         \label{fig:stateErrorSinewave}%
+%%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/sinewave/stateErrorSinewaveDistance} }
+%%     \\
+%%     \subfigure[][]{%
+%%         \label{fig:controlInputSinewave}%
+%%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/sinewave/controlInputSinewaveDistance} }
+%%     \subfigure[][]{%
+%%         \label{fig:weightSinewaveDistance}%
+%%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/sinewave/weightSinewaveDistance} }
+%%     \caption[Leader-follower performance for nonlinear trajectory.]{Second scenario (sinusoidal trajectory): 
+%%         \subref{fig:trajectorySinewave} leader-follower trajectories,~\subref{fig:stateErrorSinewave} state tracking errors,~\subref{fig:controlInputSinewave} linear speed and steering angle of the follower, and    \subref{fig:weightSinewaveDistance} critic weights.}%
+%%     \label{fig:performanceSinewaveTrajectory}%
+%% \end{figure*}
+% 
+%
+%
+%\textit{In the third case study we rely on completley random path for the leader robot to evaluate the effectivenss of the proposed algorithm as a solution for the leader follower tracking problem.
 The leader is to follow a random path defined by the model described in (2), with $\gamma$ being a random value, The follwer is to maitain an offset distance of $d = 0.5 $ [m].
@@
 \ref{fig:peformanceRandomTrajectory}.
-%
+}
 

### 2020-06-29 paperMIC2020/paperIEEE-MIC2020-V1.tex
added the figure

@@
 \textit{Bradley University}, Peoria, Illinois, USA \\
-smiah@bradley.edu  and aelhussein@mail.bradley.edu}
+ aelhussein@mail.bradley.edu and smiah@bradley.edu}
 % \and
@@
 
-\comment{This paper advances the previous work done by authors by validating a model-free actor-critic reinforcement learning approach to solve dynamic target tracking problem for a car-like mobile robot.
+This paper advances the previous work done by authors by validating a model-free actor-critic reinforcement learning approach to solve dynamic target tracking problem for a car-like mobile robot.
 The learning approach generates the linear velocity and steering angle of the robot and it does not require any prior knowledge of the dynamic model of the moving target.
 Policy iteration approach is employed through Bellman's principle of optimality to assess the cost of the control actions derived by the proposed learning method.
-The algorithm is tested by coducting a set of computer expeeriments for complex secnarios using virtual robot expirementation platform widely known as CoppeliaSim.
-}{Need to be rewritten}  
+The algorithm is tested by coducting a set of computer experiments for complex secnarios using virtual robot expirementation platform widely known as CoppeliaSim.
+
+\todo[inline]{Review and expand}  
 %
@@
 Let the posistion and orientation (pose) of the target i.e leader be ${\bf q}_k\equiv[x_k,y_k,\theta_k]$.
-The robot and the target are deployed in a 2D configuration in which the Follower is to follow the target trajectory defined by  $(\mathbf{p}_k^{[\ell]})^T=[x_k^{[\ell]},y_k^{[\ell]}(t)]$ at time $t\ge 0$ with $t=k \, T_s,$ $k\in\mathbb{N}_0,$ and $T_s>0$ being the sampling time.
+The robot and the target are deployed in a 2D configuration in which the Follower is to follow the target trajectory defined by  $(\mathbf{p}_k^{[d]})^T=[x_k^{[d]},y_k^{[d]}(t)]$ at time $t\ge 0$ with $t=k \, T_s,$ $k\in\mathbb{N}_0,$ and $T_s>0$ being the sampling time.
 Note that this trajectory is completley random.
@@
    \label{eq:leaderDT}
-   \mathbf{p}_{k+1}^{[\ell]} = \mathbf{p}_k^{[\ell]} + T_s \, \mathbf{u}_k^{[\ell]},
+   \mathbf{p}_{k+1}^{[d]} = \mathbf{p}_k^{[d]} + T_s \, \mathbf{u}_k^{[d]},
  \end{align}  
@@
   \begin{figure}
-\todo[inline]{redraw figure and add coppelia sim figures}
    \centering
    \fcolorbox{gray!10}{gray!5}{
-     \includegraphics[width=0.45\textwidth]{figs/ipe/LF-Setup}
-`     }
-   \caption{Mobile robot and its leader-follower problem setup.}
+     \includegraphics[width=0.45\textwidth]{figs/ipe/LFMICSetup.eps}
+    }
+   \caption{Mobile robot and its dynamic target tracking problem setup.}
    \label{fig:leaderFollowerSetup}
@@
      \label{eq:stateError}
-   \mathbf{e}_k^T = [\sqrt{x_e^2-y_e^2},\theta_e]^T = \\
+   \mathbf {e}_k^T = [\rho_e,\theta_e]^T =
+   [\sqrt{x_e^2+y_e^2},\theta_e]^T = \\
    \begin{bmatrix}
-     \sqrt{(x_k^{[\ell]} - x_k - d\cos\theta_k^{'})^2-
-     (y_k^{[\ell]} - y_k - d\sin\theta_k^{'})^2},
+     \sqrt{(x_k^{[d]} - x_k - d\cos\theta_k^{'})^2+
+     (y_k^{[d]} - y_k - d\sin\theta_k^{'})^2},
      \theta_k^{'} - \theta_k
@@
 
- where $\theta_k^{'} = \mathrm{atan2}\left(y_k^{[\ell]}-y_k, x_k^{[\ell]}-x_k\right).$  
+ where $\theta_k^{'} = \mathrm{atan2}\left(y_k^{[d]}-y_k, x_k^{[d]}-x_k\right).$ and ${\rho_e}$ being the euclidean distance. 
 \\

### 2020-06-29 paperMIC2020/paperIEEE-MIC2020-V1.tex
updated section III equations

@@
  \end{align}    
- where ${\bf Q}\in\mathbb{R}^{3\times 3}$ and ${\bf R}\in\mathbb{R}^{2\times 2}$ are symmetric positive definite weighting matrices.
+ where ${\bf Q}\in\mathbb{R}^{2\times 2}$ and ${\bf R}\in\mathbb{R}^{2\times 2}$ are symmetric positive definite weighting matrices.
 The objective of the optimization problem, following~\cite{Lewis2013-Reinforcement}, is to find an optimal sequence of control polices $\{\mathbf{u}^*_k\}_{k=0}^\infty$ that minimizes the cost index $J$ along the state-trajectories~\eqref{eq:leaderDT}~and~\eqref{eq:robotModel1-DT}.
@@
  %
- where $\mathbf{z}_k = \left[\mathbf{e}_k ,\mathbf{u}_k\right]^T\in\mathbb{R}^5,$ $V\left(\mathbf{e}_k,\mathbf{u}_k\right) \approx \hat{V}(\mathbf{z}_k),$  and $\bar{\mathbf{P}}$ is a symmetric block-diagonal matrix formed using $(\mathbf{Q},\mathbf{R}),$~\textit{i.e.,~}$\bar{\mathbf{P}} = \mathrm{blockdiag}(\mathbf{Q},\mathbf{R}).$ %
- The approximation of the solving value function $\hat{V}(\mathbf{z}_k)$ employs a quadratic form so that $\hat{V}(\mathbf{z}_k)=\frac{1}{2}\mathbf{z}_k^T\, \mathbf{P}\, \mathbf{z}_k,$ where $\mathbf{P}\in\mathbb{R}^{5\times 5}$ is a positive definite matrix.
+ where $\mathbf{z}_k = \left[\mathbf{e}_k ,\mathbf{u}_k\right]^T\in\mathbb{R}^4,$ $V\left(\mathbf{e}_k,\mathbf{u}_k\right) \approx \hat{V}(\mathbf{z}_k),$  and $\bar{\mathbf{P}}$ is a symmetric block-diagonal matrix formed using $(\mathbf{Q},\mathbf{R}),$~\textit{i.e.,~}$\bar{\mathbf{P}} = \mathrm{blockdiag}(\mathbf{Q},\mathbf{R}).$ %
+ The approximation of the solving value function $\hat{V}(\mathbf{z}_k)$ employs a quadratic form so that $\hat{V}(\mathbf{z}_k)=\frac{1}{2}\mathbf{z}_k^T\, \mathbf{P}\, \mathbf{z}_k,$ where $\mathbf{P}\in\mathbb{R}^{4\times 4}$ is a positive definite matrix.
 Hence, the optimal control strategy $\mathbf{u}_k^*$ can be expressed as follows %
@@
  %
- This equation is utilized repeatedly in order to evaluate a certain policy during at least $\eta\ge \bar n, \bar n= (3+2)(3+2+1)/2$ evaluation steps (i.e., the lowest evaluation interval spans $k$ to $k+\bar n$ calculation samples) in order to update the critic weights vector  $\boldsymbol{\omega}=\mathrm{vec}(\mathbf{P}),$ which consists of connection weights between the neurons of the hidden layer and the output layer of the critic neural network shown in Fig.~\eqref{fig:nnCritic}.
+ This equation is utilized repeatedly in order to evaluate a certain policy during at least $\eta\ge \bar n, \bar n= (2+2)(2+2+1)/2$ evaluation steps (i.e., the lowest evaluation interval spans $k$ to $k+\bar n$ calculation samples) in order to update the critic weights vector  $\boldsymbol{\omega}=\mathrm{vec}(\mathbf{P}),$ which consists of connection weights between the neurons of the hidden layer and the output layer of the critic neural network shown in Fig.~\eqref{fig:nnCritic}.
 The operator $\mathrm{vec}(\mathbf{P})$ forms the columns of the $\mathbf{P}$ matrix into a column vector $\mathbf{\omega}$ of dimension $\bar{n}=15$ since the matrix $\mathbf{P}$ is a symmetric matrix.
@@
  %
- where $\tilde{\bm{\rho}}(\mathbf{z}_{k,k+1})=\bm{\rho}(\mathbf{z}_k)-\bm{\rho}(\mathbf{z}_{k+1}) \in \mathbb{R}^{15 \times 1}, \, \bm{\rho}(\mathbf{z}_k)=\left(\mathbf{z}^q_k\otimes\mathbf{z}^h_k\right)$ $(q=1,\dots, 5, \,\, h=q,\dots,5),$ and $\boldsymbol{\omega}^T = [0.5 \, P^{11},P^{12},P^{13},P^{14}, P^{15}, \, 0.5 \, P^{22}, P^{23},P^{24},P^{25},$ $\,0.5 \, P^{33}, P^{34},P^{35},\,0.5 \, P^{44},P^{45}, \,0.5 \, P^{55}]^T \in \mathbb{R}^{1\times 15}$ ($P^{ij}$ is the $ij^{th}$ entry of matrix $\mathbf{P}$).
+ where $\tilde{\bm{\rho}}(\mathbf{z}_{k,k+1})=\bm{\rho}(\mathbf{z}_k)-\bm{\rho}(\mathbf{z}_{k+1}) \in \mathbb{R}^{10 \times 1}, \, \bm{\rho}(\mathbf{z}_k)=\left(\mathbf{z}^q_k\otimes\mathbf{z}^h_k\right)$ $(q=1,\dots, 5, \,\, h=q,\dots,5),$ and $\boldsymbol{\omega}^T = [0.5 \, P^{11},P^{12},P^{13},P^{14},  \, 0.5 \, P^{22}, P^{23},P^{24},$ $\,0.5 \, P^{33}, P^{34},\,0.5 \ P^{44}, ]^T \in \mathbb{R}^{1\times 15}$ ($P^{ij}$ is the $ij^{th}$ entry of matrix $\mathbf{P}$).
 %
@@
  ${\bf P}=\begin{bmatrix} 
- 2\,\omega^{1}    & \omega^{2}      & \omega^{3}       & \omega^{4}       & \omega^{5} \\ 
- \omega^{2}       &2\, \omega^{6}   & \omega^{7}       & \omega^{8}       & \omega^{9} \\
- \omega^{3}       & \omega^{7}      &2\, \omega^{10}   & \omega^{11}      & \omega^{12} \\
- \omega^{4}       & \omega^{8}      & \omega^{11}      & 2\,\omega^{13}   & \omega^{14} \\
- \omega^{5}       & \omega^{9}      & \omega^{12}      & \omega^{14}      & 2\,\omega^{15}   
- \end{bmatrix}\in \mathbb{R}^{5\times 5},$
+ 2\,\omega^{1}    & \omega^{2}      & \omega^{3}       & \omega^{4}        \\ 
+ \omega^{2}       &2\, \omega^{5}   & \omega^{6}       & \omega^{7}        \\
+ \omega^{3}       & \omega^{6}      &2\, \omega^{8}   & \omega^{9}   \\   
+ \omega^{4}       & \omega^{7}      & \omega^{9}      & 2\,\omega^{10}      
+ \end{bmatrix}\in \mathbb{R}^{4\times 4},$
  \end{center}
  %
- where $\omega^{i}$ is the $i^{th}$ entry of the weight vector $\bm{\omega}.$ The complete policy iteration solution process for the leader-follower problem is detailed out in Algorithm \ref{alg:ModelFreeTracking}.
-%
+ where $\omega^{i}$ is the $i^{th}$ entry of the weight vector $\bm{\omega}.$ 
+ \todo[inline]{merge the actor weights discussion with the rest}
+ The critic wegihts are then used to update the actor weights which maps the state error to the desired ploicy (control actions) at every time step $t$ with the following equation:
+ \begin{align}
+ \label{eq:actorWeightsPolicy}    
+ \mathbf{u}_k  =  \mathbf{\omega_a^{T}} \mathbf{e}_k
+ \end{align}   
+ Applying a similar gradient descent approach as with the critic weights the actor weights are updated as follows:
+\begin{align}
+   \bm{\omega_a}^{[r+1]} = \bm{\omega}^{[r]} - \ell_a(\mathbf{u}_k-\mathbf{u}_k^*)\mathbf{e}_k, 
+ \label{eq:actorWeights}
+ \end{align}
+ where $\ell$ is the actor learning rate. 
+ \\
+ The complete policy iteration solution process for the leader-follower problem is detailed out in Algorithm \ref{alg:ModelFreeTracking}. %
  %
  \begin{algorithm2e}
-     \caption{\label{alg:ModelFreeTracking} Model-free reinforcement learning using the policy iteration solution.}
+     \caption{\label{alg:ModelFreeTracking} Model-free actor-critic reinforcement learning using the policy iteration solution.}
      \DontPrintSemicolon
@@
                  Given approximate initial poses of leader and follower, compute $\mathbf{e}_0$ using error model~\eqref{eq:stateError}\;
-                 Compute follower's input $\mathbf{u}_0^{[0]}$ using policy~\eqref{eq:modelFreePolicy}\;
+                 Compute follower's input $\mathbf{u}_0^{[0]}$ using policy~\eqref{eq:actorWeightsPolicy}\;
          \Repeat(\tcc*[h]{Main timing loop}){Tracking errors are zero}
@@
              Find $\mathbf{e}_{k+1}$ using~\eqref{eq:stateError}\;
-             Compute policy $\mathbf{u}_{k+1}^{[r]}$ using~\eqref{eq:modelFreePolicy}\;
+             Compute policy $\mathbf{u}_{k+1}^{[r]}$ using~\eqref{eq:actorWeightsPolicy}\;
              %Evaluate and record Equation~\eqref{eq:modelFreeMatrixSolution}\;
@@
              {
-                 $r\leftarrow r+1$\tcc*[h]{Evaluate policy}\;
-                 Solve for the critic-weights $\bm{\omega}$ using~\eqref{eq:criticWeights}\;
-                 Construct matrix $\mathbf{P}^{[r]}$ using vector $\bm{\omega}$\;
+                 $r\leftarrow r+1$\tcc*[h]{Evaluate policy}using~\eqref{eq:modelFreePolicy}\;
+                 Solve for the critic-weights $\bm{\omega_c}$ using~\eqref{eq:criticWeights}\;
+                 Solve for the actor-weights $\bm{\omega_a}$ using ~\eqref{eq:actorWeights}\;\;
+                 Construct matrix $\mathbf{P}^{[r]}$ using vector $\bm{\omega_c}$\;
  %                \eIf{$\|\mathbf{P}^{[r]} - \mathbf{P}^{[r+1]}\|<\varepsilon$}{Set $\mathbf{u}_{k+1}^*\leftarrow\mathbf{u}_{k+1}^{[r]}$}{$k\leftarrow k+1$ }

### 2020-06-29 paperMIC2020/paperIEEE-MIC2020-V1.tex
added simulation figure

@@
  %
- \begin{algorithm2e}
+ \begin{algorithm2e}{
      \caption{\label{alg:ModelFreeTracking} Model-free actor-critic reinforcement learning using the policy iteration solution.}
@@
                  $r\leftarrow r+1$\tcc*[h]{Evaluate policy}using~\eqref{eq:modelFreePolicy}\;
-                 Solve for the critic-weights $\bm{\omega_c}$ using~\eqref{eq:criticWeights}\;
+                 Solve for the critic-weights $\bm{\omega_c}$ using~\eqref{eq:criticWeights}eights}\;
                  Solve for the actor-weights $\bm{\omega_a}$ using ~\eqref{eq:actorWeights}\;\;
@@
 	\subfigure[][]{%    
+    \label{fig:euclideanDistance}%
+    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/euclideanDistance.eps} }
+\subfigure[][]{%
     \label{fig:stateErrorRandom}%
     \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/stateErrorRandomPathDistance.eps} }
-\\
  \subfigure[][]{%
@@
     \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/weightRandomPathDistance.eps} }
+     \subfigure[][]{%
+    \label{fig:actorWeightRandomDistance}%
+    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/weightActor.eps} }
 \caption[Leader-follower performance for random trajectory.]{Performance in tracking random trajectory: 

### 2020-06-29 paperMIC2020/matlabSim/dynamicTargetTrackingV2.m

@@ -317,7 +317,7 @@ print('-depsc2', '-r300', [savefilename, '.eps']);
 % Plot system's performance (trajectory, state error, control inputs)
 Pinit
 P
-generatePlots(length(dt), dt(1:k,:), followerPose(1:k,:) , leaderPose(1:k,:), poseError(1:k,:), u(1:k,:));
+generatePlots(length(dt), dt(1:k,:), followerPose(1:k,:) , leaderPose(1:k,:), poseError(1:k,:), u(1:k,:),trackingError(1:k,:));
 disp('... done.');
 
 
@@ -366,7 +366,7 @@ angle(i)=angle(i)-2*pi;
 i=find(angle<-pi);
 angle(i)=angle(i)+2*pi;
 
-function generatePlots(Tn, t, actualStates, desiredStates, error, u)    
+function generatePlots(Tn, t, actualStates, desiredStates, error, u,trackingError)    
     %close all; % close all opened figures
     % Tn = number of discrete time/path parameter points 
     % t = time/path parameter history, dimension = Tn x 1 
@@ -401,10 +401,10 @@ function generatePlots(Tn, t, actualStates, desiredStates, error, u)
     ymax = max(max(actualStates(:,2),desiredStates(:,2)));
     ymin = min(min(actualStates(:,2),desiredStates(:,2)));
           
-    vid = VideoWriter('OUT/trajectoryRectilinear.avi');
+%     vid = VideoWriter('OUT/trajectoryRectilinear.avi');
     vid.Quality = 100;
     vid.FrameRate = 5;
-    open(vid)
+%     open(vid)
     
     fig=figure;
     clf reset;    
@@ -432,7 +432,7 @@ function generatePlots(Tn, t, actualStates, desiredStates, error, u)
         xlabel('x [m]');
         ylabel('y [m]');
         F = getframe(fig);
-        writeVideo(vid,F);          
+%         writeVideo(vid,F);          
     end
     [Xa,Ya] = plot_DDMR(actualStates(1,:),axis(gca)); % DDMR => Differential drive mobile robot
     grid on
@@ -469,8 +469,19 @@ function generatePlots(Tn, t, actualStates, desiredStates, error, u)
     ylabel('\theta_e [rad]');
     grid on
     
-
+    %plot euclidean distance rho_e
+    
     savefilename = ['OUT/stateErrorRandomPathDistance'];
+    saveas(gcf, savefilename, 'fig');
[…]

### 2020-06-29 paperMIC2020/paperIEEE-MIC2020-V1.tex
Added abstract and NN figure

--- 2020-06-29 paperMIC2020/paperIEEE-MIC2020-V1.tex
@@
 \textit{Bradley University}, Peoria, Illinois, USA \\
- aelhussein@mail.bradley.edu and smiah@bradley.edu}
+E-mails: aelhussein@mail.bradley.edu and smiah@bradley.edu}
 % \and
@@
   %
+  Addressing the trajectory tracking problem of a mobile robot in tracking a dynamic target is still one of the challenging problems in the field of robotics.
+In this paper, we address the position tracking problem of a mobile robot where it is supposed to track the position of an mobile target whose dynamics is unknown a priori.
+This problem is even more challenging when the dynamics of the mobile robot is also assumed to be unknown, which is a basically a realistic assumption.
+Most of trajectory tracking problems proposed in the literature in the field of mobile robotics are either focused on algorithms that rely on mathematical models of the robots or driven by a  overwhelming degree of computational complexity.
+This paper proposes a model-free actor-critic reinforcement learning strategy to determine appropriate actuator commands for the robot to track the position trajectory (unknown a priori) of the target.
+We emphasize that mathematical models of both mobile robot and the target are not required in the current approach.
+Moreover, Bellman's principle of optimality is utilized to minimize the energy required for the robot to track the target.
+The performance of the proposed actor-critic reinforcement learning approach  is backed by a set of computer simulations with various complexities using a virtual circular-shaped mobile robot and a point target  modeled by an integrator.
 
-This paper advances the previous work done by authors by validating a model-free actor-critic reinforcement learning approach to solve dynamic target tracking problem for a car-like mobile robot.
+%   It is even more challenging 
+% This paper advances the previous work done by authors by validating a model-free actor-critic reinforcement learning approach to solve dynamic target tracking problem for a car-like mobile robot.
 The learning approach generates the linear velocity and steering angle of the robot and it does not require any prior knowledge of the dynamic model of the moving target.
 Policy iteration approach is employed through Bellman's principle of optimality to assess the cost of the control actions derived by the proposed learning method.
-The algorithm is tested by coducting a set of computer experiments for complex secnarios using virtual robot expirementation platform widely known as CoppeliaSim.
-
-\todo[inline]{Review and expand}  
+The algorithm is tested by coducting a set of computer expeeriments for complex secnarios using virtual robot expirementation platform widely known as CoppeliaSim.
+% }{Need to be rewritten}  
 %
@@
 
-%\textit{\todo[inline]{Take some references from the following paragraphs}
-%The task of localization and mapping in the context of leader-follower problems is very challenging.
+\todo[inline]{Take some references from the following paragraphs}
+
+  Need to be rewritten some parts of~\cite{Mi2018-c1}
+  % The task of localization and mapping in the context of leader-follower problems is very challenging.
 Such a task is becoming a ubiquitous  facet of modern life due to its promising application in addressing not only the leader-follower problem but also applicable in industry industry with heavy equipment trucks, in agriculture with autonomous crop maintenance, in home life with the autonomous vacuuming robot, along with research and design as seen in~\cite{Roberts2007,Durmus2015,Elara2014,HevrdejsKnoll2017-Indoor}.
@@
 Let the posistion and orientation (pose) of the target i.e leader be ${\bf q}_k\equiv[x_k,y_k,\theta_k]$.
-The robot and the target are deployed in a 2D configuration in which the Follower is to follow the target trajectory defined by  $(\mathbf{p}_k^{[d]})^T=[x_k^{[d]},y_k^{[d]}(t)]$ at time $t\ge 0$ with $t=k \, T_s,$ $k\in\mathbb{N}_0,$ and $T_s>0$ being the sampling time.
+The robot and the target are deployed in a 2D configuration in which the Follower is to follow the target trajectory defined by  $(\mathbf{p}_k^{[\ell]})^T=[x_k^{[\ell]},y_k^{[\ell]}(t)]$ at time $t\ge 0$ with $t=k \, T_s,$ $k\in\mathbb{N}_0,$ and $T_s>0$ being the sampling time.
 Note that this trajectory is completley random.
@@
    \label{eq:leaderDT}
-   \mathbf{p}_{k+1}^{[d]} = \mathbf{p}_k^{[d]} + T_s \, \mathbf{u}_k^{[d]},
+   \mathbf{p}_{k+1}^{[\ell]} = \mathbf{p}_k^{[\ell]} + T_s \, \mathbf{u}_k^{[\ell]},
  \end{align}  
@@
   \begin{figure}
+\todo[inline]{redraw figure and add coppelia sim figures}
    \centering
    \fcolorbox{gray!10}{gray!5}{
-     \includegraphics[width=0.45\textwidth]{figs/ipe/LFMICSetup.eps}
-    }
-   \caption{Mobile robot and its dynamic target tracking problem setup.}
+     \includegraphics[width=0.45\textwidth]{figs/ipe/LF-Setup}
+`     }
+   \caption{Mobile robot and its leader-follower problem setup.}
    \label{fig:leaderFollowerSetup}
@@
      \label{eq:stateError}
-   \mathbf {e}_k^T = [\rho_e,\theta_e]^T =
-   [\sqrt{x_e^2+y_e^2},\theta_e]^T = \\
+   \mathbf{e}_k^T = [\sqrt{x_e^2-y_e^2},\theta_e]^T = \\
    \begin{bmatrix}
-     \sqrt{(x_k^{[d]} - x_k - d\cos\theta_k^{'})^2+
-     (y_k^{[d]} - y_k - d\sin\theta_k^{'})^2},
+     \sqrt{(x_k^{[\ell]} - x_k - d\cos\theta_k^{'})^2-
+     (y_k^{[\ell]} - y_k - d\sin\theta_k^{'})^2},
      \theta_k^{'} - \theta_k
@@
 
- where $\theta_k^{'} = \mathrm{atan2}\left(y_k^{[d]}-y_k, x_k^{[d]}-x_k\right).$ and ${\rho_e}$ being the euclidean distance. 
+ where $\theta_k^{'} = \mathrm{atan2}\left(y_k^{[\ell]}-y_k, x_k^{[\ell]}-x_k\right).$  
 \\
@@
  %
-
-% A two-step solution mechanism that is based on policy iteration is employed to solve the temporal difference equation~\eqref{eq:valueFunctionEstimated} using the policy~\eqref{eq:modelFreePolicy}.
+ \todo[inline]{The following paragraph and the NN structure needs to be rewritten}
+A two-step solution mechanism that is based on policy iteration is employed to solve the temporal difference equation~\eqref{eq:valueFunctionEstimated} using the policy~\eqref{eq:modelFreePolicy}.
 First, the adaptive critics are used to approximate the solving value function $\hat V(\cdot)$ using a multi-layer critic neural network as shown in Fig.~\ref{fig:nnCritic}.
 %
- %
-% \begin{figure}
-%     \centering
-%     \fcolorbox{blue}{gray!5}{
-%         \begin{adjustbox}{max width = 0.45\textwidth}
-%             \tikzset{%
-%                 input neuron/.style={
-%                     circle,
-%                     fill=green!50,
-%                     minimum size=0.7cm
-%                 },
-%                 neuron missing/.style={
-%                     draw=none, 
-%                     scale=1,
-%                     fill=white,
-%                     text height=0.01cm,
-%                     execute at begin node=\color{black}$\vdots$
-%                 },
-%             }
-%            
-%%             \tikzset{%
-%                 hidden neuron/.style={
-%                     circle,
-%                     fill=blue!50,
-%                     minimum size=0.7cm
-%                 },
-%                 neuron missing/.style={
-%                     draw=none, 
-%                     scale=1,
-%                     fill=white,
-%                     text height=0.01cm,
-%                     execute at begin node=\color{black}$\vdots$
-%                 },
-%
-%             }
-%            
-%%             \tikzset{%
-%                 output neuron/.style={
-%                     circle,
-%                     fill=red!50,
-%                     minimum size=0.7cm
-%                 },
-%                 neuron missing/.style={
-%                     draw=none, 
-%                     scale=1,
-%                     fill=white,
-%                     text height=0.01cm,
-%                     execute at begin node=\color{black}$\vdots$
-%                 },
-%             }
-%            
-%%             \begin{tikzpicture}[x=1.5cm, y=1.5cm]
-%            
-%%             \foreach \m/\l [count=\y] in {1,2,missing,3}
-%             \node [input neuron/.try, neuron \m/.try] (input-\m) at (0,2.5-\y) {};
-%            
-%%             \foreach \m [count=\y] in {1,2,3,missing,4}
-%             \node [hidden neuron/.try, neuron \m/.try ] (hidden-\m) at (2,2.5-\y*1.1) {};
-%            
-%%             \foreach \m [count=\y] in {1}
-%             \node [output neuron/.try, neuron \m/.try] (output-\m) at (4,2.5-\y*2.8) {};
-%            
-%%             \foreach \l [count=\i] in {1,2,n+m}
-%             \draw [<-] (input-\i) -- ++(-1,0)
-%             node [above, midway] {$\mathbf{z}_{k,\l}$};
-%            
-%%             \foreach \l [count=\i] in {1,2,3,~\mbox{$\bar{n}$}}
-%             \node [above] at (hidden-\i.north) {$\rho_{\l}$};
-%            
-%%             \foreach \l [count=\i] in {1}
-%             \draw [->] (output-\i) -- ++(1,0)
-%             node [above, midway] {$\hat{V}(\mathbf{z}_{k})$};
-%             % node [above, midway] {$\hat{V}_\l$};
-%            
-%%             \foreach \i in {1,...,3}
-%             \foreach \j in {1,...,4}
-%             \draw [->] (input-\i) -- (hidden-\j);
-%            
-%%             \foreach \i in {1,...,4}
-%             \foreach \j in {1}
-%             \draw [->] (hidden-\i) -- (output-\j);
-%            
-%            
-%            
-%%             \foreach \l [count=\x from 0] in {Input, Hidden, Output}
-%             \node [align=center, above] at (\x*2,1.9) {\l \\ layer};
-%            
-%%             \node [align=center, below] at (3,-2.5) {Weights \\ $\boldsymbol{\omega}$};
-%             \draw[->,ultra thick](3,-2.5) -- (3,1.4);
-%            
-%%             \end{tikzpicture}
-%         \end{adjustbox}      
-%     }
-%     \caption{Critic neural network structure for approximating value function.}
-%     \label{fig:nnCritic}
-%       \end{figure}
+
+\begin{figure}
+    \centering
+    \fcolorbox{blue}{gray!5}{
+        \begin{adjustbox}{max width = 0.45\textwidth}
+            \tikzset{%
+                input neuron/.style={
+                    circle,
+                    fill=green!50,
+                    minimum size=0.7cm
+                },
+                neuron missing/.style={
+                    draw=none, 
+                    scale=1,
+                    fill=white,
+                    text height=0.01cm,
+                    execute at begin node=\color{black}$\vdots$
+                },
+            }
+
+            \tikzset{%
+                hidden neuron/.style={
+                    circle,
+                    fill=blue!50,
+                    minimum size=0.7cm
+                },
+                neuron missing/.style={
+                    draw=none, 
+                    scale=1,
+                    fill=white,
+                    text height=0.01cm,
+                    execute at begin node=\color{black}$\vdots$
+                },
+            }
+
+            \tikzset{%
+                output neuron/.style={
+                    circle,
+                    fill=red!50,
+                    minimum size=0.7cm
+                },
+                neuron missing/.style={
+                    draw=none, 
+                    scale=1,
+                    fill=white,
+                    text height=0.01cm,
+                    execute at begin node=\color{black}$\vdots$
+                },
+            }
+
+            \begin{tikzpicture}[x=1.5cm, y=1.5cm]
+
+            \foreach \m/\l [count=\y] in {1,2,missing,3}
+            \node [input neuron/.try, neuron \m/.try] (input-\m) at (0,2.5-\y) {};
+
+            \foreach \m [count=\y] in {1,2,3,missing,4}
+            \node [hidden neuron/.try, neuron \m/.try ] (hidden-\m) at (2,2.5-\y*1.1) {};
+
+            \foreach \m [count=\y] in {1}
+            \node [output neuron/.try, neuron \m/.try] (output-\m) at (4,2.5-\y*2.8) {};
+
+            \foreach \l [count=\i] in {1,2,n+m}
+            \draw [<-] (input-\i) -- ++(-1,0)
+            node [above, midway] {$\mathbf{z}_{k,\l}$};
+
+            \foreach \l [count=\i] in {1,2,3,~\mbox{$\bar{n}$}}
+            \node [above] at (hidden-\i.north) {$\rho_{\l}$};
+
+            \foreach \l [count=\i] in {1}
+            \draw [->] (output-\i) -- ++(1,0)
+            node [above, midway] {$\hat{V}(\mathbf{z}_{k})$};
+            % node [above, midway] {$\hat{V}_\l$};
+
+            \foreach \i in {1,...,3}
+            \foreach \j in {1,...,4}
+            \draw [->] (input-\i) -- (hidden-\j);
+
+            \foreach \i in {1,...,4}
+            \foreach \j in {1}
+            \draw [->] (hidden-\i) -- (output-\j);
+
+            \foreach \l [count=\x from 0] in {Input, Hidden, Output}
+            \node [align=center, above] at (\x*2,1.9) {\l \\ layer};
+
+            \node [align=center, below] at (3,-2.5) {Weights \\ $\boldsymbol{\omega}$};
+            \draw[->,ultra thick](3,-2.5) -- (3,1.4);
+
+            \end{tikzpicture}
+        \end{adjustbox}      
+    }
+    \caption{Critic neural network structure for approximating value function.}
+    \label{fig:nnCritic}
+      \end{figure}
  %      
@@
  \bibliographystyle{IEEEtran}
-\bibliography{bib/refsSuruzWeb,bib/refsMultiAgent,bib/refsRoboticsJournals,bib/refsRoboticsConferences,bib/refsGenericControl,bib/refsBooksTRTheses,bib/refsReinforcementLearningADP,bib/refsRL-Keshtkar}
+ \bibliography{bib/refsSuruzWeb,bib/refsBooksTRTheses,bib/refsReinforcementLearningADP}
+% \bibliography{bib/refsSuruzWeb,bib/refsMultiAgent,bib/refsRoboticsJournals,bib/refsRoboticsConferences,bib/refsGenericControl,bib/refsBooksTRTheses,bib/refsReinforcementLearningADP,bib/refsRL-Keshtkar}
 \end{document}

### 2020-06-29 paperMIC2020/paperIEEE-MIC2020-V1.tex

@@
 \textit{Bradley University}, Peoria, Illinois, USA \\
-E-mails: aelhussein@mail.bradley.edu and smiah@bradley.edu}
+ aelhussein@mail.bradley.edu and smiah@bradley.edu}
 % \and
@@
  ${\bf P}=\begin{bmatrix} 
- 2\,\omega^{1}    & \omega^{2}      & \omega^{3}       & \omega^{4}       & \omega^{5} \\ 
- \omega^{2}       &2\, \omega^{6}   & \omega^{7}       & \omega^{8}       & \omega^{9} \\
- \omega^{3}       & \omega^{7}      &2\, \omega^{10}   & \omega^{11}      & \omega^{12} \\
- \omega^{4}       & \omega^{8}      & \omega^{11}      & 2\,\omega^{13}   & \omega^{14} \\
- \omega^{5}       & \omega^{9}      & \omega^{12}      & \omega^{14}      & 2\,\omega^{15}   
- \end{bmatrix}\in \mathbb{R}^{5\times 5},$
+ 2\,\omega^{1}    & \omega^{2}      & \omega^{3}       & \omega^{4}        \\ 
+ \omega^{2}       &2\, \omega^{5}   & \omega^{6}       & \omega^{7}        \\
+ \omega^{3}       & \omega^{6}      &2\, \omega^{8}   & \omega^{9}   \\   
+ \omega^{4}       & \omega^{7}      & \omega^{9}      & 2\,\omega^{10}      
+ \end{bmatrix}\in \mathbb{R}^{4\times 4},$
  \end{center}
  %
- where $\omega^{i}$ is the $i^{th}$ entry of the weight vector $\bm{\omega}.$ The complete policy iteration solution process for the leader-follower problem is detailed out in Algorithm \ref{alg:ModelFreeTracking}.
+ where $\omega^{i}$ is the $i^{th}$ entry of the weight vector $\bm{\omega}.$ 
+ \todo[inline]{merge the actor weights discussion with the rest}
+ The critic wegihts are then used to update the actor weights which maps the state error to the desired ploicy (control actions) at every time step $t$ with the following equation:
+ \begin{align}
+ \label{eq:actorWeightsPolicy}    
+ \mathbf{u}_k  =  \mathbf{\omega_a^{T}} \mathbf{e}_k
+ \end{align}   
+ Applying a similar gradient descent approach as with the critic weights the actor weights are updated as follows:
+\begin{align}
+   \bm{\omega_a}^{[r+1]} = \bm{\omega}^{[r]} - \ell_a(\mathbf{u}_k-\mathbf{u}_k^*)\mathbf{e}_k, 
+ \label{eq:actorWeights}
+ \end{align}
+ where $\ell$ is the actor learning rate. 
+ \\
+ The complete policy iteration solution process for the leader-follower problem is detailed out in Algorithm \ref{alg:ModelFreeTracking}. %
  %
- %
- \begin{algorithm2e}
-     \caption{\label{alg:ModelFreeTracking} Model-free reinforcement learning using the policy iteration solution.}
+ \begin{algorithm2e}{
+     \caption{\label{alg:ModelFreeTracking} Model-free actor-critic reinforcement learning using the policy iteration solution.}
      \DontPrintSemicolon
@@
              {
-                 $r\leftarrow r+1$\tcc*[h]{Evaluate policy}\;
-                 Solve for the critic-weights $\bm{\omega}$ using~\eqref{eq:criticWeights}\;
-                 Construct matrix $\mathbf{P}^{[r]}$ using vector $\bm{\omega}$\;
+                 $r\leftarrow r+1$\tcc*[h]{Evaluate policy}using~\eqref{eq:modelFreePolicy}\;
+                 Solve for the critic-weights $\bm{\omega_c}$ using~\eqref{eq:criticWeights}eights}\;
+                 Solve for the actor-weights $\bm{\omega_a}$ using ~\eqref{eq:actorWeights}\;\;
+                 Construct matrix $\mathbf{P}^{[r]}$ using vector $\bm{\omega_c}$\;
  %                \eIf{$\|\mathbf{P}^{[r]} - \mathbf{P}^{[r+1]}\|<\varepsilon$}{Set $\mathbf{u}_{k+1}^*\leftarrow\mathbf{u}_{k+1}^{[r]}$}{$k\leftarrow k+1$ }

### 2020-06-30 paperMIC2020/paperIEEE-MIC2020-V1.tex

@@
 \section{Dynamic target tracking and problem setting} 
-\todo[inline]{Needs to reviewed}
+\todo[inline]{review}
  \label{sec:problemSetup}
@@
    \begin{align}
-     x_{k+1}& =x_{k}+T_s\nu_{k}\cos{(\theta_{k}+\gamma_{k})} + \zeta_1,\\  
-     y_{k+1}& =y_{k}+T_s\nu_{k}\sin{(\theta_{k}+\gamma_{k})}+ \zeta_2,\\
-     \theta_{k+1}&=\theta_{k}+T_s\nu_{k}\frac{\sin{(\gamma_{k})}}{l}+ \zeta_3,
+   	 	\nu_{k}(t) = \frac{1}{l}(\nu_{R,k} + \nu_{l,k}),\\ 
+   	 	\omega_{k}(t)=\frac{\nu_{k}(t)}{l}tan(\gamma(t)) 	
    \end{align}
@@
  \\
-\hl{Note that the follower dynamic model obeys Ackermann steering principle where $\gamma_k\in(-\frac{\pi}{2},\frac{\pi}{2})$ is the front wheel steering angle with respect to the robot's orientation $\theta_k\in[-\pi,\pi),$ $\nu_k$ is the linear speed, $l$ is the distance between the drive wheels of the robot, and $\zeta_1,\zeta_2,\zeta_3\in\mathbb{R}$ are the model uncertainties.}
+where $\omega(t)$ and $\nu_k(t)$ is the angular and linear velocity, $\gamma_k\in(-\frac{\pi}{2},\frac{\pi}{2})$ is the steering angle with respect to the robot's orientation $\theta_k\in[-\pi,\pi)$ ,$l$ is the distance between the drive wheels of the robot.
 \\
@@
  \label{sec:resultsExperiments}
- This section adopts the theoritical results discussed in the previous section by simulating the Algorithm using the Pioneer 3-DX in CoppeliaSim.
-The results obtained by the authors in \hl{cite flairs paper here} are validated using the commercial robot simulator, CoppeliaSim as a prelminary step to implement the Algorithm experimantally in real world.
-we present the dynamics of the tracking error and the convergence characterisitcs of the actor and critic weights.
+ \todo[inline]{review}
+ This section adopts the theoritical results discussed in the previous section by simulating the Algorithm using the Pioneer 3-DX  robot.
+The proposed Actor-Critic RL algorithm is tested using the commercial robot simulator CoppeliaSim in integration with Matlab software as a prelminary step to implement the Algorithm experimantally in real world.Here we present the performance of the proposed method and the convergence characterisitcs of the actor and critic weights.
 The weighting matrices are set to $\mathbf{Q} = \mathrm{diag}[0.001,0.001]$ and $\mathbf{R} = \mathrm{diag}[10^{-5}, 10^{-5}].$ %
@@
   \end{bmatrix}.\]
- The actor and critic learning rates $\ell_c$ are set to  $0.01$ and $0.0001$.
-The sampling time $T_s$ is set to $0.001 \sec.$ The desired distance offset between the leader and the follower is set to $ d = 0.5$ [m] for all scenarios.
- The CoppeliaSim simulator accuratly mimic what would happen in a realworld scenario following idustry standatrds and guidlines.
-The Pioneer robot model and the  was initally placed at position (-1,-2.5) m.The Target modeled as a cylinder was initially positioned on a random position around the origin (0,0).
-The simulation was run for
+
+ The actor and critic learning rates $\ell_c$,$\ell_a$ are set to  $0.0001$ and $0.01$ respectively.
+The sampling time $T_s$ is set to $0.001 \sec.$ The desired distance offset between the leader and the follower is set to $ d = 0.2$ [m].
+
+  During the simulation CoppeliaSim simulator accuratly mimics what would happen in a realworld scenario following idustry standatrds and guidlines.The setup of the virtual expirement is illustrated  in figure \ref{fig:CoppeliaSim Scene} where pioneer robot model was initally placed at position $(x,y) = (-1,-2.5) $ [m] with an orientation $\theta = 0 \degree$ .The Target which is modeled as a cylinder object was initially located at a random position around  $(x,y) = (0,0)$ [m].
+The simulation was run for the duration of 15 seconds.
+  The Target is set to move on a completely random trajectory starting from a random position.
+We intensify that the follower robot has no previous knoweledge of the dynamic model of the moving target nor it's initial position.
+The results obtained by the simulation are shown in figure \ref{fig:simulationResults}.
+the control actions of the pioneer robot are determined by the random actor weights .we clearly see tracking error converges to the desired value of $d$ = 0.2 [m] along with control signal converging to values that allows target tracking.
+the results reveal the ability of the proposed algorithm to sucessfully track the dynamic moving target and adapt to the changes in the target's path in an online manner.
 \begin{figure}
@@
 `     }
-   \caption{CoppeliaSim Scene.}
+   \caption{Simulation Setup}
    \label{fig:CoppeliaSim Scene}
@@
  \begin{figure*}[htbp]%
+
  \subfigure[][]{%
@@
   \label{fig:peformanceRandomTrajectory}%
+	\label{fig:simulationResults}
 \end{figure*}
 
-% \textit{In the sequel, computer experiments  are conducted to validate the performance of the proposed model-free adaptive learning algorithm in real-time.
-The results of computer experiments highlight the dynamics of the tracking errors and the convergence characteristics of the proposed algorithm (i.e., updating the critic weights).
-This will judge the ability of the follower robot to track independent motion trajectory of the leader robot under two different independent leader-motion trajectories.
-The computer experiments are realized using MATLAB simulation environment.
-The weighting matrices are set to $\mathbf{Q} = \mathrm{diag}[0.01,0.01,0.005]$ and $\mathbf{R} = \mathrm{diag}[10^{-6}, 10^{-6}].$ %
-%  \[Q=0.001 
-%  \begin{bmatrix}
-%  10       & 0   & 0\\
-%  0       & 10   & 0\\
-%  0       & 0   &5 \\
-%  \end{bmatrix},
-%  R=0.000001
-%  \begin{bmatrix}
-%  1       & 0 \\
-%  0       & 1 
-%  \end{bmatrix}.\]
-% The learning rate $\ell_c$ is set to  $0.0001$.
-The sampling time $T_s$ is set to $0.08 \sec.$ The desired distance offset between the leader and the follower is set to $ d = 0.5$ [m] for all scenarios.
-%
-%% In the first s\begin{figure*}[htbp]%
-%\centering
-%\parbox[c]{0.48\textwidth}{\centering Parallel parking}
-%\parbox[c]{0.48\textwidth}{\centering Trajectory tracking}
-%\\
-
-% 
-%%\begin{align*}
-%% $\dot x^{[\ell]}(t) = \nu^{[\ell]}(t)\cos\theta^{[\ell]}(t),$ %
-%% $\dot y^{[\ell]}(t) = \nu^{[\ell]}(t)\sin\theta^{[\ell]}(t).$
-%% \dot\theta^\ell(t) &= \omega(t),
-%%\end{align*}
-% 
-% Initially, the leader's position is set to be the same for a short period of time with $\nu^{\ell} = 0 , \gamma^{\ell} = 0$.
-Then it starts to move on a horizontal line with $\nu^{\ell} = 0.1 $ [m/s], eventually the leader starts to move on an inclined path with $\nu^{\ell} = 0.2$ [m/s], $\gamma^{\ell} = 45\degree$.
-The leader is initially placed at $(x,y) = (5, 2)~\si{[\meter]}$ with an orientation of $\theta = 0 \degree $, while the follower  is initially placed at $(x,y) = (0, 0)~\si{[\meter]}$ with an orientation of $\theta = 0\degree$.
-Note that during this scenario, the critic weights converge rapidly and the tracking errors decay till the follower tracks the leader.
-The trajectory phase plan plot, tracking error states, control signals, and tuning of critic weights are shown in Fig.~\ref{fig:performanceRectilinearTrajectory}.
-%
-% 
-%% \begin{figure*}[htbp]%
-%%     \centering
-%%     \parbox[c]{0.48\textwidth}{\centering Parallel parking}
-%%     \parbox[c]{0.48\textwidth}{\centering Trajectory tracking}
-%%     \\
-%%     \subfigure[][]{%
-%%         \label{fig:trajectoryRectilinearDistance}%
-%%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/rectilinear/trajectoryRectlinearDistance} }
-%%     \subfigure[][]{%
-%%         \label{fig:stateErrorRectilinearDistance}%
-%%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/rectilinear/stateErrorRectlinearDistance} }
-%%     \\
-%%     \subfigure[][]{%
-%%         \label{fig:controlInputsRectilinearDistance}%
-%%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/rectilinear/controlInputRectlinearDistance} }
-%%     \subfigure[][]{%
-%%         \label{fig:weightRectilinearDistance}%
-%%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/rectilinear/weightRectilinearDistance} }
-%%     \caption[Leader-follower performance for rectilinear trajectory.]{First scenario (rectilinear trajectory): 
-%%         \subref{fig:trajectoryRectilinearDistance} leader-follower trajectories,~\subref{fig:stateErrorRectilinearDistance} state tracking errors,~\subref{fig:controlInputsRectilinearDistance} linear speed and steering angle of the follower, and    \subref{fig:weightRectilinearDistance} critic weights.}%
-%%     \label{fig:performanceRectilinearTrajectory}%
-%% \end{figure*}
-% 
-%
-%
-% A relatively unplanned complex trajectory-tracking scenario is considered. The leader moves according to a sinusoidal trajectory so that %
-% 
-%%  \begin{align*}
-%% $x^{[\ell]}(t) = \alpha (t) \in [0,10\pi],$ %
-%% $y^{[\ell]}(t) = 5 \,\sin(\alpha t),$ and %
-%% $\theta^{[\ell]}(t) = cos(\alpha t).$  %
-%%        \end{align*}
-%% 
-% The leader robot  was initially placed at $(x,y) = (0, 0)~\si{[\meter]}$ with an orientation of $\theta = 0 \degree$ while the follower robot was initially placed at a random position around $(x,y) = (0, 0)~\si{[\meter]}$ with a random orientation.
-The simulation results are summarized in Figure~\ref{fig:performanceSinewaveTrajectory}.
-It is observed that the critic weights take more time to converge compared to the earlier scenario,  which is reluctant to the complexity of the independent trajectory of the leader.
-This result emphasizes the adaptability of the proposed adaptive learning mechanism to different scenarios.
-Further, the follower starts to move away from the leader at the beginning of the simulation before it finally converges to the leader where the tracking errors are bounded by a safe distance $d.$ %
-% 
-%% \begin{figure*}[htbp]%
-%%     \centering
-%%     \parbox[c]{0.48\textwidth}{\centering Parallel parking}
-%%     \parbox[c]{0.48\textwidth}{\centering Trajectory tracking}
-%%     \\
-%%     \subfigure[][]{%
-%%         \label{fig:trajectorySinewave}%
-%%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/sinewave/trajectorySinewaveDistance} }
-%%     \subfigure[][]{%
-%%         \label{fig:stateErrorSinewave}%
-%%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/sinewave/stateErrorSinewaveDistance} }
-%%     \\
-%%     \subfigure[][]{%
-%%         \label{fig:controlInputSinewave}%
-%%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/sinewave/controlInputSinewaveDistance} }
-%%     \subfigure[][]{%
-%%         \label{fig:weightSinewaveDistance}%
-%%         \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/sinewave/weightSinewaveDistance} }
-%%     \caption[Leader-follower performance for nonlinear trajectory.]{Second scenario (sinusoidal trajectory): 
-%%         \subref{fig:trajectorySinewave} leader-follower trajectories,~\subref{fig:stateErrorSinewave} state tracking errors,~\subref{fig:controlInputSinewave} linear speed and steering angle of the follower, and    \subref{fig:weightSinewaveDistance} critic weights.}%
-%%     \label{fig:performanceSinewaveTrajectory}%
-%% \end{figure*}
-% 
-%
-%
-%\textit{In the third case study we rely on completley random path for the leader robot to evaluate the effectivenss of the proposed algorithm as a solution for the leader follower tracking problem.
-The leader is to follow a random path defined by the model described in (2), with $\gamma$ being a random value, The follwer is to maitain an offset distance of $d = 0.5 $ [m].
-Note that the path of the leader is not pre defined and the algorithm being completlety model free.
-The results are summerized in Fig.
-\ref{fig:peformanceRandomTrajectory}.
-}
-
-%The results are summarized in Fig.~\ref{fig:peformanceRandomTrajectory}. %
-%
-%\begin{figure*}[htbp]%
-%\centering
-%\parbox[c]{0.48\textwidth}{\centering Parallel parking}
-%\parbox[c]{0.48\textwidth}{\centering Trajectory tracking}
-%\\
-%\subfigure[][]{%
-%    \label{fig:trajectoryRandom}%
-%    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/randomPath/trajectorySinewave} }
-%\subfigure[][]{%
-%    \label{fig:stateErrorRandom}%
-%    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/randomPath/stateErrorSinewave} }
-%\\
-% \subfigure[][]{%
-%    \label{fig:controlInputsRandom}%
-%    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/randomPath/controlInputSinewave} }
-% \subfigure[][]{%
-%    \label{fig:weightRandomDistance}%
-%    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/randomPath/weightRectilinearDistance} }
-%\caption[Leader-follower performance for random trajectory.]{Performance in tracking random trajectory: 
-%  \subref{fig:trajectoryRandom} leader-follower trajectories,~\subref{fig:stateErrorRandom} state error,~\subref{fig:controlInputsRandom} linear speed and steering angle of the follower; and    \subref{fig:weightRandomDistance} learning weights.}%
-%  \label{fig:peformanceRandomTrajectory}%
-%\end{figure*}
-
  \section{Conclusion} \label{sec:conclusion}
-
-% A novel policy iteration mechanism based on a model-free reinforcement learning approach is presented for solving a conventional leader-follower formation problem using car-like mobile robots.
-The proposed approach does not rely on model parameters inherent in the mobile robots employed in this work.
-The follower robot is able to follow the leader robot that navigates along unplanned trajectories of various complexities while maintaining a nonzero safe distance between them.
-To the best of authors' knowledge, this is the first milestone of its kind where a model-free policy iteration based reinforcement learning approach is employed in a multi-robot formation control problem.
-The future work is going  to extend the learning algorithm for solving a time-varying formation control problem using networked robots.
-
-% \section*{Acknowledgment}
-
-% The preferred spelling of the word ``acknowledgment'' in America is without 
- an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
- G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
- acknowledgments in the unnumbered footnote on the first page.
+	\todo[inline]{review}
+	A model free actor-critic reinfoncement learning algorithm for dynamic target tracking has been validated using virtual robot experimantation platform where a differenitial drive mobile robot and a randomly moving target are utilized in the simulation.Opposed to previous approaches in the litrature this Algorithm possess the advantage of being completlety model free and doesn't rely on any dynamic model to be known in priori.
+The actor weights which drives the control actions of the robot sucessfully converge to values that enable the robot to track the moving target through unplanned trajectory.
+To the authors knowlege this work is the first of its kind to employ a model-free actor-critic RL approach  in the context of dynamic target tracking.
+In future work the proposed approach will be applied to multi-robot scenarios where a number of robots are to achieve a certain task in unknown enviroments.
 
@@
  \bibliography{bib/refsSuruzWeb,bib/refsBooksTRTheses,bib/refsReinforcementLearningADP}
-% \bibliography{bib/refsSuruzWeb,bib/refsMultiAgent,bib/refsRoboticsJournals,bib/refsRoboticsConferences,bib/refsGenericControl,bib/refsBooksTRTheses,bib/refsReinforcementLearningADP,bib/refsRL-Keshtkar}
+\bibliography{bib/refsSuruzWeb,bib/refsMultiAgent,bib/refsRoboticsJournals,bib/refsRoboticsConferences,bib/refsGenericControl,bib/refsBooksTRTheses,bib/refsReinforcementLearningADP,bib/refsRL-Keshtkar}
 \end{document}

### 2020-06-30 paperMIC2020/paperIEEE-MIC2020-V1.tex
Problem Setting section is rewritten
Follow the description of this section throughout the document

@@
 Tracking a random moving target using a mobile robot, for instance, is a challenging task.
-This is mainly due to their inherent complex nonlinear dynamics dynamics.
+This is mainly due to their inherent complex nonlinear dynamics.
 Most of the target tracking algorithms proposed in the literature either rely on A) complex mathematical models, B) simplified mathematical models, and C) nonlinear control techniques or driven by large amount of mostly offline data that leads to an overwhelming degree of computational complexity.
@@
 
-\section{Dynamic target tracking and problem setting} 
-\todo[inline]{review}
- \label{sec:problemSetup}
+\section{Problem Setting} 
+\label{sec:problemSetting}
 
-Suppose that a wheeled mobile robot (follower) with coordinate $(x,y)$ and orientation $\theta\in[-\pi,\pi)~\si{\radian}$ with respect to the global X-Y coordinate has a linear speed $\nu$ and steering angle $\gamma$ which are considered as the two control actions.
-Let the posistion and orientation (pose) of the target i.e leader be ${\bf q}_k\equiv[x_k,y_k,\theta_k]$.
-The robot and the target are deployed in a 2D configuration in which the Follower is to follow the target trajectory defined by  $(\mathbf{p}_k^{[d]})^T=[x_k^{[d]},y_k^{[d]}(t)]$ at time $t\ge 0$ with $t=k \, T_s,$ $k\in\mathbb{N}_0,$ and $T_s>0$ being the sampling time.
-Note that this trajectory is completley random.
-The target motion is modeled by the following discrete-time system:
+Fig.~\ref{fig:leaderFollowerSetup} shows the setup of the problem that we address in this manuscript.
+The robot is characterized by its 2D position $(x_k,y_k)$ and orientation $\theta_k\in[-\pi,\pi)$ with respect to global coordinate frame X-Y at discrete time index $k=0,1,\ldots,$ where time $t=kT$ with $T>0$ being the sampling time.
+The time-varying position of the target is denoted by ${\bf p}_k^{[d]}= [x_k^{[d]},y_k^{[d]}]^T\in\mathbb{R}^2.$  Let the position and orientation (pose) of the robot is denoted by the vector  ${\bf q}_k^T\equiv[x_k,y_k,\theta_k]\in\mathbb{R}^2\times\mathbb{S}^1.$ Without loss of generality, assume that the robot tracks the target's trajectory while maintaining line-of-sight distance (also known as safe distance between the robot and the target) $d>0.$ We emphasize that the mathematical models of both robot and the target are not required in the proposed control technology.
+For illustration, let us assume that the robot (rear-wheel drive) follows the discrete-time kinematic model described by %
+%
+\begin{subequations}
+  \begin{align}
+    \label{eq:robotModelDT}
+    x_{k+1} &= x_k +T\nu_k\cos\theta_k\\
+    y_{k+1} &= y_k +T\nu_k\sin\theta_k\\
+    \theta_{k+1} &= \theta_k + T\frac{\nu_k}{L}\tan\gamma_k
+  \end{align}
+\end{subequations}
+%
+where $\gamma_k\in(-\frac{\pi}{2},\frac{\pi}{2})$ is the steering angle of the font castor of the robot (see Fig.~\ref{fig:leaderFollowerSetup}), and $\nu_k\in\mathbb{R}$ is the linear speed.
+Without loss of generality, this work considers a target modeled by an integrator and its discrete-time kinematic model is described by
  \begin{align}
@@
  \end{align}  
-with $\mathbf{u}_k^{[\ell]}\in\mathbb{R}^2$ being the control inputs of the target movment. 
-\\ The follower robot is to maintain a constant safe-distance $d>0$ from target. The dynamic car-like model of the follower robot is defined as follows:
+with $\mathbf{u}_k^{[d]}\in\mathbb{R}^2$ being the control input vector (velocity) that defines the trajectory (considered random in this work) of the target.
+In case, the robot modeled by~\eqref{eq:robotModelDT} is described by a differential drive mobile robot, then its left-wheel velocity $\nu_{L,k}$ and right-wheel velocity $(\nu_{R,k})$ are related as
   \begin{figure}
@@
    \begin{align}
-   	 	\nu_{k}(t) = \frac{1}{l}(\nu_{R,k} + \nu_{l,k}),\\ 
-   	 	\omega_{k}(t)=\frac{\nu_{k}(t)}{l}tan(\gamma(t)) 	
+     \nu_{k} &= \frac{1}{2}(\nu_{R,k} + \nu_{L,k}),\\
+     \omega_{k} &= \frac{1}{\ell}(\nu_{R,k} - \nu_{L,k}) = \frac{\nu_{k}}{L}\tan(\gamma_k) 	
    \end{align}
@@
  \end{subequations}
- \\
-where $\omega(t)$ and $\nu_k(t)$ is the angular and linear velocity, $\gamma_k\in(-\frac{\pi}{2},\frac{\pi}{2})$ is the steering angle with respect to the robot's orientation $\theta_k\in[-\pi,\pi)$ ,$l$ is the distance between the drive wheels of the robot.
-\\
-We then define the error vector as:
+ %
+ where $\omega_k = \frac{\nu_k}{L}\tan\gamma_k$ is the angular velocity of the robot's center $(x_k,y_k).$ Let us define the error vector as 
  \begin{multline}
      \label{eq:stateError}
-   \mathbf {e}_k^T = [\rho_e,\theta_e]^T =
-   [\sqrt{x_e^2+y_e^2},\theta_e]^T = \\
+   \mathbf{e}_k = [\rho_k,\tilde\theta_k]^T =
+   % [\sqrt{x_e^2+y_e^2},\tilde{\theta_k}]^T = \\
    \begin{bmatrix}
@@
  \end{multline}
-
- where $\theta_k^{'} = \mathrm{atan2}\left(y_k^{[d]}-y_k, x_k^{[d]}-x_k\right).$ and ${\rho_e}$ being the euclidean distance. 
-\\
-\hl{The control problem can then be formally stated as follows}: Find $\nu_k$ and $\gamma_k$ such that ${\bf e}_k\to {\bf 0}$ as  $k\to\infty$ subject to~\eqref{eq:leaderDT}~\text{and}~\eqref{eq:robotModel1-DT}.
+% 
+ where $\theta_k^{'} = \mathrm{atan2}\left(y_k^{[d]}-y_k, x_k^{[d]}-x_k\right)$ and ${\rho_k}$ the Euclidean distance at time instant $k$ as shown in Fig.~\ref{fig:leaderFollowerSetup}.
+The control problem can then be formally stated as follows: Find $\nu_k$ and $\gamma_k$ such that ${\bf e}_k\to {\bf 0}$ as  $k\to\infty$ subject to~\eqref{eq:robotModelDT}~and~\eqref{eq:leaderDT}.
 
@@
  \bibliographystyle{IEEEtran}
- \bibliography{bib/refsSuruzWeb,bib/refsBooksTRTheses,bib/refsReinforcementLearningADP}
-\bibliography{bib/refsSuruzWeb,bib/refsMultiAgent,bib/refsRoboticsJournals,bib/refsRoboticsConferences,bib/refsGenericControl,bib/refsBooksTRTheses,bib/refsReinforcementLearningADP,bib/refsRL-Keshtkar}
+\bibliography{bib/refsSuruzWeb,bib/refsMultiAgent,bib/refsRoboticsJournals,bib/refsRoboticsConferences,bib/refsBooksTRTheses,bib/refsReinforcementLearningADP,bib/refsRL-Keshtkar}
 \end{document}

### 2020-06-30 paperMIC2020/paperIEEE-MIC2020-V1.tex
fixed bib

--- 2020-06-30 paperMIC2020/paperIEEE-MIC2020-V1.tex
@@
 Tracking a random moving target using a mobile robot, for instance, is a challenging task.
-This is mainly due to their inherent complex nonlinear dynamics dynamics.
+This is mainly due to their inherent complex nonlinear dynamics.
 Most of the target tracking algorithms proposed in the literature either rely on A) complex mathematical models, B) simplified mathematical models, and C) nonlinear control techniques or driven by large amount of mostly offline data that leads to an overwhelming degree of computational complexity.
 
-Over the past years mobile robots has been used in several applications in commercial and military sectors such as surveillance, search and rescue missions,coverage optimization, cooperative localization and dynamic target tracking tasks.
+Over the past years mobile robots has been used in several applications in commercial and military sectors such as surveillance, search and rescue missions,coverage optimization, cooperative localization and dynamic target tracking tasks \cite{kolling2006},\cite{Encarnacao2001},\cite{Ju2001}.
 In all of these mentioned applications a fleet of robot i.e agents interact with each other to achieve a certain goal.
@@
 \\(3) expensive hardware platforms are used to achieve the mobile target tracking.
- \\The main contribution of this work is the development of a model-free learning approach to control the follower robot by which it overcome many of the limitations mentiond above as it does not rely on any prior information of the mathmetical model or the dynamic model.
+
+The main contribution of this work is the development of a model-free learning approach to control the follower robot by which it overcome many of the limitations mentiond above as it does not rely on any prior information of the mathmetical model or the dynamic model.
 The steering angle and the linear speed of the follower robot are determined by collecting the position and orientation of both the leader and the follower.
 This set of information is gathered online over a finite period of time.
-The optimal control actions are then generated by utilizing Bellman's principal of optimality which acts as model free-reinfocment learning approach that allows the follower robot to follow the path of the leader while oviding collision by maintaining a safe distance.
+The optimal control actions are then generated by utilizing Bellman's principal of optimality which acts as model free-reinfocment learning approach that allows the follower robot to follow the path of the leader while avoiding collision by maintaining a safe distance.
 In this paper the proposed algorithm is further validated using a commercially available robot simulator, CoppeliaSim.
@@
 \hl{cite area coverage papers}
- \\The rest of the paper is orgnized as follows.
+The rest of the paper is orgnized as follows.
 Section II lays down the problem setting of the leader follower problem and mathemetical models of the robots and the state error.
 The model free actor-critic reinforcment learning and its key steps are described in section III.Section IV illustrates computer simulations for different secnarios that reflects the effectivness of the proposed method followed by conlusion and future work presented in section V.
-
-\todo[inline]{Take some references from the following paragraphs}
-
-  Need to be rewritten some parts of~\cite{Mi2018-c1}
-  % The task of localization and mapping in the context of leader-follower problems is very challenging.
-Such a task is becoming a ubiquitous  facet of modern life due to its promising application in addressing not only the leader-follower problem but also applicable in industry industry with heavy equipment trucks, in agriculture with autonomous crop maintenance, in home life with the autonomous vacuuming robot, along with research and design as seen in~\cite{Roberts2007,Durmus2015,Elara2014,HevrdejsKnoll2017-Indoor}.
-In most leader-follower problem addressed in the literature to date, it is assumed that leader/target's position/state is known \textit{a priori}, which may not be the case in many applications such as tracking a mobile point source~\cite{Xu2013}.
-Furthermore, the localization and mapping task is of a paramount importance in addressing the problem of mobile target tracking, which has a number of promising applications, such as robotic navigation, search and rescue mission, wildlife monitoring, autonomous surveillance, to name a few.
-A large body of research has been conducted in the literature to address the localization and mapping problem.
-Relatively few papers have addressed the localization and mapping problem in the context of leader-follower tasks, where either (i) a static leader/target is used~\cite{Fernando2015}, (ii) the leader/target's location is predetermined, or (iii) expensive hardware platforms are used to implement the mobile target tracking strategy (see the work presented in~\cite{Yang2014}, for example).
-%
-%The work done in this paper addresses some of the aforementioned issues by carrying out a cost-effective and easy-to-implement localization and mapping algorithm in the context of a leader--follower problem, a wheeled mobile robot is employed as a follower and a target moving on a two-dimensional (2D) plane is used as a leader.
-We emphasize that the position of the  leader is unknown to the follower robot \emph{a priori.} Therefore, the position and orientation of the follower robot and the position of the leader are to be simultaneously estimated while building the map of the environment of the robot using a set of networked wireless radio sensors placed on the ground.
-It is assumed that a radio sensor is mounted on the leader.
-The follower robot receives range measurements [herein the received signal strength indicator (RSSI) from radio sensors] from all radio sensors in its operating range.
-These measurements are then used to estimate the position and orientation of the follower robot, the 2D position of the leader, and the 2D positions of radio sensors placed in the robot's environment.
-Once the follower robot estimates its states (position and orientation) and the position of the leader, it moves towards the leader using the motion controller running onboard the follower robot.
-The design and implementation of the current work are based on the preliminary work of the robot navigation and mapping strategy conducted by the authors in~\cite{HevrdejsKnoll2017-Indoor,KnHeMi2017-c1,HeKnMi2017-c1}.
-Therefore, the main objective is to advance the work in~\cite{HevrdejsKnoll2017-Indoor,KnHeMi2017-c1,HeKnMi2017-c1} for a more general case, where a mobile robot is to follow a leader  whose position is unknown \emph{a priori.}
-%n}
 
@@
  \end{multline*}
- where $\bm{\Lambda} = [{\bf o}_0,{\bf o}_1,\ldots,{\bf o}_{\eta-1}]^T \in \mathbb{R}^{\eta\times 15}$ with ${\bf o}_\kappa = \tilde{\bm{\rho}}^T({\bf z}_{k+\kappa, k+\kappa+1}) \in \mathbb{R}^{1\times 15}$ and ${\bf v} =[v_0,v_1,\ldots,v_{\eta-1}]^T \in \mathbb{R}^{\eta}$ with $v_\kappa = \frac{1}{2}\mathbf{z}_{k+\kappa}^T \, \bar{\mathbf{P}} \, \mathbf{z}_{k+\kappa}$ for $\kappa = 0,1,\ldots, \eta-1$.
+ where $\bm{\Lambda} = [{\bf o}_0,{\bf o}_1,\ldots,{\bf o}_{\eta-1}]^T \in \mathbb{R}^{\eta\times 10}$ with ${\bf o}_\kappa = \tilde{\bm{\rho}}^T({\bf z}_{k+\kappa, k+\kappa+1}) \in \mathbb{R}^{1\times 15}$ and ${\bf v} =[v_0,v_1,\ldots,v_{\eta-1}]^T \in \mathbb{R}^{\eta}$ with $v_\kappa = \frac{1}{2}\mathbf{z}_{k+\kappa}^T \, \bar{\mathbf{P}} \, \mathbf{z}_{k+\kappa}$ for $\kappa = 0,1,\ldots, \eta-1$.
 %
@@
 	\bibliographystyle{IEEEtran}
- \bibliography{bib/refsSuruzWeb,bib/refsBooksTRTheses,bib/refsReinforcementLearningADP}
 \bibliography{bib/refsSuruzWeb,bib/refsMultiAgent,bib/refsRoboticsJournals,bib/refsRoboticsConferences,bib/refsGenericControl,bib/refsBooksTRTheses,bib/refsReinforcementLearningADP,bib/refsRL-Keshtkar}

### 2020-06-30 paperMIC2020/paperIEEE-MIC2020-V1.tex
Problem setting section has been rewritten

@@
  where $\omega_k = \frac{\nu_k}{L}\tan\gamma_k$ is the angular velocity of the robot's center $(x_k,y_k).$ Let us define the error vector as 
- \begin{multline}
+ \begin{align}
      \label{eq:stateError}
-   \mathbf{e}_k = [\rho_k,\tilde\theta_k]^T =
-   % [\sqrt{x_e^2+y_e^2},\tilde{\theta_k}]^T = \\
-   \begin{bmatrix}
-     \sqrt{(x_k^{[d]} - x_k - d\cos\theta_k^{'})^2+
-     (y_k^{[d]} - y_k - d\sin\theta_k^{'})^2},
-     \theta_k^{'} - \theta_k
-   \end{bmatrix},
- \end{multline}
+   \mathbf{e}_k = [\rho_k,\tilde\theta_k]^T=[\sqrt{\tilde{x}_k^2+\tilde{y}_k^2},\tilde{\theta_k}]^T% = \\
+   % \begin{bmatrix}
+   %   \sqrt{(x_k^{[d]} - x_k - d\cos\theta_k^{'})^2+
+   %   (y_k^{[d]} - y_k - d\sin\theta_k^{'})^2},
+   %   \theta_k^{'} - \theta_k
+   % \end{bmatrix},
+ \end{align}
 % 
- where $\theta_k^{'} = \mathrm{atan2}\left(y_k^{[d]}-y_k, x_k^{[d]}-x_k\right)$ and ${\rho_k}$ the Euclidean distance at time instant $k$ as shown in Fig.~\ref{fig:leaderFollowerSetup}.
-The control problem can then be formally stated as follows: Find $\nu_k$ and $\gamma_k$ such that ${\bf e}_k\to {\bf 0}$ as  $k\to\infty$ subject to~\eqref{eq:robotModelDT}~and~\eqref{eq:leaderDT}.
+ where $\theta_k^{'} = \mathrm{atan2}\left(y_k^{[d]}-y_k, x_k^{[d]}-x_k\right)$
+ and ${\rho_k} =\sqrt{\tilde{x}_k^2+\tilde{y}_k^2} $ is the Euclidean distance at time instant $k$ as shown in Fig.~\ref{fig:leaderFollowerSetup} with $\tilde{x}_k = x_k^{[d]} - x_k - d\cos\theta_k^{'},$ $\tilde{y}_k = y_k^{[d]} - y_k - d\sin\theta_k^{'},$ and $\tilde{\theta}_k = \theta_k^{'} - \theta_k.$ The control problem can then be formally stated as follows: Find $\nu_k$ and $\gamma_k$ such that ${\bf e}_k\to {\bf 0}$ as  $k\to\infty$ subject to~\eqref{eq:robotModelDT}~and~\eqref{eq:leaderDT}.
 

### 2020-07-01 paperMIC2020/paperIEEE-MIC2020-V1.tex
Modified RL section but need more work

@@
 
-\section{Proposed actor-critic RL Approach}
+\section{Model-Free Reinforcement Learning Approach}
 \todo[inline]{Needs to be rewritten}
-
  \label{sec:RLSolution}
 
- The solution of the leader-follower formation problem is realized using a reinforcement learning approach.
-It employs model-free strategies for solving a temporal difference equation developed herein.
-This solution is equivalent to solving the underlying Bellman optimality equation for  the dynamical error model~\eqref{eq:stateError}.
-The relative importance of the states in the error vector ${\bf e}_k$ and the control decisions (linear velocity and steering angle) of the follower-robot are evaluated using the  performance (cost) index: %
+ Reinforcement learning is a promising  machine learning technique that is widely used in solving problems of many cyber-physical systems that pertain to the goal-directed learning from interaction~\cite{sutton2020reinforcement}.
+In this paper, tracking a mobile target using a wheeled mobile robot is formulated as a reinforcement learning problem, where the goal of the robot is to track the trajectory of the target while maintaining the safe-distance $d>0.$ The RL solution employed in the current problem leverages Bellman's principle of optimality to decide on the appropriate control actions (actuator commands) for the robot to track the position trajectory of the target.
+The relative importance of the states in the error vector ${\bf e}_k$ and the control decisions (linear velocity $\nu_k$ and steering angle $\gamma_k$) of the robot are evaluated using the  performance (cost) index: %
  \begin{align}
@@
  \end{align}    
- where ${\bf Q}\in\mathbb{R}^{2\times 2}$ and ${\bf R}\in\mathbb{R}^{2\times 2}$ are symmetric positive definite weighting matrices.
-The objective of the optimization problem, following~\cite{Lewis2013-Reinforcement}, is to find an optimal sequence of control polices $\{\mathbf{u}^*_k\}_{k=0}^\infty$ that minimizes the cost index $J$ along the state-trajectories~\eqref{eq:leaderDT}~and~\eqref{eq:robotModel1-DT}.
+ where ${\bf Q}\in\mathbb{R}^{2\times 2}$ and ${\bf R}\in\mathbb{R}^{2\times 2}$ are symmetric positive definite weighting matrices, and ${\bf u}_k^T = [\nu_k,\gamma_k]$ is the control input vector.
+The objective of the optimization problem, following~\cite{Lewis2013-Reinforcement}, is to find an optimal sequence of control polices $\{\mathbf{u}^*_k\}_{k=0}^\infty$ that minimizes the cost index $J$ along the state-trajectories~\eqref{eq:leaderDT}~and~\eqref{eq:robotModelDT}.
 Motivated by the structure of the convex quadratic cost functional~\eqref{eq:costFunctional}, let the solution of the tracking control problem employ the value function $V({\bf e}_k,{\bf u}_k)$ defined by %
@@
  \begin{align}
- \hat{V}(\mathbf{z}_k) = \frac{1}{2}\mathbf{z}_k^T\, \bar{\mathbf{P}}\, \mathbf{z}_k + \hat{V}(\mathbf{z}_{k+1}),
+   V(\mathbf{z}_k) = \frac{1}{2}\mathbf{z}_k^T\, \bar{\mathbf{P}}\, \mathbf{z}_k + V(\mathbf{z}_{k+1}),
  \label{eq:valueFunctionEstimated}
@@
  where $\mathbf{z}_k = \left[\mathbf{e}_k ,\mathbf{u}_k\right]^T\in\mathbb{R}^4,$ $V\left(\mathbf{e}_k,\mathbf{u}_k\right) \approx \hat{V}(\mathbf{z}_k),$  and $\bar{\mathbf{P}}$ is a symmetric block-diagonal matrix formed using $(\mathbf{Q},\mathbf{R}),$~\textit{i.e.,~}$\bar{\mathbf{P}} = \mathrm{blockdiag}(\mathbf{Q},\mathbf{R}).$ %
- The approximation of the solving value function $\hat{V}(\mathbf{z}_k)$ employs a quadratic form so that $\hat{V}(\mathbf{z}_k)=\frac{1}{2}\mathbf{z}_k^T\, \mathbf{P}\, \mathbf{z}_k,$ where $\mathbf{P}\in\mathbb{R}^{4\times 4}$ is a positive definite matrix.
-Hence, the optimal control strategy $\mathbf{u}_k^*$ can be expressed as follows %
+ The approximation of the solving value function $\hat{V}(\mathbf{z}_k)$ employs a quadratic form so that $\hat{V}(\mathbf{z}_k)=\frac{1}{2}\mathbf{z}_k^T\, \mathbf{P}\, \mathbf{z}_k,$ for some positive definite matrix  $\mathbf{P}\in\mathbb{R}^{4\times 4}.$ The optimal control input ${\bf u}_k*$ is then determined by setting $\frac{\partial\hat{V}({\bf z}_k)}{\partial{\bf u}_k} = 0,$ which yields %
  %
@@
  \label{eq:modelFreePolicy}    
- \mathbf{u}_k^* = \argmin_{\mathbf{u}_k}\left[\hat{V}(\mathbf{z}_k)\right] = -\,  \mathbf{P}_{uu}^{-1}\, \mathbf{P}_{ue}\, \mathbf{e}_k,
+ \mathbf{u}_k^* = -\,  \mathbf{P}_{uu}^{-1}\, \mathbf{P}_{ue}\, \mathbf{e}_k,
  \end{align}
  %
- where $\mathbf{P}_{uu}$ and $\mathbf{P}_{ue}$ are sub-blocks of symmetric matrix $\mathbf{P}.$ %   
- %
- \todo[inline]{The following paragraph and the NN structure needs to be rewritten}
-A two-step solution mechanism that is based on policy iteration is employed to solve the temporal difference equation~\eqref{eq:valueFunctionEstimated} using the policy~\eqref{eq:modelFreePolicy}.
-First, the adaptive critics are used to approximate the solving value function $\hat V(\cdot)$ using a multi-layer critic neural network as shown in Fig.~\ref{fig:nnCritic}.
-%
-
+ where $\mathbf{P}_{uu}$ and $\mathbf{P}_{ue}$ are sub-blocks of symmetric matrix $\mathbf{P}.$ The proposed approach approximates the block matrix ${\bf P}$ by following a two-step solution mechanism based on policy iteration method~\cite{sutton2020reinforcement}, which in turn approximates the value function~$\hat V(\cdot)$ given by ~\eqref{eq:valueFunctionEstimated}.
+First, a multi-layer critic neural network shown in Fig.~\ref{fig:nnCritic} is used to estimate the value function, $\hat V({\bf z}_k).$
 \begin{figure}

### 2020-07-01 paperMIC2020/paperIEEE-MIC2020-V1.tex
added matlab simulation

@@
 In all of these mentioned applications a fleet of robot i.e agents interact with each other to achieve a certain goal.
-Leader-Follower or dynamic target tracking problem has recieved an extensive amount of study and research in the world of cooperative control theory due to it's wide promising applications such as search and rescure missions, wildlife monitoring and survillance to name a few .
-In a typical leader follower formation a number of robots referred to as followers apply local control actions to follow leader's robots in a specific predefined path such as \hl {cyclic, circular motion and time varying communication topologies.} \hl {limitations of other methods} many control methods were proposed however they have had the following limitations:
+Leader-Follower or dynamic target tracking problem has recieved an extensive amount of study and research in the world of cooperative control theory due to it's wide promising applications.
+In a typical leader follower formation a number of robots referred to as followers apply local control actions to follow leader's robots in a specific predefined path such as \hl {cyclic, circular motion and time varying communication topologies.} many control methods were proposed however they have had the following limitations:
 \\(1) a static leader/target is used.

### 2020-07-01 paperMIC2020/matlabsim/mainLF_OdometricLocalizationV9.m

@@ -1,0 +1,532 @@
+% Odometric localization or dead reckoning%   Script for simulating mobile robot.
+%Edited by AMR Elhussein on May, 29,2020.
+%gradient descent Appraoch, three cases comined fixed point, horzintal and inclined line, 
+%converged Example
+function mainLF_OdometricLocalizationV7
+
+% Created by S. Miah on Nov. 03, 2015.
+%edited by AMR Elhussein on Aug, 30,2019.
+close all
+clear all
+clc
+
+disp('Please wait while the simulation runs ...');
+
+% ---------------------
+% SIMULATION PARAMETERS
+% ---------------------
+
+% Simulation time
+t0 = 0; tf = 60; % initial and final simulation time [s]
+T = 0.001;  % Sampling time [s]
+tsteps = ceil((tf-t0)/T); % number of time steps
+dt = T*(0:tsteps)'; % Discrete time vector (include time t0 to plot initial state too)
+
+d = 0; %[m] safe distance
+%ROBOT PARAMETERS
+%==========================================================================
+l = 0.381; % [m]
+rad = 0.0925; % [m] radius
+%==========================================================================
+
+
+
+% dimension of system;
+N = 2;  % state vector dimension
+M = 2;  % input vector dimension
+
+
+% Leader's initial position
+pLeaderInit = [5;1]+rand(2,1); %[m]
+pLeaderTheta= 0; %[rad]
+
+QD(1,:) = [pLeaderInit' pLeaderTheta];
+QDinit = QD(1,:);
+%Leader's velocity 
+vLeader = 0.1; % [m/s]
+uLeader=[vLeader pLeaderTheta];
+
+% Follower robot initialization% 
+qp = [0;0]; % [m] Follower robot's position
+qTheta = 0 ;% [rad] Follower robot's orientation 
+ qInit = [qp',qTheta] ;%+ rand(1,3); % row vector
+vMax = 2; % [m/s] Follower's maximum linear speed 
+
+Q(1,:) = qInit;
+
+% ----------------------
+% RUN SIMULATION 
+% ----------------------
+
+% Run the true model
+q(1,:) = qInit';
[…]

### 2020-07-01 paperMIC2020/paperIEEE-MIC2020-V1.tex
added figure

@@
 
-Over the past years mobile robots has been used in several applications in commercial and military sectors such as surveillance, search and rescue missions,coverage optimization, cooperative localization and dynamic target tracking tasks \cite{kolling2006},\cite{Encarnacao2001},\cite{Ju2001}.
+Over the past years mobile robots has been used in several applications in commercial and military sectors such as surveillance, search and rescue missions,coverage optimization, cooperative localization and dynamic target tracking tasks to name a few \cite{kolling2006},\cite{Encarnacao2001},\cite{Ju2001}.
 In all of these mentioned applications a fleet of robot i.e agents interact with each other to achieve a certain goal.
-Leader-Follower or dynamic target tracking problem has recieved an extensive amount of study and research in the world of cooperative control theory due to it's wide promising applications.
-In a typical leader follower formation a number of robots referred to as followers apply local control actions to follow leader's robots in a specific predefined path such as \hl {cyclic, circular motion and time varying communication topologies.} many control methods were proposed however they have had the following limitations:
+Leader-Follower or dynamic target tracking problem has recieved an extensive amount of study and research in the world of cooperative control theory due to it's promising applications in research and industry.
+In a typical target tracking formation a number of robots referred to as followers apply local control actions to follow a target in a specific predefined path such as \hl {cyclic, circular motion and time varying communication topologies.} many control methods were proposed however they have had the following limitations:
 \\(1) a static leader/target is used.

### 2020-07-01 paperMIC2020/paperIEEE-MIC2020-V1.tex
Update RL section

--- 2020-07-01 paperMIC2020/paperIEEE-MIC2020-V1.tex
@@
 \section{Model-Free Reinforcement Learning Approach}
-\todo[inline]{Needs to be rewritten}
  \label{sec:RLSolution}
@@
  %
- Applying Bellman's optimality principle yields the optimal control policies ${\bf u}_k^*,~k\ge 0,$ such that~\cite{Lewis2012} %
+ Following Bellman's optimality principle yields the optimal control policies ${\bf u}_k^*,~k\ge 0,$ such that~\cite{Lewis2012} %
  %
@@
 
-            \foreach \m/\l [count=\y] in {1,2,missing,3}
+            \foreach \m/\l [count=\y] in {1,2,3,4}
             \node [input neuron/.try, neuron \m/.try] (input-\m) at (0,2.5-\y) {};
@@
 
-            \foreach \l [count=\i] in {1,2,n+m}
+            \foreach \l [count=\i] in {1,2,3,4}
             \draw [<-] (input-\i) -- ++(-1,0)
@@
 
-            \foreach \i in {1,...,3}
+            \foreach \i in {1,...,4}
             \foreach \j in {1,...,4}
@@
 
-            \node [align=center, below] at (3,-2.5) {Weights \\ $\boldsymbol{\omega}$};
-            \draw[->,ultra thick](3,-2.5) -- (3,1.4);
+            \node [align=center, below] at (3,-2.5) {Weights \\ $\boldsymbol{\omega}_c$};
+            \draw[-stealth,ultra thick](3,-2.5) to[bend left] (3,1.4);
 
@@
     }
-    \caption{Critic neural network structure for approximating value function.}
+    \caption{Multi-layer critic neural network for approximating value function $V({\bf z}_k).$}
     \label{fig:nnCritic}
@@
  %      
- Second, the policy evaluation step of this process updates the critic weights $\bm{\omega}$ in real-time without acquiring any formation about the dynamics of the leader or follower dynamical systems  (the calculation mechanism of the critic weighs $\boldsymbol{\omega}$ is explained later on).
-This is done to search for a strictly better policy.
-%
- %
-
-% Note that, the policy iteration computational setup rearranges the temporal difference expression~\eqref{eq:valueFunctionEstimated} such that %
+ Second, the policy evaluation step that follows is utilized to update the critic weights $\bm{\omega}_c$ in real-time regardless of the mathematical models of the robot and the target.
+This step is aimed to search for a strictly better policy using the updated critic weights $\bm{\omega}_c.$ Note that $\hat V({\bf z}_k)$ can also be written using temporal difference form as $\hat V({\bf z}_k) = \mathbf{z}_k^T\, \bar{\mathbf{P}}\, \mathbf{z}_k + \hat V({\bf z}_{k+1}),$ which is described by
  %
@@
  %
- This equation is utilized repeatedly in order to evaluate a certain policy during at least $\eta\ge \bar n, \bar n= (2+2)(2+2+1)/2$ evaluation steps (i.e., the lowest evaluation interval spans $k$ to $k+\bar n$ calculation samples) in order to update the critic weights vector  $\boldsymbol{\omega}=\mathrm{vec}(\mathbf{P}),$ which consists of connection weights between the neurons of the hidden layer and the output layer of the critic neural network shown in Fig.~\eqref{fig:nnCritic}.
-The operator $\mathrm{vec}(\mathbf{P})$ forms the columns of the $\mathbf{P}$ matrix into a column vector $\mathbf{\omega}$ of dimension $\bar{n}=15$ since the matrix $\mathbf{P}$ is a symmetric matrix.
+ Equation~\eqref{eq:const} is evaluated repeatedly to collect data online for at least $\eta\ge \bar n, \bar n= (2+2)(2+2+1)/2 = 10$ evaluation steps due to the fact that the matrix ${\bf P}$ is positive definite and symmetric.
+The strictly better policy ${\bf P},$ is determined every $\eta$ time/evaluation steps.
+To find the better policy in terms of matrix ${\bf P},$ let us define the vector $\boldsymbol{\omega}=\mathrm{vec}(\mathbf{P})\in\mathbb{R}^{16},$ which is formed by stacking columns of ${\bf P}$ matrix.
+However, since ${\bf P}$ is symmetric, we only need determine the weight $\bm{\omega}_c\in\mathbb{R}^{\bar n}$ using the critic neural network shown in Fig.~\eqref{fig:nnCritic}.
 The left hand side of~\eqref{eq:const} is expressed using the following critic approximation form %
  %
- $$\hat{V}(\mathbf{z}_k)-\hat{V}(\mathbf{z}_{k+1})=\boldsymbol{\omega}^T\tilde{\bm{\rho}}(\mathbf{z}_{k,k+1}),$$
+ $$\hat{V}(\mathbf{z}_k)-\hat{V}(\mathbf{z}_{k+1})=\boldsymbol{\omega}_c^T\tilde{\bm{\rho}}(\mathbf{z}_{k,k+1}),$$
  %
- where $\tilde{\bm{\rho}}(\mathbf{z}_{k,k+1})=\bm{\rho}(\mathbf{z}_k)-\bm{\rho}(\mathbf{z}_{k+1}) \in \mathbb{R}^{10 \times 1}, \, \bm{\rho}(\mathbf{z}_k)=\left(\mathbf{z}^q_k\otimes\mathbf{z}^h_k\right)$ $(q=1,\dots, 5, \,\, h=q,\dots,5),$ and $\boldsymbol{\omega}^T = [0.5 \, P^{11},P^{12},P^{13},P^{14},  \, 0.5 \, P^{22}, P^{23},P^{24},$ $\,0.5 \, P^{33}, P^{34},\,0.5 \ P^{44}, ]^T \in \mathbb{R}^{1\times 15}$ ($P^{ij}$ is the $ij^{th}$ entry of matrix $\mathbf{P}$).
+ where $\tilde{\bm{\rho}}(\mathbf{z}_{k,k+1})=\bm{\rho}(\mathbf{z}_k)-\bm{\rho}(\mathbf{z}_{k+1}) \in \mathbb{R}^{10 \times 1}, \, \bm{\rho}(\mathbf{z}_k)=\left(\mathbf{z}_k\otimes\mathbf{z}_k\right)$, which is a Kronecker product that generates the basis function vector with components $z_{k,1}^2,$ $z_{k,1}z_{k,2},$ $z_{k,1}z_{k,3},$ $z_{k,1}z_{k,4},$ $z_{k,2}^2,$ $z_{k,2}z_{k,3},$ $z_{k,2}z_{k,4},$ $z_{k,3}^2,$ $z_{k,3}z_{k,4},$ and $z_{k,4}^2.$ Note that the critic weight $\bm{\omega}_c$ is related to the policy matrix ${\bf P}$ as  $\boldsymbol{\omega}_c^T = [0.5 \, P^{11},P^{12},P^{13},P^{14},  \, 0.5 \, P^{22}, P^{23},P^{24},$ $\,0.5 \, P^{33}, P^{34},\,0.5 \ P^{44}, ]^T \in \mathbb{R}^{1\times 10}$ with $P^{ij}$ being the $ij^{th}$ entry of matrix $\mathbf{P}.$ %
  %
- %
- The critic weights $\boldsymbol{\omega}$ are updated using a gradient descent approach, where the tuning error $\varepsilon_k$ at each computational instance $k$ follows $\varepsilon_k =\boldsymbol{\omega}^T\tilde{\bm{\rho}}(\mathbf{z}_{k,k+1})-{v}_k,$ where $v_\kappa = \frac{1}{2}\mathbf{z}_{k}^T \, \bar{\mathbf{P}} \, \mathbf{z}_{k}$.
-As detailed earlier, it is required to perform at least $\eta \ge \bar n$ evaluation steps before updating the critic weights $\boldsymbol{\omega}$ (i.e., finding the new improved policy).
-Hence, it is required to minimize the sum of square errors such that %
+ Here, the critic weights $\boldsymbol{\omega}_c$ are updated using a gradient descent update rule.
+The tuning error $\varepsilon_k$ at each computational instance $k$ is given by $\varepsilon_k =\boldsymbol{\omega}_c^T\tilde{\bm{\rho}}(\mathbf{z}_{k,k+1})-{v}_k,$ where $v_\kappa = \frac{1}{2}\mathbf{z}_{k}^T \, \bar{\mathbf{P}} \, \mathbf{z}_{k}$.
+The error data $\varepsilon_k$ is collected online for at least  $\eta \ge \bar n$ evaluation steps before updating the critic weights $\boldsymbol{\omega}_c$ that is used to determine the improved policy ${\bf P}.$ The sum of squared tuning errors is given by
  %
  \begin{multline*}
-   \delta_c =\sum_{\kappa=0}^{\eta-1}\frac{1}{2}(\boldsymbol{\omega}^T\tilde{\bm{\rho}}(\mathbf{z}_{k+\kappa,k+\kappa+1})-{v}_{k+\kappa})^2 = \frac{1}{2}\| \mathbf{v} - \bm{\Lambda}\bm{\omega}\|^2\\
+   \delta_c =\sum_{\kappa=0}^{\eta-1}\frac{1}{2}\varepsilon_{k+\kappa}^2=\sum_{\kappa=0}^{\eta-1}\frac{1}{2}(\boldsymbol{\omega}^T\tilde{\bm{\rho}}(\mathbf{z}_{k+\kappa,k+\kappa+1})-{v}_{k+\kappa})^2 = \frac{1}{2}\| \mathbf{v} - \bm{\Lambda}\bm{\omega}\|^2\\
    =\frac{1}{2}\left(\mathbf{v} - \bm{\Lambda}\bm{\omega}\right)^T \left(\mathbf{v} - \bm{\Lambda}\bm{\omega}\right), 
  \end{multline*}
- where $\bm{\Lambda} = [{\bf o}_0,{\bf o}_1,\ldots,{\bf o}_{\eta-1}]^T \in \mathbb{R}^{\eta\times 10}$ with ${\bf o}_\kappa = \tilde{\bm{\rho}}^T({\bf z}_{k+\kappa, k+\kappa+1}) \in \mathbb{R}^{1\times 15}$ and ${\bf v} =[v_0,v_1,\ldots,v_{\eta-1}]^T \in \mathbb{R}^{\eta}$ with $v_\kappa = \frac{1}{2}\mathbf{z}_{k+\kappa}^T \, \bar{\mathbf{P}} \, \mathbf{z}_{k+\kappa}$ for $\kappa = 0,1,\ldots, \eta-1$.
+ where $\bm{\Lambda} = [{\bf o}_0,{\bf o}_1,\ldots,{\bf o}_{\eta-1}]^T \in \mathbb{R}^{\eta\times 10}$ with ${\bf o}_\kappa = \tilde{\bm{\rho}}^T({\bf z}_{k+\kappa, k+\kappa+1}) \in \mathbb{R}^{1\times 10}$ and ${\bf v} =[v_0,v_1,\ldots,v_{\eta-1}]^T \in \mathbb{R}^{\eta}$ with $v_\kappa = \frac{1}{2}\mathbf{z}_{k+\kappa}^T \, \bar{\mathbf{P}} \, \mathbf{z}_{k+\kappa}$ for $\kappa = 0,1,\ldots, \eta-1$.
 %
- Therefore, the update law of the critic weights using the gradient decent approach for at least $\bar n$ samples is given by %
+ The sum of squared error $\delta_c$ can be minimized by adapting the critic weight using the gradient decent approach for at least $\bar n$ data samples as 
  \begin{multline}
-   \bm{\omega}^{[r+1]} = \bm{\omega}^{[r]} - \ell_c\frac{\partial\delta_c}{\partial \bm{\omega}} = \bm{\omega}^{[r]} - \ell_c\left(-\bm{\Lambda}^T\mathbf{v} + \bm{\Lambda}^T \bm{\Lambda}\bm{\omega}^{[r]}\right)\\
- =\bm{\omega}^{[r]} - \ell_c \bm{\Lambda}^T\left(\bm{\Lambda}\bm{\omega}^{[r]}-\mathbf{v}\right), 
+   \bm{\omega}_c^{[r+1]} = \bm{\omega}_c^{[r]} - \ell_c\frac{\partial\delta_c}{\partial \bm{\omega}} = \bm{\omega}_c^{[r]} - \ell_c\left(-\bm{\Lambda}^T\mathbf{v} + \bm{\Lambda}^T \bm{\Lambda}\bm{\omega}_c^{[r]}\right)\\
+ =\bm{\omega}_c^{[r]} - \ell_c \bm{\Lambda}^T\left(\bm{\Lambda}\bm{\omega}_c^{[r]}-\mathbf{v}\right), 
  \label{eq:criticWeights}
@@
  %
- where $0<\ell_c<1$ is a critic learning rate and $r$ is the  update index of the critic weights.
+ where $0<\ell_c<1$ is a critic learning rate and $r$ is known as iteration index for updating the policy. The updated critic weights can be used to reconstruct the policy matrix ${\bf P}$ as
 
-% The newly computed critic weights $\boldsymbol{\omega}$ are used to reconstruct the matrix ${\bf P}$ (i.e., updating the solving value function and hence calculating the associated policy) such that
- %
  \begin{center}
  ${\bf P}=\begin{bmatrix} 
- 2\,\omega^{1}    & \omega^{2}      & \omega^{3}       & \omega^{4}        \\ 
- \omega^{2}       &2\, \omega^{5}   & \omega^{6}       & \omega^{7}        \\
- \omega^{3}       & \omega^{6}      &2\, \omega^{8}   & \omega^{9}   \\   
- \omega^{4}       & \omega^{7}      & \omega^{9}      & 2\,\omega^{10}      
+ 2\,\omega^{[1]}    & \omega^{[2]}      & \omega^{[3]}       & \omega^{[4]}        \\ 
+ \omega^{[2]}       &2\, \omega^{[5]}   & \omega^{[6]}       & \omega^{[7]}        \\
+ \omega^{[3]}       & \omega^{[6]}      &2\, \omega^{[8]}   & \omega^{[9]}   \\   
+ \omega^{[4]}       & \omega^{[7]}      & \omega^{[9]}      & 2\,\omega^{[10]}      
  \end{bmatrix}\in \mathbb{R}^{4\times 4},$
@@
  %
- where $\omega^{i}$ is the $i^{th}$ entry of the weight vector $\bm{\omega}.$ 
- \todo[inline]{merge the actor weights discussion with the rest}
- The critic wegihts are then used to update the actor weights which maps the state error to the desired ploicy (control actions) at every time step $t$ with the following equation:
+ where $\omega^{[i]}$ is the $i^{th}$ entry of the weight vector $\bm{\omega}_c.$
+
+ The critic weights are then used to update the actor weights $W_a\mathbb{R}^{n\times m}$ (here $n=2$ and $m=2$) which maps the state error to the desired policy (control actions) as  at every time step $t$ with the following equation:
  \begin{align}
  \label{eq:actorWeightsPolicy}    
- \mathbf{u}_k  =  \mathbf{\omega_a^{T}} \mathbf{e}_k
+ \mathbf{u}_k  =  {\bf W}_a^T \mathbf{e}_k
  \end{align}
+%
+ Equation~\eqref{eq:actorWeightsPolicy} is realized using a multi-layer actor neural network shown in Fig.~
+
  Applying a similar gradient descent approach as with the critic weights the actor weights are updated as follows:

### 2020-07-01 paperMIC2020/paperIEEE-MIC2020-V1.tex

@@
 
-Over the past years mobile robots has been used in several applications in commercial and military sectors such as surveillance, search and rescue missions,coverage optimization, cooperative localization and dynamic target tracking tasks \cite{kolling2006},\cite{Encarnacao2001},\cite{Ju2001}.
+Over the past years mobile robots has been used in several applications in commercial and military sectors such as surveillance, search and rescue missions,coverage optimization, cooperative localization and dynamic target tracking tasks to name a few \cite{kolling2006},\cite{Encarnacao2001},\cite{Ju2001}.
 In all of these mentioned applications a fleet of robot i.e agents interact with each other to achieve a certain goal.
-Leader-Follower or dynamic target tracking problem has recieved an extensive amount of study and research in the world of cooperative control theory due to it's wide promising applications such as search and rescure missions, wildlife monitoring and survillance to name a few .
-In a typical leader follower formation a number of robots referred to as followers apply local control actions to follow leader's robots in a specific predefined path such as \hl {cyclic, circular motion and time varying communication topologies.} \hl {limitations of other methods} many control methods were proposed however they have had the following limitations:
+Leader-Follower or dynamic target tracking problem has recieved an extensive amount of study and research in the world of cooperative control theory due to it's promising applications in research and industry.
+In a typical target tracking formation a number of robots referred to as followers apply local control actions to follow a target in a specific predefined path such as \hl {cyclic, circular motion and time varying communication topologies.} many control methods were proposed however they have had the following limitations:
 \\(1) a static leader/target is used.

### 2020-07-02 paperMIC2020/paperIEEE-MIC2020-V1.tex
Finished RL section

@@
  \label{eq:actorWeightsPolicy}    
- \mathbf{u}_k  =  {\bf W}_a^T \mathbf{e}_k
+ \hat{\mathbf{u}}_k  =  {\bf W}_a^T \bm{\sigma}(\mathbf{e}_k),
  \end{align}
  %
- Equation~\eqref{eq:actorWeightsPolicy} is realized using a multi-layer actor neural network shown in Fig.~
+ where ${\bf W}_a\in\mathbb{R}^{2\times n^{'}}$ is the actor weight matrix and $\bm{\sigma}:\mathbb{R}^2 \to \mathbb{R}^{n^{'}}$ is the basis function vector.
+Equation~\eqref{eq:actorWeightsPolicy} is realized using a multi-layer actor neural network shown in Fig.~\ref{fig:nnActor}.
+%
+ %
+\begin{figure}
+  \centering
+  \boxed{
+    \begin{adjustbox}{max width = 0.48\textwidth}
+      \tikzset{%
+        input neuron/.style={
+          circle,
+          fill=green!50,
+          minimum size=0.7cm
+        },
+        neuron missing/.style={
+          draw=none, 
+          scale=1,
+          fill=white,
+          text height=0.01cm,
+          execute at begin node=\color{black}$\vdots$
+        },
+      }
 
- Applying a similar gradient descent approach as with the critic weights the actor weights are updated as follows:
+      \tikzset{%
+        hidden neuron/.style={
+          circle,
+          fill=blue!50,
+          minimum size=0.7cm
+        },
+        neuron missing/.style={
+          draw=none, 
+          scale=1,
+          fill=white,
+          text height=0.01cm,
+          execute at begin node=\color{black}$\vdots$
+        },
+      }
+
+      \tikzset{%
+        output neuron/.style={
+          circle,
+          fill=red!50,
+          minimum size=0.7cm
+        },
+        neuron missing/.style={
+          draw=none, 
+          scale=1,
+          fill=white,
+          text height=0.01cm,
+          execute at begin node=\color{black}$\vdots$
+        },
+      }
+
+      \begin{tikzpicture}[x=1.5cm, y=1.5cm]
+
+        \foreach \m/\l [count=\y] in {1,2}
+        \node [input neuron/.try, neuron \m/.try] (input-\m) at (0,2.5-\y) {};
+
+        \foreach \m [count=\y] in {1,2,missing,3}
+        \node [hidden neuron/.try, neuron \m/.try ] (hidden-\m) at (2,2.5-\y*1.1) {};
+
+        \foreach \m [count=\y] in {1,2}
+        \node [output neuron/.try, neuron \m/.try] (output-\m) at (4,2.5-\y*1.2) {};
+
+        \foreach \l [count=\i] in {1,2}
+        \draw [<-] (input-\i) -- ++(-1,0)
+        node [above, midway] {$\mathbf{e}_{k,\l}$};
+
+        \foreach \l [count=\i] in {1,2,\mbox{$n^{'}$}}
+        \node [above] at (hidden-\i.north) {$\sigma_{\l}$};
+
+        \foreach \l [count=\i] in {1,2}
+        \draw [->] (output-\i) -- ++(1,0)
+        node [above, midway] {$\hat{u}_{k,\l}$};
+
+        \foreach \i in {1,...,2}
+        \foreach \j in {1,...,3}
+        \draw [->] (input-\i) -- (hidden-\j);
+
+        \foreach \i in {1,...,3}
+        \foreach \j in {1,2}
+        \draw [->] (hidden-\i) -- (output-\j);
+
+        \foreach \l [count=\x from 0] in {Input, Hidden, Ouput}
+        \node [align=center, above] at (\x*2,1.9) {\l \\ layer};
+
+        \draw[->,ultra thick]
+        (3,-1.5)node[anchor=west]{Weight~${\bf W}_a$} to[bend left] (3,1.6);
+
+      \end{tikzpicture}
+    \end{adjustbox}      
+    }
+  \caption{Actor neural network structure for approximating control input.}
+  \label{fig:nnActor}
+\end{figure}
+%
+The elements of the vector $\bm{\sigma}$ are the activation functions of the neurons in the hidden layer shown in Fig.~\ref{fig:nnActor}.
+We will need to determine the actor weight matrix ${\bf W}_a$ that minimizes the error between the estimated control inputs determined by model~\eqref{eq:actorWeightsPolicy} and the that determined by critic neural network approximation model~\eqref{eq:modelFreePolicy}.
+For that, let us define the error %
+%
 \begin{align}
-   \bm{\omega_a}^{[r+1]} = \bm{\omega}^{[r]} - \ell_a(\mathbf{u}_k-\mathbf{u}_k^*)\mathbf{e}_k, 
+  \label{eq:deltaActor}
+  \delta_a = \frac{1}{2}\|\hat{{\bf u}}_k - {\bf u}_k^*\|^2,
+\end{align}
+%
+which can be written as %
+%
+\begin{align*}
+  \delta_a = \frac{1}{2}\left( {\bf W}_a^T\bm{\sigma}({\bf e}_k) -  {\bf u}_k^*\right)^T\left( {\bf W}_a^T\bm{\sigma}({\bf e}_k) -  {\bf u}_k^*\right). 
+\end{align*}
+%
+Taking partial derivative of the above expression $\delta_a$  with respect to ${\bf W}_a$ gives %
+%
+\begin{align*}
+  \frac{\partial \delta_a}{\partial{\bf W}_a} = {\bf W}_a^T\bm{\sigma}({\bf e}_k)\bm{\sigma}^T({\bf e}_k) - {\bf u}_k^*\bm{\sigma}^T({\bf e}_k).
+\end{align*}
+%
+Therefore, actor weight matrix ${\bf W}_a$ in every policy iteration $r = 01,2,\ldots$ can be updated using the learning rule %
+%
+\begin{multline}
+  {\bf W}_a^{[r+1]} = {\bf W}_a^{[r]} - \ell_a\frac{\partial\delta_a}{\partial{\bf W}_a}\\
+  = {\bf W}_a^{[r]} - \ell_a\left( {\bf W}_a^T\bm{\sigma}({\bf e}_k)-\mathbf{u}_k^* \right)\bm{\sigma}^T({\bf e}_k), 
  \label{eq:actorWeights}
- \end{align}
- where $\ell$ is the actor learning rate. 
- \\
- The complete policy iteration solution process for the leader-follower problem is detailed out in Algorithm \ref{alg:ModelFreeTracking}. %
+ \end{multline}
+ where $\ell_a$ is the actor learning rate.  The complete policy iteration solution process for the leader-follower problem is detailed out in Algorithm \ref{alg:ModelFreeTracking}. %
  %
@@
  \end{algorithm2e}    
+ %
+For clarity, number of hidden neurons chosen in the actor neural network shown in Fig.~\ref{fig:nnActor} is $n^{'} = 2$ and the basis function vector is simply $\bm{\sigma}({\bf e}_k) = {\bf e}_k.$ In the following, we provide the computer simulation results to highlight the performance of the proposed model-free trajectory tracking approach for a mobile robot in tracking a random target while maintaining a geometric safe distance $d>0.$
 

### 2020-07-03 paperMIC2020/paperIEEE-MIC2020-V1.tex
Latex file is updated and merged
fixed issues

@@
 
-\title{A Novel Model-Free Learning Approach for Dynamic Target Tracking Problem and its Validation using Virtual Robot Experimentation Platform 
+\title{A Novel Model-Free Actor-Critic  Reinforcement Learning Approach for Dynamic Target Tracking  
 %  
@@
 \begin{IEEEkeywords}
-Leader-follower formation, mobile robots, reinforcement learning, policy iteration, trajectory tracking
+target tracking, mobile robots, reinforcement learning, policy iteration, trajectory tracking
 \end{IEEEkeywords}
@@
 \label{sec:introduction}
-\todo[inline]{Need to discuss in details the limitations of previous work, we
-  can also add RL applications to robotics navigation}
 
-Tracking a random moving target using a mobile robot, for instance, is a challenging task.
+Tracking a random moving target using a mobile robot is a key problem and a fundemental feature in Autonomus robots in areas such as survillance,search and rescure missions, enviromental monitoring and household cleaning to name a few \cite{kolling2006},\cite{Encarnacao2001},\cite{Ju2001},\cite{Kitowski2012},\cite{Zhang2013}.
+Throught the years dynamic target tracking problem has recieved profound amount of research in academia and industry.
 This is mainly due to their inherent complex nonlinear dynamics.
-Most of the target tracking algorithms proposed in the literature either rely on A) complex mathematical models, B) simplified mathematical models, and C) nonlinear control techniques or driven by large amount of mostly offline data that leads to an overwhelming degree of computational complexity.
+Most of the target tracking algorithms proposed in the literature either rely on A) mathematical and kinematic models of both the robot and the target \cite{Huang2008}, B) the assumption that the target or it's path are static and known in prior, and C) nonlinear control techniques or driven by large amount of mostly offline data that leads to an overwhelming degree of computational complexity \cite{KD2007},\cite{Cren2017}.
+In a typical tracking problem a robot is to apply a local control actions that enables the robot to maintain a relative position and orientation from the designated target while following a certain path.It can also be applied on a fleet of robots where multiple robots mainatin a geometric configuration relative to the target\cite{Oh2015-Survey},\cite{Liu2017-Modular}.
 
-Over the past years mobile robots has been used in several applications in commercial and military sectors such as surveillance, search and rescue missions,coverage optimization, cooperative localization and dynamic target tracking tasks to name a few \cite{kolling2006},\cite{Encarnacao2001},\cite{Ju2001}.
+%Tracking a random moving target using a mobile robot, for instance, is a challenging task.
+
+%Over the past years mobile robots has been used in several applications in commercial and military sectors such as surveillance, search and rescue missions,coverage optimization, cooperative localization and dynamic target tracking tasks to name a few .
 In all of these mentioned applications a fleet of robot i.e agents interact with each other to achieve a certain goal.
 Leader-Follower or dynamic target tracking problem has recieved an extensive amount of study and research in the world of cooperative control theory due to it's promising applications in research and industry.
-In a typical target tracking formation a number of robots referred to as followers apply local control actions to follow a target in a specific predefined path such as \hl {cyclic, circular motion and time varying communication topologies.} many control methods were proposed however they have had the following limitations:
-\\(1) a static leader/target is used.
-\\(2) the leade/target's location or dynamic model is predetermined.  
-\\(3) expensive hardware platforms are used to achieve the mobile target tracking.
+In a typical target tracking formation a number of robots referred to as followers apply local control actions to follow a target in a specific predefined path such as \hl {cyclic, circular motion and time varying communication topologies.}
 
-The main contribution of this work is the development of a model-free learning approach to control the follower robot by which it overcome many of the limitations mentiond above as it does not rely on any prior information of the mathmetical model or the dynamic model.
-The steering angle and the linear speed of the follower robot are determined by collecting the position and orientation of both the leader and the follower.
+Reinforcement learning (RL) is an emerging field of machine learning which refers to a set of algorithms and techniques in which agent learn by interacting with the enviroment and generates it's own set of data.
+Reinorcement learning has long been applied on games and simulated enviroments but it has recently extended to robots in real world applications such as localization and mapping,area coverage, path planning and obstacle avoidance \cite{kober2013reinforcement},\cite{smart2002},\cite{michels2005},\cite{adekunle2016}.
+
+In this paper we develop a model-free actor-critic learning  approach to control a non-holonomic wheeled mobile robot.The proposed method offers many advantages over other methods mentioned in the litreature such as being completely model free and does not require any knowledge of the mathemtaical model of the robot or the moving target and without the need for large computational power.
+The steering angle and the linear speed of the robot referred to as the policy are determined by collecting the position and orientation of both the target and the robot.
 This set of information is gathered online over a finite period of time.
-The optimal control actions are then generated by utilizing Bellman's principal of optimality which acts as model free-reinfocment learning approach that allows the follower robot to follow the path of the leader while avoiding collision by maintaining a safe distance.
-In this paper the proposed algorithm is further validated using a commercially available robot simulator, CoppeliaSim.
-This paper acts as first milestone in generalizing the algorithm to solve more sophisticated problem such as coverage and mapping.
-\hl{cite area coverage papers}
+The optimal control actions are then generated by utilizing Bellman's principal of optimality which acts as model free-reinfocment learning approach that allows the  robot to follow the path of the target while avoiding collision by maintaining a safe distance.
+Here we extend the work proposed by authors in \cite{miah2020} by incorporating actor neural network along with critic network to find optimal control policy for the trajectory tracking problem.
+This work acts as first milestone in generalizing the algorithm to solve more sophisticated problem such as coverage and mapping.
+
 The rest of the paper is orgnized as follows.
-Section II lays down the problem setting of the leader follower problem and mathemetical models of the robots and the state error.
-The model free actor-critic reinforcment learning and its key steps are described in section III.Section IV illustrates computer simulations for different secnarios that reflects the effectivness of the proposed method followed by conlusion and future work presented in section V.
+Section II lays down the problem setting of the dynamic target tracking problem and mathemetical models of the robot and the state error.
+The model free actor-critic reinforcment learning algorithm and all the mathemetical equations are detailed in section III.Section IV illustrates computer simulations for different secnarios that reflects the effectivness of the proposed method followed by conlusion and future work presented in section V.
 
@@
      \label{eq:stateError}
-   \mathbf{e}_k = [\rho_k,\tilde\theta_k]^T=[\sqrt{\tilde{x}_k^2+\tilde{y}_k^2},\tilde{\theta_k}]^T% = \\
+   \mathbf{e}_k = [\tilde{\rho_k},\tilde\theta_k]^T=[\sqrt{\tilde{x}_k^2+\tilde{y}_k^2},\tilde{\theta_k}]^T% = \\
    % \begin{bmatrix}
@@
  %
- \begin{multline*}
-   \delta_c =\sum_{\kappa=0}^{\eta-1}\frac{1}{2}\varepsilon_{k+\kappa}^2=\sum_{\kappa=0}^{\eta-1}\frac{1}{2}(\boldsymbol{\omega}^T\tilde{\bm{\rho}}(\mathbf{z}_{k+\kappa,k+\kappa+1})-{v}_{k+\kappa})^2 = \frac{1}{2}\| \mathbf{v} - \bm{\Lambda}\bm{\omega}\|^2\\
-   =\frac{1}{2}\left(\mathbf{v} - \bm{\Lambda}\bm{\omega}\right)^T \left(\mathbf{v} - \bm{\Lambda}\bm{\omega}\right), 
- \end{multline*}
+ \begin{align}
+   \delta_c =\sum_{\kappa=0}^{\eta-1}\frac{1}{2}\varepsilon_{k+\kappa}^2 &=\sum_{\kappa=0}^{\eta-1}\frac{1}{2}(\boldsymbol{\omega_c}^T\tilde{\bm{\rho}}(\mathbf{z}_{k+\kappa,k+\kappa+1})-{v}_{k+\kappa})^2 \nonumber \\
+   	&=\frac{1}{2}\| \mathbf{v} - \bm{\Lambda}\bm{\omega_c}\|^2 \nonumber \\
+   &=\frac{1}{2}\left(\mathbf{v} - \bm{\Lambda}\bm{\omega_c}\right)^T \left(\mathbf{v} - \bm{\Lambda}\bm{\omega_c}\right), 
+ \end{align}
  where $\bm{\Lambda} = [{\bf o}_0,{\bf o}_1,\ldots,{\bf o}_{\eta-1}]^T \in \mathbb{R}^{\eta\times 10}$ with ${\bf o}_\kappa = \tilde{\bm{\rho}}^T({\bf z}_{k+\kappa, k+\kappa+1}) \in \mathbb{R}^{1\times 10}$ and ${\bf v} =[v_0,v_1,\ldots,v_{\eta-1}]^T \in \mathbb{R}^{\eta}$ with $v_\kappa = \frac{1}{2}\mathbf{z}_{k+\kappa}^T \, \bar{\mathbf{P}} \, \mathbf{z}_{k+\kappa}$ for $\kappa = 0,1,\ldots, \eta-1$.
@@
  \begin{multline}
-   \bm{\omega}_c^{[r+1]} = \bm{\omega}_c^{[r]} - \ell_c\frac{\partial\delta_c}{\partial \bm{\omega}} = \bm{\omega}_c^{[r]} - \ell_c\left(-\bm{\Lambda}^T\mathbf{v} + \bm{\Lambda}^T \bm{\Lambda}\bm{\omega}_c^{[r]}\right)\\
+   \bm{\omega}_c^{[r+1]} = \bm{\omega}_c^{[r]} - \ell_c\frac{\partial\delta_c}{\partial \bm{\omega_c}} = \bm{\omega}_c^{[r]} - \ell_c\left(-\bm{\Lambda}^T\mathbf{v} + \bm{\Lambda}^T \bm{\Lambda}\bm{\omega}_c^{[r]}\right)\\
  =\bm{\omega}_c^{[r]} - \ell_c \bm{\Lambda}^T\left(\bm{\Lambda}\bm{\omega}_c^{[r]}-\mathbf{v}\right), 
@@
  ${\bf P}=\begin{bmatrix} 
- 2\,\omega^{[1]}    & \omega^{[2]}      & \omega^{[3]}       & \omega^{[4]}        \\ 
- \omega^{[2]}       &2\, \omega^{[5]}   & \omega^{[6]}       & \omega^{[7]}        \\
- \omega^{[3]}       & \omega^{[6]}      &2\, \omega^{[8]}   & \omega^{[9]}   \\   
- \omega^{[4]}       & \omega^{[7]}      & \omega^{[9]}      & 2\,\omega^{[10]}      
+ 2\,\omega_c^{[1]}    & \omega_c^{[2]}      & \omega_c^{[3]}       & \omega_c^{[4]}        \\ 
+ \omega_c^{[2]}       &2\, \omega_c^{[5]}   & \omega_c^{[6]}       & \omega_c^{[7]}        \\
+ \omega_c^{[3]}       & \omega_c^{[6]}      &2\, \omega_c^{[8]}   & \omega_c^{[9]}   \\   
+ \omega_c^{[4]}       & \omega_c^{[7]}      & \omega_c^{[9]}      & 2\,\omega_c^{[10]}      
  \end{bmatrix}\in \mathbb{R}^{4\times 4},$
@@
 
-        \foreach \l [count=\i] in {1,2}
+        \foreach \l [count=\i] in {1}
         \draw [<-] (input-\i) -- ++(-1,0)
-        node [above, midway] {$\mathbf{e}_{k,\l}$};
-
+        node [above, midway] {$\mathbf{e}_{k,1}=\tilde{\rho_{k}}$};
+		\draw [<-] (input-2) -- ++(-1,0)
+        node [above, midway] {$\mathbf{e}_{k,2}=\tilde{\theta_{k}}$};
         \foreach \l [count=\i] in {1,2,\mbox{$n^{'}$}}
@@
                  $r\leftarrow r+1$\tcc*[h]{Evaluate policy}using~\eqref{eq:modelFreePolicy}\;
-                 Solve for the critic-weights $\bm{\omega_c}$ using~\eqref{eq:criticWeights}eights}\;
-                 Solve for the actor-weights $\bm{\omega_a}$ using ~\eqref{eq:actorWeights}\;\;
+                 Solve for the critic-weights $\bm{\omega_c}$ using~\eqref{eq:criticWeights}\;
+                 Solve for the actor-weights $\bm{\omega_a}$ using ~\eqref{eq:actorWeights}\;
                  Construct matrix $\mathbf{P}^{[r]}$ using vector $\bm{\omega_c}$\;
  %                \eIf{$\|\mathbf{P}^{[r]} - \mathbf{P}^{[r+1]}\|<\varepsilon$}{Set $\mathbf{u}_{k+1}^*\leftarrow\mathbf{u}_{k+1}^{[r]}$}{$k\leftarrow k+1$ }
-             }
+             }}
  %        {
@@
  \label{sec:resultsExperiments}
- \todo[inline]{review}
- This section adopts the theoritical results discussed in the previous section by simulating the Algorithm using the Pioneer 3-DX  robot.
-The proposed Actor-Critic RL algorithm is tested using the commercial robot simulator CoppeliaSim in integration with Matlab software as a prelminary step to implement the Algorithm experimantally in real world.Here we present the performance of the proposed method and the convergence characterisitcs of the actor and critic weights.
+
+ This section adopts the theoritical results discussed in the previous section by simulating the Algorithm using a differential drive mobile robot.
+The proposed Actor-Critic RL algorithm is tested  utilizing Matlab software and Robot Operating system (ROS)  as a prelminary step to implement the Algorithm experimantally in real world.Here we present the performance of the proposed method and the convergence characterisitcs of the actor and critic weights.
 The weighting matrices are set to $\mathbf{Q} = \mathrm{diag}[0.001,0.001]$ and $\mathbf{R} = \mathrm{diag}[10^{-5}, 10^{-5}].$ %
@@
  The actor and critic learning rates $\ell_c$,$\ell_a$ are set to  $0.0001$ and $0.01$ respectively.
-The sampling time $T_s$ is set to $0.001 \sec.$ The desired distance offset between the leader and the follower is set to $ d = 0.2$ [m].
+The sampling time $T_s$ is set to $0.001 \sec.$ The desired distance offset between the leader and the follower is set to $ d = 0.2$ [m] for the first scenario and $d = 0.5$ [m] for the second.
 
-  During the simulation CoppeliaSim simulator accuratly mimics what would happen in a realworld scenario following idustry standatrds and guidlines.The setup of the virtual expirement is illustrated  in figure \ref{fig:CoppeliaSim Scene} where pioneer robot model was initally placed at position $(x,y) = (-1,-2.5) $ [m] with an orientation $\theta = 0 \degree$ .The Target which is modeled as a cylinder object was initially located at a random position around  $(x,y) = (0,0)$ [m].
-The simulation was run for the duration of 15 seconds.
-  The Target is set to move on a completely random trajectory starting from a random position.
-We intensify that the follower robot has no previous knoweledge of the dynamic model of the moving target nor it's initial position.
+   In the first scenario the differential drive robot was initally placed at position $(x^d,y^d) = (-1,-5) $ [m] with an orientation $\theta = 0 \degree$ .The Target which is modeled as a cylinder object was initially located at a random position around  $(x,y) = (0,0)$ [m].
+The simulation was run for the duration of 60 seconds.The targer is set to move following a sinusoidal path modeled as  $
+ x^{[d]}(t) = \alpha (t) \in [0,10\pi], %
+ y^{[d]}(t) = 5 \,\sin(\alpha t),$  and %
+ $\theta^{[d]}(t) = cos(\alpha t).  %
+$ In the begining of the simulation the robot starts to move away from the target according to the intial random actor weights.As the robot collects more information the robot adjust the control actions as the actor and critic weights started to converge and the robot asymptotically follows the target's trajectory.
+
+  In the second scenario the Target is set to move on a completely random trajectory starting from a random position around $(x^[d],y^[d])=(1,5)$ with 
+ $\dot x^{[d]}(t) = \nu^{[d]}(t)\cos\theta^{[\ell]}(t),$ %
+ $\dot y^{[d]}(t) = \nu^{[d]}(t)\sin\theta^{[\ell]}(t).$
+$ \dot\theta^{[d]}(t) = \omega(t)$,
+ where $\nu^{[d]}(t)=0.2$ [m].
+The robot intial position and orientation being $(x,y) = (0,0)$.
+We intensify that the robot has no previous knoweledge of the dynamic model of the moving target nor it's initial position.
 The results obtained by the simulation are shown in figure \ref{fig:simulationResults}.
-the control actions of the pioneer robot are determined by the random actor weights .we clearly see tracking error converges to the desired value of $d$ = 0.2 [m] along with control signal converging to values that allows target tracking.
-the results reveal the ability of the proposed algorithm to sucessfully track the dynamic moving target and adapt to the changes in the target's path in an online manner.
-\begin{figure}
-   \centering
-   \fcolorbox{gray!10}{gray!5}{
-     \includegraphics[width=0.45\textwidth]{figs/coppeliasim.png}
-`     }
-   \caption{Simulation Setup}
-   \label{fig:CoppeliaSim Scene}
- \end{figure}
+the control actions of the robot are determined by the random actor weights .we clearly see tracking error converges and approaches zero as the control signal converging to values that allows target tracking.
+the results reveal the ability of the proposed algorithm to sucessfully track the dynamic moving target and adapt to the changes in the target's trajectory and learns online by trial and error in different scenarios.
+%\begin{figure}
+%   \centering
+%   \fcolorbox{gray!10}{gray!5}{
+%     \includegraphics[width=0.45\textwidth]{figs/coppeliasim.png}
+%`     }
+%   \caption{Simulation Setup}
+%   \label{fig:CoppeliaSim Scene}
+% \end{figure}  
+ \begin{figure*}[htbp]%
+
+ \subfigure[][]{%
+    \label{fig:trajectoryRandom}%
+    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/trajectoryRandomPathDistance.eps} }
+	\subfigure[][]{%    
+    \label{fig:euclideanDistance}%
+    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/euclideanDistance.eps} }
+\subfigure[][]{%
+    \label{fig:stateErrorRandom}%
+    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/stateErrorRandomPathDistance.eps} }
+ \subfigure[][]{%
+    \label{fig:controlInputsRandom}%
+    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/controlInputRandomPathDistance.eps} }
+ \subfigure[][]{%
+    \label{fig:weightRandomDistance}%
+    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/weightRandomPathDistance.eps} }
+     \subfigure[][]{%
+    \label{fig:actorWeightRandomDistance}%
+    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/weightActor.eps} }
+\caption[Leader-follower performance for random trajectory.]{Performance in tracking random trajectory: 
+  \subref{fig:trajectoryRandom} leader-follower trajectories,~\subref{fig:stateErrorRandom} state error,~\subref{fig:controlInputsRandom} linear speed and steering angle of the follower; and    \subref{fig:weightRandomDistance} learning weights.}%
+  \label{fig:peformanceRandomTrajectory}%
+	\label{fig:simulationResults}
+\end{figure*}
 
@@
  \section{Conclusion} \label{sec:conclusion}
-	\todo[inline]{review}
-	A model free actor-critic reinfoncement learning algorithm for dynamic target tracking has been validated using virtual robot experimantation platform where a differenitial drive mobile robot and a randomly moving target are utilized in the simulation.Opposed to previous approaches in the litrature this Algorithm possess the advantage of being completlety model free and doesn't rely on any dynamic model to be known in priori.
-The actor weights which drives the control actions of the robot sucessfully converge to values that enable the robot to track the moving target through unplanned trajectory.
+
+	A model free actor-critic reinfoncement learning algorithm for dynamic target tracking has been validated using set of computer simulation where a differenitial drive mobile robot and a randomly moving target are utilized in the simulation.Opposed to previous approaches in the litrature this Algorithm possess the advantage of being completlety model free and doesn't rely on any dynamic model to be known in priori.
+The actor weights which drives the control actions of the robot sucessfully converge to values that enable the robot to asymptotically track the moving target through unplanned trajectory.
 To the authors knowlege this work is the first of its kind to employ a model-free actor-critic RL approach  in the context of dynamic target tracking.
@@
 	\bibliographystyle{IEEEtran}
-\bibliography{bib/refsSuruzWeb,bib/refsMultiAgent,bib/refsRoboticsJournals,bib/refsRoboticsConferences,bib/refsGenericControl,bib/refsBooksTRTheses,bib/refsReinforcementLearningADP,bib/refsRL-Keshtkar}
+\bibliography{bib/refsSuruzWeb,bib/refsMultiAgent,bib/refsRoboticsJournals,bib/refsRoboticsConferences,bib/refsGenericControl,bib/refsBooksTRTheses,bib/refsReinforcementLearningADP,bib/refsRL-Keshtkar,bib/amrsRefs}
 \end{document}

### 2020-07-03 paperMIC2020/matlabsim/mainLF_OdometricLocalizationV9Sinewave.m

@@ -22,7 +22,7 @@ T = 0.001;  % Sampling time [s]
 tsteps = ceil((tf-t0)/T); % number of time steps
 dt = T*(0:tsteps)'; % Discrete time vector (include time t0 to plot initial state too)
 
-d = 0.2; %[m] safe distance
+d = 0.5; %[m] safe distance
 %ROBOT PARAMETERS
 %==========================================================================
 l = 0.381; % [m]
@@ -36,20 +36,22 @@ M = 2;  % input vector dimension
 
 
 % Leader's initial position
-pLeaderInit = [5;1]+rand(2,1); %[m]
-pLeaderTheta= 0; %[rad]
+pLeaderInit = [0;0]+ rand(2,1); %[m]
+pLeaderTheta(1:tsteps,1)= 0:(10*pi)/(tsteps-1):10*pi; %[rad]
+pLeaderTheta(tsteps+1,:)=10*pi;
+QD(1,:) = [pLeaderInit' cos(0.2*pLeaderTheta(1,:))];
 
-QD(1,:) = [pLeaderInit' pLeaderTheta];
+
 QDinit = QD(1,:);
 %Leader's velocity 
-vLeader = 0.1; % [m/s]
-uLeader=[vLeader pLeaderTheta];
+vLeader = 5; % [m/s]
+
 
 % Follower robot initialization% 
-qp = [0;0]; % [m] Follower robot's position
+qp = [-2;-5]; % [m] Follower robot's position
 qTheta = 0 ;% [rad] Follower robot's orientation 
  qInit = [qp',qTheta] ;%+ rand(1,3); % row vector
-vMax = 2; % [m/s] Follower's maximum linear speed 
+vMax = 5; % [m/s] Follower's maximum linear speed 
 
 Q(1,:) = qInit;
 
@@ -66,7 +68,7 @@ P = [3  0   2   0.5;
       0   3   0.5    2;
       1 0.5   3      0;
     0.5   1    0      3]
- P = P+2*rand;
+ P = P+5*rand;
 eig(P)
 Pinit = P;
 
@@ -82,17 +84,17 @@ lc = 0.00001; %learnging rate
 la= 0.01; %actor learning rate
 
 %initlize actor weights
-Wa=0.001*rand(2,2);
+Wa=0.01*rand(2,2);
 
 %reconstruct the P matrix to get the wheights matrix
- w(1,1) = 0.5 * P(1,1);
[…]

### 2020-07-05 paperMIC2020/paperIEEE-MIC2020-V1.tex
Updated the paper up to part of results section
Need to discuss about the changes.

@@
 In this paper, we address the position tracking problem of a mobile robot where it is supposed to track the position of an mobile target whose dynamics is unknown a priori.
-This problem is even more challenging when the dynamics of the mobile robot is also assumed to be unknown, which is a basically a realistic assumption.
+This problem is even more challenging when the dynamics of the mobile robot is also assumed to be unknown, which is indeed a realistic assumption.
 Most of trajectory tracking problems proposed in the literature in the field of mobile robotics are either focused on algorithms that rely on mathematical models of the robots or driven by a  overwhelming degree of computational complexity.
-This paper proposes a model-free actor-critic reinforcement learning strategy to determine appropriate actuator commands for the robot to track the position trajectory (unknown a priori) of the target.
+This paper proposes a model-free actor-critic reinforcement learning strategy to determine appropriate actuator commands for the robot to track the position of the target.
 We emphasize that mathematical models of both mobile robot and the target are not required in the current approach.
@@
 The performance of the proposed actor-critic reinforcement learning approach  is backed by a set of computer simulations with various complexities using a virtual circular-shaped mobile robot and a point target  modeled by an integrator.
-
-%   It is even more challenging 
-% This paper advances the previous work done by authors by validating a model-free actor-critic reinforcement learning approach to solve dynamic target tracking problem for a car-like mobile robot.
-The learning approach generates the linear velocity and steering angle of the robot and it does not require any prior knowledge of the dynamic model of the moving target.
-Policy iteration approach is employed through Bellman's principle of optimality to assess the cost of the control actions derived by the proposed learning method.
-The algorithm is tested by coducting a set of computer expeeriments for complex secnarios using virtual robot expirementation platform widely known as CoppeliaSim.
-% }{Need to be rewritten}  
 %
@@
 
-Tracking a random moving target using a mobile robot is a key problem and a fundemental feature in Autonomus robots in areas such as survillance,search and rescure missions, enviromental monitoring and household cleaning to name a few \cite{kolling2006},\cite{Encarnacao2001},\cite{Ju2001},\cite{Kitowski2012},\cite{Zhang2013}.
-Throught the years dynamic target tracking problem has recieved profound amount of research in academia and industry.
+Tracking a random moving target using a mobile robot is a key problem and a fundamental feature in autonomous robots operating in areas such as surveillance, search and rescue missions, environmental monitoring, household cleaning, to name a few~\cite{kolling2006,Encarnacao2001,Ju2001,Kitowski2012,Zhang2013}.
+Throughout the years, the dynamic target tracking problem has received a profound amount of research in academia and industry\todo{Add 2 recent references}.
 This is mainly due to their inherent complex nonlinear dynamics.
-Most of the target tracking algorithms proposed in the literature either rely on A) mathematical and kinematic models of both the robot and the target \cite{Huang2008}, B) the assumption that the target or it's path are static and known in prior, and C) nonlinear control techniques or driven by large amount of mostly offline data that leads to an overwhelming degree of computational complexity \cite{KD2007},\cite{Cren2017}.
-In a typical tracking problem a robot is to apply a local control actions that enables the robot to maintain a relative position and orientation from the designated target while following a certain path.It can also be applied on a fleet of robots where multiple robots mainatin a geometric configuration relative to the target\cite{Oh2015-Survey},\cite{Liu2017-Modular}.
+Most of the target tracking algorithms proposed in the literature either rely on A) mathematical and kinematic models of both the robot and the target \cite{Huang2008}, B) the assumption that the target or its trajectory are static and known a priori, and C) nonlinear control or soft-computing techniques that are driven by large amount of mostly offline data that leads to an overwhelming degree of computational complexity \cite{KD2007,Cren2017}.
+In a typical tracking problem, a robot is to apply a local control actions that enable it to maintain a relative position and orientation from the designated target while following a certain trajectory.
+It can also be applied on a fleet of robots where multiple robots maintain a geometric configuration relative to the target\cite{Oh2015-Survey,Liu2017-Modular}.
 
@@
 
-Reinforcement learning (RL) is an emerging field of machine learning which refers to a set of algorithms and techniques in which agent learn by interacting with the enviroment and generates it's own set of data.
-Reinorcement learning has long been applied on games and simulated enviroments but it has recently extended to robots in real world applications such as localization and mapping,area coverage, path planning and obstacle avoidance \cite{kober2013reinforcement},\cite{smart2002},\cite{michels2005},\cite{adekunle2016}.
+Reinforcement learning (RL) is an emerging field of machine learning which refers to a set of algorithms and techniques in which agents learn by interacting with the environment and determine their own sets of actions that define trajectories.
+Reinforcement learning has long been applied on games and simulated environments but it has recently been explored to robots in real world applications, such as localization and mapping, area coverage, path planning and obstacle avoidance \cite{kober2013reinforcement,smart2002,michels2005,adekunle2016}.
 
-In this paper we develop a model-free actor-critic learning  approach to control a non-holonomic wheeled mobile robot.The proposed method offers many advantages over other methods mentioned in the litreature such as being completely model free and does not require any knowledge of the mathemtaical model of the robot or the moving target and without the need for large computational power.
-The steering angle and the linear speed of the robot referred to as the policy are determined by collecting the position and orientation of both the target and the robot.
+In this paper, we develop a model-free actor-critic learning approach to control a non-holonomic wheeled mobile robot.
+The proposed method offers many advantages over other methods mentioned in the literature, such as being completely model free and does not require any knowledge of the mathematical model of the robot or the moving target and without the need for large computational power.
+The steering angle and the linear speed of the robot referred to as the policy (control actions) are determined by collecting the position and orientation of both the target and the robot.
 This set of information is gathered online over a finite period of time.
-The optimal control actions are then generated by utilizing Bellman's principal of optimality which acts as model free-reinfocment learning approach that allows the  robot to follow the path of the target while avoiding collision by maintaining a safe distance.
-Here we extend the work proposed by authors in \cite{miah2020} by incorporating actor neural network along with critic network to find optimal control policy for the trajectory tracking problem.
-This work acts as first milestone in generalizing the algorithm to solve more sophisticated problem such as coverage and mapping.
+The optimal control actions are then generated by utilizing Bellman's principle of optimality which acts as model free-reinforcement learning approach that allows the robot to follow the trajectory of the target while avoiding collision by maintaining a safe distance.
+Here, we extend the work proposed by authors in \cite{miah2020} by incorporating actor neural network along with critic network to find optimal control policy for the trajectory tracking problem.
+This work acts as first milestone in generalizing the algorithm to solve more sophisticated problem such as typical area coverage and mapping problems in the field of robotics.
 
-The rest of the paper is orgnized as follows.
-Section II lays down the problem setting of the dynamic target tracking problem and mathemetical models of the robot and the state error.
-The model free actor-critic reinforcment learning algorithm and all the mathemetical equations are detailed in section III.Section IV illustrates computer simulations for different secnarios that reflects the effectivness of the proposed method followed by conlusion and future work presented in section V.
+The rest of the paper is organized as follows.
+Section~\ref{sec:problemSetting} lays down the problem setting of the dynamic target tracking problem and mathematical models of the robot and the state error.
+The model free actor-critic reinforcement learning algorithm and its associated  mathematical derivations are detailed in section~\ref{sec:RLSolution}.
+Section~\ref{sec:resultsExperiments} illustrates computer simulations for different scenarios that reflect the effectiveness of the proposed method followed by conlusion and future work presented in section~\ref{sec:conclusion}.
 
@@
 Fig.~\ref{fig:leaderFollowerSetup} shows the setup of the problem that we address in this manuscript.
-The robot is characterized by its 2D position $(x_k,y_k)$ and orientation $\theta_k\in[-\pi,\pi)$ with respect to global coordinate frame X-Y at discrete time index $k=0,1,\ldots,$ where time $t=kT$ with $T>0$ being the sampling time.
-The time-varying position of the target is denoted by ${\bf p}_k^{[d]}= [x_k^{[d]},y_k^{[d]}]^T\in\mathbb{R}^2.$  Let the position and orientation (pose) of the robot is denoted by the vector  ${\bf q}_k^T\equiv[x_k,y_k,\theta_k]\in\mathbb{R}^2\times\mathbb{S}^1.$ Without loss of generality, assume that the robot tracks the target's trajectory while maintaining line-of-sight distance (also known as safe distance between the robot and the target) $d>0.$ We emphasize that the mathematical models of both robot and the target are not required in the proposed control technology.
+The robot is characterized by its 2D position $(x_k,y_k)$ and orientation $\theta_k\in[-\pi,\pi)$ with respect to the global coordinate frame X-Y at discrete time index $k=0,1,\ldots,$ where time $t=kT$ with $T>0$ being the sampling time.
+The time-varying position of the target is denoted by the position vector ${\bf p}_k^{[d]}= [x_k^{[d]},y_k^{[d]}]^T\in\mathbb{R}^2.$  Let the position and orientation (pose) of the robot is denoted by the vector  ${\bf q}_k^T\equiv[x_k,y_k,\theta_k]\in\mathbb{R}^2\times\mathbb{S}^1.$ Without loss of generality, assume that the robot tracks the target trajectory while maintaining line-of-sight distance (also known as the safe distance between the robot and the target) $d>0.$ We emphasize that the mathematical models of both robot and the target are not required in the proposed control technology.
 For illustration, let us assume that the robot (rear-wheel drive) follows the discrete-time kinematic model described by %
@@
 \begin{subequations}
+  \label{eq:robotModelDT}  
   \begin{align}
-    \label{eq:robotModelDT}
-    x_{k+1} &= x_k +T\nu_k\cos\theta_k\\
-    y_{k+1} &= y_k +T\nu_k\sin\theta_k\\
-    \theta_{k+1} &= \theta_k + T\frac{\nu_k}{L}\tan\gamma_k
+    x_{k+1} &= x_k +T\nu_k\cos\theta_k,\\
+    y_{k+1} &= y_k +T\nu_k\sin\theta_k,\\
+    \theta_{k+1} &= \theta_k + T\frac{\nu_k}{L}\tan\gamma_k,
   \end{align}
@@
 %
-where $\gamma_k\in(-\frac{\pi}{2},\frac{\pi}{2})$ is the steering angle of the font castor of the robot (see Fig.~\ref{fig:leaderFollowerSetup}), and $\nu_k\in\mathbb{R}$ is the linear speed.
-Without loss of generality, this work considers a target modeled by an integrator and its discrete-time kinematic model is described by
+where $\gamma_k\in(-\frac{\pi}{2},\frac{\pi}{2})$ is the steering angle of the font wheel/castor of the robot (see Fig.~\ref{fig:leaderFollowerSetup}), and $\nu_k\in\mathbb{R}$ is the linear speed.
+Without loss of generality, this work considers a target modeled by an integrator.
+The discrete-time kinematic model of the target is given as %
+%
  \begin{align}
@@
  \end{align}
+% 
  with $\mathbf{u}_k^{[d]}\in\mathbb{R}^2$ being the control input vector (velocity) that defines the trajectory (considered random in this work) of the target.
-In case, the robot modeled by~\eqref{eq:robotModelDT} is described by a differential drive mobile robot, then its left-wheel velocity $\nu_{L,k}$ and right-wheel velocity $(\nu_{R,k})$ are related as
+In case, the robot modeled by~\eqref{eq:robotModelDT} is described by a differential drive mobile robot, then its left-wheel velocity $\nu_{L,k}$ and right-wheel velocity $\nu_{R,k}$ are related by
+ %
   \begin{figure}
@@
     }
-   \caption{Mobile robot and its dynamic target tracking problem setup.}
+   \caption{Mobile robot and its dynamic target tracking problem setup. \todo[inline]{In this figure, replace $\tilde\theta_k$ with $\theta_k^{'}$}}
    \label{fig:leaderFollowerSetup}
  \end{figure}
+ %
  \begin{subequations}
@@
      \label{eq:stateError}
-   \mathbf{e}_k = [\tilde{\rho_k},\tilde\theta_k]^T=[\sqrt{\tilde{x}_k^2+\tilde{y}_k^2},\tilde{\theta_k}]^T% = \\
+   \mathbf{e}_k = \left[ \tilde{\rho_k},\tilde\theta_k \right]^T=\left[ \sqrt{\tilde{x}_k^2+\tilde{y}_k^2},\tilde{\theta_k} \right]^T% = \\
    % \begin{bmatrix}
@@
  where $\theta_k^{'} = \mathrm{atan2}\left(y_k^{[d]}-y_k, x_k^{[d]}-x_k\right)$
- and ${\rho_k} =\sqrt{\tilde{x}_k^2+\tilde{y}_k^2} $ is the Euclidean distance at time instant $k$ as shown in Fig.~\ref{fig:leaderFollowerSetup} with $\tilde{x}_k = x_k^{[d]} - x_k - d\cos\theta_k^{'},$ $\tilde{y}_k = y_k^{[d]} - y_k - d\sin\theta_k^{'},$ and $\tilde{\theta}_k = \theta_k^{'} - \theta_k.$ The control problem can then be formally stated as follows: Find $\nu_k$ and $\gamma_k$ such that ${\bf e}_k\to {\bf 0}$ as  $k\to\infty$ subject to~\eqref{eq:robotModelDT}~and~\eqref{eq:leaderDT}.
+ and $\tilde{\rho}_k =\sqrt{\tilde{x}_k^2+\tilde{y}_k^2} $ is the Euclidean distance (position error) at time instant $k$ as shown in Fig.~\ref{fig:leaderFollowerSetup} with $\tilde{x}_k = x_k^{[d]} - x_k - d\cos\theta_k^{'},$ $\tilde{y}_k = y_k^{[d]} - y_k - d\sin\theta_k^{'},$ and $\tilde{\theta}_k = \theta_k^{'} - \theta_k$ is the orientation error.
+The control problem can then be formally stated as follows: Find $\nu_k$ and $\gamma_k$ such that ${\bf e}_k\to {\bf 0}$ as  $k\to\infty$ subject to~\eqref{eq:robotModelDT}~and~\eqref{eq:leaderDT}.
 
@@
  Reinforcement learning is a promising  machine learning technique that is widely used in solving problems of many cyber-physical systems that pertain to the goal-directed learning from interaction~\cite{sutton2020reinforcement}.
-In this paper, tracking a mobile target using a wheeled mobile robot is formulated as a reinforcement learning problem, where the goal of the robot is to track the trajectory of the target while maintaining the safe-distance $d>0.$ The RL solution employed in the current problem leverages Bellman's principle of optimality to decide on the appropriate control actions (actuator commands) for the robot to track the position trajectory of the target.
-The relative importance of the states in the error vector ${\bf e}_k$ and the control decisions (linear velocity $\nu_k$ and steering angle $\gamma_k$) of the robot are evaluated using the  performance (cost) index: %
+In this paper, tracking a mobile target using a wheeled mobile robot is formulated as a reinforcement learning problem, where the goal of the robot is to track the trajectory of a target while maintaining the safe-distance $d>0.$ The RL solution employed in the current problem leverages Bellman's principle of optimality to decide on the appropriate control actions (actuator commands) for the robot to track the position trajectory of the target.
+The relative importance of the states in the error vector ${\bf e}_k$ and the control decisions (linear velocity $\nu_k$ and steering angle $\gamma_k$) of the robot are evaluated using the  performance (cost) index %
+ %
  \begin{align}
  \label{eq:costFunctional}
-   J = \sum_{k=0}^\infty \frac{1}{2}\left[{\bf e}_k^T \, {\bf Q} \, {\bf e}_k + {\bf u}_k^T \, {\bf R} \, {\bf u_k}\right],
+   J =  \frac{1}{2} \sum_{k=0}^\infty\left[{\bf e}_k^T \, {\bf Q} \, {\bf e}_k + {\bf u}_k^T \, {\bf R} \, {\bf u_k}\right],
  \end{align}
+ %
  where ${\bf Q}\in\mathbb{R}^{2\times 2}$ and ${\bf R}\in\mathbb{R}^{2\times 2}$ are symmetric positive definite weighting matrices, and ${\bf u}_k^T = [\nu_k,\gamma_k]$ is the control input vector.
@@
  %
- Following Bellman's optimality principle yields the optimal control policies ${\bf u}_k^*,~k\ge 0,$ such that~\cite{Lewis2012} %
+ Bellman's optimality principle yields the optimal control policies ${\bf u}_k^*,~k\ge 0,$ such that~\cite{Lewis2012} %
  %
@@
    {\bf u}^*_k = \argmin_{{\bf u}_k}\left[\frac{1}{2}\left[{\bf e}^T_k\,  {\bf Q}\, {\bf e}_k +{\bf u}^T_k\,  {\bf R} \,  {\bf u}_k\right]   +
- V({\bf e}_{k+1},{\bf u}_{k+1})\right].
+   V^*({\bf e}_{k+1},{\bf u}_{k+1}^*)\right].
    \label{eq:argMinControlAction}
@@
  %
- where $V^*(\cdot,\cdot)$ is the optimal solution for Bellman optimality equation.
+ where $V^*(\cdot,\cdot)$ is the optimal solution for Bellman's optimality equation.
 This temporal difference equation is utilized by reinforcement learning process which solves the following temporal difference approximation form %
@@
  %
- where $\mathbf{z}_k = \left[\mathbf{e}_k ,\mathbf{u}_k\right]^T\in\mathbb{R}^4,$ $V\left(\mathbf{e}_k,\mathbf{u}_k\right) \approx \hat{V}(\mathbf{z}_k),$  and $\bar{\mathbf{P}}$ is a symmetric block-diagonal matrix formed using $(\mathbf{Q},\mathbf{R}),$~\textit{i.e.,~}$\bar{\mathbf{P}} = \mathrm{blockdiag}(\mathbf{Q},\mathbf{R}).$ %
- The approximation of the solving value function $\hat{V}(\mathbf{z}_k)$ employs a quadratic form so that $\hat{V}(\mathbf{z}_k)=\frac{1}{2}\mathbf{z}_k^T\, \mathbf{P}\, \mathbf{z}_k,$ for some positive definite matrix  $\mathbf{P}\in\mathbb{R}^{4\times 4}.$ The optimal control input ${\bf u}_k*$ is then determined by setting $\frac{\partial\hat{V}({\bf z}_k)}{\partial{\bf u}_k} = 0,$ which yields %
+ where $\mathbf{z}_k = \left[\mathbf{e}_k ,\mathbf{u}_k\right]^T\in\mathbb{R}^4,$ $V\left(\mathbf{e}_k,\mathbf{u}_k\right) \equiv V(\mathbf{z}_k),$  and $\bar{\mathbf{P}}$ is a symmetric block-diagonal matrix formed using $(\mathbf{Q},\mathbf{R}),$~\textit{i.e.,~}$\bar{\mathbf{P}} = \mathrm{blockdiag}(\mathbf{Q},\mathbf{R}).$ %
+ The approximation of the solving value function $V(\mathbf{z}_k)$ employs a quadratic form so that $\hat{V}(\mathbf{z}_k)=\frac{1}{2}\mathbf{z}_k^T\, \mathbf{P}\, \mathbf{z}_k,$ for some positive definite matrix  $\mathbf{P}\in\mathbb{R}^{4\times 4}.$ The optimal control input ${\bf u}_k^*$ is then determined by setting $\frac{\partial\hat{V}({\bf z}_k)}{\partial{\bf u}_k} = 0,$ which yields %
  %
@@
  %
- where $\mathbf{P}_{uu}$ and $\mathbf{P}_{ue}$ are sub-blocks of symmetric matrix $\mathbf{P}.$ The proposed approach approximates the block matrix ${\bf P}$ by following a two-step solution mechanism based on policy iteration method~\cite{sutton2020reinforcement}, which in turn approximates the value function~$\hat V(\cdot)$ given by ~\eqref{eq:valueFunctionEstimated}.
-First, a multi-layer critic neural network shown in Fig.~\ref{fig:nnCritic} is used to estimate the value function, $\hat V({\bf z}_k).$
+ where $\mathbf{P}_{uu}$ and $\mathbf{P}_{ue}$ are sub-blocks of symmetric matrix $\mathbf{P}.$ The proposed approach approximates the block matrix ${\bf P}$ by following a two-step solution mechanism based on policy iteration method~\cite{sutton2020reinforcement}, which in turn approximates the value function~$V(\cdot).$ First, a multi-layer critic neural network shown in Fig.~\ref{fig:nnCritic} is used for determining the estimated value function, $\hat V({\bf z}_k).$
 \begin{figure}
@@
 
-            \node [align=center, below] at (3,-2.5) {Weights \\ $\boldsymbol{\omega}_c$};
-            \draw[-stealth,ultra thick](3,-2.5) to[bend left] (3,1.4);
+            \draw[-stealth,ultra thick](3,-2.5)node[right]{Weights $\boldsymbol{\omega}_c$} to[bend left] (3,1.4);
 
@@
  %
- Equation~\eqref{eq:const} is evaluated repeatedly to collect data online for at least $\eta\ge \bar n, \bar n= (2+2)(2+2+1)/2 = 10$ evaluation steps due to the fact that the matrix ${\bf P}$ is positive definite and symmetric.
-The strictly better policy ${\bf P},$ is determined every $\eta$ time/evaluation steps.
+ Equation~\eqref{eq:const} is evaluated repeatedly to collect data online for at least $\eta\ge \bar n,$ with $\bar n= (2+2)(2+2+1)/2 = 10$ evaluation steps due to the fact that the matrix ${\bf P}$ is positive definite and symmetric.
+The strictly better policy matrix ${\bf P},$ is determined every $\eta$ time/evaluation steps.
 To find the better policy in terms of matrix ${\bf P},$ let us define the vector $\boldsymbol{\omega}=\mathrm{vec}(\mathbf{P})\in\mathbb{R}^{16},$ which is formed by stacking columns of ${\bf P}$ matrix.
-However, since ${\bf P}$ is symmetric, we only need determine the weight $\bm{\omega}_c\in\mathbb{R}^{\bar n}$ using the critic neural network shown in Fig.~\eqref{fig:nnCritic}.
+However, since ${\bf P}$ is symmetric, we only need to determine the weight $\bm{\omega}_c\in\mathbb{R}^{\bar n}$ using the critic neural network shown in Fig.~\eqref{fig:nnCritic}.
 The left hand side of~\eqref{eq:const} is expressed using the following critic approximation form %
@@
 The tuning error $\varepsilon_k$ at each computational instance $k$ is given by $\varepsilon_k =\boldsymbol{\omega}_c^T\tilde{\bm{\rho}}(\mathbf{z}_{k,k+1})-{v}_k,$ where $v_\kappa = \frac{1}{2}\mathbf{z}_{k}^T \, \bar{\mathbf{P}} \, \mathbf{z}_{k}$.
-The error data $\varepsilon_k$ is collected online for at least  $\eta \ge \bar n$ evaluation steps before updating the critic weights $\boldsymbol{\omega}_c$ that is used to determine the improved policy ${\bf P}.$ The sum of squared tuning errors is given by
+The error data $\varepsilon_k$ is collected online for at least  $\eta \ge \bar n$ evaluation steps before updating the critic weights $\boldsymbol{\omega}_c$ that is used to determine the improved policy matrix ${\bf P}.$ The sum of squared tuning errors is given by
  %
  \begin{align}
-   \delta_c =\sum_{\kappa=0}^{\eta-1}\frac{1}{2}\varepsilon_{k+\kappa}^2 &=\sum_{\kappa=0}^{\eta-1}\frac{1}{2}(\boldsymbol{\omega_c}^T\tilde{\bm{\rho}}(\mathbf{z}_{k+\kappa,k+\kappa+1})-{v}_{k+\kappa})^2 \nonumber \\
+   \delta_c =\frac{1}{2}\sum_{\kappa=0}^{\eta-1}\varepsilon_{k+\kappa}^2 &=\frac{1}{2}\sum_{\kappa=0}^{\eta-1}(\boldsymbol{\omega_c}^T\tilde{\bm{\rho}}(\mathbf{z}_{k+\kappa,k+\kappa+1})-{v}_{k+\kappa})^2 \nonumber \\
    	&=\frac{1}{2}\| \mathbf{v} - \bm{\Lambda}\bm{\omega_c}\|^2 \nonumber \\
@@
 
- The critic weights are then used to update the actor weights $W_a\mathbb{R}^{n\times m}$ (here $n=2$ and $m=2$) which maps the state error to the desired policy (control actions) as  at every time step $t$ with the following equation:
+ The critic weights are then used to update the actor weights $W_a\in\mathbb{R}^{n\times m}$ (here $n=2$ and $m=2$) which maps the state error to the desired policy (control actions) at time step $k$ with the following equation:
  \begin{align}
@@
  %
- where ${\bf W}_a\in\mathbb{R}^{2\times n^{'}}$ is the actor weight matrix and $\bm{\sigma}:\mathbb{R}^2 \to \mathbb{R}^{n^{'}}$ is the basis function vector.
+ where ${\bf W}_a\in\mathbb{R}^{n^{'}\times 2}$ is the actor weight matrix and $\bm{\sigma}:\mathbb{R}^2 \to \mathbb{R}^{n^{'}}$ is the basis function vector.
 Equation~\eqref{eq:actorWeightsPolicy} is realized using a multi-layer actor neural network shown in Fig.~\ref{fig:nnActor}.
@@
         (3,-1.5)node[anchor=west]{Weight~${\bf W}_a$} to[bend left] (3,1.6);
-
       \end{tikzpicture}
@@
 %
-The elements of the vector $\bm{\sigma}$ are the activation functions of the neurons in the hidden layer shown in Fig.~\ref{fig:nnActor}.
-We will need to determine the actor weight matrix ${\bf W}_a$ that minimizes the error between the estimated control inputs determined by model~\eqref{eq:actorWeightsPolicy} and the that determined by critic neural network approximation model~\eqref{eq:modelFreePolicy}.
+The elements of the vector function $\bm{\sigma}(\cdot)$ are the activation functions of the neurons in the hidden layer shown in Fig.~\ref{fig:nnActor}.
+We will need to determine the actor weight matrix ${\bf W}_a$ that minimizes the error between the estimated control inputs determined by model~\eqref{eq:actorWeightsPolicy} and that determined by critic neural network approximation model~\eqref{eq:modelFreePolicy}.
 For that, let us define the error %
@@
 %
-Taking partial derivative of the above expression $\delta_a$  with respect to ${\bf W}_a$ gives %
+Taking partial derivative of the above expression of $\delta_a$  with respect to ${\bf W}_a$ gives %
 %
-\begin{align*}
-  \frac{\partial \delta_a}{\partial{\bf W}_a} = {\bf W}_a^T\bm{\sigma}({\bf e}_k)\bm{\sigma}^T({\bf e}_k) - {\bf u}_k^*\bm{\sigma}^T({\bf e}_k).
-\end{align*}
+\begin{multline*}
+  \frac{\partial \delta_a}{\partial{\bf W}_a} = \bm{\sigma}({\bf e}_k)\bm{\sigma}^T({\bf e}_k){\bf W}_a - \bm{\sigma}({\bf e}_k)\left( {\bf u}_k^* \right)^T\\
+  =\bm{\sigma}({\bf e}_k)\left[ \bm{\sigma}^T({\bf e}_k){\bf W}_a -\left( {\bf u}_k^* \right)^T \right].
+\end{multline*}
 %
-Therefore, actor weight matrix ${\bf W}_a$ in every policy iteration $r = 01,2,\ldots$ can be updated using the learning rule %
+Therefore, actor weight matrix ${\bf W}_a$ in every policy iteration $r = 0,1,2,\ldots$ can be updated using the learning rule %
 %
@@
   {\bf W}_a^{[r+1]} = {\bf W}_a^{[r]} - \ell_a\frac{\partial\delta_a}{\partial{\bf W}_a}\\
-  = {\bf W}_a^{[r]} - \ell_a\left( {\bf W}_a^T\bm{\sigma}({\bf e}_k)-\mathbf{u}_k^* \right)\bm{\sigma}^T({\bf e}_k), 
+  = {\bf W}_a^{[r]} - \ell_a\bm{\sigma}({\bf e}_k)\left[ \bm{\sigma}^T({\bf e}_k){\bf W}_a -\left( {\bf u}_k^* \right)^T \right], 
  \label{eq:actorWeights}
 \end{multline}
- where $\ell_a$ is the actor learning rate.  The complete policy iteration solution process for the leader-follower problem is detailed out in Algorithm \ref{alg:ModelFreeTracking}. %
+%
+ where $\ell_a$ is the actor learning rate.
+The complete policy iteration solution process for the leader-follower problem is detailed out in Algorithm~\ref{alg:ModelFreeTracking}.
+\todo[inline]{In Algorithm 1, add a line with $n=2$ (state error dimension) and $m=2$ (input dimension)} %
  %
@@
 
- This section adopts the theoritical results discussed in the previous section by simulating the Algorithm using a differential drive mobile robot.
-The proposed Actor-Critic RL algorithm is tested  utilizing Matlab software and Robot Operating system (ROS)  as a prelminary step to implement the Algorithm experimantally in real world.Here we present the performance of the proposed method and the convergence characterisitcs of the actor and critic weights.
+ This section adopts the theoretical results discussed in the previous section by simulating Algorithm~\ref{alg:ModelFreeTracking} using a differential drive mobile robot.
+The proposed actor-critic RL algorithm is tested  utilizing MATLAB software and Robot Operating System (ROS)  as a preliminary step to implement the Algorithm experimentally in real world.
+Here we present the performance of the proposed method and the convergence characteristics of the actor and critic weights.
 The weighting matrices are set to $\mathbf{Q} = \mathrm{diag}[0.001,0.001]$ and $\mathbf{R} = \mathrm{diag}[10^{-5}, 10^{-5}].$ %
-  \[Q=0.001 
-  \begin{bmatrix}
-  1       & 0   \\
-  0       & 1   \\
-  \end{bmatrix},
-  R=0.00001
-  \begin{bmatrix}
-  1       & 0 \\
-  0       & 1 
-  \end{bmatrix}.\]
+  % \[Q=0.001 
+  % \begin{bmatrix}
+  % 1       & 0   \\
+  % 0       & 1   \\
+  % \end{bmatrix},
+  % R=0.00001
+  % \begin{bmatrix}
+  % 1       & 0 \\
+  % 0       & 1 
+  % \end{bmatrix}.\]
 
- The actor and critic learning rates $\ell_c$,$\ell_a$ are set to  $0.0001$ and $0.01$ respectively.
-The sampling time $T_s$ is set to $0.001 \sec.$ The desired distance offset between the leader and the follower is set to $ d = 0.2$ [m] for the first scenario and $d = 0.5$ [m] for the second.
+ The actor and critic learning rates are set to $\ell_c = 0.00001$ and $\ell_a=0.01,$ respectively.
+The sampling time $T$ is set to $0.001 \sec.$ The desired distance offset between the target and the robot is set to $ d = 0.2~[\si{\meter}]$ for the first scenario and $d = 0.5~[\si{\meter}]$ for the second scenario.
 
-   In the first scenario the differential drive robot was initally placed at position $(x^d,y^d) = (-1,-5) $ [m] with an orientation $\theta = 0 \degree$ .The Target which is modeled as a cylinder object was initially located at a random position around  $(x,y) = (0,0)$ [m].
-The simulation was run for the duration of 60 seconds.The targer is set to move following a sinusoidal path modeled as  $
- x^{[d]}(t) = \alpha (t) \in [0,10\pi], %
+ In the first scenario, the differential drive robot was initially placed at position $(x^d,y^d) = (-1,-5)~[\si{\meter}] $ with an orientation of $\theta = 0\degree.$ The target which is modeled as a \comment{cylinder object}{we are running MATLAB simulation and using point robot as a target} was initially located at a random position around  $(x,y) = (0,0)~[\si{\meter}].$ The simulation was run for the duration of $t_f=60~[\second].$ The target is set to move following a sinusoidal path modeled as  $
+ x^{[d]}(t) = \alpha t, %
  y^{[d]}(t) = 5 \,\sin(\alpha t),$  and %
- $\theta^{[d]}(t) = cos(\alpha t).  %
-$ In the begining of the simulation the robot starts to move away from the target according to the intial random actor weights.As the robot collects more information the robot adjust the control actions as the actor and critic weights started to converge and the robot asymptotically follows the target's trajectory.
+ $\theta^{[d]}(t) = cos(\alpha t),
+ $ with $\alpha = 10\pi/t_f.$ Simulation results are shown in Fig.~\ref{fig:peformanceSinTrajectory}.
+In the beginning of the simulation, the robot starts to move away from the target according to the initial random actor weights.
+As the robot collects more data, the robot adjust the control actions as the actor and critic weights started to converge and the robot asymptotically follows the target's trajectory.
+%
+%
+ \begin{figure*}[htbp]%
 
-  In the second scenario the Target is set to move on a completely random trajectory starting from a random position around $(x^[d],y^[d])=(1,5)$ with 
+ \subfigure[][]{%
+    \label{fig:trajectorySin}%
+    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/trajectoryRandomPathDistance.eps} }
+	\subfigure[][]{%    
+    \label{fig:euclideanDistanceSin}%
+    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/euclideanDistance.eps} }
+  \\
+\subfigure[][]{%
+    \label{fig:stateErrorSin}%
+    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/stateErrorRandomPathDistance.eps} }
+ \subfigure[][]{%
+    \label{fig:controlInputsSin}%
+    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/controlInputRandomPathDistance.eps} }
+  \\
+ \subfigure[][]{%
+    \label{fig:weightCriticSin}%
+    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/weightRandomPathDistance.eps} }
+     \subfigure[][]{%
+    \label{fig:actorWeightSin}%
+    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/weightActor.eps} }
+\caption[Target tracking performance in following a sinusoidal trajectory.]{\comment{Target tracking performance in following a sinusoidal trajectory:}{Are you using CoppeliaSim results?} 
+  \subref{fig:trajectorySin} robot and target trajectories,~\subref{fig:stateErrorSin} position error $\tilde\rho_k$,~\subref{fig:controlInputsSin} linear speed and steering angle of the target, \subref{fig:weightCriticSin} critic learning weights~$\bm{\omega}_c,$ and \subref{fig:actorWeightSin} actor learning weights~${\bf W}_a$}%
+  \label{fig:peformanceSinTrajectory}%
+\end{figure*} 
+%
+\todo[inline]{Update the text below following the description for th first scenario.} %
+
+  In the second scenario, the target is set to move on a completely random trajectory starting from a random position around $(x^{[d]},y^{[d]})=(1,5)$ with 
  $\dot x^{[d]}(t) = \nu^{[d]}(t)\cos\theta^{[\ell]}(t),$ %
@@
 $ \dot\theta^{[d]}(t) = \omega(t)$,
- where $\nu^{[d]}(t)=0.2$ [m].
-The robot intial position and orientation being $(x,y) = (0,0)$.
-We intensify that the robot has no previous knoweledge of the dynamic model of the moving target nor it's initial position.
-The results obtained by the simulation are shown in figure \ref{fig:simulationResults}.
-the control actions of the robot are determined by the random actor weights .we clearly see tracking error converges and approaches zero as the control signal converging to values that allows target tracking.
-the results reveal the ability of the proposed algorithm to sucessfully track the dynamic moving target and adapt to the changes in the target's trajectory and learns online by trial and error in different scenarios.
-%\begin{figure}
-%   \centering
-%   \fcolorbox{gray!10}{gray!5}{
-%     \includegraphics[width=0.45\textwidth]{figs/coppeliasim.png}
-%`     }
-%   \caption{Simulation Setup}
-%   \label{fig:CoppeliaSim Scene}
-% \end{figure}  
- \begin{figure*}[htbp]%
+ where $\nu^{[d]}(t)=0.2~[\si{\meter}].$\comment{~}{What about $\omega$?} The robot initial position and orientation being $(x,y) = (0,0)$.
+We intensify that the robot has no previous knowledge of the dynamic model of the moving target nor it's initial position.
+The results obtained by the simulation are shown in~Fig.\ref{fig:simulationResults}.
+The control actions of the robot are determined by the random actor weights.
+We clearly see tracking error converges and approaches zero as the control signal converging to values that allows target tracking.
+The results reveal the ability of the proposed algorithm to sucessfully track the dynamic moving target and adapt to the changes in the target's trajectory and learns online by trial and error in different scenarios.
 
- \subfigure[][]{%
-    \label{fig:trajectoryRandom}%
-    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/trajectoryRandomPathDistance.eps} }
-	\subfigure[][]{%    
-    \label{fig:euclideanDistance}%
-    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/euclideanDistance.eps} }
-\subfigure[][]{%
-    \label{fig:stateErrorRandom}%
-    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/stateErrorRandomPathDistance.eps} }
- \subfigure[][]{%
-    \label{fig:controlInputsRandom}%
-    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/controlInputRandomPathDistance.eps} }
- \subfigure[][]{%
-    \label{fig:weightRandomDistance}%
-    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/weightRandomPathDistance.eps} }
-     \subfigure[][]{%
-    \label{fig:actorWeightRandomDistance}%
-    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/weightActor.eps} }
-\caption[Leader-follower performance for random trajectory.]{Performance in tracking random trajectory: 
-  \subref{fig:trajectoryRandom} leader-follower trajectories,~\subref{fig:stateErrorRandom} state error,~\subref{fig:controlInputsRandom} linear speed and steering angle of the follower; and    \subref{fig:weightRandomDistance} learning weights.}%
-  \label{fig:peformanceRandomTrajectory}%
-	\label{fig:simulationResults}
-\end{figure*}
+%  \begin{figure*}[htbp]%
 
- \begin{figure*}[htbp]%
-
- \subfigure[][]{%
-    \label{fig:trajectoryRandom}%
-    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/trajectoryRandomPathDistance.eps} }
-	\subfigure[][]{%    
-    \label{fig:euclideanDistance}%
-    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/euclideanDistance.eps} }
-\subfigure[][]{%
-    \label{fig:stateErrorRandom}%
-    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/stateErrorRandomPathDistance.eps} }
- \subfigure[][]{%
-    \label{fig:controlInputsRandom}%
-    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/controlInputRandomPathDistance.eps} }
- \subfigure[][]{%
-    \label{fig:weightRandomDistance}%
-    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/weightRandomPathDistance.eps} }
-     \subfigure[][]{%
-    \label{fig:actorWeightRandomDistance}%
-    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/weightActor.eps} }
-\caption[Leader-follower performance for random trajectory.]{Performance in tracking random trajectory: 
-  \subref{fig:trajectoryRandom} leader-follower trajectories,~\subref{fig:stateErrorRandom} state error,~\subref{fig:controlInputsRandom} linear speed and steering angle of the follower; and    \subref{fig:weightRandomDistance} learning weights.}%
-  \label{fig:peformanceRandomTrajectory}%
-	\label{fig:simulationResults}
-\end{figure*}
+%  \subfigure[][]{%
+%     \label{fig:trajectoryRandom}%
+%     \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/trajectoryRandomPathDistance.eps} }
+% 	\subfigure[][]{%    
+%     \label{fig:euclideanDistance}%
+%     \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/euclideanDistance.eps} }
+% \subfigure[][]{%
+%     \label{fig:stateErrorRandom}%
+%     \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/stateErrorRandomPathDistance.eps} }
+%  \subfigure[][]{%
+%     \label{fig:controlInputsRandom}%
+%     \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/controlInputRandomPathDistance.eps} }
+%  \subfigure[][]{%
+%     \label{fig:weightRandomDistance}%
+%     \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/weightRandomPathDistance.eps} }
+%      \subfigure[][]{%
+%     \label{fig:actorWeightRandomDistance}%
+%     \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/weightActor.eps} }
+% \caption[Leader-follower performance for random trajectory.]{Performance in tracking random trajectory: 
+%   \subref{fig:trajectoryRandom} robot and target trajectories,~\subref{fig:stateErrorRandom} position error~$\tilde{\rho}_k$,~\subref{fig:controlInputsRandom} linear speed and steering angle of the follower; and    \subref{fig:weightRandomDistance} learning weights.}%
+%   \label{fig:peformanceRandomTrajectory}%
+% 	\label{fig:simulationResults}
+% \end{figure*}
 

### 2020-07-05 paperMIC2020/paperIEEE-MIC2020-V1.tex
Results and Conclusion sections are updated with some comments

@@
  $\theta^{[d]}(t) = cos(\alpha t),
- $ with $\alpha = 10\pi/t_f.$ Simulation results are shown in Fig.~\ref{fig:peformanceSinTrajectory}.
+ $ with $\alpha = 10\pi/t_f.$ Simulation results are shown in Fig.~\ref{fig:performanceSin}.
 In the beginning of the simulation, the robot starts to move away from the target according to the initial random actor weights.
@@
  \subfigure[][]{%
-    \label{fig:weightCriticSin}%
+    \label{fig:criticWeightSin}%
     \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/weightRandomPathDistance.eps} }
@@
     \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/weightActor.eps} }
-\caption[Target tracking performance in following a sinusoidal trajectory.]{\comment{Target tracking performance in following a sinusoidal trajectory:}{Are you using CoppeliaSim results?} 
-  \subref{fig:trajectorySin} robot and target trajectories,~\subref{fig:stateErrorSin} position error $\tilde\rho_k$,~\subref{fig:controlInputsSin} linear speed and steering angle of the target, \subref{fig:weightCriticSin} critic learning weights~$\bm{\omega}_c,$ and \subref{fig:actorWeightSin} actor learning weights~${\bf W}_a$}%
-  \label{fig:peformanceSinTrajectory}%
+\caption[Robot tracking a target that is following a sinusoidal trajectory.]{\comment{Robot tracking a target that is  following a sinusoidal trajectory:}{Are you using CoppeliaSim results?} 
+  \subref{fig:trajectorySin} robot and target trajectories,~\subref{fig:stateErrorSin} position error $\tilde\rho_k$,~\subref{fig:controlInputsSin} linear speed and steering angle of the target, \subref{fig:criticWeightSin} critic learning weights~$\bm{\omega}_c,$ and \subref{fig:actorWeightSin} actor learning weights~${\bf W}_a$}%
+  \label{fig:performanceSin}%
 \end{figure*} 
 %
-\todo[inline]{Update the text below following the description for th first scenario.} %
 
-  In the second scenario, the target is set to move on a completely random trajectory starting from a random position around $(x^{[d]},y^{[d]})=(1,5)$ with 
- $\dot x^{[d]}(t) = \nu^{[d]}(t)\cos\theta^{[\ell]}(t),$ %
- $\dot y^{[d]}(t) = \nu^{[d]}(t)\sin\theta^{[\ell]}(t).$
-$ \dot\theta^{[d]}(t) = \omega(t)$,
- where $\nu^{[d]}(t)=0.2~[\si{\meter}].$\comment{~}{What about $\omega$?} The robot initial position and orientation being $(x,y) = (0,0)$.
-We intensify that the robot has no previous knowledge of the dynamic model of the moving target nor it's initial position.
-The results obtained by the simulation are shown in~Fig.\ref{fig:simulationResults}.
+In the second scenario, the target is set to move on a completely random trajectory starting from a random initial position $(x^{[d]},y^{[d]})\approx (1,5)~[\si{\meter}],$ where the \comment{target is now modeled as an unicycle robot}{Previously we talk about point robot model for the target but now you are using the following model for the target} described by %
+%
+ $x_{k+1}^{[d]} = x_k^{[d]} + T\nu_k^{[d]}\cos\theta_k^{[d]},$ %
+ $y_{k+1}^{[d]} = y_k^{[d]} + T\nu_k^{[d]}\sin\theta_k^{[d]},$ %
+ $\theta_{k+1}^{[d]} = \theta_k^{[d]} +T\omega_k^{[d]},$ %
+ %
+ where $\nu^{[d]}(t)=0.2~[\si{\meter}]$\comment{~}{What about $\omega$?} The robot initial position and orientation being $(x,y) = (0,0)~[\si{\meter}]$ and $\theta_0 = $ We intensify that the robot has no previous knowledge of the dynamic model of the moving target\comment{nor it's initial position}{Robot does need to know the target's position through the sensors}.
+The results obtained by the simulation are shown in Fig.~\ref{fig:performanceRandom}.
 The control actions of the robot are determined by the random actor weights.
 We clearly see tracking error converges and approaches zero as the control signal converging to values that allows target tracking.
-The results reveal the ability of the proposed algorithm to sucessfully track the dynamic moving target and adapt to the changes in the target's trajectory and learns online by trial and error in different scenarios.
-
-%  \begin{figure*}[htbp]%
-
-%  \subfigure[][]{%
-%     \label{fig:trajectoryRandom}%
-%     \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/trajectoryRandomPathDistance.eps} }
-% 	\subfigure[][]{%    
-%     \label{fig:euclideanDistance}%
-%     \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/euclideanDistance.eps} }
-% \subfigure[][]{%
-%     \label{fig:stateErrorRandom}%
-%     \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/stateErrorRandomPathDistance.eps} }
-%  \subfigure[][]{%
-%     \label{fig:controlInputsRandom}%
-%     \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/controlInputRandomPathDistance.eps} }
-%  \subfigure[][]{%
-%     \label{fig:weightRandomDistance}%
-%     \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/weightRandomPathDistance.eps} }
-%      \subfigure[][]{%
-%     \label{fig:actorWeightRandomDistance}%
-%     \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/weightActor.eps} }
-% \caption[Leader-follower performance for random trajectory.]{Performance in tracking random trajectory: 
-%   \subref{fig:trajectoryRandom} robot and target trajectories,~\subref{fig:stateErrorRandom} position error~$\tilde{\rho}_k$,~\subref{fig:controlInputsRandom} linear speed and steering angle of the follower; and    \subref{fig:weightRandomDistance} learning weights.}%
-%   \label{fig:peformanceRandomTrajectory}%
-% 	\label{fig:simulationResults}
-% \end{figure*}
+The results reveal the ability of the proposed algorithm to successfully track the dynamic moving target and adapt to the changes in the target's trajectory and learns online by trial and error in different scenarios.
+%
+%    
+ \begin{figure*}[htbp]%
+ \subfigure[][]{%
+    \label{fig:trajectoryRandom}%
+    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/trajectoryRandomPathDistance.eps} }
+	\subfigure[][]{%    
+    \label{fig:euclideanDistanceRandom}%
+    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/euclideanDistance.eps} }
+\subfigure[][]{%
+    \label{fig:stateErrorRandom}%
+    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/stateErrorRandomPathDistance.eps} }
+ \subfigure[][]{%
+    \label{fig:controlInputsRandom}%
+    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/controlInputRandomPathDistance.eps} }
+ \subfigure[][]{%
+    \label{fig:criticWeightRandom}%
+    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/weightRandomPathDistance.eps} }
+     \subfigure[][]{%
+    \label{fig:actorWeightRandom}%
+    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/weightActor.eps} }
+  \caption[Robot tracking a target that is  following a random trajectory.]{Robot tracking a target that is  following a random trajectory:
+  \subref{fig:trajectoryRandom} robot and target trajectories,~\subref{fig:stateErrorRandom} position error $\tilde\rho_k$,~\subref{fig:controlInputsRandom} linear speed and steering angle of the target, \subref{fig:criticWeightRandom} critic learning weights~$\bm{\omega}_c,$ and \subref{fig:actorWeightRandom} actor learning weights~${\bf W}_a$}%
+  \label{fig:performanceRandom}%
+\end{figure*}
 
@@
 
-	A model free actor-critic reinfoncement learning algorithm for dynamic target tracking has been validated using set of computer simulation where a differenitial drive mobile robot and a randomly moving target are utilized in the simulation.Opposed to previous approaches in the litrature this Algorithm possess the advantage of being completlety model free and doesn't rely on any dynamic model to be known in priori.
-The actor weights which drives the control actions of the robot sucessfully converge to values that enable the robot to asymptotically track the moving target through unplanned trajectory.
-To the authors knowlege this work is the first of its kind to employ a model-free actor-critic RL approach  in the context of dynamic target tracking.
-In future work the proposed approach will be applied to multi-robot scenarios where a number of robots are to achieve a certain task in unknown enviroments.
+A model free actor-critic reinforcement learning algorithm for dynamic target
+tracking has been proposed and validated using a set of computer simulation
+where a differential drive mobile robot and a randomly moving target are
+utilized in the simulation. As opposed to previous approaches in the literature,
+the proposed approach possess the advantage of being completely model free and
+does not  rely on any dynamic model of robots. The actor weights which
+drives the control actions of the robot successfully converge to values that
+enable the robot to asymptotically track the moving target through unplanned
+trajectory. In future work, the proposed approach will be applied to multi-robot scenarios
+where a number of robots are to achieve a certain task in unknown environments.
 

### 2020-07-10 paperMIC2020/paperIEEE-MIC2020-V1.tex
addressed issues

@@
     }
-   \caption{Mobile robot and its dynamic target tracking problem setup. \todo[inline]{In this figure, replace $\tilde\theta_k$ with $\theta_k^{'}$}}
+   \caption{Mobile robot and its dynamic target tracking problem setup.}
    \label{fig:leaderFollowerSetup}
@@
          $k=0, r = 0$ \tcc*[h]{Discrete time and policy indices}\;
+         n = 2 , m = 2 \tcc*[h]{state error and input dimensions}\;
          $\eta = (n+m)(n+m+1)/2$\;
@@
  This section adopts the theoretical results discussed in the previous section by simulating Algorithm~\ref{alg:ModelFreeTracking} using a differential drive mobile robot.
-The proposed actor-critic RL algorithm is tested  utilizing MATLAB software and Robot Operating System (ROS)  as a preliminary step to implement the Algorithm experimentally in real world.
+The proposed actor-critic RL algorithm is tested  utilizing MATLAB software in a laptop computer running Ubuntu 18.04 as a preliminary step to implement the Algorithm experimentally in real world.
 Here we present the performance of the proposed method and the convergence characteristics of the actor and critic weights.
@@
 
- In the first scenario, the differential drive robot was initially placed at position $(x^d,y^d) = (-1,-5)~[\si{\meter}] $ with an orientation of $\theta = 0\degree.$ The target which is modeled as a \comment{cylinder object}{we are running MATLAB simulation and using point robot as a target} was initially located at a random position around  $(x,y) = (0,0)~[\si{\meter}].$ The simulation was run for the duration of $t_f=60~[\second].$ The target is set to move following a sinusoidal path modeled as  $
+ In the first scenario, the differential drive robot was initially placed at position $(x^d,y^d) = (-2,-2)~[\si{\meter}] $ with an orientation of $\theta = 0\degree.$ The target which is modeled as a point robot was initially located at a random position around  $(x,y) = (0,0)~[\si{\meter}].$ The simulation was run for the duration of $t_f=60~[\second].$ The target is set to move following a sinusoidal path modeled as  $
  x^{[d]}(t) = \alpha t, %
@@
  $\theta^{[d]}(t) = cos(\alpha t),
- $ with $\alpha = 10\pi/t_f.$ Simulation results are shown in Fig.~\ref{fig:performanceSin}.
-In the beginning of the simulation, the robot starts to move away from the target according to the initial random actor weights.
-As the robot collects more data, the robot adjust the control actions as the actor and critic weights started to converge and the robot asymptotically follows the target's trajectory.
+ $ with $\alpha = 4\pi/t_f.$ and $t=kT$, $T$ represents the sampling time while $k$ being timing index.
+Simulation results are shown in Fig.~\ref{fig:performanceSin}.
+In the beginning of the simulation, the robot starts to move away from the target according to the initial random actor weights as we see in \ref{fig:trajectorySin}.In Fig \ref{fig:euclideanDistanceSin} the euclidean distance overshoots before finally approaching zero.
+As the robot collects more data, the robot adjust the control actions as the actor and critic weights started to converge and the robot asymptotically follows the target's trajectory as can be seen in Fig \ref{fig:criticWeightSin} and \ref{fig:actorWeightSin}.
 %
@@
     \label{fig:trajectorySin}%
-    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/trajectoryRandomPathDistance.eps} }
+    \includegraphics[width=0.48\textwidth,height=0.15\textheight]{matlabsim/sinePath/OUT/trajectorySineWave.eps} }
 	\subfigure[][]{%    
     \label{fig:euclideanDistanceSin}%
-    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/euclideanDistance.eps} }
-  \\
-\subfigure[][]{%
-    \label{fig:stateErrorSin}%
-    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/stateErrorRandomPathDistance.eps} }
- \subfigure[][]{%
-    \label{fig:controlInputsSin}%
-    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/controlInputRandomPathDistance.eps} }
+    \includegraphics[width=0.48\textwidth,height=0.15\textheight]{matlabsim/sinePath/OUT/euclideanDistanceSineWave.eps} }
+%  \\
+%\subfigure[][]{%
+%    \label{fig:stateErrorSin}%
+%    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/stateErrorRandomPathDistance.eps} }
+% \subfigure[][]{%
+%    \label{fig:controlInputsSin}%
+%    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/controlInputRandomPathDistance.eps} }
   \\
@@
     \label{fig:criticWeightSin}%
-    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/weightRandomPathDistance.eps} }
+    \includegraphics[width=0.48\textwidth,height=0.15\textheight]{matlabsim/sinePath/OUT/weightSineWave.eps} }
      \subfigure[][]{%
     \label{fig:actorWeightSin}%
-    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/weightActor.eps} }
-\caption[Robot tracking a target that is following a sinusoidal trajectory.]{\comment{Robot tracking a target that is  following a sinusoidal trajectory:}{Are you using CoppeliaSim results?} 
-  \subref{fig:trajectorySin} robot and target trajectories,~\subref{fig:stateErrorSin} position error $\tilde\rho_k$,~\subref{fig:controlInputsSin} linear speed and steering angle of the target, \subref{fig:criticWeightSin} critic learning weights~$\bm{\omega}_c,$ and \subref{fig:actorWeightSin} actor learning weights~${\bf W}_a$}%
+    \includegraphics[width=0.48\textwidth,height=0.15\textheight]{matlabsim/sinePath/OUT/weightActorSineWave.eps} }
+\caption[Robot tracking a target that is  following a random trajectory.]{Robot tracking a target that is  following a random trajectory:
+  \subref{fig:trajectoryRandom} robot and target trajectories,~\subref{fig:euclideanDistanceRandom} position error $\tilde\rho_k$, \subref{fig:criticWeightRandom} critic learning weights~$\bm{\omega}_c,$ and \subref{fig:actorWeightRandom} actor learning weights~${\bf W}_a$}
     \label{fig:performanceSin}%
@@
 
-In the second scenario, the target is set to move on a completely random trajectory starting from a random initial position $(x^{[d]},y^{[d]})\approx (1,5)~[\si{\meter}],$ where the \comment{target is now modeled as an unicycle robot}{Previously we talk about point robot model for the target but now you are using the following model for the target} described by %
+In the second scenario, the target is set to move on a completely random trajectory starting from a random initial position $(x^{[d]},y^{[d]})\approx (2,-1)~[\si{\meter}],$ where the target is now modeled as a point robot as described in ~\eqref{eq:leaderDT}
  %
- $x_{k+1}^{[d]} = x_k^{[d]} + T\nu_k^{[d]}\cos\theta_k^{[d]},$ %
- $y_{k+1}^{[d]} = y_k^{[d]} + T\nu_k^{[d]}\sin\theta_k^{[d]},$ %
- $\theta_{k+1}^{[d]} = \theta_k^{[d]} +T\omega_k^{[d]},$ %
- %
- where $\nu^{[d]}(t)=0.2~[\si{\meter}]$\comment{~}{What about $\omega$?} The robot initial position and orientation being $(x,y) = (0,0)~[\si{\meter}]$ and $\theta_0 = $ We intensify that the robot has no previous knowledge of the dynamic model of the moving target\comment{nor it's initial position}{Robot does need to know the target's position through the sensors}.
-The results obtained by the simulation are shown in Fig.~\ref{fig:performanceRandom}.
+ where $\mathbf{u}_k^{[d]}=[\nu^{[d]},\omega^{[d]}] $ with $\nu^{[d]}(t)=0.2~[\si{\meter}]$ and $\omega$ randomly chaning in the range of $({-\pi},{\pi}) $.
+The robot initial position and orientation are $(x,y) = (0,0)~[\si{\meter}]$ and $\theta_0=0$ .We intensify that the robot has no previous knowledge of the dynamic model of the moving target.
+The results obtained by the simulation are shown in Fig.~\ref{fig:performanceRandom}.Figure \ref{fig:trajectoryRandom} describes the trajectory of the robot and the target during the simulation.
 The control actions of the robot are determined by the random actor weights.
-We clearly see tracking error converges and approaches zero as the control signal converging to values that allows target tracking.
+We clearly see euclidean distance in Fig \ref{fig:euclideanDistanceRandom} converges and approaches zero as actor and critic weights converges to values that allows target tracking as can be seen in fig \ref{fig:criticWeightRandom} and \ref{fig:actorWeightRandom}.
 The results reveal the ability of the proposed algorithm to successfully track the dynamic moving target and adapt to the changes in the target's trajectory and learns online by trial and error in different scenarios.
@@
     \label{fig:trajectoryRandom}%
-    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/trajectoryRandomPathDistance.eps} }
+    \includegraphics[width=0.48\textwidth,height=0.15\textheight]{matlabsim/randomPath/OUT/trajectoryRandom.eps} }
 	\subfigure[][]{%    
     \label{fig:euclideanDistanceRandom}%
-    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/euclideanDistance.eps} }
-\subfigure[][]{%
-    \label{fig:stateErrorRandom}%
-    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/stateErrorRandomPathDistance.eps} }
- \subfigure[][]{%
-    \label{fig:controlInputsRandom}%
-    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/controlInputRandomPathDistance.eps} }
+    \includegraphics[width=0.48\textwidth,height=0.15\textheight]{matlabsim/randomPath/OUT/euclideanDistanceRandom.eps} }
+%\subfigure[][]{%
+%    \label{fig:stateErrorRandom}%
+%    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/stateErrorRandomPathDistance.eps} }
+% \subfigure[][]{%
+%    \label{fig:controlInputsRandom}%
+%    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/controlInputRandomPathDistance.eps} }
  \subfigure[][]{%
     \label{fig:criticWeightRandom}%
-    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/weightRandomPathDistance.eps} }
+    \includegraphics[width=0.48\textwidth,height=0.15\textheight]{matlabsim/randomPath/OUT/weightRandom.eps} }
      \subfigure[][]{%
     \label{fig:actorWeightRandom}%
-    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/weightActor.eps} }
+    \includegraphics[width=0.48\textwidth,height=0.15\textheight]{matlabsim/randomPath/OUT/weightActorRandom.eps} }
   \caption[Robot tracking a target that is  following a random trajectory.]{Robot tracking a target that is  following a random trajectory:
-  \subref{fig:trajectoryRandom} robot and target trajectories,~\subref{fig:stateErrorRandom} position error $\tilde\rho_k$,~\subref{fig:controlInputsRandom} linear speed and steering angle of the target, \subref{fig:criticWeightRandom} critic learning weights~$\bm{\omega}_c,$ and \subref{fig:actorWeightRandom} actor learning weights~${\bf W}_a$}%
+  \subref{fig:trajectoryRandom} robot and target trajectories,~\subref{fig:euclideanDistanceRandom} position error $\tilde\rho_k$, \subref{fig:criticWeightRandom} critic learning weights~$\bm{\omega}_c,$ and \subref{fig:actorWeightRandom} actor learning weights~${\bf W}_a$}%
   \label{fig:performanceRandom}%

### 2020-07-10 paperMIC2020/matlabsim/mainLF_OdometricLocalizationV9.m

@@ -1,496 +1,0 @@
-% Odometric localization or dead reckoning%   Script for simulating mobile robot.
-%Edited by AMR Elhussein on May, 29,2020.
-%gradient descent Appraoch, three cases comined fixed point, horzintal and inclined line, 
-%converged Example
-function mainLF_OdometricLocalizationV7
-
-% Created by S. Miah on Nov. 03, 2015.
-%edited by AMR Elhussein on Aug, 30,2019.
-close all
-clear all
-clc
-
-disp('Please wait while the simulation runs ...');
-
-% ---------------------
-% SIMULATION PARAMETERS
-% ---------------------
-
-% Simulation time
-t0 = 0; tf = 60; % initial and final simulation time [s]
-T = 0.001;  % Sampling time [s]
-tsteps = ceil((tf-t0)/T); % number of time steps
-dt = T*(0:tsteps)'; % Discrete time vector (include time t0 to plot initial state too)
-
-d = 0.2; %[m] safe distance
-%ROBOT PARAMETERS
-%==========================================================================
-l = 0.381; % [m]
-rad = 0.0925; % [m] radius
-%==========================================================================
-
-
-% dimension of system;
-N = 2;  % state vector dimension
-M = 2;  % input vector dimension
-
-
-% Leader's initial position
-pLeaderInit = [5;1]+rand(2,1); %[m]
-pLeaderTheta= 0; %[rad]
-
-QD(1,:) = [pLeaderInit' pLeaderTheta];
-QDinit = QD(1,:);
-%Leader's velocity 
-vLeader = 0.1; % [m/s]
-uLeader=[vLeader pLeaderTheta];
-
-% Follower robot initialization% 
-qp = [0;0]; % [m] Follower robot's position
-qTheta = 0 ;% [rad] Follower robot's orientation 
- qInit = [qp',qTheta] ;%+ rand(1,3); % row vector
-vMax = 2; % [m/s] Follower's maximum linear speed 
-
-Q(1,:) = qInit;
-
-% ----------------------
-% RUN SIMULATION 
-% ----------------------
-
-% Run the true model
-q(1,:) = qInit';
-pk = pLeaderInit;
-
-%initiating matrices
-P = [3  0   2   0.5;
[…]

### 2020-07-10 paperMIC2020/matlabsim/mainLF_OdometricLocalizationV9Sinewave.m

@@ -1,483 +1,0 @@
-% Odometric localization or dead reckoning%   Script for simulating mobile robot.
-%Edited by AMR Elhussein on May, 29,2020.
-%gradient descent Appraoch, three cases comined fixed point, horzintal and inclined line, 
-%converged Example
-function mainLF_OdometricLocalizationV7
-
-% Created by S. Miah on Nov. 03, 2015.
-%edited by AMR Elhussein on Aug, 30,2019.
-close all
-clear all
-clc
-
-disp('Please wait while the simulation runs ...');
-
-% ---------------------
-% SIMULATION PARAMETERS
-% ---------------------
-
-% Simulation time
-t0 = 0; tf = 60; % initial and final simulation time [s]
-T = 0.001;  % Sampling time [s]
-tsteps = ceil((tf-t0)/T); % number of time steps
-dt = T*(0:tsteps)'; % Discrete time vector (include time t0 to plot initial state too)
-
-d = 0.5; %[m] safe distance
-%ROBOT PARAMETERS
-%==========================================================================
-l = 0.381; % [m]
-rad = 0.0925; % [m] radius
-%==========================================================================
-
-
-% dimension of system;
-N = 2;  % state vector dimension
-M = 2;  % input vector dimension
-
-
-% Leader's initial position
-pLeaderInit = [0;0]+ rand(2,1); %[m]
-pLeaderTheta(1:tsteps,1)= 0:(10*pi)/(tsteps-1):10*pi; %[rad]
-pLeaderTheta(tsteps+1,:)=10*pi;
-QD(1,:) = [pLeaderInit' cos(0.2*pLeaderTheta(1,:))];
-
-
-QDinit = QD(1,:);
-%Leader's velocity 
-vLeader = 5; % [m/s]
-
-
-% Follower robot initialization% 
-qp = [-2;-5]; % [m] Follower robot's position
-qTheta = 0 ;% [rad] Follower robot's orientation 
- qInit = [qp',qTheta] ;%+ rand(1,3); % row vector
-vMax = 5; % [m/s] Follower's maximum linear speed 
-
-Q(1,:) = qInit;
-
-% ----------------------
-% RUN SIMULATION 
-% ----------------------
-
-% Run the true model
-q(1,:) = qInit';
[…]

### 2020-07-10 paperMIC2020/matlabsim/randomPath/mainLF_OdometricLocalizationV9.m

@@ -1,0 +1,504 @@
+% Odometric localization or dead reckoning%   Script for simulating mobile robot.
+%Edited by AMR Elhussein on May, 29,2020.
+%gradient descent Appraoch, three cases comined fixed point, horzintal and inclined line, 
+%converged Example
+function mainLF_OdometricLocalizationV7
+
+% Created by S. Miah on Nov. 03, 2015.
+%edited by AMR Elhussein on Aug, 30,2019.
+close all
+clear all
+clc
+
+disp('Please wait while the simulation runs ...');
+
+% ---------------------
+% SIMULATION PARAMETERS
+% ---------------------
+
+% Simulation time
+t0 = 0; tf = 60; % initial and final simulation time [s]
+T = 0.001;  % Sampling time [s]
+tsteps = ceil((tf-t0)/T); % number of time steps
+dt = T*(0:tsteps)'; % Discrete time vector (include time t0 to plot initial state too)
+
+d = 0.2; %[m] safe distance
+%ROBOT PARAMETERS
+%==========================================================================
+l = 0.381; % [m]
+rad = 0.0925; % [m] radius
+%==========================================================================
+
+
+% dimension of system;
+N = 2;  % state vector dimension
+M = 2;  % input vector dimension
+
+
+% Leader's initial position
+pLeaderInit = [2;-1]+rand(2,1); %[m]
+pLeaderTheta= 0; %[rad]
+
+QD(1,:) = [pLeaderInit' pLeaderTheta];
+QDinit = QD(1,:);
+%Leader's velocity 
+vLeader = 0.1; % [m/s]
+uLeader=[vLeader pLeaderTheta];
+
+% Follower robot initialization% 
+qp = [0;0]; % [m] Follower robot's position
+qTheta = 0 ;% [rad] Follower robot's orientation 
+ qInit = [qp',qTheta] ;%+ rand(1,3); % row vector
+vMax = 2; % [m/s] Follower's maximum linear speed 
+
+Q(1,:) = qInit;
+
+% ----------------------
+% RUN SIMULATION 
+% ----------------------
+
+% Run the true model
+q(1,:) = qInit';
+pk = pLeaderInit;
+
+%initiating matrices
[…]

### 2020-07-10 paperMIC2020/matlabsim/sinePath/mainLF_OdometricLocalizationV9Sinewave.m

@@ -1,0 +1,492 @@
+% Odometric localization or dead reckoning%   Script for simulating mobile robot.
+%Edited by AMR Elhussein on May, 29,2020.
+%gradient descent Appraoch, three cases comined fixed point, horzintal and inclined line, 
+%converged Example
+function mainLF_OdometricLocalizationV7
+
+% Created by S. Miah on Nov. 03, 2015.
+%edited by AMR Elhussein on Aug, 30,2019.
+close all
+clear all
+clc
+
+disp('Please wait while the simulation runs ...');
+
+% ---------------------
+% SIMULATION PARAMETERS
+% ---------------------
+
+% Simulation time
+t0 = 0; tf = 60; % initial and final simulation time [s]
+T = 0.0009;  % Sampling time [s]
+tsteps = ceil((tf-t0)/T); % number of time steps
+dt = T*(0:tsteps)'; % Discrete time vector (include time t0 to plot initial state too)
+
+d = 0.5; %[m] safe distance
+%ROBOT PARAMETERS
+%==========================================================================
+l = 0.381; % [m]
+rad = 0.0925; % [m] radius
+%==========================================================================
+
+
+% dimension of system;
+N = 2;  % state vector dimension
+M = 2;  % input vector dimension
+
+
+% Leader's initial position
+pLeaderInit = [0;0];%+ rand(2,1); %[m]
+pLeaderTheta(:,1)= 0:(4*pi)/(tsteps-1):4*pi; %[rad]
+alpha = 4*pi/tf;
+pLeaderTheta(tsteps+1,:)=4*pi;
+
+QD(1,:) = [pLeaderInit' cos(0.1*pLeaderTheta(1,:))];
+
+
+QDinit = QD(1,:);
+%Leader's velocity 
+vLeader = 2; % [m/s]
+
+
+% Follower robot initialization% 
+qp = [-2;-2]; % [m] Follower robot's position
+qTheta = 0 ;% [rad] Follower robot's orientation 
+ qInit = [qp',qTheta] ;%+ rand(1,3); % row vector
+vMax = 5; % [m/s] Follower's maximum linear speed 
+
+Q(1,:) = qInit;
+
+% ----------------------
+% RUN SIMULATION 
+% ----------------------
+
[…]

### 2020-07-10 paperMIC2020/paperIEEE-MIC2020-V1.tex
cleaned and removed pdf
add refrences

@@
 Tracking a random moving target using a mobile robot is a key problem and a fundamental feature in autonomous robots operating in areas such as surveillance, search and rescue missions, environmental monitoring, household cleaning, to name a few~\cite{kolling2006,Encarnacao2001,Ju2001,Kitowski2012,Zhang2013}.
-Throughout the years, the dynamic target tracking problem has received a profound amount of research in academia and industry\todo{Add 2 recent references}.
+Throughout the years, the dynamic target tracking problem has received a profound amount of research in academia and industry \cite{wei2018}, \cite{liu2019}  .
 This is mainly due to their inherent complex nonlinear dynamics.
@@
 %
- where $\ell_a$ is the actor learning rate.
-The complete policy iteration solution process for the leader-follower problem is detailed out in Algorithm~\ref{alg:ModelFreeTracking}.
-\todo[inline]{In Algorithm 1, add a line with $n=2$ (state error dimension) and $m=2$ (input dimension)} %
+ where $\ell_a$ is the actor learning rate.  The complete policy iteration solution process for the leader-follower problem is detailed out in Algorithm~\ref{alg:ModelFreeTracking}. 
  %

### 2020-07-10 paperMIC2020/paperIEEE-MIC2020-V1.tex
Paper edited.

--- 2020-07-10 paperMIC2020/paperIEEE-MIC2020-V1.tex
@@
 \author{%~
-\IEEEauthorblockN{Amr Elhussein and Md Suruz Miah}
-\IEEEauthorblockA{\textit{Electrical \& Computer Eng.} \\
-\textit{Bradley University}, Peoria, Illinois, USA \\
- aelhussein@mail.bradley.edu and smiah@bradley.edu}
-% \and
-% \IEEEauthorblockN{Fazel Keshtkar}
-% \IEEEauthorblockA{\textit{Div. of Computer Science, Math. and Science} \\
-% \textit{St John's University}, Queens, NY, USA \\
-% keshtkaf@stjohns.edu}
-% \and
-% \IEEEauthorblockN{Mohammed Abouheaf}
-% \IEEEauthorblockA{\textit{School of EECS} \\
-% \textit{Univ. of Ottawa}, Canada\\
-% mabouhea@uottawa.ca}
-%
+  ~ % Author names removed for blind review 
+% \IEEEauthorblockN{Amr Elhussein and Md Suruz Miah}
+% \IEEEauthorblockA{\textit{Electrical \& Computer Eng.} \\
+% \textit{Bradley University}, Peoria, Illinois, USA \\
+%  aelhussein@mail.bradley.edu and smiah@bradley.edu}
 }
@@
   %
-  Addressing the trajectory tracking problem of a mobile robot in tracking a dynamic target is still one of the challenging problems in the field of robotics.
-In this paper, we address the position tracking problem of a mobile robot where it is supposed to track the position of an mobile target whose dynamics is unknown a priori.
-This problem is even more challenging when the dynamics of the mobile robot is also assumed to be unknown, which is indeed a realistic assumption.
-Most of trajectory tracking problems proposed in the literature in the field of mobile robotics are either focused on algorithms that rely on mathematical models of the robots or driven by a  overwhelming degree of computational complexity.
-This paper proposes a model-free actor-critic reinforcement learning strategy to determine appropriate actuator commands for the robot to track the position of the target.
-We emphasize that mathematical models of both mobile robot and the target are not required in the current approach.
-Moreover, Bellman's principle of optimality is utilized to minimize the energy required for the robot to track the target.
-The performance of the proposed actor-critic reinforcement learning approach  is backed by a set of computer simulations with various complexities using a virtual circular-shaped mobile robot and a point target  modeled by an integrator.
+  Addressing the trajectory tracking problem of a mobile robot in tracking a
+  dynamic target is still one of the challenging problems in the field of
+  robotics. In this paper, we address the position tracking problem of a mobile
+  robot where it is supposed to track the position of an mobile target whose
+  dynamics is unknown a priori. This problem is even more challenging when the
+  dynamics of the mobile robot is also assumed to be unknown, which is indeed a
+  realistic assumption. Most of the trajectory tracking solutions proposed in the
+  literature in the field of mobile robotics are either focused on algorithms
+  that rely on mathematical models of the robots or driven by a overwhelming
+  degree of computational complexity. This paper proposes a model-free
+  actor-critic reinforcement learning strategy to determine appropriate actuator
+  commands for the robot to track the position of the target. We emphasize that
+  mathematical models of both mobile robot and the target are not required in
+  the current approach. Moreover, Bellman's principle of optimality is utilized
+  to minimize the energy required for the robot to track the target. The
+  performance of the proposed actor-critic reinforcement learning approach is
+  backed by a set of computer experiments with various complexities using a
+  virtual circular-shaped mobile robot and a point target modeled by an
+  integrator.
 %
@@
 \begin{IEEEkeywords}
-target tracking, mobile robots, reinforcement learning, policy iteration, trajectory tracking
+  Mobile robots, policy iteration, reinforcement learning, target tracking, trajectory tracking
 \end{IEEEkeywords}
@@
 
-Tracking a random moving target using a mobile robot is a key problem and a fundamental feature in autonomous robots operating in areas such as surveillance, search and rescue missions, environmental monitoring, household cleaning, to name a few~\cite{kolling2006,Encarnacao2001,Ju2001,Kitowski2012,Zhang2013}.
-Throughout the years, the dynamic target tracking problem has received a profound amount of research in academia and industry\todo{Add 2 recent references}.
-This is mainly due to their inherent complex nonlinear dynamics.
-Most of the target tracking algorithms proposed in the literature either rely on A) mathematical and kinematic models of both the robot and the target \cite{Huang2008}, B) the assumption that the target or its trajectory are static and known a priori, and C) nonlinear control or soft-computing techniques that are driven by large amount of mostly offline data that leads to an overwhelming degree of computational complexity \cite{KD2007,Cren2017}.
-In a typical tracking problem, a robot is to apply a local control actions that enable it to maintain a relative position and orientation from the designated target while following a certain trajectory.
-It can also be applied on a fleet of robots where multiple robots maintain a geometric configuration relative to the target\cite{Oh2015-Survey,Liu2017-Modular}.
+Tracking a random moving target using a mobile robot is a key problem and a
+fundamental feature in autonomous robots operating in areas such as
+surveillance, search and rescue missions, environmental monitoring, household
+cleaning, to name a
+few~\cite{kolling2006,Encarnacao2001,Ju2001,Kitowski2012,Zhang2013}. Throughout
+the years, the dynamic target tracking problem has received a profound amount of
+research in academia and industry\todo{Add 2 recent references}. This is mainly
+due to their inherent complex nonlinear dynamics. Most of the target tracking
+algorithms proposed in the literature either rely on A) mathematical and
+kinematic models of both the robot and the target \cite{Huang2008}, B) the
+assumption that the target or its trajectory are static and known a priori, and
+C) nonlinear control or soft-computing techniques that are driven by large
+amount of mostly offline data that leads to an overwhelming degree of
+computational complexity~\cite{KD2007,Cren2017}. In a typical target tracking problem,
+a robot is to apply local control actions that enable it to maintain a
+relative position and orientation from the designated target while following a
+certain trajectory. It can also be applied on a fleet of robots where multiple
+robots maintain a geometric configuration relative to the
+target~\cite{Oh2015-Survey,Liu2017-Modular}.
 
@@
 
-Reinforcement learning (RL) is an emerging field of machine learning which refers to a set of algorithms and techniques in which agents learn by interacting with the environment and determine their own sets of actions that define trajectories.
-Reinforcement learning has long been applied on games and simulated environments but it has recently been explored to robots in real world applications, such as localization and mapping, area coverage, path planning and obstacle avoidance \cite{kober2013reinforcement,smart2002,michels2005,adekunle2016}.
+Reinforcement learning (RL) is an emerging sub-field of machine learning which
+refers to a set of algorithms and techniques in which agents learn by
+interacting with the environment and determine their own sets of actions that
+define trajectories. Reinforcement learning has long been applied on games and
+simulated environments but it has recently been explored to robots in real world
+applications, such as localization and mapping, area coverage, path planning and
+obstacle avoidance
+\cite{kober2013reinforcement,smart2002,michels2005,adekunle2016}.
 
-In this paper, we develop a model-free actor-critic learning approach to control a non-holonomic wheeled mobile robot.
-The proposed method offers many advantages over other methods mentioned in the literature, such as being completely model free and does not require any knowledge of the mathematical model of the robot or the moving target and without the need for large computational power.
-The steering angle and the linear speed of the robot referred to as the policy (control actions) are determined by collecting the position and orientation of both the target and the robot.
-This set of information is gathered online over a finite period of time.
-The optimal control actions are then generated by utilizing Bellman's principle of optimality which acts as model free-reinforcement learning approach that allows the robot to follow the trajectory of the target while avoiding collision by maintaining a safe distance.
-Here, we extend the work proposed by authors in \cite{miah2020} by incorporating actor neural network along with critic network to find optimal control policy for the trajectory tracking problem.
-This work acts as first milestone in generalizing the algorithm to solve more sophisticated problem such as typical area coverage and mapping problems in the field of robotics.
+In this paper, we develop a model-free actor-critic learning approach to control
+a non-holonomic wheeled mobile robot. The proposed method offers many advantages
+over other methods mentioned in the literature, such as being completely model
+free and does not require any knowledge of the mathematical model of the robot
+or the moving target and without the need for large computational power. The
+steering angle and the linear speed of the robot referred to as the policy
+(control actions) are determined by collecting the position and orientation of
+both the target and the robot. This set of information is gathered online over a
+finite period of time. The optimal control actions are then generated by
+utilizing Bellman's principle of optimality which acts as model-free reinforcement learning approach that allows the robot to follow the
+trajectory of the target while avoiding collision by maintaining a safe
+distance. Here, we extend the work proposed by authors in~\cite{miah2020} by
+incorporating actor neural network along with critic network to find optimal
+control policy for the trajectory tracking problem. This work acts as the first
+milestone in generalizing the algorithm to solve more sophisticated problem such
+as typical area coverage and mapping problems in the field of robotics.
 
-The rest of the paper is organized as follows.
-Section~\ref{sec:problemSetting} lays down the problem setting of the dynamic target tracking problem and mathematical models of the robot and the state error.
-The model free actor-critic reinforcement learning algorithm and its associated  mathematical derivations are detailed in section~\ref{sec:RLSolution}.
-Section~\ref{sec:resultsExperiments} illustrates computer simulations for different scenarios that reflect the effectiveness of the proposed method followed by conlusion and future work presented in section~\ref{sec:conclusion}.
+The rest of the paper is organized as follows. Section~\ref{sec:problemSetting}
+lays down the problem setting of the dynamic target tracking problem and
+mathematical models of the robot and the state error. The model~free
+actor-critic reinforcement learning algorithm and its associated  mathematical
+derivations are detailed in section~\ref{sec:RLSolution}.
+Section~\ref{sec:resultsExperiments} illustrates computer experiments for different scenarios that reflect the effectiveness of the proposed method followed by conclusion and future work presented in section~\ref{sec:conclusion}.
 
@@
 
- Reinforcement learning is a promising  machine learning technique that is widely used in solving problems of many cyber-physical systems that pertain to the goal-directed learning from interaction~\cite{sutton2020reinforcement}.
-In this paper, tracking a mobile target using a wheeled mobile robot is formulated as a reinforcement learning problem, where the goal of the robot is to track the trajectory of a target while maintaining the safe-distance $d>0.$ The RL solution employed in the current problem leverages Bellman's principle of optimality to decide on the appropriate control actions (actuator commands) for the robot to track the position trajectory of the target.
-The relative importance of the states in the error vector ${\bf e}_k$ and the control decisions (linear velocity $\nu_k$ and steering angle $\gamma_k$) of the robot are evaluated using the  performance (cost) index %
+ Reinforcement learning is a promising machine learning technique that is widely
+ used for solving problems of many cyber-physical systems that pertain to  
+ goal-directed learning from interaction~\cite{sutton2020reinforcement}. In this
+ paper, tracking a mobile target using a wheeled mobile robot is formulated as a
+ reinforcement learning problem, where the goal of the robot is to track the
+ trajectory of a target while maintaining the safe-distance $d>0.$ The RL
+ solution employed in the current problem leverages Bellman's principle of
+ optimality to decide on the appropriate control actions (actuator commands) for
+ the robot to track the position trajectory of the target. The relative
+ importance of the states in the error vector ${\bf e}_k$ and the control
+ decisions (linear velocity $\nu_k$ and steering angle $\gamma_k$) of the robot
+ are evaluated using the performance (cost) index %
  %
@@
 %
- where $\ell_a$ is the actor learning rate.
-The complete policy iteration solution process for the leader-follower problem is detailed out in Algorithm~\ref{alg:ModelFreeTracking}.
-\todo[inline]{In Algorithm 1, add a line with $n=2$ (state error dimension) and $m=2$ (input dimension)} %
+ where $\ell_a$ is the actor learning rate.  The complete policy iteration
+ solution process for the target tracking problem is detailed out in Algorithm~\ref{alg:ModelFreeTracking}. 
  %
@@
 
- In the first scenario, the differential drive robot was initially placed at position $(x^d,y^d) = (-2,-2)~[\si{\meter}] $ with an orientation of $\theta = 0\degree.$ The target which is modeled as a point robot was initially located at a random position around  $(x,y) = (0,0)~[\si{\meter}].$ The simulation was run for the duration of $t_f=60~[\second].$ The target is set to move following a sinusoidal path modeled as  $
- x^{[d]}(t) = \alpha t, %
+ In the first scenario, the differential drive robot was initially placed at
+ position $(x^d,y^d) = (-2,-2)~[\si{\meter}] $ with an orientation of $\theta =
+ 0\degree.$ The target which is modeled as a point robot was initially located
+ at a random position around $(x,y) = (0,0)~[\si{\meter}].$ The simulation was
+ run for the duration of $t_f=60~[\second].$ The target is set to move following
+ a sinusoidal path modeled as $ x^{[d]}(t) = \alpha t, %
  y^{[d]}(t) = 5 \,\sin(\alpha t),$ and %
- $\theta^{[d]}(t) = cos(\alpha t),
- $ with $\alpha = 4\pi/t_f.$ and $t=kT$, $T$ represents the sampling time while $k$ being timing index.
-Simulation results are shown in Fig.~\ref{fig:performanceSin}.
-In the beginning of the simulation, the robot starts to move away from the target according to the initial random actor weights as we see in \ref{fig:trajectorySin}.In Fig \ref{fig:euclideanDistanceSin} the euclidean distance overshoots before finally approaching zero.
-As the robot collects more data, the robot adjust the control actions as the actor and critic weights started to converge and the robot asymptotically follows the target's trajectory as can be seen in Fig \ref{fig:criticWeightSin} and \ref{fig:actorWeightSin}.
-%
+ $\theta^{[d]}(t) = cos(\alpha t), $ with $\alpha = 4\pi/t_f.$ and $t=kT$, $T$
+ represents the sampling time while $k$ being timing index. Simulation results
+ are shown in Fig.~\ref{fig:performanceSin}. In the beginning of the simulation,
+ the robot starts to move away from the target according to the initial random
+ actor weights as we see in \ref{fig:trajectorySin}. In Fig.~\ref{fig:euclideanDistanceSin} the euclidean distance overshoots before finally
+ approaching zero. As the robot collects more data, the robot adjust the control
+ actions as the actor and critic weights started to converge and the robot
+ asymptotically follows the target's trajectory as can be seen in Fig.~\ref{fig:criticWeightSin}~and~\ref{fig:actorWeightSin}. %
 %
@@
     \includegraphics[width=0.48\textwidth,height=0.15\textheight]{matlabsim/sinePath/OUT/weightActorSineWave.eps} }
-\caption[Robot tracking a target that is  following a random trajectory.]{Robot tracking a target that is  following a random trajectory:
-  \subref{fig:trajectoryRandom} robot and target trajectories,~\subref{fig:euclideanDistanceRandom} position error $\tilde\rho_k$, \subref{fig:criticWeightRandom} critic learning weights~$\bm{\omega}_c,$ and \subref{fig:actorWeightRandom} actor learning weights~${\bf W}_a$}
+\caption[Robot tracking a target that is  following a sinusoidal trajectory.]{Robot tracking a target that is  following a sinusoidal trajectory:
+  \subref{fig:trajectorySin} robot and target trajectories,~\subref{fig:euclideanDistanceSin} position error $\tilde\rho_k$, \subref{fig:criticWeightSin} critic learning weights~$\bm{\omega}_c,$ and \subref{fig:actorWeightRandom} actor learning weights~${\bf W}_a$}
     \label{fig:performanceSin}%
@@
 
-In the second scenario, the target is set to move on a completely random trajectory starting from a random initial position $(x^{[d]},y^{[d]})\approx (2,-1)~[\si{\meter}],$ where the target is now modeled as a point robot as described in ~\eqref{eq:leaderDT}
+In the second scenario, the target is set to move on a completely random trajectory starting from a random initial position $(x^{[d]},y^{[d]})\approx (2,-1)~[\si{\meter}],$ where the target is now modeled as a point robot as described in~\eqref{eq:leaderDT}
  %
- where $\mathbf{u}_k^{[d]}=[\nu^{[d]},\omega^{[d]}] $ with $\nu^{[d]}(t)=0.2~[\si{\meter}]$ and $\omega$ randomly chaning in the range of $({-\pi},{\pi}) $.
-The robot initial position and orientation are $(x,y) = (0,0)~[\si{\meter}]$ and $\theta_0=0$ .We intensify that the robot has no previous knowledge of the dynamic model of the moving target.
-The results obtained by the simulation are shown in Fig.~\ref{fig:performanceRandom}.Figure \ref{fig:trajectoryRandom} describes the trajectory of the robot and the target during the simulation.
-The control actions of the robot are determined by the random actor weights.
-We clearly see euclidean distance in Fig \ref{fig:euclideanDistanceRandom} converges and approaches zero as actor and critic weights converges to values that allows target tracking as can be seen in fig \ref{fig:criticWeightRandom} and \ref{fig:actorWeightRandom}.
-The results reveal the ability of the proposed algorithm to successfully track the dynamic moving target and adapt to the changes in the target's trajectory and learns online by trial and error in different scenarios.
-%
+where $\mathbf{u}_k^{[d]}=[\nu^{[d]},\omega^{[d]}] $ with
+$\nu^{[d]}(t)=0.2~[\si{\meter}]$ and $\omega$ randomly changing in the range of
+$({-\pi},{\pi}) $. The robot initial position and orientation are $(x,y) =
+(0,0)~[\si{\meter}]$ and $\theta_0=0$. We intensify that the robot has no
+previous knowledge of the dynamic model of the moving target. The results
+obtained by the simulation are shown in Fig.~\ref{fig:performanceRandom}. Fig.~\ref{fig:trajectoryRandom} describes the trajectory of the robot and the target
+during the simulation. The control actions of the robot are determined by the
+random actor weights. We clearly see Euclidean distance in Fig.~\ref{fig:euclideanDistanceRandom} converges and approaches zero as actor and
+critic weights converges to values that allows target tracking as can be seen in
+Fig.~\ref{fig:criticWeightRandom}~and~\ref{fig:actorWeightRandom}. The results
+reveal the ability of the proposed algorithm to successfully track the dynamic
+moving target and adapt to the changes in the target's trajectory and learns
+online by trial and error in different scenarios. %
 %    
@@
 A model free actor-critic reinforcement learning algorithm for dynamic target
-tracking has been proposed and validated using a set of computer simulation
+tracking has been proposed and validated using a set of computer experiments  
 where a differential drive mobile robot and a randomly moving target are

### 2020-07-10 paperMIC2020/paperIEEE-MIC2020-V1.tex

@@
 
-Tracking a random moving target using a mobile robot is a key problem and a
-fundamental feature in autonomous robots operating in areas such as
-surveillance, search and rescue missions, environmental monitoring, household
-cleaning, to name a
-few~\cite{kolling2006,Encarnacao2001,Ju2001,Kitowski2012,Zhang2013}. Throughout
-the years, the dynamic target tracking problem has received a profound amount of
-research in academia and industry\todo{Add 2 recent references}. This is mainly
-due to their inherent complex nonlinear dynamics. Most of the target tracking
-algorithms proposed in the literature either rely on A) mathematical and
-kinematic models of both the robot and the target \cite{Huang2008}, B) the
-assumption that the target or its trajectory are static and known a priori, and
-C) nonlinear control or soft-computing techniques that are driven by large
-amount of mostly offline data that leads to an overwhelming degree of
-computational complexity~\cite{KD2007,Cren2017}. In a typical target tracking problem,
-a robot is to apply local control actions that enable it to maintain a
-relative position and orientation from the designated target while following a
-certain trajectory. It can also be applied on a fleet of robots where multiple
-robots maintain a geometric configuration relative to the
-target~\cite{Oh2015-Survey,Liu2017-Modular}.
+Tracking a random moving target using a mobile robot is a key problem and a fundamental feature in autonomous robots operating in areas such as surveillance, search and rescue missions, environmental monitoring, household cleaning, to name a few~\cite{kolling2006,Encarnacao2001,Ju2001,Kitowski2012,Zhang2013}.
+Throughout the years, the dynamic target tracking problem has received a profound amount of research in academia and industry \cite{wei2018,liu2019}.
+This is mainly due to their inherent complex nonlinear dynamics.
+Most of the target tracking algorithms proposed in the literature either rely on A) mathematical and kinematic models of both the robot and the target~\cite{Huang2008}, B) the assumption that the target or its trajectory are static and known a priori, and C) nonlinear control or soft-computing techniques that are driven by large amount of mostly off-line data that leads to an overwhelming degree of computational complexity~\cite{KD2007,Cren2017}.
+In a typical tracking problem, a robot is to apply a local control actions that enable it to maintain a relative position and orientation from the designated target while following a certain trajectory.
+It can also be applied on a fleet of robots where multiple robots maintain a geometric configuration relative to the target\cite{Oh2015-Survey,Liu2017-Modular}.
 

### 2020-07-10 paperMIC2020/paperIEEE-MIC2020-V1.tex
Paper has been edited and merged with latest references

@@
 
-Tracking a random moving target using a mobile robot is a key problem and a fundamental feature in autonomous robots operating in areas such as surveillance, search and rescue missions, environmental monitoring, household cleaning, to name a few~\cite{kolling2006,Encarnacao2001,Ju2001,Kitowski2012,Zhang2013}.
-Throughout the years, the dynamic target tracking problem has received a profound amount of research in academia and industry \cite{wei2018,liu2019}.
-This is mainly due to their inherent complex nonlinear dynamics.
-Most of the target tracking algorithms proposed in the literature either rely on A) mathematical and kinematic models of both the robot and the target~\cite{Huang2008}, B) the assumption that the target or its trajectory are static and known a priori, and C) nonlinear control or soft-computing techniques that are driven by large amount of mostly off-line data that leads to an overwhelming degree of computational complexity~\cite{KD2007,Cren2017}.
-In a typical tracking problem, a robot is to apply a local control actions that enable it to maintain a relative position and orientation from the designated target while following a certain trajectory.
-It can also be applied on a fleet of robots where multiple robots maintain a geometric configuration relative to the target\cite{Oh2015-Survey,Liu2017-Modular}.
+Tracking a random moving target using a mobile robot is a key problem and a
+fundamental feature in autonomous robots operating in areas such as
+surveillance, search and rescue missions, environmental monitoring, household
+cleaning, to name a
+few~\cite{kolling2006,Encarnacao2001,Ju2001,Kitowski2012,Zhang2013}. Throughout
+the years, the dynamic target tracking problem has received a profound amount of
+research in academia and industry \cite{wei2018,liu2019}. This is mainly due to
+their inherent complex nonlinear dynamics. Most of the target tracking
+algorithms proposed in the literature either rely on A) mathematical and
+kinematic models of both the robot and the target~\cite{Huang2008}, B) 
+assumption that the target or its trajectory are static and known a priori, and
+C) nonlinear control or soft-computing techniques that are driven by large
+amount of mostly off-line data that leads to an overwhelming degree of
+computational complexity~\cite{KD2007,Cren2017}. In a typical tracking problem,
+a robot is to apply a local control actions that enable it to maintain a
+relative position and orientation from the designated target while following a
+certain trajectory. It can also be applied on a fleet of robots where multiple
+robots maintain a geometric configuration relative to the
+target\cite{Oh2015-Survey,Liu2017-Modular}.
 

### 2020-07-10 paperMIC2020/paperIEEE-MIC2020-V1.tex
review

@@
   robotics. In this paper, we address the position tracking problem of a mobile
-  robot where it is supposed to track the position of an mobile target whose
+  robot where it is supposed to track the position of a mobile target whose
   dynamics is unknown a priori. This problem is even more challenging when the

### 2020-07-10 paperMIC2020/matlabsim/randomPath/mainActorCriticRL_TargetTrackingRnd.m
Renamed matlab files

@@ -2,7 +2,7 @@
 %Edited by AMR Elhussein on May, 29,2020.
 %gradient descent Appraoch, three cases comined fixed point, horzintal and inclined line, 
 %converged Example
-function mainLF_OdometricLocalizationV7
+function mainActorCriticRL_TargetTrackingRnd
 
 % Created by S. Miah on Nov. 03, 2015.
 %edited by AMR Elhussein on Aug, 30,2019.
@@ -36,7 +36,7 @@ M = 2;  % input vector dimension
 
 
 % Leader's initial position
-pLeaderInit = [5;1]+rand(2,1); %[m]
+pLeaderInit = [2;-1]+rand(2,1); %[m]
 pLeaderTheta= 0; %[rad]
 
 QD(1,:) = [pLeaderInit' pLeaderTheta];
@@ -82,7 +82,7 @@ lc = 0.00001; %learnging rate
 la= 0.01; %actor learning rate
 
 %initlize actor weights
-Wa=0.001*rand(2,2);
+Wa=0.0001*rand(2,2);
 
 %reconstruct the P matrix to get the wheights matrix
  w(1,1) = 0.5 * P(1,1);
@@ -137,19 +137,19 @@ for k = 1:tsteps    % Main timing loop, k = time index
     
 %generating random path for the leader
     if k == 1
-        pLeaderTheta = pLeaderTheta + 0.5*rand*pi/4;
+        pLeaderTheta = pLeaderTheta + 0.5*rand*pi;
     end
 
     if k == tsteps/4  % change orientation of the leader
-        pLeaderTheta = pLeaderTheta-0.5*rand;        
+        pLeaderTheta = pLeaderTheta-0.5*rand*pi;        
     end
 
     if k == tsteps/2 % change orientation of the leader
-        pLeaderTheta = pLeaderTheta+0.5*rand*pi/4;
+        pLeaderTheta = pLeaderTheta+0.5*rand*pi;
     end
 
     if k ==3* tsteps/4 % change orientation of the leader
-        pLeaderTheta = pLeaderTheta-0.5*rand*pi/4;
+        pLeaderTheta = pLeaderTheta-0.5*rand*pi;
     end
     
     %saving leader control actions

### 2020-07-10 paperMIC2020/matlabsim/randomPath/mainLF_OdometricLocalizationV9.m

@@ -1,504 +1,0 @@
-% Odometric localization or dead reckoning%   Script for simulating mobile robot.
-%Edited by AMR Elhussein on May, 29,2020.
-%gradient descent Appraoch, three cases comined fixed point, horzintal and inclined line, 
-%converged Example
-function mainLF_OdometricLocalizationV7
-
-% Created by S. Miah on Nov. 03, 2015.
-%edited by AMR Elhussein on Aug, 30,2019.
-close all
-clear all
-clc
-
-disp('Please wait while the simulation runs ...');
-
-% ---------------------
-% SIMULATION PARAMETERS
-% ---------------------
-
-% Simulation time
-t0 = 0; tf = 60; % initial and final simulation time [s]
-T = 0.001;  % Sampling time [s]
-tsteps = ceil((tf-t0)/T); % number of time steps
-dt = T*(0:tsteps)'; % Discrete time vector (include time t0 to plot initial state too)
-
-d = 0.2; %[m] safe distance
-%ROBOT PARAMETERS
-%==========================================================================
-l = 0.381; % [m]
-rad = 0.0925; % [m] radius
-%==========================================================================
-
-
-% dimension of system;
-N = 2;  % state vector dimension
-M = 2;  % input vector dimension
-
-
-% Leader's initial position
-pLeaderInit = [2;-1]+rand(2,1); %[m]
-pLeaderTheta= 0; %[rad]
-
-QD(1,:) = [pLeaderInit' pLeaderTheta];
-QDinit = QD(1,:);
-%Leader's velocity 
-vLeader = 0.1; % [m/s]
-uLeader=[vLeader pLeaderTheta];
-
-% Follower robot initialization% 
-qp = [0;0]; % [m] Follower robot's position
-qTheta = 0 ;% [rad] Follower robot's orientation 
- qInit = [qp',qTheta] ;%+ rand(1,3); % row vector
-vMax = 2; % [m/s] Follower's maximum linear speed 
-
-Q(1,:) = qInit;
-
-% ----------------------
-% RUN SIMULATION 
-% ----------------------
-
-% Run the true model
-q(1,:) = qInit';
-pk = pLeaderInit;
-
-%initiating matrices
[…]

### 2020-08-07 paperMIC2020/paperIEEE-MIC2020-V1.tex
Paper reader for final review before submission
Added author names in the paper
update
final submission

@@
 \author{%~
+
   ~ % Author names removed for blind review 
-% \IEEEauthorblockN{Amr Elhussein and Md Suruz Miah}
-% \IEEEauthorblockA{\textit{Electrical \& Computer Eng.} \\
-% \textit{Bradley University}, Peoria, Illinois, USA \\
-%  aelhussein@mail.bradley.edu and smiah@bradley.edu}
+ \IEEEauthorblockN{Amr Elhussein and Md Suruz Miah}
+ \IEEEauthorblockA{\textit{Electrical \& Computer Eng.} \\
+ \textit{Bradley University}, Peoria, Illinois, USA \\
+  aelhussein@mail.bradley.edu and smiah@bradley.edu}
+
 }
-
+\IEEEoverridecommandlockouts
+\IEEEpubid{\makebox[\columnwidth]{978-1-7281-8386-2/20/\$31.00~\copyright2020 IEEE \hfill} \hspace{\columnsep}\makebox[\columnwidth]{ }}
 \maketitle
@@
   dynamic target is still one of the challenging problems in the field of
-  robotics. In this paper, we address the position tracking problem of a mobile
-  robot where it is supposed to track the position of a mobile target whose
-  dynamics is unknown a priori. This problem is even more challenging when the
-  dynamics of the mobile robot is also assumed to be unknown, which is indeed a
+
+  robotics.
+In this paper, we address the position tracking problem of a mobile robot where it is supposed to track the position of a  mobile target whose dynamics is unknown a priori.
+This problem is even more challenging when the dynamics of the mobile robot is also assumed to be unknown, which is indeed a
   realistic assumption. Most of the trajectory tracking solutions proposed in the

### 2021-02-13 paperFLAIRS34-2021/paperFLAIRS2021.tex
creating paper FLAIRS34

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{amssymb,amsmath,bm}
\usepackage{graphics,adjustbox}
\usepackage{tikz}
\usepackage{subfigure}
\usepackage{epstopdf}
\epstopdfsetup{suffix={}}
\usepackage{siunitx}
\sisetup{unitsep = \cdot}

\usepackage[figuresright]{rotating}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[english,algo2e,algoruled,vlined,linesnumbered]{algorithm2e}   % package for algorithm
\usepackage{enumerate}

\usepackage{easyReview}
\newtheorem{assumption}{Assumption}

\DeclareMathOperator*{\argmin}{arg min}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Model-free Reinforcement Learning Approach for Area Coverage Control using Heterogeneous Mobile Robots %
  %Model-free Reinforcement Learning Approach for Leader-Follower Formation Control Problems %
%  
% \thanks{This work was supported in part by the Bradley University’s Caterpillar fellowship grant.}
}

\author{%~
\IEEEauthorblockN{Amr Elhussein and Md Suruz Miah}
\IEEEauthorblockA{\textit{Electrical \& Computer Eng.} \\
\textit{Bradley University}, Peoria, Illinois, USA \\
aelhussein@mail.bradley.edu  and smiah@bradley.edu}
%\and
%\IEEEauthorblockN{Fazel Keshtkar}
%\IEEEauthorblockA{\textit{Div. of Computer Science, Math. and Science} \\
%\textit{St John's University}, Queens, NY, USA \\
%keshtkaf@stjohns.edu}
%\and
%\IEEEauthorblockN{Mohammed Abouheaf}
%\IEEEauthorblockA{\textit{School of EECS} \\
%\textit{Univ. of Ottawa}, Canada\\
%mabouhea@uottawa.ca}
%
}

\maketitle

\begin{abstract}
  %
In this paper, we present a novel model-free reinforcement learning approach for solving a conventional leader-follower problem using autonomous wheeled mobile robots. Specifically, the proposed learning approach decides the desired linear velocity and the steering angle (control actions) of a follower robot to follow the time-varying motion trajectory of
a leader robot. The setup of the online adaptive learning mechanism does not rely on any dynamical or kinematic information,~\textit{i.e.,} ``model-free'', of the car-like robots used in this work. Bellman's principle of optimality is employed to approximate the reward of the control actions determined by the proposed model-free adaptive learning algorithm. A set of computer experiments has been conducted to validate the performance of the proposed algorithm under various unplanned leader-trajectories. 
%
\end{abstract}

\begin{IEEEkeywords}
Leader-follower formation, mobile robots, reinforcement learning, policy iteration, trajectory tracking
\end{IEEEkeywords}

% \begin{nomenclature}
% \begin{deflist}[A]
% \defitem{ADP} \defterm{Approximate dynamic programming}
% \defitem{AL}\defterm{Approximate linearization}
% \defitem{RL}\defterm{Reinforcement learning}
% \end{deflist}
% \end{nomenclature}

\section{Introduction}
\label{sec:introduction}
The field of multi-agent systems %control theory 
is of a paramount importance in recent years due to its extensive applications in perimeter surveillance, search and rescue missions, cooperative localization, and target tracking tasks~\cite{Ma2019-Cooperative,Kia2018-ServerAssisted,Khan2018-Cooperative}. Multi-robot formation is one of many  active research topics within the realm of multi-agent systems and cooperative control theory~\cite{Oh2015-Survey}. In particular, the leader-follower problem has received thorough attention to the robotics community, where mobile robots follow leader robot(s) satisfying certain geometric constraints, such as cyclic pursuit~\cite{Yu2019-Cooperative,Marshall2004}, circular motion~\cite{Ma2019-Cooperative}, and time-varying communication topologies~\cite{Sakai208-Leader,Li2019-TimeVarying}. However,  many formation control strategies which are proposed in the literature to date rely on mathematical models of various mobile robots, such as underactuated autonomous surface vehicles~\cite{Liu2017-Modular}, nonholonomic wheeled mobile robots~\cite{Miao2018-Distributed}, unmanned underwater vehicles~\cite{Liu2019-Robust,Bechlioulis2019-Robust}, and unmanned helicopters~\cite{Kuo2019-Intelligent}.  In some cases, tools of computational intelligence are used to solve leader-follower problems, see~\cite{Xiao2019-LeaderFollower, Kuo2019-Intelligent}, for example, and some references therein, however, their learning mechanisms still rely on the underlying system dynamics. Recently, Miah~\textit{et~al.} developed several motion control strategies~\cite{MiKaCh2019-j1,MiKn2018-j1,MiFaChGu2017-j1,MiGu2015-j1,MiGu2014-j1} for nonholonomic mobile robots and fixed-base helicopters, where partial or full dynamical models are required for determining the desired control actions.

The current manuscript overcomes some shortcomings associated with many leader-follower control approaches proposed in the literature by introducing an online model-free adaptive learning control mechanism. The proposed learning approach determines the actuator commands of a follower robot to follow an independent virtual leader. Note that the actuator commands (control actions) are the linear speed and steering angle of the follower robot. The learning mechanism relies on collecting the state information (i.e., position and orientation) of motion trajectories generated from both the leader and follower robots online over a finite time period. Bellman's principle of optimality is then formulated as a model-free reinforcement learning strategy to determine the optimal linear speed and the steering angle of the follower robot so that it follows the motion trajectories of the leader while maintaining a pre-defined safe distance between them. We emphasize that model parameters of both the leader and follower robots are unknown. Furthermore, the effectiveness of the proposed model-free reinforcement learning approach is validated by taking into consideration that the leader robot is a physical robot model as opposed to a simple point robot model, that is considered in many formation control, trajectory tracking, and leader-follower problems in the literature~\cite{Marshall2004}.

% \emph{Notation:} Throughout this paper, sets will be denoted by caligraphic letters. For positive integers $m,n>0,$ $\mathbb{R}^n(\mathbb{R}^{m\times n})$ denotes a set of $n$--dimensional column vectors ($m\times n$-dimensional matrices) with entries taken from a set of real numbers $\mathbb{R}.$ Vectors (matrices) will be denoted with lowercase (uppercase) bold letters. A standard n-element column vector ${\bf x}$ will sometimes be represented as $[x_1,x_2,\ldots, x_n]^T$ with $[\cdot]^T$ being the transposition of the quantity $[\cdot].$ This allows to represent a column vector of vectors as $\mathbb{R}^{n^2}\ni{\bf v} = [{\bf x}_1,{\bf x}_2,\ldots,{\bf x}_n]^T.$ The standard Euclidean norm of the vector  ${\bf x}\in\mathbb{R}^n$ and the matrix ${\bf A}$ are given by $\Vert x \Vert = \left(\sum_{i=1}^n\lvert x_i\rvert^2\right)^{1/2}$ and $\Vert A \Vert = \left(\sum_{i=1}^m\sum_{j=1}^n\lvert a_{ij}\rvert^2\right)^{1/2}$  with $x_i,a_{ij}$ being the entries of ${\bf x}$ and ${\bf A},$ respectively. The scalar products of quantities ${\bf x},{\bf y}\in\mathbb{R}^n$ and ${\bf A}, {\bf B}\in\mathbb{R}^{m\times n},$ are given by %
% %
% \begin{align*}
%   {\bf x}^T{\bf y} = \sum_{i=1}^nx_iy_i~~\mathrm{and}~~{\bf A}\cdot {\bf B} =\mathrm{Tr}\left({\bf A}^T{\bf B}\right) = \mathrm{Tr}\left({\bf A}{\bf B}^T\right),
% \end{align*}
% %
% respectively, where $\mathrm{Tr}(\cdot)$ is the trace of matrix $(\cdot).$ Clearly, $\mathrm{Tr}({\bf A}^T{\bf A}) = \Vert {\bf A}\Vert^2.$ $\mathrm{diag}(a_1,a_2,\ldots, a_n)$ will denote an $n\times n$ diagonal matrix with elements $a_1,a_2,\ldots, a_n$ starting from its upper left corner. %

\section{Problem Setup} 
\label{sec:problemSetup}

Suppose that a car-like robot (follower) is deployed in a planar (2D) environment. Therefore, the coordinate $(x,y)$ is the position of the follower robot with an orientation of $\theta\in[-\pi,\pi)~\si{\radian}$ with respect to the global X-Y  coordinate frame.  Without loss of generality, the action commands of the robot are considered to be its linear speed $\nu$ and the steering angle $\gamma.$ Let ${\bf q}_k\equiv[x_k,y_k,\theta_k]^T$ denote the pose (position and orientation) vector of the robot at time $t\ge 0$ with $t=k \, T_s,$ $k\in\mathbb{N}_0,$ and $T_s>0$ being the sampling time.  The robot follows a leader trajectory defined by $(\mathbf{p}_k^{[\ell]})^T=[x_k^{[\ell]},y_k^{[\ell]}(t)]$ with the dynamics given in discrete-time as: %
%
\begin{align}
  \label{eq:leaderDT}
  \mathbf{p}_{k+1}^{[\ell]} = \mathbf{p}_k^{[\ell]} + T_s \, \mathbf{u}_k^{[\ell]},
\end{align}
%
where $\mathbf{u}_k^{[\ell]}\in\mathbb{R}^2$ is the control input vector of the leader at time instant $k,$ $k=0,1,\ldots.$ A standard setup of a leader-follower problem using car-like mobile robots is shown in Fig.~\ref{fig:leaderFollowerSetup}. The leader is supposed to maintain a constant safe distance $d>0.$
%
\begin{figure}
  \centering
  \fcolorbox{gray!10}{gray!5}{
    \includegraphics[width=0.45\textwidth]{figs/ipe/LF-Setup}
    }
  \caption{Mobile robot and its leader-follower problem setup.}
  \label{fig:leaderFollowerSetup}
\end{figure}
%
The robot's discrete-time model is approximated by the first-order Euler integration law given as: %
%
\begin{subequations}
  \begin{align}
    x_{k+1}& =x_{k}+T_s\nu_{k}\cos{(\theta_{k}+\gamma_{k})} + \zeta_1,\\  
    y_{k+1}& =y_{k}+T_s\nu_{k}\sin{(\theta_{k}+\gamma_{k})}+ \zeta_2,\\
    \theta_{k+1}&=\theta_{k}+T_s\nu_{k}\frac{\sin{(\gamma_{k})}}{l}+ \zeta_3,
  \end{align}
\label{eq:robotModel1-DT}
\end{subequations}
\\
where $\gamma_k\in(-\frac{\pi}{2},\frac{\pi}{2})$ is the front wheel steering angle with respect to the robot's orientation $\theta_k\in[-\pi,\pi),$ $\nu_k$ is the linear speed, $l$ is the distance between the drive wheels of the robot, and $\zeta_1,\zeta_2,\zeta_3\in\mathbb{R}$ are the model uncertainties. %
% A compact form of model~\eqref{eq:robotModel1-DT} can be written as %
% %
% \begin{align}
%   {\bf q}_{k+1} = {\bf q}_k + {\bf f}({\bf q}_k,{\bf u}_k,\bm{\zeta}_k),
%   \label{eq:robotModel1-DT1}
% \end{align}
% %
% where ${\bf f}:\mathbb{R}^3\times\mathbb{R}^2\times\mathbb{R}^3\to\mathbb{R}^3$ is a vector-valued vector function, ${\bf u}_k=[\nu_k,\gamma_k]^T\in\mathbb{R}^2$ is the robot's motion control input, and the model uncertainty vector is denoted by $\bm{\zeta}^T= [\zeta_1,\zeta_2,\zeta_3].$ %
%
It is assumed that, the left and right wheels of the robot steer together under a no-slip condition~\cite{Corke2011}. The state error between the follower and the leader is defined such that %
%
\begin{multline}
    \label{eq:stateError}
  \mathbf{e}_k^T = [x_e,y_e,\theta_e]^T = \\
  \begin{bmatrix}
    x_k^{[\ell]} - x_k - d\cos\theta_k^{'},
    y_k^{[\ell]} - y_k - d\sin\theta_k^{'},
    \theta_k^{'} - \theta_k
  \end{bmatrix},
\end{multline}
%
where $\theta_k^{'} = \mathrm{atan2}\left(y_k^{[\ell]}-y_k, x_k^{[\ell]}-x_k\right).$  %
%
The control problem can then be formally stated as follows: Find $\nu_k$ and $\gamma_k$ such that ${\bf e}_k\to {\bf 0}$ as  $k\to\infty$ subject to~\eqref{eq:leaderDT}~\text{and}~\eqref{eq:robotModel1-DT}. %
%     &\text{subject to}~\eqref{eq:leaderDT}~\text{and}~\eqref{eq:robotModel1-DT}.    %
% \begin{equation}
%   \begin{split}
%     &\mathrm{Find}~~\nu_k~\mathrm{and}~~\gamma_k~~\mathrm{such~that}\\
%     &{\bf e}_k\to {\bf 0}~~\mathrm{as}~ k\to\infty\\
%     &\text{subject to}~\eqref{eq:leaderDT}~\text{and}~\eqref{eq:robotModel1-DT}.    
%   \end{split}
%   \label{eq:problem}
% \end{equation}
%
The optimization goal is to let the follower robot asymptotically follow the leader robot while maintaining a safe distance $d>0$ regardless of motion trajectories with various complexities generated by the independent leader. It is emphasized that, the current model-free reinforcement learning mechanism determines  the control actions $\nu_k$ and $\gamma_k$ based on the error vectors $\mathbf{e}_k$ (data collected over a finite-time interval) as $k\to\infty.$ Before illustrating the proposed learning algorithm, let us briefly revisit the preliminaries of reinforcement learning in the next section.

% In the next section, a conventional trajectory tracking method is investigated to solve the problem~\eqref{eq:problem}. This is followed by the proposed approximate dynamic programming technique which is illustrated in section~\ref{sec:solutionADP}.

\section{Preliminaries of Reinforcement Learning}
\label{sec:reinf-learn}
% greek letters: https://www.overleaf.com/learn/latex/List_of_Greek_letters_and_math_symbols

Reinforcement learning (RL) highlights a class of problems in the  field of multi-agent systems, where an agent determines sequential decisions (control actions) while learning from its associated environment. That is, an agent takes into account its learning  experience from the environment  and the cumulative reward to optimize decision~\cite{Francois-Lavet:2018}. The RL technology is described by four finite state tuples~$(\mathcal{S},\Omega,\mathcal{R},\mathcal{A}),$ that are  environment $(s \in \mathcal{S})$, agent $(w \in \Omega)$, reward $(r \in \mathcal{R})$, and action $(a \in \mathcal{A})$ as illustrated in Fig.~\ref{fig:fig-rl}. %
%
\begin{figure}
  \centering
  \includegraphics[scale=0.25]{figs/img/Ref-L-agent}
  \caption{A typical framing of a reinforcement learning scenario.}
  % \caption{A typical framing of a reinforcement learning scenario: an agent takes actions in an environment, which is interpreted into a reward and a representation of the state, which are fed back into the agent.}
  \label{fig:fig-rl}
\end{figure}
%
As pioneered by Barto~\textit{et al.} in~\cite{Barto1983-Neuronlike}, an agent determines its action in environment $s_0 \in \mathcal{S}$ by collecting information via agent $w_0 \in \Omega.$ Since the learning process is a sequential time based process, therefore, at each time step $k,$ an  agent determines  the action $a_k \in \mathcal{A}$ following three cascaded phases: (i) obtaining a reward $r_k \in \mathcal{R},$ % value function 
%
(ii) state transitions from agent state $s_k \in \mathcal{S}$ to $s_{k+1} \in \mathcal{S},$ % robot's state transition 
and (iii) the agent obtains an observation $w_{k+1} \in \Omega.$ %(error data)
% To summary, an RL model contains a four finite states tuples, Environment, Agent, Action, and Reward: $(S,\Omega, A, R)$. 
% \subsection{Our Reinforcement Learning Model} %
%
The leader-follower problem addressed in this paper is formulated using a model-free reinforcement learning approach as follows: %
%
%
%We defined and formulated the problem in mathematical models in section~\ref{sec:problemSetup}. To formulate RL for our problem, we define the four tuples as following:
\begin{enumerate}
    \item \textbf{Environment}: It is a 2D planar space where agents (leader and follower) interact with each other.
    \item \textbf{Agent}: Agents considered in this work are two robots (leader robot and follower robot). The robot motion behaviors are modeled using models~\eqref{eq:leaderDT}~and~\eqref{eq:robotModel1-DT}. The follower robot mimics the behavior of the leader robot. %The only information that follower robots received from the leader robot are its speed and steering angle.
    \item \textbf{Action}: The actions are the linear velocity and steering angles of the follower robot. Robots' state-transition task is performed using the control actions applied to their actuators. The main parameters that agents use to interact with the operating environment are the current position and orientation, speed, steering angle, and distance between the robots. 
    \item \textbf{Reward}: The goal here is to determine how follower robot can learn the leader robot's behavior to keep the minimum distance at any time and location to adjust its speed and distance. Therefore, follower robot will obtain reward $r_k \in \mathcal{R}$ at time instant $k$ if the distance between the follower and the leader is close to a safe distance $d.$ Herein, robots' state error is formulated as in \eqref{eq:robotModel1-DT}. Hence, once the error $\|\mathbf{e}_k\|$ is minimized at time instant $k,$ the follower robot will obtain reward $V,$ which is a modeled solving value function. This will be detailed out in the following section.
\end{enumerate}

\section{Proposed Model-Free RL Approach}
\label{sec:RLSolution}

The solution of the leader-follower formation problem is realized using a reinforcement learning approach. It employs model-free strategies for solving a temporal difference equation developed herein. This solution is equivalent to solving the underlying Bellman optimality equation for  the dynamical error model~\eqref{eq:stateError}. The relative importance of the states in the error vector ${\bf e}_k$ and the control decisions (linear velocity and steering angle) of the follower-robot are evaluated using the  performance (cost) index: %
\begin{align}
\label{eq:costFunctional}
J = \sum_{k=0}^\infty \frac{1}{2}\left[{\bf e}_k^T \, {\bf Q} \, {\bf e}_k + {\bf u}_k^T \, {\bf R} \, {\bf u_k}\right],
\end{align}    
where ${\bf Q}\in\mathbb{R}^{3\times 3}$ and ${\bf R}\in\mathbb{R}^{2\times 2}$ are symmetric positive definite weighting matrices. The objective of the optimization problem, following~\cite{Lewis2013-Reinforcement}, is to find an optimal sequence of control polices $\{\mathbf{u}^*_k\}_{k=0}^\infty$ that minimizes the cost index $J$ along the state-trajectories~\eqref{eq:leaderDT}~and~\eqref{eq:robotModel1-DT}. Motivated by the structure of the convex quadratic cost functional~\eqref{eq:costFunctional}, let the solution of the tracking control problem employ the value function $V({\bf e}_k,{\bf u}_k)$ defined by %
%
\begin{equation*}
\label{eq:valueFunction}
V({\bf e}_k,{\bf u}_k) = \sum_{\kappa=k}^\infty \frac{1}{2}\left({\bf e}_\kappa^T\, {\bf Q}\, {\bf e}_\kappa + {\bf u}_\kappa^T \, {\bf R}\, {\bf u_\kappa}\right).
\end{equation*}
%
This structure yields a temporal difference form (i.e., Bellman equation) as follows
\begin{equation*}
\label{eq:tempraldiffeq}
V({\bf e}_k,{\bf u}_k)= \frac{1}{2}\left[{\bf e}_k^T\, {\bf Q}\, {\bf e}_k + {\bf u}_k^T\, {\bf R}\, {\bf u_k}\right] +V({\bf e}_{k+1},{\bf u}_{k+1}).
\end{equation*}
%
Applying Bellman's optimality principle yields the optimal control policies ${\bf u}_k^*,~k\ge 0,$ such that~\cite{Lewis2012} %
%
\begin{align*}
{\bf u}^*_k = \argmin_{{\bf u}_k}\left[\frac{1}{2}\left[{\bf e}^T_k\,  {\bf Q}\, {\bf e}_k +{\bf u}^T_k\,  {\bf R} \,  {\bf u}_k\right]   +
V({\bf e}_{k+1},{\bf u}_{k+1})\right].
\label{eq:argMinControlAction}
\end{align*}
%
Alternatively, this optimal  policy form is equivalent to ${\bf u}^*_k = \argmin_{{\bf u}_k}\left[
V({\bf e}_{k},{\bf u}_{k})\right].$
Therefore, the underlying Bellman optimality equation follows %
%
\begin{equation*}
\label{eq:BellOpt}
V^*({\bf e}_k,{\bf u}^*_k)= \frac{1}{2}\left[{\bf e}_k^T\, {\bf Q}\, {\bf e}_k + {\bf u}_k^{*T}\, {\bf R}\, {\bf u}^*_k\right] +V^*({\bf e}_{k+1},{\bf u}^*_{k+1}),
\end{equation*}
%
where $V^*(\cdot,\cdot)$ is the optimal solution for Bellman optimality equation. This temporal difference equation is utilized by reinforcement learning process which solves the following temporal difference approximation form %
%
\begin{align}
\hat{V}(\mathbf{z}_k) = \frac{1}{2}\mathbf{z}_k^T\, \bar{\mathbf{P}}\, \mathbf{z}_k + \hat{V}(\mathbf{z}_{k+1}),
\label{eq:valueFunctionEstimated}
\end{align}
%
where $\mathbf{z}_k = \left[\mathbf{e}_k ,\mathbf{u}_k\right]^T\in\mathbb{R}^5,$ $V\left(\mathbf{e}_k,\mathbf{u}_k\right) \approx \hat{V}(\mathbf{z}_k),$  and $\bar{\mathbf{P}}$ is a symmetric block-diagonal matrix formed using $(\mathbf{Q},\mathbf{R}),$~\textit{i.e.,~}$\bar{\mathbf{P}} = \mathrm{blockdiag}(\mathbf{Q},\mathbf{R}).$ %
The approximation of the solving value function $\hat{V}(\mathbf{z}_k)$ employs a quadratic form so that $\hat{V}(\mathbf{z}_k)=\frac{1}{2}\mathbf{z}_k^T\, \mathbf{P}\, \mathbf{z}_k,$ where $\mathbf{P}\in\mathbb{R}^{5\times 5}$ is a positive definite matrix. Hence, the optimal control strategy $\mathbf{u}_k^*$ can be expressed as follows %
%
\begin{align}
\label{eq:modelFreePolicy}    
\mathbf{u}_k^* = \argmin_{\mathbf{u}_k}\left[\hat{V}(\mathbf{z}_k)\right] = -\,  \mathbf{P}_{uu}^{-1}\, \mathbf{P}_{ue}\, \mathbf{e}_k,
\end{align}
%
where $\mathbf{P}_{uu}$ and $\mathbf{P}_{ue}$ are sub-blocks of symmetric matrix $\mathbf{P}.$ %   
%

A two-step solution mechanism that is based on policy iteration is employed to solve the temporal difference equation~\eqref{eq:valueFunctionEstimated} using the policy~\eqref{eq:modelFreePolicy}. First, the adaptive critics are used to approximate the solving value function $\hat V(\cdot)$ using a multi-layer critic neural network as shown in Fig.~\ref{fig:nnCritic}. %
%
\begin{figure}
    \centering
    \fcolorbox{blue}{gray!5}{
        \begin{adjustbox}{max width = 0.45\textwidth}
            \tikzset{%
                input neuron/.style={
                    circle,
                    fill=green!50,
                    minimum size=0.7cm
                },
                neuron missing/.style={
                    draw=none, 
                    scale=1,
                    fill=white,
                    text height=0.01cm,
                    execute at begin node=\color{black}$\vdots$
                },
            }

            \tikzset{%
                hidden neuron/.style={
                    circle,
                    fill=blue!50,
                    minimum size=0.7cm
                },
                neuron missing/.style={
                    draw=none, 
                    scale=1,
                    fill=white,
                    text height=0.01cm,
                    execute at begin node=\color{black}$\vdots$
                },
            }

            \tikzset{%
                output neuron/.style={
                    circle,
                    fill=red!50,
                    minimum size=0.7cm
                },
                neuron missing/.style={
                    draw=none, 
                    scale=1,
                    fill=white,
                    text height=0.01cm,
                    execute at begin node=\color{black}$\vdots$
                },
            }

            \begin{tikzpicture}[x=1.5cm, y=1.5cm]

            \foreach \m/\l [count=\y] in {1,2,missing,3}
            \node [input neuron/.try, neuron \m/.try] (input-\m) at (0,2.5-\y) {};

            \foreach \m [count=\y] in {1,2,3,missing,4}
            \node [hidden neuron/.try, neuron \m/.try ] (hidden-\m) at (2,2.5-\y*1.1) {};

            \foreach \m [count=\y] in {1}
            \node [output neuron/.try, neuron \m/.try] (output-\m) at (4,2.5-\y*2.8) {};

            \foreach \l [count=\i] in {1,2,n+m}
            \draw [<-] (input-\i) -- ++(-1,0)
            node [above, midway] {$\mathbf{z}_{k,\l}$};

            \foreach \l [count=\i] in {1,2,3,~\mbox{$\bar{n}$}}
            \node [above] at (hidden-\i.north) {$\rho_{\l}$};

            \foreach \l [count=\i] in {1}
            \draw [->] (output-\i) -- ++(1,0)
            node [above, midway] {$\hat{V}(\mathbf{z}_{k})$};
            % node [above, midway] {$\hat{V}_\l$};

            \foreach \i in {1,...,3}
            \foreach \j in {1,...,4}
            \draw [->] (input-\i) -- (hidden-\j);

            \foreach \i in {1,...,4}
            \foreach \j in {1}
            \draw [->] (hidden-\i) -- (output-\j);

            \foreach \l [count=\x from 0] in {Input, Hidden, Output}
            \node [align=center, above] at (\x*2,1.9) {\l \\ layer};

            \node [align=center, below] at (3,-2.5) {Weights \\ $\boldsymbol{\omega}$};
            \draw[->,ultra thick](3,-2.5) -- (3,1.4);

            \end{tikzpicture}
        \end{adjustbox}      
    }
    \caption{Critic neural network structure for approximating value function.}
    \label{fig:nnCritic}
      \end{figure}
%      
Second, the policy evaluation step of this process updates the critic weights $\bm{\omega}$ in real-time without acquiring any formation about the dynamics of the leader or follower dynamical systems  (the calculation mechanism of the critic weighs $\boldsymbol{\omega}$ is explained later on). This is done to search for a strictly better policy. %
%

Note that, the policy iteration computational setup rearranges the temporal difference expression~\eqref{eq:valueFunctionEstimated} such that %
%
\begin{equation}
\label{eq:const}
\mathbf{z}_k^T\, \mathbf{P}\, \mathbf{z}_k - \mathbf{z}_{k+1}^T\, \mathbf{P}\, \mathbf{z}_{k+1} = \mathbf{z}_k^T\, \bar{\mathbf{P}}\, \mathbf{z}_k. 
\end{equation}
%
This equation is utilized repeatedly in order to evaluate a certain policy during at least $\eta\ge \bar n, \bar n= (3+2)(3+2+1)/2$ evaluation steps (i.e., the lowest evaluation interval spans $k$ to $k+\bar n$ calculation samples) in order to update the critic weights vector  $\boldsymbol{\omega}=\mathrm{vec}(\mathbf{P}),$ which consists of connection weights between the neurons of the hidden layer and the output layer of the critic neural network shown in Fig.~\eqref{fig:nnCritic}. The operator $\mathrm{vec}(\mathbf{P})$ forms the columns of the $\mathbf{P}$ matrix into a column vector $\mathbf{\omega}$ of dimension $\bar{n}=15$ since the matrix $\mathbf{P}$ is a symmetric matrix. The left hand side of~\eqref{eq:const} is expressed using the following critic approximation form %
%
$$\hat{V}(\mathbf{z}_k)-\hat{V}(\mathbf{z}_{k+1})=\boldsymbol{\omega}^T\tilde{\bm{\rho}}(\mathbf{z}_{k,k+1}),$$
%
where $\tilde{\bm{\rho}}(\mathbf{z}_{k,k+1})=\bm{\rho}(\mathbf{z}_k)-\bm{\rho}(\mathbf{z}_{k+1}) \in \mathbb{R}^{15 \times 1}, \, \bm{\rho}(\mathbf{z}_k)=\left(\mathbf{z}^q_k\otimes\mathbf{z}^h_k\right)$ $(q=1,\dots, 5, \,\, h=q,\dots,5),$ and $\boldsymbol{\omega}^T = [0.5 \, P^{11},P^{12},P^{13},P^{14}, P^{15}, \, 0.5 \, P^{22}, P^{23},P^{24},P^{25},$ $\,0.5 \, P^{33}, P^{34},P^{35},\,0.5 \, P^{44},P^{45}, \,0.5 \, P^{55}]^T \in \mathbb{R}^{1\times 15}$ ($P^{ij}$ is the $ij^{th}$ entry of matrix $\mathbf{P}$). %
%
The critic weights $\boldsymbol{\omega}$ are updated using a gradient descent approach, where the tuning error $\varepsilon_k$ at each computational instance $k$ follows $\varepsilon_k =\boldsymbol{\omega}^T\tilde{\bm{\rho}}(\mathbf{z}_{k,k+1})-{v}_k,$ where $v_\kappa = \frac{1}{2}\mathbf{z}_{k}^T \, \bar{\mathbf{P}} \, \mathbf{z}_{k}$. As detailed earlier, it is required to perform at least $\eta \ge \bar n$ evaluation steps before updating the critic weights $\boldsymbol{\omega}$ (i.e., finding the new improved policy). Hence, it is required to minimize the sum of square errors such that %
%
\begin{multline*}
  \delta_c =\sum_{\kappa=0}^{\eta-1}\frac{1}{2}(\boldsymbol{\omega}^T\tilde{\bm{\rho}}(\mathbf{z}_{k+\kappa,k+\kappa+1})-{v}_{k+\kappa})^2 = \frac{1}{2}\| \mathbf{v} - \bm{\Lambda}\bm{\omega}\|^2\\
  =\frac{1}{2}\left(\mathbf{v} - \bm{\Lambda}\bm{\omega}\right)^T \left(\mathbf{v} - \bm{\Lambda}\bm{\omega}\right), 
\end{multline*}
where $\bm{\Lambda} = [{\bf o}_0,{\bf o}_1,\ldots,{\bf o}_{\eta-1}]^T \in \mathbb{R}^{\eta\times 15}$ with ${\bf o}_\kappa = \tilde{\bm{\rho}}^T({\bf z}_{k+\kappa, k+\kappa+1}) \in \mathbb{R}^{1\times 15}$ and ${\bf v} =[v_0,v_1,\ldots,v_{\eta-1}]^T \in \mathbb{R}^{\eta}$ with $v_\kappa = \frac{1}{2}\mathbf{z}_{k+\kappa}^T \, \bar{\mathbf{P}} \, \mathbf{z}_{k+\kappa}$ for $\kappa = 0,1,\ldots, \eta-1$. %
Therefore, the update law of the critic weights using the gradient decent approach for at least $\bar n$ samples is given by %
\begin{multline}
  \bm{\omega}^{[r+1]} = \bm{\omega}^{[r]} - \ell_c\frac{\partial\delta_c}{\partial \bm{\omega}} = \bm{\omega}^{[r]} - \ell_c\left(-\bm{\Lambda}^T\mathbf{v} + \bm{\Lambda}^T \bm{\Lambda}\bm{\omega}^{[r]}\right)\\ 
=\bm{\omega}^{[r]} - \ell_c \bm{\Lambda}^T\left(\bm{\Lambda}\bm{\omega}^{[r]}-\mathbf{v}\right), 
\label{eq:criticWeights}
\end{multline}
%
where $0<\ell_c<1$ is a critic learning rate and $r$ is the  update index of the critic weights.

The newly computed critic weights $\boldsymbol{\omega}$ are used to reconstruct the matrix ${\bf P}$ (i.e., updating the solving value function and hence calculating the associated policy) such that 
%
\begin{center}
${\bf P}=\begin{bmatrix} 
2\,\omega^{1}    & \omega^{2}      & \omega^{3}       & \omega^{4}       & \omega^{5} \\ 
\omega^{2}       &2\, \omega^{6}   & \omega^{7}       & \omega^{8}       & \omega^{9} \\
\omega^{3}       & \omega^{7}      &2\, \omega^{10}   & \omega^{11}      & \omega^{12} \\
\omega^{4}       & \omega^{8}      & \omega^{11}      & 2\,\omega^{13}   & \omega^{14} \\
\omega^{5}       & \omega^{9}      & \omega^{12}      & \omega^{14}      & 2\,\omega^{15}   
\end{bmatrix}\in \mathbb{R}^{5\times 5},$
\end{center}
%
where $\omega^{i}$ is the $i^{th}$ entry of the weight vector $\bm{\omega}.$ The complete policy iteration solution process for the leader-follower problem is detailed out in Algorithm \ref{alg:ModelFreeTracking}. %
%
\begin{algorithm2e}
    \caption{\label{alg:ModelFreeTracking} Model-free reinforcement learning using the policy iteration solution.}
    \DontPrintSemicolon
    \KwIn{Sampling-time $T_s,$ $\mathbf{Q},~\text{and}~\mathbf{R}$ }
    \KwOut{Error trajectory $\mathbf{e}_k,$ for $k=0,1,\ldots$}
    % \KwData{Map representation using occupancy grid technique}
    % \KwResult{output******************************}
    \Begin{
        $k=0, r = 0$ \tcc*[h]{Discrete time and policy indices}\;
        $\eta = (n+m)(n+m+1)/2$\;
        Initialize $\mathbf{P}^{[0]}$ \tcc*[h]{Positive definite}\;
                Set offset distance $d$\;
                Given approximate initial poses of leader and follower, compute $\mathbf{e}_0$ using error model~\eqref{eq:stateError}\;
                Compute follower's input $\mathbf{u}_0^{[0]}$ using policy~\eqref{eq:modelFreePolicy}\;
        \Repeat(\tcc*[h]{Main timing loop}){Tracking errors are zero}
        {
            Find $\mathbf{e}_{k+1}$ using~\eqref{eq:stateError}\;
            Compute policy $\mathbf{u}_{k+1}^{[r]}$ using~\eqref{eq:modelFreePolicy}\;
            %Evaluate and record Equation~\eqref{eq:modelFreeMatrixSolution}\;
            \If{[$(k+1)~\mathrm{modulo}~\eta]==0$ }
            {
                $r\leftarrow r+1$\tcc*[h]{Evaluate policy}\;
                Solve for the critic-weights $\bm{\omega}$ using~\eqref{eq:criticWeights}\;
                Construct matrix $\mathbf{P}^{[r]}$ using vector $\bm{\omega}$\;
%                \eIf{$\|\mathbf{P}^{[r]} - \mathbf{P}^{[r+1]}\|<\varepsilon$}{Set $\mathbf{u}_{k+1}^*\leftarrow\mathbf{u}_{k+1}^{[r]}$}{$k\leftarrow k+1$ }
            }
%        {
%                $k\leftarrow k+1$
%            }
        $k\leftarrow k+1$
        }
    }
\end{algorithm2e}

\section{Computer Experiments and Results}
\label{sec:resultsExperiments}
In the sequel, computer experiments  are conducted to validate the performance of the proposed model-free adaptive learning algorithm in real-time. The results of computer experiments highlight the dynamics of the tracking errors and the convergence characteristics of the proposed algorithm (i.e., updating the critic weights). This will judge the ability of the follower robot to track independent motion trajectory of the leader robot under two different independent leader-motion trajectories. The computer experiments are realized using MATLAB simulation environment. The weighting matrices are set to $\mathbf{Q} = \mathrm{diag}[0.01,0.01,0.005]$ and $\mathbf{R} = \mathrm{diag}[10^{-6}, 10^{-6}].$ % 
% \[Q=0.001 
% \begin{bmatrix}
% 10       & 0   & 0\\
% 0       & 10   & 0\\
% 0       & 0   &5 \\
% \end{bmatrix},
% R=0.000001
% \begin{bmatrix}
% 1       & 0 \\
% 0       & 1 
% \end{bmatrix}.\]
The learning rate $\ell_c$ is set to  $0.0001$. The sampling time $T_s$ is set to $0.08 \sec.$ The desired distance offset between the leader and the follower is set to $ d = 0.5$ [m] for all scenarios.

In the first scenario, the leader trajectory motion is described by a unicycle model so that %
%
% \begin{align*}
$\dot x^{[\ell]}(t) = \nu^{[\ell]}(t)\cos\theta^{[\ell]}(t),$ %
$\dot y^{[\ell]}(t) = \nu^{[\ell]}(t)\sin\theta^{[\ell]}(t).$
%\dot\theta^\ell(t) &= \omega(t),
% \end{align*}
%
Initially, the leader's position is set to be the same for a short period of time with $\nu^{\ell} = 0 , \gamma^{\ell} = 0$. Then it starts to move on a horizontal line with $\nu^{\ell} = 0.1 $ [m/s], eventually the leader starts to move on an inclined path with $\nu^{\ell} = 0.2$ [m/s], $\gamma^{\ell} = 45\degree$. The leader is initially placed at $(x,y) = (5, 2)~\si{[\meter]}$ with an orientation of $\theta = 0 \degree $, while the follower  is initially placed at $(x,y) = (0, 0)~\si{[\meter]}$ with an orientation of $\theta = 0\degree$. Note that during this scenario, the critic weights converge rapidly and the tracking errors decay till the follower tracks the leader. The trajectory phase plan plot, tracking error states, control signals, and tuning of critic weights are shown in Fig.~\ref{fig:performanceRectilinearTrajectory}. %
%
\begin{figure*}[htbp]%
    \centering
    %\parbox[c]{0.48\textwidth}{\centering Parallel parking}
    %\parbox[c]{0.48\textwidth}{\centering Trajectory tracking}
    %\\
    \subfigure[][]{%
        \label{fig:trajectoryRectilinearDistance}%
        \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/rectilinear/trajectoryRectlinearDistance} }
    \subfigure[][]{%
        \label{fig:stateErrorRectilinearDistance}%
        \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/rectilinear/stateErrorRectlinearDistance} }
    \\
    \subfigure[][]{%
        \label{fig:controlInputsRectilinearDistance}%
        \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/rectilinear/controlInputRectlinearDistance} }
    \subfigure[][]{%
        \label{fig:weightRectilinearDistance}%
        \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/rectilinear/weightRectilinearDistance} }
    \caption[Leader-follower performance for rectilinear trajectory.]{First scenario (rectilinear trajectory): 
        \subref{fig:trajectoryRectilinearDistance} leader-follower trajectories,~\subref{fig:stateErrorRectilinearDistance} state tracking errors,~\subref{fig:controlInputsRectilinearDistance} linear speed and steering angle of the follower, and    \subref{fig:weightRectilinearDistance} critic weights.}%
    \label{fig:performanceRectilinearTrajectory}%
\end{figure*}
%

A relatively unplanned complex trajectory-tracking scenario is considered. The leader moves according to a sinusoidal trajectory so that %
%
% \begin{align*}
$x^{[\ell]}(t) = \alpha (t) \in [0,10\pi],$ %
$y^{[\ell]}(t) = 5 \,\sin(\alpha t),$ and %
$\theta^{[\ell]}(t) = cos(\alpha t).$  %
    %   \end{align*}
%
The leader robot  was initially placed at $(x,y) = (0, 0)~\si{[\meter]}$ with an orientation of $\theta = 0 \degree$ while the follower robot was initially placed at a random position around $(x,y) = (0, 0)~\si{[\meter]}$ with a random orientation. The simulation results are summarized in Figure~\ref{fig:performanceSinewaveTrajectory}. It is observed that the critic weights take more time to converge compared to the earlier scenario,  which is reluctant to the complexity of the independent trajectory of the leader. This result emphasizes the adaptability of the proposed adaptive learning mechanism to different scenarios. Further, the follower starts to move away from the leader at the beginning of the simulation before it finally converges to the leader where the tracking errors are bounded by a safe distance $d.$ % 
%
\begin{figure*}[htbp]%
    \centering
    %\parbox[c]{0.48\textwidth}{\centering Parallel parking}
    %\parbox[c]{0.48\textwidth}{\centering Trajectory tracking}
    %\\
    \subfigure[][]{%
        \label{fig:trajectorySinewave}%
        \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/sinewave/trajectorySinewaveDistance} }
    \subfigure[][]{%
        \label{fig:stateErrorSinewave}%
        \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/sinewave/stateErrorSinewaveDistance} }
    \\
    \subfigure[][]{%
        \label{fig:controlInputSinewave}%
        \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/sinewave/controlInputSinewaveDistance} }
    \subfigure[][]{%
        \label{fig:weightSinewaveDistance}%
        \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/sinewave/weightSinewaveDistance} }
    \caption[Leader-follower performance for nonlinear trajectory.]{Second scenario (sinusoidal trajectory): 
        \subref{fig:trajectorySinewave} leader-follower trajectories,~\subref{fig:stateErrorSinewave} state tracking errors,~\subref{fig:controlInputSinewave} linear speed and steering angle of the follower, and    \subref{fig:weightSinewaveDistance} critic weights.}%
    \label{fig:performanceSinewaveTrajectory}%
\end{figure*}
%

%In the third case study we rely on completley random path for the leader robot to evaluate the effectivenss of the proposed algorithm as a solution for the leader follower tracking problem. The leader is to follow a random path defined by the model described in (2), with $\gamma$ being a random value, The follwer is to maitain an offset distance of $d = 0.5 $ [m]. Note that the path of the leader is not pre defined and the algorithm being completlety model free. The results are summerized in Fig. \ref{fig:peformanceRandomTrajectory}. %

%The results are summarized in Fig.~\ref{fig:peformanceRandomTrajectory}. %
%
%\begin{figure*}[htbp]%
%\centering
%%\parbox[c]{0.48\textwidth}{\centering Parallel parking}
%%\parbox[c]{0.48\textwidth}{\centering Trajectory tracking}
%%\\
%\subfigure[][]{%
%    \label{fig:trajectoryRandom}%
%    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/randomPath/trajectorySinewave} }
%\subfigure[][]{%
%    \label{fig:stateErrorRandom}%
%    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/randomPath/stateErrorSinewave} }
%\\
% \subfigure[][]{%
%    \label{fig:controlInputsRandom}%
%    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/randomPath/controlInputSinewave} }
% \subfigure[][]{%
%    \label{fig:weightRandomDistance}%
%    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/matlab/randomPath/weightRectilinearDistance} }
%\caption[Leader-follower performance for random trajectory.]{Performance in tracking random trajectory: 
%  \subref{fig:trajectoryRandom} leader-follower trajectories,~\subref{fig:stateErrorRandom} state error,~\subref{fig:controlInputsRandom} linear speed and steering angle of the follower; and    \subref{fig:weightRandomDistance} learning weights.}%
%  \label{fig:peformanceRandomTrajectory}%
%\end{figure*}
%

\section{Conclusion} \label{sec:conclusion}

A novel policy iteration mechanism based on a model-free reinforcement learning approach is presented for solving a conventional leader-follower formation problem using car-like mobile robots. The proposed approach does not rely on model parameters inherent in the mobile robots employed in this work. The follower robot is able to follow the leader robot that navigates along unplanned trajectories of various complexities while maintaining a nonzero safe distance between them. To the best of authors' knowledge, this is the first milestone of its kind where a model-free policy iteration based reinforcement learning approach is employed in a multi-robot formation control problem. The future work is going  to extend the learning algorithm for solving a time-varying formation control problem using networked robots.

% \section*{Acknowledgment}

% The preferred spelling of the word ``acknowledgment'' in America is without 
% an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
% G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
% acknowledgments in the unnumbered footnote on the first page.

\bibliographystyle{IEEEtran}
\bibliography{bib/refsSuruzWeb,bib/refsMultiAgent,bib/refsRoboticsJournals,bib/refsRoboticsConferences,bib/refsGenericControl,bib/refsBooksTRTheses,bib/refsReinforcementLearningADP,bib/refsRL-Keshtkar}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2021-02-13 paperMIC2020/paperIEEE-MIC2020-V1.tex
creating paper FLAIRS34

@@
   Addressing the trajectory tracking problem of a mobile robot in tracking a
-  dynamic target is still one of the challenging problems in the field of
-
-  robotics.
+  dynamic target is still one of the challenging problems in the field of robotics.
 In this paper, we address the position tracking problem of a mobile robot where it is supposed to track the position of a  mobile target whose dynamics is unknown a priori.
-This problem is even more challenging when the dynamics of the mobile robot is also assumed to be unknown, which is indeed a
-  realistic assumption. Most of the trajectory tracking solutions proposed in the
+This problem is even more challenging when the dynamics of the mobile robot is also assumed to be unknown, which is indeed a realistic assumption.
+Most of the trajectory tracking solutions proposed in the
   literature in the field of mobile robotics are either focused on algorithms

### 2021-02-13 paperFLAIRS34-2021/CoppeliaMatlabSim/CoppeliaMatlabSim2020/Pioneer/OLD/areaCoveragePioneerAmr2020Sim.m

@@ -1,0 +1,637 @@
+% Sample script for simulating the full area coverage algorithm
+% using three Pioneer robots
+% Eric Jones 1/7/2019
+
+clear
+clc
+close all
+
+disp('Please wait while the simulation runs ...');
+
+%==========================================================================
+% SIMULATION PARAMETERS
+%==========================================================================
+% Simulation time
+t0 = 0; tf = 8;    % Initial and final simulation time [s]
+Ts = 0.1;          % Sampling time [s]
+Ti = floor((tf-t0)/Ts); % number of time steps
+dt = Ts*(0:Ti)';    % Discrete time vector (include time t0 to plot initial state too) 
+%==========================================================================
+Kg = 0.65;    % formerly 1.0 proportional gain on Gamma
+vk = 0.20; % [m/s] Velocity of agents - NOTE: the speed is much higher than it 
+%                                          will be in implementation for 
+%                                          simulation purposes
+%==========================================================================
+l = 0.381; % [m]
+rad = 0.0925; % [m] radius
+%==========================================================================
+
+
+%==========================================================================
+% ROS SETUP
+%==========================================================================
+posesub_1 = rossubscriber('/pioneerPose_1'); %Subscribes to topic '/pioneerPose_1'
+[vpub_1,msg_1] = rospublisher('/desiredVel_1','geometry_msgs/Vector3'); %Publishes on topic '/desiredVel_1'
+
+posesub_2 = rossubscriber('/pioneerPose_2');
+[vpub_2,msg_2] = rospublisher('/desiredVel_2','geometry_msgs/Vector3');
+
+posesub_3 = rossubscriber('/pioneerPose_3');
+[vpub_3,msg_3] = rospublisher('/desiredVel_3','geometry_msgs/Vector3');
+%==========================================================================
+
+
+%==========================================================================
+% INITIALIZATION
+%==========================================================================
+area = [0,5,5,0;
+        0, 0, 5,5];  % [m]; vertices of area 
+agents = [1,   4, 3.25;
[…]

### 2021-02-13 paperFLAIRS34-2021/CoppeliaMatlabSim/CoppeliaMatlabSim2020/Pioneer/areaCoveragePioneerSim.m

@@ -1,0 +1,883 @@
+% Sample script for simulating the full area coverage algorithm
+% using three Pioneer robots
+% Amr Elhussein 29/3/2020
+
+clear
+clc
+close all
+
+disp('Please wait while the simulation runs ...');
+
+%==========================================================================
+% SIMULATION PARAMETERS
+%==========================================================================
+% Simulation time
+t0 = 0; tf = 4;    % Initial and final simulation time [s]
+Ts = 0.01;          % Sampling time [s]
+Ti = floor((tf-t0)/Ts); % number of time steps
+dt = Ts*(0:Ti)';    % Discrete time vector (include time t0 to plot initial state too) 
+%==========================================================================
+Kg = 0.65;    % formerly 1.0 proportional gain on Gamma
+vk = 0.20; % [m/s] Velocity of agents - NOTE: the speed is much higher than it 
+%                                          will be in implementation for 
+%                                          simulation purposes
+%==========================================================================
+l = 0.381; % [m]
+rad = 0.0925; % [m] radius
+%==========================================================================
+k = 1; %main timing index
+%data collection index
+kappa1 = 1;
+kappa2 = 1;
+kappa3 = 1;
+%==========================================================================
+% ROS SETUP
+%==========================================================================
+
+posesub_1 = rossubscriber('/pioneerPose_1'); %Subscribes to topic '/pioneerPose_1'
+[vpub_1,msg_1] = rospublisher('/desiredVel_1','geometry_msgs/Vector3'); %Publishes on topic '/desiredVel_1'
+
+posesub_2 = rossubscriber('/pioneerPose_2');
+[vpub_2,msg_2] = rospublisher('/desiredVel_2','geometry_msgs/Vector3');
+
+posesub_3 = rossubscriber('/pioneerPose_3');
+[vpub_3,msg_3] = rospublisher('/desiredVel_3','geometry_msgs/Vector3');
+%==========================================================================
+
+
[…]

### 2021-02-13 paperFLAIRS34-2021/CoppeliaMatlabSim/CoppeliaMatlabSim2020/PioneerActor/areaCoveragePioneerSimActor.m

@@ -1,0 +1,913 @@
+% Sample script for simulating the full area coverage algorithm
+% using three Pioneer robots
+% Amr Elhussein 29/3/2020
+
+clear
+clc
+close all
+
+disp('Please wait while the simulation runs ...');
+
+%==========================================================================
+% SIMULATION PARAMETERS
+%==========================================================================
+% Simulation time
+t0 = 0; tf = 4;    % Initial and final simulation time [s]
+Ts = 0.01;          % Sampling time [s]
+Ti = floor((tf-t0)/Ts); % number of time steps
+dt = Ts*(0:Ti)';    % Discrete time vector (include time t0 to plot initial state too) 
+%==========================================================================
+Kg = 0.65;    % formerly 1.0 proportional gain on Gamma
+vk = 0.20; % [m/s] Velocity of agents - NOTE: the speed is much higher than it 
+%                                          will be in implementation for 
+%                                          simulation purposes
+%==========================================================================
+l = 0.381; % [m]
+rad = 0.0925; % [m] radius
+%==========================================================================
+k = 1; %main timing index
+%data collection index
+kappa1 = 1;
+kappa2 = 1;
+kappa3 = 1;
+%==========================================================================
+% ROS SETUP
+%==========================================================================
+%centroids position publishers
+[vpub_4,msg_4] = rospublisher('/cent1_pose','geometry_msgs/Vector3'); %Publishes on topic '/desiredVel_1'
+[vpub_5,msg_5] = rospublisher('/cent2_pose','geometry_msgs/Vector3'); %Publishes on topic '/desiredVel_1'
+[vpub_6,msg_6] = rospublisher('/cent3_pose','geometry_msgs/Vector3'); %Publishes on topic '/desiredVel_1'
+
+posesub_1 = rossubscriber('/pioneerPose_1'); %Subscribes to topic '/pioneerPose_1'
[…]

### 2021-02-13 paperFLAIRS34-2021/matlabSim/matlabSimAmr2020/actor/areaCoverageMatlabSimAmrActor2020.m

@@ -1,0 +1,1014 @@
+%last updated by AMR 6/10/2020
+%%%%%%%%%%%%%%%%%%%%%
+%the algorithm is now working but i'm relying on the previous directions
+%formula instead of the steering angle, 
+%also need to figure out what's wrong with the policy formula and come up
+%with more consistent one
+%%%%%%%%%%%%%%%%%%%%%%%%
+%function areaCoverageAdJo_V2()
+close all
+clear 
+clc
+
+area = [0,5,5,0;
+        0, 0, 5,5];  % [m]; vertices of area 
+agents = [1,   4, 3.25;
+          2.5, 3, 0.75]; % [m] agents position in cm
+      
+gridSize = 0.05; % [m]; grid size of the area 
+ 
+t = 0;  % [s] Time variable
+Ts = 0.1; % [s] Simulation time 
+Tf = 10; % [s] Final Simulation time
+tsteps = ceil((Tf-0)/Ts); % number of time steps
+Ti = Tf/Ts; % Time used in indexing
+Vk = 0.25; % [m/s] Velocity of agents - NOTE: the speed is much higher than it 
+%                                          will be in implementation for 
+%                                          simulation purposes
+
+% %%=================== 3D video of risk density function =================%%
+% vid = VideoWriter('videos/3DPhi.avi');
+% vid.Quality = 100;
+% vid.FrameRate = 5;
+% open(vid);
+% %%=======================================================================
+%%=========================================================================
+q = 1; % Variables used to index in for loops
+r = 1;
+s = 1;
+k = 1; %main timming loop
+kappa1 = 1; %data colection index
+kappa2 = 1;
+kappa3 = 1;
+
+yy = min(area(2,:)):gridSize:max(area(2,:));
+xx = min(area(1,:)):gridSize:max(area(1,:));
+
+sigma = 0.35; % Density factor 
+n = 3; % number of agents
+alpha = 5; % Scaling variable used in sensor function
+beta = 0.5; % Scaling variable used in sensor function
+
+qBar = [2.5, 4,    1.5; 
+        4,   0.75, 1];    
+
+positions(1,:) = [agents(1,1), agents(2,1)];
[…]

### 2021-02-13 paperFLAIRS34-2021/matlabSim/matlabSimAmr2020/critic/areaCoverageMatlabSimAmr2020.m

@@ -1,0 +1,761 @@
+%last updated by AMR 3/13/2020
+%%%%%%%%%%%%%%%%%%%%%
+%the algorithm is now working but i'm relying on the previous directions
+%formula instead of the steering angle, 
+%also need to figure out what's wrong with the policy formula and come up
+%with more consistent one
+%%%%%%%%%%%%%%%%%%%%%%%%
+%function areaCoverageAdJo_V2()
+close all
+clear 
+clc
+
+area = [0,5,5,0;
+        0, 0, 5,5];  % [m]; vertices of area 
+agents = [1,   4, 3.25;
+          2.5, 3, 0.75]; % [m] agents position in cm
+      
+gridSize = 0.05; % [m]; grid size of the area 
+ 
+t = 0;  % [s] Time variable
+Ts = 0.05; % [s] Simulation time 
+Tf = 20; % [s] Final Simulation time
+Ti = Tf/Ts; % Time used in indexing
+Vk = 0.25; % [m/s] Velocity of agents - NOTE: the speed is much higher than it 
+%                                          will be in implementation for 
+%                                          simulation purposes
+
+% %%=================== 3D video of risk density function =================%%
+% vid = VideoWriter('videos/3DPhi.avi');
+% vid.Quality = 100;
+% vid.FrameRate = 5;
+% open(vid);
+% %%=======================================================================
+%%=========================================================================
+q = 1; % Variables used to index in for loops
+r = 1;
+s = 1;
+k = 1; %main timming loop
+kappa1 = 1; %data colection index
+kappa2 = 1;
+kappa3 = 1;
+
+yy = min(area(2,:)):gridSize:max(area(2,:));
+xx = min(area(1,:)):gridSize:max(area(1,:));
+
+sigma = 0.35; % Density factor 
+n = 3; % number of agents
+alpha = 5; % Scaling variable used in sensor function
+beta = 0.5; % Scaling variable used in sensor function
+
+qBar = [2.5, 4,    1.5; 
+        4,   0.75, 1];    
+
+positions(1,:) = [agents(1,1), agents(2,1)];
+positions(2,:) = [agents(1,2), agents(2,2)];
+positions(3,:) = [agents(1,3), agents(2,3)];
[…]

### 2021-02-13 paperMIC2020/matlabsim/randomPath/mainActorCriticRL_TargetTrackingRnd.m

@@ -1,4 +1,4 @@
-% Odometric localization or dead reckoning%   Script for simulating mobile robot.
+ %Odometric localization or dead reckoning%   Script for simulating mobile robot.
 %Edited by AMR Elhussein on May, 29,2020.
 %gradient descent Appraoch, three cases comined fixed point, horzintal and inclined line, 
 %converged Example

### 2021-02-13 paperFLAIRS34-2021/matlabSim/matlabSimAmr2020/critic/areaCoverageMatlabSimAmr2020.m
deleted critic

@@ -1,761 +1,0 @@
-%last updated by AMR 3/13/2020
-%%%%%%%%%%%%%%%%%%%%%
-%the algorithm is now working but i'm relying on the previous directions
-%formula instead of the steering angle, 
-%also need to figure out what's wrong with the policy formula and come up
-%with more consistent one
-%%%%%%%%%%%%%%%%%%%%%%%%
-%function areaCoverageAdJo_V2()
-close all
-clear 
-clc
-
-area = [0,5,5,0;
-        0, 0, 5,5];  % [m]; vertices of area 
-agents = [1,   4, 3.25;
-          2.5, 3, 0.75]; % [m] agents position in cm
-      
-gridSize = 0.05; % [m]; grid size of the area 
- 
-t = 0;  % [s] Time variable
-Ts = 0.05; % [s] Simulation time 
-Tf = 20; % [s] Final Simulation time
-Ti = Tf/Ts; % Time used in indexing
-Vk = 0.25; % [m/s] Velocity of agents - NOTE: the speed is much higher than it 
-%                                          will be in implementation for 
-%                                          simulation purposes
-
-% %%=================== 3D video of risk density function =================%%
-% vid = VideoWriter('videos/3DPhi.avi');
-% vid.Quality = 100;
-% vid.FrameRate = 5;
-% open(vid);
-% %%=======================================================================
-%%=========================================================================
-q = 1; % Variables used to index in for loops
-r = 1;
-s = 1;
-k = 1; %main timming loop
-kappa1 = 1; %data colection index
-kappa2 = 1;
-kappa3 = 1;
-
-yy = min(area(2,:)):gridSize:max(area(2,:));
-xx = min(area(1,:)):gridSize:max(area(1,:));
-
-sigma = 0.35; % Density factor 
-n = 3; % number of agents
-alpha = 5; % Scaling variable used in sensor function
-beta = 0.5; % Scaling variable used in sensor function
-
-qBar = [2.5, 4,    1.5; 
-        4,   0.75, 1];    
-
-positions(1,:) = [agents(1,1), agents(2,1)];
-positions(2,:) = [agents(1,2), agents(2,2)];
-positions(3,:) = [agents(1,3), agents(2,3)];
[…]
